### 2023-12-01 paper/main.tex
initial commit for paper

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
% \usepackage[backend=biber]{biblatex}
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
\usepackage{fontspec} %XeLatex
\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
% \definecolor{myudblue}{RGB}{0, 83, 159}
\begin{document}
HELLOOOOOOOOO

aw;lesfajfp 8uyf

% \begin{figure}
%     \centering
%     \includegraphics{/figures/test.png}
% \end{figure}

\end{document}

### 2023-12-04 src/plot_functions.py
trying to get add_all_letters right

@@ -9,13 +9,15 @@ from string import ascii_uppercase
 
 class NewFigure:
     def __init__(self, mosaic, figsize = (6.5,4), dpi=150, layout="constrained", sharex=False,sharey=False,
-                 ):
+                 hspace = None, wspace = None):
+        
         self.fig, self.axes = plt.subplot_mosaic(mosaic, 
                                                  dpi=dpi,
                                                 layout=layout,
                                                 figsize=figsize,
                                                 sharex=sharex,
                                                 sharey=sharey,
+                                                gridspec_kw={'wspace':wspace,"hspace":hspace}
                                                 )
         
         self.figw,self.figh = self.fig.get_size_inches()
@@ -84,16 +86,26 @@ class NewFigure:
             ax.text(xy[0], xy[1], letter, transform=ax.transAxes,
                     fontsize=fontsize, va=va,ha=ha, fontfamily=fontfamily, 
                     fontweight=fontweight)
+            
     def add_all_letters(self, xy = (0,1), ax=None, fontsize=12,
                         va="top",ha='left',fontfamily="sans-serif",fontweight="bold"):
+        # for i,(label, ax) in enumerate(self.axes.items()):
+        #     ax_bbox = ax.get_tightbbox().transformed(self.axmain.transData.inverted())
+        #     # label physical distance to the left and up:
+        #     letter = ascii_uppercase[i]
+        #     # trans = mtransforms.ScaledTranslation(-20/72, 7/72, self.fig.dpi_scale_trans)
+        #     self.axmain.text(ax_bbox.x0, ax_bbox.y1, letter,
+        #             fontsize=fontsize, va=va,ha=ha, fontfamily=fontfamily, 
+        #             fontweight=fontweight)
         for i,(label, ax) in enumerate(self.axes.items()):
-            ax_bbox = ax.get_tightbbox().transformed(self.axmain.transData.inverted())
-            # label physical distance to the left and up:
+            # label physical distance in and down:
             letter = ascii_uppercase[i]
-            # trans = mtransforms.ScaledTranslation(-20/72, 7/72, self.fig.dpi_scale_trans)
-            ax.text(ax_bbox.x0, ax_bbox.y1, letter, transform=self.axmain.transData,
-                    fontsize=fontsize, va=va,ha=ha, fontfamily=fontfamily, 
-                    fontweight=fontweight)
+            trans = mtransforms.ScaledTranslation(-30/72, 16/72, self.fig.dpi_scale_trans)
[…]

### 2023-12-18 src/constants.py
changed xticklabels

@@ -17,8 +17,9 @@ xticklabel_colors_means = [wheel.rak_blue, wheel.rak_red, wheel.rak_orange,
 xticklabel_colors_sd = [wheel.rak_blue, wheel.dark_blue_hc, 
                         wheel.rak_red, wheel.lighten_color(wheel.rak_red,1.5),
                         wheel.rak_orange,wheel.burnt_orange,]
-xticklabels = ["(1000, 50)", "(1100, 50)", "(1200, 50)", "(1000, 150)", "(1100, 150)", "(1200, 150)"]
-
+# xticklabels = ["(1000, 50)", "(1100, 50)", "(1200, 50)", "(1000, 150)", "(1100, 150)", "(1200, 150)"]
+xticklabels = ["Early\nLow", "Middle\nLow", "Late\nLow",
+               "Early\nHigh", "Middle\nHigh", "Late\nHigh"]
 MODELS_PATH = find_parent(Path.cwd(),"MatchPennies-Agent-Expirement") / "results" / "models"
 MODEL_INPUT_PATH = find_parent(Path.cwd(),"MatchPennies-Agent-Expirement") / "results" / "model_inputs"
 

### 2023-12-18 src/plot_functions.py
figured out transforms for adding figure letters

@@ -19,7 +19,7 @@ class NewFigure:
                                                 sharey=sharey,
                                                 gridspec_kw={'wspace':wspace,"hspace":hspace}
                                                 )
-        
+        self.num_axes = len(self.axes.values())
         self.figw,self.figh = self.fig.get_size_inches()
         # Create axmain box for visualization of the bounds and coordinates
         self.axmain  = self.fig.add_axes((0,0,1,1))
@@ -31,6 +31,15 @@ class NewFigure:
         self.axmain.set_ylim(0,figsize[1])
         
         self.letters = []
+        
+    def fig_data_to_axis_transform(self,ax):
+        '''
+        Transformation for figure data coordinates (aka axmain) to ax coordinates desired
+        '''
+        return self.axmain.transData + ax.transAxes.inverted()
+    
+    def axis_to_fig_data_transform(self,ax):
+        return ax.transAxes + self.axmain.transData.inverted()
                 
     def pad_fig(self, w_pad, h_pad, w_space, h_space):
         self.fig.get_layout_engine().set(w_pad=w_pad/self.figw, 
@@ -77,34 +86,46 @@ class NewFigure:
         self.fig.set_layout_engine('none')
         ax.set_position((x/self.figw, y/self.figh, (w+dw)/self.figw, (h+dh)/self.figh))
 
-    def add_all_letters_old(self, xy = (0,1), ax=None, fontsize=12,
-                        va="top",ha='center',fontfamily="sans-serif",fontweight="bold"):
-        for i,(label, ax) in enumerate(self.axes.items()):
-            # label physical distance to the left and up:
-            letter = ascii_uppercase[i]
-            # trans = mtransforms.ScaledTranslation(-20/72, 7/72, self.fig.dpi_scale_trans)
-            ax.text(xy[0], xy[1], letter, transform=ax.transAxes,
-                    fontsize=fontsize, va=va,ha=ha, fontfamily=fontfamily, 
-                    fontweight=fontweight)
+    # def add_all_letters_v2(self, xy = (0,1), ax=None, fontsize=12,
+    #                     va="top",ha='left',fontfamily="sans-serif",fontweight="bold",
+    #                     verticalshift=0, horizontalshift=0):
+    #     if not isinstance(verticalshift, list):
+    #         verticalshift = np.array([verticalshift]*self.num_axes)
+    #     if not isinstance(horizontalshift, list):
[…]

### 2024-01-08 src/plot_functions.py
added property to NewFigure to get axes in alphabetic order of their keys

@@ -140,6 +140,13 @@ class NewFigure:
         ax.text(x, y, letter_to_add, ha = ha, va = va, transform=ax.transAxes,
                 fontweight = "bold", color = color, fontsize = fontsize, zorder = zorder)
     
+    @property
+    def alphabetic_axes(self) -> list:
+        sorted_keys = sorted(self.axes)
+        return {k:self.axes[k] for k in sorted_keys}
+        
+        
+        
     def remove_figure_borders(self):
         # for spine in ['top','right','bottom','left']:
         self.axmain.axis("off")

### 2024-01-08 src/constants.py
created xticklabels sd so 1000,50 then 1000,150

@@ -30,6 +30,12 @@ xticklabels = [r"Early Mean"+"\n"+r"Low Variance",
                r"Early Mean"+"\n"+r"High Variance", 
                r"Middle Mean"+"\n"+r"High Variance", 
                r"Late Mean"+"\n"+r"High Variance"]
+xticklabels_sd = [r"Early Mean"+"\n"+r"Low Variance", 
+               r"Early Mean"+"\n"+r"High Variance", 
+               r"Middle Mean"+"\n"+r"Low Variance",
+               r"Middle Mean"+"\n"+r"High Variance", 
+               r"Late Mean"+"\n"+r"Low Variance", 
+               r"Late Mean"+"\n"+r"High Variance"]
 MODELS_PATH = find_parent(Path.cwd(),"MatchPennies-Agent-Expirement") / "results" / "models"
 MODEL_INPUT_PATH = find_parent(Path.cwd(),"MatchPennies-Agent-Expirement") / "results" / "model_inputs"
 

### 2024-01-08 src/Optimal_Stopping_Object.py
removed nlopt import bc I don't use it

@@ -17,7 +17,6 @@ import multiprocessing as mp
 import loss_functions as lf
 import constants
 import dill
-import nlopt
 wheel = dv.ColorWheel()
 """
 Functions and Classes to generate and fit the optimal model

### 2024-01-09 src/constants.py
added model_colors

@@ -48,3 +48,4 @@ input_keys = ["rt","rt_sd","mt","mt_sd","timing_sd",]
 agent_means = np.array([1000.0,1000.0,1100.0,1100.0,1200.0,1200.0])
 agent_sds = np.array([50.0,150.0,50.0,150.0,50.0,150.0])
 
+model_colors = [wheel.light_grey, wheel.dark_grey, wheel.black]

### 2024-01-09 scripts/optimal_model/update_model_result_dataframes.py
more datas

@@ -3,7 +3,7 @@ import numpy as np
 import pandas as pd
 import dill
 import model_helper_functions as mhf
-import tqdm as tqdm
+from tqdm import tqdm
 from Optimal_Stopping_Object import ModelConstructor
 
 '''
@@ -20,23 +20,35 @@ def create_results_row_dict(model,loss,model_name,free_param_keys):
         model.results.optimal_decision_time,
         get_metric(model.player_behavior.wtd_reach_time,metric_type='true',decision_type='optimal'),
         get_metric(model.player_behavior.wtd_reach_time_sd,metric_type='true',decision_type='optimal'),
+        get_metric(model.player_behavior.guess_reach_time,metric_type='true',decision_type='optimal'),
+        model.player_behavior.guess_reach_time_sd.squeeze(),
+        get_metric(model.player_behavior.reaction_reach_time,metric_type='true',decision_type='optimal'),
+        get_metric(model.player_behavior.reaction_reach_time_sd,metric_type='true',decision_type='optimal'),
+        get_metric(model.player_behavior.prob_selecting_guess,metric_type='true',decision_type='optimal'),
+        get_metric(model.player_behavior.prob_selecting_reaction,metric_type='true',decision_type='optimal'),
         get_metric(model.player_behavior.wtd_leave_time,metric_type='true',decision_type='optimal'),
         get_metric(model.player_behavior.wtd_leave_time_sd,metric_type='true',decision_type='optimal'),
         get_metric(model.score_metrics.prob_indecision,metric_type='true',decision_type='optimal')*100,
         get_metric(model.score_metrics.prob_win,metric_type='true',decision_type='optimal')*100,
         get_metric(model.score_metrics.prob_incorrect,metric_type='true',decision_type='optimal')*100,
     ]
-    results_row = {
-        "Model":model_name,"Loss":loss,"fit_parameters":free_param_keys,
-        "decision_times":model_data[0],
-        "target_reach_times":model_data[1],
-        "target_reach_times_sd":model_data[2],
-        "median_movement_onset_time":model_data[3],
-        "sd_movement_onset_time":model_data[4],
-        "indecisions":model_data[5],
-        "wins":model_data[6],
-        "incorrects":model_data[7],
-    }
+    results_keys = [
+        "decision_times",
+        "target_reach_times",
+        "target_reach_times_sd",
+        "target_reach_times_guess",
+        "target_reach_times_guess_sd",
[…]

### 2024-01-12 src/constants.py
update model colors and add model names

@@ -48,4 +48,5 @@ input_keys = ["rt","rt_sd","mt","mt_sd","timing_sd",]
 agent_means = np.array([1000.0,1000.0,1100.0,1100.0,1200.0,1200.0])
 agent_sds = np.array([50.0,150.0,50.0,150.0,50.0,150.0])
 
-model_colors = [wheel.light_grey, wheel.dark_grey, wheel.black]
+model_colors = [wheel.grey, wheel.lighten_color(wheel.dark_grey,1.15), wheel.black]
+model_names = ["No Switch Time Model", "Known Switch Time Model", "Unknown Switch Time Model"]

### 2024-01-12 src/plot_functions.py
added PrettyTable

@@ -154,7 +154,81 @@ class NewFigure:
     def savefig(self,path,dpi=300, transparent = True):
         self.remove_figure_borders()
         self.fig.savefig(path,dpi=dpi,transparent=transparent)
-
+class PrettyTable:
+    def __init__(self, ax, table_values: np.ndarray, 
+                 text_xshift=0.5, line_yshift=0, ha='center',va='center', fontsize=9, fontweight='light', 
+                 vertical_ls='-', horizontal_ls='-',inner_line_color = 'grey', inner_lw=1, border_color='grey',
+                 border_fill=None, border_lw=1, border_ls='-'):
+        self.ax = ax
+        self.table_values = table_values
+        self.num_rows, self.num_cols = table_values.shape 
+        
+        self.ax.set_alpha(0)
+        self.ax.patch.set_alpha(0)
+        self.ax.set_xlim(0,self.num_cols)
+        self.ax.set_ylim(0,self.num_rows)
+        self.ax.invert_yaxis()
+        
+        
+        if isinstance(ha,str):
+            self.ha = np.full_like(table_values, ha, dtype=object)
+        elif isinstance(ha,(list,np.ndarray)):
+            self.ha = ha
+        else:
+            raise ValueError("'ha' should be a string (left, right, center) or an array of strings with the same shape as table_values")
+        
+        if isinstance(va,str):
+            self.va = np.full_like(table_values, va, dtype=object)
+        elif isinstance(va,(list,np.ndarray)):
+            self.va = va
+        else:
+            raise ValueError("'ha' should be a string (left, right, center) or an array of strings with the same shape as table_values")
+            
+        self._plot_table_values(text_xshift, fontsize, fontweight)
+        self._plot_table_lines(line_yshift, vertical_ls=vertical_ls, horizontal_ls=horizontal_ls, inner_line_color=inner_line_color, inner_lw=inner_lw)
+        self._plot_table_boundary(line_yshift, border_color=border_color, border_fill=border_fill, border_lw=border_lw)
+        
+    def _plot_table_values(self, text_xshift, fontsize, fontweight):
+        self.text_store = []
+        for i,row in enumerate(self.table_values):
+            for j, element in enumerate(row):
+                t = self.ax.text(x=j+text_xshift, y=i+0.5, s=element, ha=self.ha[i,j], va=self.va[i,j], transform=self.ax.transData, 
+                        fontsize=fontsize,fontweight=fontweight)        
+                self.text_store.append(t)
+    
+    
[…]

### 2024-01-15 src/plot_functions.py
PrettyTable coming along

@@ -3,6 +3,7 @@ import numpy as np
 import data_visualization as dv
 from scipy import stats
 from copy import deepcopy
+import matplotlib as mpl
 wheel = dv.ColorWheel()
 import matplotlib.transforms as mtransforms
 from string import ascii_uppercase
@@ -155,12 +156,20 @@ class NewFigure:
         self.remove_figure_borders()
         self.fig.savefig(path,dpi=dpi,transparent=transparent)
 class PrettyTable:
-    def __init__(self, ax, table_values: np.ndarray, 
-                 text_xshift=0.5, line_yshift=0, ha='center',va='center', fontsize=9, fontweight='light', 
-                 vertical_ls='-', horizontal_ls='-',inner_line_color = 'grey', inner_lw=1, border_color='grey',
-                 border_fill=None, border_lw=1, border_ls='-'):
-        self.ax = ax
+    def __init__(self, ax, table_values: np.ndarray,
+                 text_xshift=0.5, line_yshift=0, ha='center',va='center', fontsize=9, fontweight='light', fontcolor=wheel.grey,
+                inner_ls='-',inner_line_color = 'grey', inner_lw=1, border_color='grey',
+                 border_fill=None, border_lw=1, border_ls='-', bold_first_row=False, bold_first_column=False):
         self.table_values = table_values
+        
+        self.ha = self._check_kwargs(ha, "ha", str)
+        self.va = self._check_kwargs(va, "va", str)
+        fontweight = self._check_kwargs(fontweight, "fontweight", str)
+        fontsize = self._check_kwargs(fontsize, "fontsize", (float, int))
+        fontcolor = self._check_kwargs(fontcolor, "fontcolor", str)
+        inner_ls = self._check_kwargs(inner_ls, "inner_ls", str)
+        
+        self.ax = ax
         self.num_rows, self.num_cols = table_values.shape 
         
         self.ax.set_alpha(0)
@@ -169,47 +178,49 @@ class PrettyTable:
         self.ax.set_ylim(0,self.num_rows)
         self.ax.invert_yaxis()
         
-        
-        if isinstance(ha,str):
-            self.ha = np.full_like(table_values, ha, dtype=object)
-        elif isinstance(ha,(list,np.ndarray)):
-            self.ha = ha
-        else:
-            raise ValueError("'ha' should be a string (left, right, center) or an array of strings with the same shape as table_values")
-        
-        if isinstance(va,str):
[…]

### 2024-01-16 src/plot_functions.py
more changes to PrettyTable

@@ -158,7 +158,7 @@ class NewFigure:
 class PrettyTable:
     def __init__(self, ax, table_values: np.ndarray,
                  text_xshift=0.5, line_yshift=0, ha='center',va='center', fontsize=9, fontweight='light', fontcolor=wheel.grey,
-                inner_ls='-',inner_line_color = 'grey', inner_lw=1, border_color='grey',
+                inner_horizontal_ls='-', inner_vertical_ls='-', inner_line_color = 'grey', inner_lw=1, border_color='grey',
                  border_fill=None, border_lw=1, border_ls='-', bold_first_row=False, bold_first_column=False):
         self.table_values = table_values
         
@@ -167,7 +167,8 @@ class PrettyTable:
         fontweight = self._check_kwargs(fontweight, "fontweight", str)
         fontsize = self._check_kwargs(fontsize, "fontsize", (float, int))
         fontcolor = self._check_kwargs(fontcolor, "fontcolor", str)
-        inner_ls = self._check_kwargs(inner_ls, "inner_ls", str)
+        inner_horizontal_ls = self._check_kwargs(inner_horizontal_ls, "inner_horizontal_ls", str)
+        inner_vertical_ls = self._check_kwargs(inner_vertical_ls, "inner_vertical_ls", str)
         
         self.ax = ax
         self.num_rows, self.num_cols = table_values.shape 
@@ -184,7 +185,7 @@ class PrettyTable:
             fontweight[:,0] = "bold"
             
         self._plot_table_values(text_xshift, fontsize, fontweight, fontcolor=fontcolor)
-        self._plot_table_lines(line_yshift, inner_ls=inner_ls,
+        self._plot_table_lines(line_yshift, inner_horizontal_ls=inner_horizontal_ls, inner_vertical_ls=inner_vertical_ls,
                                inner_line_color=inner_line_color, inner_lw=inner_lw)
         self._plot_table_boundary(line_yshift, border_color=border_color, 
                                   border_fill=border_fill, border_lw=border_lw)
@@ -206,28 +207,28 @@ class PrettyTable:
                         fontsize=fontsize[i,j],fontweight=fontweight[i,j], color=fontcolor[i,j])        
                 self.coordinate_store.append((i,j, i+(1/self.num_cols), j+(1/self.num_rows)))
     
-    def _plot_table_lines(self, line_yshift, inner_ls, inner_line_color, inner_lw):
[…]

### 2024-01-16 paper/main.tex
testing figures
committing paper
checking out figures
all figures in there, not quite done tho

@@
 \usepackage{graphicx,wrapfig}
+\usepackage{float}
+\graphicspath{ {./figures/} }
 % \usepackage[backend=biber]{biblatex}
@@
 ]
+\newcommand{\SethCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
+\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
+\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{black}{#1}}\normalsize }
+
 % \definecolor{myudblue}{RGB}{0, 83, 159}
 \begin{document}
-HELLOOOOOOOOO
+\SectionHeader{Main Figures}
 
-aw;lesfajfp 8uyf
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figures/exp1_experimental_design.png}
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{/figures/test.png}
-% \end{figure}
+    \SethCaption{Figure 1.}{Experimental Design}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
+
+    \SethCaption{Figure 2.}{Data}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
+
+    \SethCaption{Figure 3.}{Data}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/model_diagram.png}
+
+    \SethCaption{Figure 4.}{Data}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}
+
+    \SethCaption{Figure 5.}{Data w/ models}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/exp2_design.png}
+
+    \SethCaption{Figure 6.}{Experiment 2 Design}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/exp2_reaction_panel.png}
+
+    \SethCaption{Figure 7.}{React or Guess panel}
+\end{figure}
 

### 2024-02-08 src/constants.py
added agent_color and player_color

@@ -56,3 +56,6 @@ agent_sds = np.array([50.0,150.0,50.0,150.0,50.0,150.0])
 
 model_colors = [wheel.grey, wheel.lighten_color(wheel.dark_grey,1.25), wheel.black]
 model_names = ["No Switch Time Model", "Known Switch Time Model", "Unknown Switch Time Model"]
+
+agent_color = wheel.lighten_color(wheel.yellow, 1.75)
+player_color = wheel.purple

### 2024-02-08 src/plot_functions.py
lw type check needed to be float not string

@@ -33,7 +33,7 @@ class NewFigure:
         self.axmain.set_xlim(0,figsize[0])
         self.axmain.set_ylim(0,figsize[1])
         
-        self.letters = []
+        self.letters = []  
         
     def fig_data_to_axis_transform(self,ax):
         '''
@@ -183,13 +183,13 @@ class PrettyTable:
                                                                                  a=self.table_values[0,:])
                                                  )
         
-        inner_horizontal_lw = self._check_kwargs(inner_horizontal_lw, "inner_horizontal_lw", str, 
+        inner_horizontal_lw = self._check_kwargs(inner_horizontal_lw, "inner_horizontal_lw", float, 
                                                  fill_function=partial(np.full_like, 
-                                                                                 a=self.table_values[:,0])
+                                                                        a=self.table_values[:,0])
                                                  )
-        inner_vertical_lw = self._check_kwargs(inner_vertical_lw, "inner_vertical_lw", str, 
+        inner_vertical_lw = self._check_kwargs(inner_vertical_lw, "inner_vertical_lw", float, 
                                                  fill_function=partial(np.full_like, 
-                                                                                 a=self.table_values[0,:])
+                                                                        a=self.table_values[0,:])
                                                  )
         
         self.ax = ax

### 2024-02-08 src/plot_functions.py
fixed zorder on bootstrappd model results

@@ -162,7 +162,7 @@ class PrettyTable:
                  text_xshift=0.5, line_yshift=0, ha='center',va='center', 
                  fontsize=9, fontweight='light', fontcolor=wheel.grey,
                  inner_horizontal_ls='-', inner_vertical_ls='-', 
-                 inner_vertical_lw=1,inner_horizontal_lw=1, 
+                 inner_vertical_lw=1.0,inner_horizontal_lw=1.0, 
                  inner_line_color = 'grey', border_color='grey',
                  border_fill=None, border_lw=1, 
                  border_ls='-', bold_first_row=False, 
@@ -644,7 +644,7 @@ def plot_boostrapped_model_results(ax, x, y, percentiles, color, horizontal_lw =
         ax.plot([x, x], [top, bottom], color=color)
         ax.plot([left, right], [top, top], color=color)
         ax.plot([left, right], [bottom, bottom], color=color)
-    ax.plot(x, y, 'o', color=color, markersize=markersize)
+    ax.plot(x, y, 'o', color=color, markersize=markersize, zorder=99, clip_on=False)
     
 def plot_models(ax, xlocs, data, line_colors, linestyles, bw, 
                 markersize, legend_labels, legend_linewidth, 

### 2024-03-20 paper/main.tex
added supplementary
new updates with math

--- 2023-12-01 paper/main.tex
@@
 \documentclass[12pt,letterpaper]{article}
-\usepackage[utf8]{inputenc}
+\usepackage{inputenc}
 \usepackage{amsmath}
@@
 \usepackage{amssymb}
+\usepackage{bbm}
 \usepackage{fontspec} %XeLatex
@@
 \usepackage{graphicx,wrapfig}
-% \usepackage[backend=biber]{biblatex}
+\usepackage{float}
+\usepackage{caption}
+\graphicspath{ {./figures/} }
+\usepackage[backend=biber]{biblatex}
 \usepackage[paper=letterpaper,
@@
 ]
+% Set caption styles
+% \DeclareCaptionLabelFormat{table}{1-2}
+\captionsetup[table]{labelfont=bf,labelsep=period}
+\captionsetup[figure]{labelfont=bf,labelsep=period}
+
+\newcommand{\SethCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
+\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
+\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{black}{#1}}\normalsize }
+
 % \definecolor{myudblue}{RGB}{0, 83, 159}
 \begin{document}
-HELLOOOOOOOOO
+% \SectionHeader{Main Figures}
 
-aw;lesfajfp 8uyf
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figures/exp1_experimental_design.png}
 
-% \begin{figure}
+%     \SethCaption{Figure 1.}{Experimental Design}
+% \end{figure}
+% \begin{figure}[H]
 %     \centering
-%     \includegraphics{/figures/test.png}
+%     \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
+
+%     \SethCaption{Figure 2.}{Data}
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
+
+%     \SethCaption{Figure 3.}{Data}
 % \end{figure}
 
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/model_diagram.png}
+
+%     \SethCaption{Figure 4.}{Data}
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}
+
+%     \SethCaption{Figure 5.}{Data w/ models}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/exp2_design.png}
+
+%     \SethCaption{Figure 6.}{Experiment 2 Design}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/exp2_reaction_panel.png}
+
+%     \SethCaption{Figure 7.}{React or Guess panel}
+% \end{figure}
+
+% \SectionHeader{Supplementary Figures}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/reaction_guess_decisions.png}
+
+%     \SethCaption{Supplementary Figure 1.}{Reaction and Guess Decisions}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/model_losses.png}
+
+%     \SethCaption{Supplementary Figure 2.}{Model Loss Comparison}
+% \end{figure}
+
+\SectionHeader{Methods}
+\begin{table}[h]
+    \centering
+    \begin{tabular}{|l | c|}
+        \hline
+        Agent Movement Onset Time Mean        & $\mu_{A}$         \\
+        Agent Movement Onset Time Uncertainty & $\sigma_{A}$      \\
+        Reaction Time Mean                    & $\mu_{RT}$        \\
+        Reaction Time Uncertainty             & $\sigma_{RT}$     \\
+        Movement Time Mean                    & $\mu_{MT}$        \\
+        Movement Time Uncertainty             & $\sigma_{MT}$     \\
+        Neuromechanical Delay Mean            & $\mu_{NMD}$       \\
+        Neuromechanical Delay Uncertainty     & $\sigma_{NMD}$    \\
+        Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
+        Switch Time Mean                      & $\mu_{switch}$    \\
+        Switch Time Uncertainty               & $\sigma_{switch}$ \\
+        \hline
+    \end{tabular}
+    \caption[]{Inputs to the model}
+\end{table}
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{|l | c|}
+        \hline
+        Reaction Time Delay       & $\mathcal{N}(\mu_{RT},\sigma_{RT})$         \\
+        Movement Time Delay       & $\mathcal{N}(\mu_{MT},\sigma_{MT})$         \\
+        Neuromechanical Delay     & $\mathcal{N}(\mu_{NMD},\sigma_{NMD})$       \\
+        Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
+        Switch Time Delay         & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
+        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
+        \hline
+    \end{tabular}
+    \caption[]{Inputs to the model}
+\end{table}
+
+% Define pdf and cdf
+\begin{equation}
+    f(t) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{t-\mu}{\sigma})^2}
+\end{equation}
+\begin{equation}
+    F(t) = P(T\leq t) = \int_{-\infty}^{t} f(t)dt
+\end{equation}
+\begin{equation}
+    t \in [0,1500]
+\end{equation}
+\begin{equation}
+    T\sim\mathcal{N}(\mu,\sigma)
+\end{equation}
+
+% Define prob react and guess
+\begin{equation}
+    P(React|\tau) = P(\tau>\mu_{A}; \sigma_{tau}, \sigma_{A})
+\end{equation}
+\begin{equation}
+    P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{tau}, \sigma_{A})
+\end{equation}
+
+% Define expected value
+\begin{equation}
+    \mu_{X} = \sum_{i = -\infty}^{\infty}x_{i}f(x_{i};\mu_{X}, \sigma_{X})
+\end{equation}
+
+% Define indicator function
+\begin{equation}
+    \mathbbm{1}_{a_{i},t_{i} \in S} = 
+    \begin{cases}
+        1, & \text{if } a_{i},t_{i} \in S \\
+        0, & \text{if }  a_{i},t_{i} \notin S
+    \end{cases}    
+\end{equation}
+
+% Define
+
+% Movement Onset times
+\begin{equation}
+    \mu_{RMO} = \mu_{A_{cutoff}} + \mu_{RT}
+\end{equation}
+\begin{equation}
+    \sigma_{RMO} = \sqrt{\sigma_{A_{cutoff}}^2 + \sigma_{RT}^2}
+\end{equation}
+\begin{equation}
+    \mu_{GMO} = \\tau +  \mu_{NMD} + \mu_{switch}
+\end{equation}
+\begin{equation}
+    \sigma_{GMO} = \sqrt{\sigma_{\tau}^2 + \sigma_{NMD}^2 + \sigma_{switch}^2}
+\end{equation}
+
+% Scores
+
+\begin{equation}
+    R_{win} = 1
+\end{equation}
+\begin{equation}
+    R_{indecision} = 0
+\end{equation}
+\begin{equation}
+    R_{incorrect} = 0
+\end{equation}
+
 \end{document}

### 2024-03-21 src/Optimal_Stopping_Object.py
added comments to finding agent moments for clarity

@@ -75,10 +75,16 @@ def get_moments(timesteps:np.ndarray, time_means:np.ndarray, time_sds:np.ndarray
             #* Looping over possible mean decision times
             for k in nb.prange(time_means.shape[0]):
                 # mu_y = time_means[k] # Put the timing mean in an easy to use variable,
+                #* y_integrated is the stopping time distribution for every timestep
+                #* Instead of the double integral, I figured out that the this integral can be simplified to the cdf so I didn't have to double loop
+                #* See pg 83 in grid notebook where I pull out the integral for p(y) aka p(t_i) from -inf to +inf
+                #* It's 1 - norm.cdf bc the integral is from the current timestep k (aka time_means[k]) to +inf (pg 84 says integral is from x to inf)
                 y_integrated = 1 - norm.cdf(timesteps, time_means[k], time_sds[i,j]) # For ALL timesteps, what's the probabilit for every timing mean (from 0 to 2000) that the timing mean is greater than that current timestep
                 # y_inverse_integrated = 1 - y_integrated
                 if prob_agent_less_player[i,j,k]!=0:
                     # integral_sum_R = nb_sum(timesteps*agent_pdf[i,j,:]*y_integrated)*dx
+                    #* Remember, timesteps here is all the possible values of a_{i} aka the realization of the agent's random variable
+                    #* so it's a_i*p(a_i)*P(T)/P(A<T) 
                     EX_R[i,j,k] = nb_sum(timesteps*agent_pdf[i,j,:]*y_integrated)*dx/prob_agent_less_player[i,j,k]
                     # SECOND CENTRAL MOMENT = VARIANCE
                     # integral_sum2_R = nb_sum((timesteps - EX_R[i,j,k])**2*agent_pdf[i,j,:]*y_integrated)*dx

### 2024-03-29 paper/main.tex
Equations almost finalized

@@
 \captionsetup[table]{labelfont=bf,labelsep=period}
-\captionsetup[figure]{labelfont=bf,labelsep=period}
+% \captionsetup[figure]{labelfont=bf,labelsep=period}
+
+\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
 
@@
         \hline
-        Agent Movement Onset Time Mean        & $\mu_{A}$         \\
-        Agent Movement Onset Time Uncertainty & $\sigma_{A}$      \\
-        Reaction Time Mean                    & $\mu_{RT}$        \\
-        Reaction Time Uncertainty             & $\sigma_{RT}$     \\
-        Movement Time Mean                    & $\mu_{MT}$        \\
-        Movement Time Uncertainty             & $\sigma_{MT}$     \\
-        Neuromechanical Delay Mean            & $\mu_{NMD}$       \\
-        Neuromechanical Delay Uncertainty     & $\sigma_{NMD}$    \\
+        Agent Movement Onset Time Mean        & $\mu_{a}$         \\
+        Agent Movement Onset Time Uncertainty & $\sigma_{a}$      \\
+        Reaction Time Mean                    & $\mu_{rt}$        \\
+        Reaction Time Uncertainty             & $\sigma_{rt}$     \\
+        Movement Time Mean                    & $\mu_{mt}$        \\
+        Movement Time Uncertainty             & $\sigma_{mt}$     \\
+        Neuromechanical Delay Mean            & $\mu_{nmd}$       \\
+        Neuromechanical Delay Uncertainty     & $\sigma_{nmd}$    \\
         Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
@@
         \hline
-        Reaction Time Delay       & $\mathcal{N}(\mu_{RT},\sigma_{RT})$         \\
-        Movement Time Delay       & $\mathcal{N}(\mu_{MT},\sigma_{MT})$         \\
-        Neuromechanical Delay     & $\mathcal{N}(\mu_{NMD},\sigma_{NMD})$       \\
+        Reaction Time             & $\mathcal{N}(\mu_{rt},\sigma_{rt})$         \\
+        Movement Time             & $\mathcal{N}(\mu_{mt},\sigma_{mt})$         \\
+        Neuromechanical Delay     & $\mathcal{N}(\mu_{nmd},\sigma_{nmd})$       \\
+        Switch Time               & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
+        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
         Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
-        Switch Time Delay         & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
-        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
         \hline
@@
 \begin{equation}
-    f(t) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{t-\mu}{\sigma})^2}
+    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
 \end{equation}
 \begin{equation}
-    F(t) = P(T\leq t) = \int_{-\infty}^{t} f(t)dt
+    P(u\leq X\leq v) = \int_{u}^{v} f_{X}(x; \mu, \sigma)dt
 \end{equation}
+% \begin{equation}
+%     t \in [0,1500]
+% \end{equation}
 \begin{equation}
-    t \in [0,1500]
-\end{equation}
-\begin{equation}
-    T\sim\mathcal{N}(\mu,\sigma)
+    X\sim\mathcal{N}(\mu,\sigma)
 \end{equation}
 
-% Define prob react and guess
+% % Define prob react and guess
+% \begin{equation}
+%     P(React|\tau) = P(\tau>\mu_{A}; \sigma_{\tau}, \sigma_{A})
+% \end{equation}
+% \begin{equation}
+%     P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{\tau}, \sigma_{A})
+% \end{equation}
+
+% Define random variables A and T
+% Define expected value
 \begin{equation}
-    P(React|\tau) = P(\tau>\mu_{A}; \sigma_{tau}, \sigma_{A})
-\end{equation}
-\begin{equation}
-    P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{tau}, \sigma_{A})
+    \mu_{A} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{A}(a)dx
 \end{equation}
 
-% Define expected value
+\begin{align}
+    A & \sim\mathcal{N}(\mu_{A},\sigma_{A}) \\
+    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
+\end{align}
+
+% Define indicator function and the set S
+\begin{align}
+     & \mathbbm{1}_{a \in S} =
+    \begin{cases}
+        1, & \text{if } a \in S     \\
+        0, & \text{if }  a \notin S
+    \end{cases}                                                             \\
+     & \text{\emph{where} } S = \{a \mid a < t; \hspace{2pt} a,t \in \mathbb{R}\} \nonumber
+\end{align}
+
+% Define Cutoff react mean 
 \begin{equation}
-    \mu_{X} = \sum_{i = -\infty}^{\infty}x_{i}f(x_{i};\mu_{X}, \sigma_{X})
+    \mu_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} a \cdot p(a) \cdot p(t) \cdot \mathbbm{1}_{a \in S} \ dxdt} {P(A<T) }
 \end{equation}
 
-% Define indicator function
 \begin{equation}
-    \mathbbm{1}_{a_{i},t_{i} \in S} = 
-    \begin{cases}
-        1, & \text{if } a_{i},t_{i} \in S \\
-        0, & \text{if }  a_{i},t_{i} \notin S
-    \end{cases}    
+    \sigma^2_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (a - \mu_{A_{react}})^2 \cdot p(a) \cdot p(t_{j}) \cdot \mathbbm{1}_{a \in S} \ dx \ dt}{P(A<T)}
 \end{equation}
-
-% Define
 
@@
 \begin{equation}
-    \mu_{RMO} = \mu_{A_{cutoff}} + \mu_{RT}
+    \mu_{mo_{react}} = \mu_{A_{react}} + \mu_{rt}
 \end{equation}
 \begin{equation}
-    \sigma_{RMO} = \sqrt{\sigma_{A_{cutoff}}^2 + \sigma_{RT}^2}
+    \sigma_{mo_{react}} = \sqrt{\sigma_{A_{react}}^2 + \sigma_{rt}^2}
 \end{equation}
 \begin{equation}
-    \mu_{GMO} = \\tau +  \mu_{NMD} + \mu_{switch}
+    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
 \end{equation}
 \begin{equation}
-    \sigma_{GMO} = \sqrt{\sigma_{\tau}^2 + \sigma_{NMD}^2 + \sigma_{switch}^2}
+    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
 \end{equation}
@@
 % Scores 
-
 \begin{equation}
@@
 
+% Prob React and Guess
+\begin{align}
+    P(React)             & = P(A<T) \nonumber                                      \\
+                         & = P(A-T<0) \nonumber                                    \\
+                         & = P(Z<0)                                                \\
+    \text{\emph{where} } & Z\sim \mathcal{N}(\mu_{z}, \sigma_{z})   \nonumber      \\
+                         & \mu_z = \mu_A - \mu_\tau                 \nonumber      \\
+                         & \sigma_z = \sqrt{\sigma_{A}^2 + \sigma_{T}^2} \nonumber
+\end{align}
+
+\begin{align}
+    P(G) = 1 - P(React)
+\end{align}
+
+% Target Reach Time 
+\begin{align}
+    \mu_{reach_{react}} =\mu_{mo_{react}} + \mu_{mt}                      \\
+    \sigma_{reach_{react}} = \sqrt{\sigma_{mo_{react}}^2 + \sigma_{mt}^2} \\
+    \mu_{reach_{guess}} =\mu_{mo_{guess}} + \mu_{mt}                      \\
+    \sigma_{reach_{guess}} = \sqrt{\sigma_{mo_{guess}}^2 + \sigma_{mt}^2}
+\end{align}
+
+% Probability of Reaching Target
+\begin{align}
+    P(Reach|React) = P(X_{reach_{react}} < 1500) \\
+    \text{\emph{where} } X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \nonumber
+\end{align}
+\begin{align}
+    P(Reach|Guess) = P(X_{reach_{guess}} < 1500) \\
+    \text{\emph{where} } X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \nonumber
+\end{align}
+
+% Probability of being correct
+\begin{equation}
+    P(Correct|React) = 1.0
+\end{equation}
+\begin{equation}
+    P(Correct|Guess) = 0.5
+\end{equation}
+
+% Probability of winning sequence
+\begin{equation}
+    P(Win|React) = P(Reach|React) \cdot P(Correct|React)
+\end{equation}
+\begin{equation}
+    P(Win|Guess) = P(Reach|Guess) \cdot P(Correct|Guess)
+\end{equation}
+\begin{equation}
+    P(Win) = P(React) \cdot P(Win|React) + P(Guess) \cdot P(Win|Guess) 
+\end{equation}
+
+% Probability of incorrect sequence 
+\begin{equation}
+    P(Incorrect|React) = P(Reach|React) \cdot (1 - P(Correct|React))
+\end{equation}
+\begin{equation}
+    P(Incorrect|Guess) = P(Reach|Guess) \cdot (1 - P(Correct|Guess))
+\end{equation}
+\begin{equation}
+    P(Incorrect) = P(React) \cdot P(Incorrect|React) + P(Guess) \cdot P(Incorrect|Guess) 
+\end{equation}
+
+% Probability of incorrect sequence 
+\begin{equation}
+    P(Indecision|React) = 1 - P(Reach|React)
+\end{equation}
+\begin{equation}
+    P(Indecision|Guess) = 1 - P(Reach|Guess)
+\end{equation}
+\begin{equation}
+    P(Indecision) = P(React) \cdot P(Indecision|React) + P(Guess) \cdot P(Indecision|Guess) 
+\end{equation}
+
+% Expected Reward
+\begin{equation}
+    R_{win} = 1
+\end{equation}
+\begin{equation}
+    R_{indecision} = 0
+\end{equation}
+\begin{equation}
+    R_{incorrect} = 0
+\end{equation}
+
+\begin{align}
+    \mathbb{E}[R] = & P(Win) \cdot R_{Win} + P(Incorrect) \cdot R_{Incorrect} + P(Indecision) \cdot R_{Indecision}
+\end{align}
+
+% Maximize expected reward with tau
+\begin{equation}
+    \tau = \underset{\tau \in [0,2000]}{argmax}(\mathbb{E}[R])
+\end{equation}
+
 \end{document}

### 2024-04-23 paper/main.tex
updated equations

@@
 % \DeclareCaptionLabelFormat{table}{1-2}
-\captionsetup[table]{labelfont=bf,labelsep=period}
-% \captionsetup[figure]{labelfont=bf,labelsep=period}
+\captionsetup[table]{labelfont=bf, labelsep=period}
+\captionsetup[figure]{labelfont=bf, labelsep=colon, font=footnotesize, justification=justified}
 
@@
 
-\newcommand{\SethCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
+\newcommand{\SuppCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
 \newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
@@
 
+% Condition variables
+\def\emlv{\emph{early mean low variance}}
+\def\emhv{\emph{early mean high variance}}
+\def\mmlv{\emph{middle mean low variance}}
+\def\mmhv{\emph{middle mean high variance}}
+\def\lmlv{\emph{late mean low variance}}
+\def\lmhv{\emph{late mean high variance}}
+
 % \definecolor{myudblue}{RGB}{0, 83, 159}
 \begin{document}
-% \SectionHeader{Main Figures}
+\SectionHeader{Main Figures}
 
@@
 
-%     \SethCaption{Figure 1.}{Experimental Design}
+%     \caption{\textbf{Experimental Design.} \textbf{A)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
+An LCD projected images (start position, targets) onto a semi-silvered mirror that occluded vision of the hand and upper arm.
+Participants began each trial by moving their cursor (purple) into the start position (solid white circle).
+They then heard a tone and saw two targets (white rings) and a timing bar (white rectangle) appear on the screen.
+During each trial, an agent (yellow) would move quickly in a straight line to one of the two targets.
+Participants were instructed to reach the same target as the agent within a time constraint of 1500ms.
+This time constraint was visually represented with a timing bar (white rectangle) that decreased in width according to the elapsed time.
+\textbf{B)} A trial was considered a win and the participant received one point if they successfully reached the same target as the agent within the time constraint.
+A trial was considered incorrect and the participant received zero points if they reached the opposite target as the agent within the time constraint.
+A trial was considered an indecision and the participant received 0 points if they failed to reach a target within the time constraint.
+\textbf{C)} Agent movement onset time on each trial was randomly drawn from a specific probability distribution in each condition.
+Using a within experimental design, we manipulated the mean and standard deviation of the agent movement onset time probability distribution for each of the following six conditions: 1) early mean low variance, 2) middle mean low variance, 3) late mean low variance, 4) early mean high variance, 5) middle mean high variance, 6) late mean high variance.
+%     }
 % \end{figure}
@@
 
-%     \SethCaption{Figure 2.}{Data}
+%     \caption{\textbf{Timing Behaviour.} \textbf{A)} Average participant movement onset time (y-axis) for each of the six experimental conditions (x-axis).
+\textbf{B)} Corresponding participant movement onset time (y-axis) for the three different mean onset times (x-axis) when collapsed across variance.
+During the early mean conditions, participants had a high probability of reacting to the agent and reaching a target within the time constraint.
+For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions.
+Waiting longer to react and/or late guessing led to longer movement onset times.
+In the late mean condition participants either guessed early to avoid a late reaction to the agent, or waited to react but ended up producing a late guess.
+The combination of early and late guesses led to an early movement onset time compared to the middle mean condition.
+For both the middle mean and late mean conditions, late guessing often led to indecisions (see Fig.
+3A).
+\textbf{C)} Participant movement onset time standard deviation (y-axis) for each of the six experimental conditions (x-axis).
+\textbf{D)} Corresponding participant movement onset time standard deviation (y-axis) for the three different mean onset times (x-axis), when collapsed across variance.
+In the late mean conditions, the combination of early and late guesses led to a larger participant movement onset time standard deviation compared to the early mean and middle mean conditions.
+Box and whisker plots display the 25th, 50th, and 75th percentiles.
+Open gray circles and connecting lines represent individual data.
+}
 % \end{figure}
@@
 
-%     \SethCaption{Figure 3.}{Data}
+%     \caption{\textbf{Trial Outcomes.} \textbf{A)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition.
+\textbf{A)} We found that the middle mean low variance and late mean low variance conditions had a significantly greater number of indecisions compared to the early mean low variance condition.
+That is, in the middle mean low variance and late mean low variance conditions, participants often waited to react to the agent but ended up guessing late.
+These late guesses often led to indecisions.
+\textbf{B)} Interestingly, we also found that the average win percentage (4X.X\%) was significantly below the 50\% chance level (p < 0.001) in the late mean low variance condition, clearly demonstrating suboptimal behaviour.
+Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the agent.
+Collectively, these results show that participants were suboptimal decision makers that led to excessively indecisive behaviour.}
 % \end{figure}
@@
 
-%     \SethCaption{Figure 4.}{Data}
+%     \caption{\textbf{Models.} \textbf{A)} Predicted target reach times from three models: No Switch Time Model (light gray), Known Switch Time Model (dark gray), and Unknown Switch Time Model (black).
+Agent movement onset time is shown in pink, which corresponds to the late mean low variance condition.
+The time constraint on the task is shown in purple.
+Predicted indecision proportion is the area shown in dark blue.
+The Unknown Switch Time Model (black) is the only model that predicts indecisions for the late mean low variance condition, aligning with the data (see Figure 5C).
+\textbf{B)} Each model has inputs that represent the delays and uncertainties inherent to the sensorimotor system and the agent movement onset distribution.
+The decision policy finds the stopping time that maximizes reward.
+Given that the agent has not yet moved, the stopping time represents the time that participants transition from reacting to guessing.
+It is important to note that each model will react to the agent if it moves prior to the stopping time.
+The decision policy accounts for only the known inputs to determine stopping time.
+The decision policy is unaware of the unknown inputs when determining the stopping time, but these unknown inputs still influence the model outputs.
+The No Switch Time Model (light gray) has knowledge of all its model inputs.
+However, it does not consider the potential delay and uncertainties associated with switching from reaching to guessing, which we term ‘switch time’.
+The Known Switch Time Model (dark gray) has knowledge of all model inputs, including the switch time.
+Finally, the Unknown Switch Time Model (black) has knowledge of several of the model inputs, but is unaware of decision uncertainty and the switch time.
+\textbf{C)} Outputs for each of the models.}
 % \end{figure}
+
+% % Figure 5 Model Outputs
 % \begin{figure}[H]
-%     \centering
+%     \begin{minipage}[c]{0.67\textwidth}
+
 %         \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}
-
-%     \SethCaption{Figure 5.}{Data w/ models}
+%     \end{minipage}\hfill
+%     \begin{minipage}[c]{0.3\textwidth}
+%         \caption{
+%             Model Outputs: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{A)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
+The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the late mean low variance and late mean high variance conditions.
+Conversely, the Unknown Switch Time Model (black) is able to accurately predict the participant data for all conditions across all metrics.
+As a reminder, the Unknown Switch time Model does not account for the delay and uncertainties associated with switching from reacting to guessing.
+Critically, in \textbf{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the late mean low variance condition, whereas the other two models predict zero indecisions for that condition.
+Further, in \textbf{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the late mean low variance condition.
+Collectively, our findings show that humans are suboptimal and excessively indecisive, which can be captured by a model that does not account  for the delay and uncertainties associated with switching from reacting to guessing.
+%         } 
+%     \end{minipage}
 % \end{figure}
@@
 
-%     \SethCaption{Figure 6.}{Experiment 2 Design}
+%     \caption{\textbf{Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1.
+\textbf{A)} Participants responded to two different types of stimuli.
+In the react trials (pink), the agent (yellow cursor) would move to one of the two potential targets.
+Participants were instructed to reach the same target as the agent as quickly as possible.
+\textbf{B)} In the guess trials (blue), the agent disappeared from the start position.
+Once the agent disappeared, participants were instructed to guess which target the agent would appear in and select that target as quickly as possible.
+After the participant reached the target, the agent’s cursor would appear in one of the targets.
+\textbf{C)} We had three experimental conditions.
+In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+Participants were informed that the agent would either move to one of the targets or disappear.
+In the only react condition, participants were informed that the agent would alway move to one of the two targets (50 react trials and 0 guess trials).
+They were also told that the agent would not disappear.
+In the only guess condition, participants were informed that the agent would always disappear (0 react trials and 50 guess trials).
+They were also informed the agent would not move.
+}
 % \end{figure}
@@
 
-%     \SethCaption{Figure 7.}{React or Guess panel}
+%     \caption{A) Response time (y-axis) for each of the experimental conditions (x-axis).
+Participants had significantly greater response times for guess trials in the react or guess condition compared to the only guess condition.
+Critically, this result suggests there is an additional delay when participants initially wait to react to the agent and then switch to guessing.
+B) Interquartile range (IQR) of response times (y-axis) was used to quantify participants’ response time uncertainty for each of the experimental conditions (x-axis).
+Participants had significantly greater response time uncertainty for guess trials in the react or guess condition than in the only guess condition.
+Similarly, this finding suggests there is additional uncertainty when participants initially wait to react to the agent and then switch to guessing.
+Taken together, these results match the predictions of our model in Experiment 1, providing empirical evidence for an additional delay and uncertainty when switching from reacting to guessing.}
 % \end{figure}
@@
 
-%     \SethCaption{Supplementary Figure 1.}{Reaction and Guess Decisions}
+%     \SuppCaption{Supplementary Figure 1.}{Reaction and Guess Decision Percentages for Experiment 1: Estimated percentage of reaction (pink) and guess (blue) decision percentages (y-axis) for each experimental condition (x-axis).
+During Experiment 1 participants were rewarded for successful trials and experienced a time constraint.
+Thus, we would expect participants to have faster reaction times in Experiment 1 than in the Reaction Time task (citation).
+To account for this, we adjusted participants’ reaction times by subtracting 25ms from their median reaction time in the Reaction Time task.
+A trial was a reaction decision if the difference between the agent’s movement onset time and participant’s movement onset time was greater than that participant’s adjusted reaction time.
+Conversely, a trial was a guess decision if the difference between the agent movement onset time and participant movement onset time was less than that participant’s adjusted reaction time.
+We found that participants guessed significantly more often as the agent’s mean movement onset time approached the time constraint.
+}
 % \end{figure}
@@
 
-%     \SethCaption{Supplementary Figure 2.}{Model Loss Comparison}
+%     \SuppCaption{Supplementary Figure 2.}{Model Loss Comparison}
 % \end{figure}
 
-\SectionHeader{Methods}
-\begin{table}[h]
-    \centering
-    \begin{tabular}{|l | c|}
-        \hline
-        Agent Movement Onset Time Mean        & $\mu_{a}$         \\
-        Agent Movement Onset Time Uncertainty & $\sigma_{a}$      \\
-        Reaction Time Mean                    & $\mu_{rt}$        \\
-        Reaction Time Uncertainty             & $\sigma_{rt}$     \\
-        Movement Time Mean                    & $\mu_{mt}$        \\
-        Movement Time Uncertainty             & $\sigma_{mt}$     \\
-        Neuromechanical Delay Mean            & $\mu_{nmd}$       \\
-        Neuromechanical Delay Uncertainty     & $\sigma_{nmd}$    \\
-        Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
-        Switch Time Mean                      & $\mu_{switch}$    \\
-        Switch Time Uncertainty               & $\sigma_{switch}$ \\
-        \hline
-    \end{tabular}
-    \caption[]{Inputs to the model}
-\end{table}
+% \SectionHeader{Methods}
+% \begin{table}[h]
+%     \centering
+%     \begin{tabular}{|l | c|}
+%         \hline
+%         Agent Movement Onset Time Mean        & $\mu_{a}$         \\
+%         Agent Movement Onset Time Uncertainty & $\sigma_{a}$      \\
+%         Reaction Time Mean                    & $\mu_{rt}$        \\
+%         Reaction Time Uncertainty             & $\sigma_{rt}$     \\
+%         Movement Time Mean                    & $\mu_{mt}$        \\
+%         Movement Time Uncertainty             & $\sigma_{mt}$     \\
+%         Neuromechanical Delay Mean            & $\mu_{nmd}$       \\
+%         Neuromechanical Delay Uncertainty     & $\sigma_{nmd}$    \\
+%         Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
+%         Switch Time Mean                      & $\mu_{switch}$    \\
+%         Switch Time Uncertainty               & $\sigma_{switch}$ \\
+%         \hline
+%     \end{tabular}
+%     \caption[]{Inputs to the model}
+% \end{table}
 
-\begin{table}[h]
-    \centering
-    \begin{tabular}{|l | c|}
-        \hline
-        Reaction Time             & $\mathcal{N}(\mu_{rt},\sigma_{rt})$         \\
-        Movement Time             & $\mathcal{N}(\mu_{mt},\sigma_{mt})$         \\
-        Neuromechanical Delay     & $\mathcal{N}(\mu_{nmd},\sigma_{nmd})$       \\
-        Switch Time               & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
-        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
-        Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
-        \hline
-    \end{tabular}
-    \caption[]{Inputs to the model}
-\end{table}
+% \begin{table}[h]
+%     \centering
+%     \begin{tabular}{|l | c|}
+%         \hline
+%         Reaction Time             & $\mathcal{N}(\mu_{rt},\sigma_{rt})$         \\
+%         Movement Time             & $\mathcal{N}(\mu_{mt},\sigma_{mt})$         \\
+%         Neuromechanical Delay     & $\mathcal{N}(\mu_{nmd},\sigma_{nmd})$       \\
+%         Switch Time               & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
+%         Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
+%         Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
+%         \hline
+%     \end{tabular}
+%     \caption[]{Inputs to the model}
+% \end{table}
 
@@
 \begin{equation}
-    P(u\leq X\leq v) = \int_{u}^{v} f_{X}(x; \mu, \sigma)dt
+    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
 \end{equation}
@@
 % Define random variables A and T
-% Define expected value
-\begin{equation}
-    \mu_{A} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{A}(a)dx
-\end{equation}
-
 \begin{align}
@@
 
-% Define indicator function and the set S
+% Define indicator function 
 \begin{align}
-     & \mathbbm{1}_{a \in S} =
+     & \mathbbm{1}_{a<t} =
     \begin{cases}
-        1, & \text{if } a \in S     \\
-        0, & \text{if }  a \notin S
-    \end{cases}                                                             \\
-     & \text{\emph{where} } S = \{a \mid a < t; \hspace{2pt} a,t \in \mathbb{R}\} \nonumber
+        1, & \text{if } a <t, \, \forall a,t \in \mathbb{R}; \\
+        0, & \text{otherwise.}
+    \end{cases}
 \end{align}
+
+% Define expected value
+\begin{equation}
+    \mu_{A} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{A}(a)da
+\end{equation}
 
@@
 \begin{equation}
-    \mu_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} a \cdot p(a) \cdot p(t) \cdot \mathbbm{1}_{a \in S} \ dxdt} {P(A<T) }
+    \mu_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} a \cdot f_{A}(a) \cdot f_{T}(t) \cdot \mathbbm{1}_{a \in S} \ dxdt} {P(A<T)}
 \end{equation}
@@
 \begin{equation}
-    \sigma^2_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (a - \mu_{A_{react}})^2 \cdot p(a) \cdot p(t_{j}) \cdot \mathbbm{1}_{a \in S} \ dx \ dt}{P(A<T)}
+    \sigma^2_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (a - \mu_{A_{react}})^2 \cdot f_{A}(a) \cdot f_{T}(t) \cdot \mathbbm{1}_{a<t} \ da \ dt}{P(A<T)}
 \end{equation}
@@
 \begin{equation}
-    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
+    \mu_{mo_{guess}} = \tau +  \mu_{nmd}
 \end{equation}
 \begin{equation}
-    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
+    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
 \end{equation}
-
-% Scores 
-\begin{equation}
-    R_{win} = 1
-\end{equation}
-\begin{equation}
-    R_{indecision} = 0
-\end{equation}
-\begin{equation}
-    R_{incorrect} = 0
-\end{equation}
-
-% Prob React and Guess
-\begin{align}
-    P(React)             & = P(A<T) \nonumber                                      \\
-                         & = P(A-T<0) \nonumber                                    \\
-                         & = P(Z<0)                                                \\
-    \text{\emph{where} } & Z\sim \mathcal{N}(\mu_{z}, \sigma_{z})   \nonumber      \\
-                         & \mu_z = \mu_A - \mu_\tau                 \nonumber      \\
-                         & \sigma_z = \sqrt{\sigma_{A}^2 + \sigma_{T}^2} \nonumber
-\end{align}
-
-\begin{align}
-    P(G) = 1 - P(React)
-\end{align}
 
@@
 
+% Reach random variables
+\begin{align}
+    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
+    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}})
+\end{align}
+
 % Probability of Reaching Target
 \begin{align}
-    P(Reach|React) = P(X_{reach_{react}} < 1500) \\
-    \text{\emph{where} } X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \nonumber
+    P(Reach|React) = P(X_{reach_{react}} < 1500)
 \end{align}
 \begin{align}
-    P(Reach|Guess) = P(X_{reach_{guess}} < 1500) \\
-    \text{\emph{where} } X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \nonumber
+    P(Reach|Guess) = P(X_{reach_{guess}} < 1500)
 \end{align}
+
+% Probability of incorrect sequence 
+\begin{equation}
+    P(Indecision|React) = 1 - P(Reach|React)
+\end{equation}
+\begin{equation}
+    P(Indecision|Guess) = 1 - P(Reach|Guess)
+\end{equation}
 
@@
 \end{equation}
-\begin{equation}
-    P(Win) = P(React) \cdot P(Win|React) + P(Guess) \cdot P(Win|Guess) 
-\end{equation}
 
@@
 \end{equation}
-\begin{equation}
-    P(Incorrect) = P(React) \cdot P(Incorrect|React) + P(Guess) \cdot P(Incorrect|Guess) 
-\end{equation}
 
-% Probability of incorrect sequence 
-\begin{equation}
-    P(Indecision|React) = 1 - P(Reach|React)
-\end{equation}
-\begin{equation}
-    P(Indecision|Guess) = 1 - P(Reach|Guess)
-\end{equation}
-\begin{equation}
-    P(Indecision) = P(React) \cdot P(Indecision|React) + P(Guess) \cdot P(Indecision|Guess) 
-\end{equation}
+% Prob React and Guess
+% \begin{align}
+%     P(React|\tau)             & = P(A<T) \nonumber                                      \\
+%                          & = P(A-T<0) \nonumber                                    \\
+%                          & = P(Z<0)                                                \\
+%     \text{\emph{where} } & Z\sim \mathcal{N}(\mu_{z}, \sigma_{z})   \nonumber      \\
+%                          & \mu_z = \mu_A - \mu_\tau                 \nonumber      \\
+%                          & \sigma_z = \sqrt{\sigma_{A}^2 + \sigma_{T}^2} \nonumber
+% \end{align}
+
+\begin{align}
+    P(React|\tau) = P(A<T)
+\end{align}
+\begin{align}
+    P(Guess|\tau) = 1 - P(React|\tau)
+\end{align}
+
+\begin{align}
+    P(Win|\tau)        =& P(React|\tau) \cdot P(Win|React) \nonumber \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
+    P(Indecision|\tau) =& P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
+    P(Incorrect|\tau)  =& P(React|\tau) \cdot P(Incorrect|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess)
+\end{align}
 
@@
 \begin{align}
-    \mathbb{E}[R] = & P(Win) \cdot R_{Win} + P(Incorrect) \cdot R_{Incorrect} + P(Indecision) \cdot R_{Indecision}
+    \mathbb{E}[R|\tau] = &P(Win|\tau) \cdot R_{Win} \nonumber\\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
 \end{align}
@@
 \begin{equation}
-    \tau = \underset{\tau \in [0,2000]}{argmax}(\mathbb{E}[R])
+    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
+\end{equation}
+
+% Switch time included in movement onset times
+\begin{equation}
+    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
+\end{equation}
+\begin{equation}
+    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
+\end{equation}
+
+% Expected switch time 
+\begin{equation}
+    \hat{\mu}_{mo_{guess}} = \tau +  \mu_{nmd} + \hat{\mu}_{switch}
+\end{equation}
+\begin{equation}
+    \hat{\sigma}_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \hat{\sigma}_{switch}^2}
+\end{equation}
+
+% Loss Equation
+
+\begin{equation}
+    \mathcal{L} = \sum_{i = 1}^{6} \sum_{j = 1}^{5} \frac{|Data_{i,j} - Model_{i,j}|}{Data_{i,j}}
 \end{equation}

### 2024-06-10 scripts/run_statistics.py
making sure I ran two-sided follow up mean comparisons

@@ -97,6 +97,7 @@ def pairwise_bootstrap(data, combos, alternative ="two-sided", M=1e6, test="mean
         return {x: alternative_dict[x] for x in alternative_dict.keys() if x in combos}
             
     alternative_dict = _get_alternative_dict(combos)
+    print(alternative_dict)
     # if self.experiment == 'Exp1':
     pvals = {}
     cles1 = {}
@@ -186,6 +187,7 @@ for i,colname in enumerate(column_names):
         test='mean'
     )
     pvals_corrected = au.holmbonferroni_correction(list(pvals.values()))
+    # print(pvals.values(), pvals_corrected)
     pvals_corrected = dict(zip(pvals.keys(),pvals_corrected))
     d1 = {"Metric":colname, "Collapsed":collapsed}
     df_row_pvals_uncorrected = d1 | pvals

### 2024-06-10 src/Subject_Object_v3.py
less than 150 instead of less than 170 for filtering reaction times

@@ -281,7 +281,7 @@ class MovementMetrics:
             self.reaction_times = self.movement_onset_times(task='reaction') - self.raw_data.agent_reaction_leave_time
         #* Filter out fault reaction times
         if filter_:
-            self.reaction_times[(self.reaction_times>650)|(self.reaction_times<170)] = np.nan
+            self.reaction_times[(self.reaction_times>650)|(self.reaction_times<150)] = np.nan
     
     @lru_cache
     def exp2_react_guess_reaction_time_all(self, react_or_guess):

### 2024-06-10 scripts/generate_df_for_stats.py
no longer filtering anything out on the exp2 trial by trial dataframe, will filter if needed in the plotting scripts

@@ -212,8 +212,8 @@ def generate_exp2_trial_dataframe(group):
     subject_number = np.repeat(np.arange(1, it.num_subjects + 1, 1, dtype=int), num_conditions*num_trials) # Get subject 1 300 times, then sub 2 300 times
     condition = np.tile(np.repeat(['mixed','react_only','guess_only'],num_trials), it.num_subjects) # Get (1 100 times, then 2 100 times etc. and then tile that for each subject)
     reaction_decision_array = np.where(group.movement_metrics.reaction_decision_array.flatten()==1.0,'right','left')
-    group.movement_metrics.get_reaction_times(filter_=False)
-    reaction_time = group.movement_metrics.reaction_times.flatten() #! FILTERING REACTION TIMES <170 or >600 out in the subject object
+    group.movement_metrics.get_reaction_times(filter_=False) #! Not filtering the trial by trial dataframe, will filter when I calculate reaction times directly in the script with the df
+    reaction_time = group.movement_metrics.reaction_times.flatten() 
     movement_time = group.movement_metrics.movement_times(task="reaction").flatten()
     decision_type = np.where(group.movement_metrics.reaction_guess_mask,"guess","react").flatten()
     df = pd.DataFrame({
@@ -236,6 +236,7 @@ SAVE_PATH = Path(r"D:\OneDrive - University of Delaware - o365\Desktop\MatchPenn
 print('here')
 # group = rdf.generate_subject_object_v3("Exp1", "All Trials", movement_metric_type='velocity')
 
+#! FILTERING REACTION TIMES <150 or >650 out in the subject object
 group2 = rdf.generate_subject_object_v3("Exp2", "All Trials", movement_metric_type='velocity')
 
 # df1 = generate_exp1_summary_dataframe(group, EXPERIMENT, DROP_SUBJECT_NUM=None)

### 2024-06-10 paper/main.tex
updated equation ordering and parameter table

@@
 \usepackage{caption}
+\usepackage{arydshln} % For \hdashline
+
 \graphicspath{ {./figures/} }
@@
 \begin{equation}
+    X\sim\mathcal{N}(\mu,\sigma)
+\end{equation}
+
+\begin{equation}
     f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
@@
 % \end{equation}
-\begin{equation}
-    X\sim\mathcal{N}(\mu,\sigma)
-\end{equation}
-
-% % Define prob react and guess
-% \begin{equation}
-%     P(React|\tau) = P(\tau>\mu_{A}; \sigma_{\tau}, \sigma_{A})
-% \end{equation}
-% \begin{equation}
-%     P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{\tau}, \sigma_{A})
-% \end{equation}
 
@@
 
+% Define prob react and guess
+\begin{equation}
+    P(React|\tau) = P(\tau>\mu_{A}; \sigma_{\tau}, \sigma_{A})
+\end{equation}
+\begin{equation}
+    P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{\tau}, \sigma_{A})
+\end{equation}
+
 % Define indicator function 
@@
     \begin{cases}
-        1, & \text{if } a <t, \, \forall a,t \in \mathbb{R}; \\
-        0, & \text{otherwise.}
+        1 & \text{if } a <t,  \\
+        0 & \text{otherwise.}
     \end{cases}
@@
 \begin{equation}
-    \mu_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} a \cdot f_{A}(a) \cdot f_{T}(t) \cdot \mathbbm{1}_{a \in S} \ dxdt} {P(A<T)}
+    \mu_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} a \cdot f_{A}(a) \cdot f_{T}(t) \cdot \mathbbm{1}_{a \in S} \ dadt} {P(A<T)}
 \end{equation}
@@
 \begin{equation}
-    \mu_{mo_{react}} = \mu_{A_{react}} + \mu_{rt}
+    \mu_{mot_{react}} = \mu_{A_{react}} + \mu_{rt}
 \end{equation}
 \begin{equation}
-    \sigma_{mo_{react}} = \sqrt{\sigma_{A_{react}}^2 + \sigma_{rt}^2}
+    \sigma_{mot_{react}} = \sqrt{\sigma_{A_{react}}^2 + \sigma_{rt}^2}
 \end{equation}
 \begin{equation}
-    \mu_{mo_{guess}} = \tau +  \mu_{nmd}
+    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
 \end{equation}
 \begin{equation}
-    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
+    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
+\end{equation}
+
+% Switch time included in movement onset times
+\begin{equation}
+    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
+\end{equation}
+\begin{equation}
+    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
 \end{equation}
@@
 \begin{align}
-    \mu_{reach_{react}} =\mu_{mo_{react}} + \mu_{mt}                      \\
-    \sigma_{reach_{react}} = \sqrt{\sigma_{mo_{react}}^2 + \sigma_{mt}^2} \\
-    \mu_{reach_{guess}} =\mu_{mo_{guess}} + \mu_{mt}                      \\
-    \sigma_{reach_{guess}} = \sqrt{\sigma_{mo_{guess}}^2 + \sigma_{mt}^2}
+    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
+    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
+    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
+    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}
+\end{align}
+
+% Hat reach time
+\begin{align}
+    \hat{\mu}_{reach_{guess}} = \hat{\mu}_{mot_{guess}} + \mu_{mt} \\
+    \hat{\sigma}_{reach_{guess}} = \sqrt{\hat{\sigma}_{mot_{guess}}^2 + \sigma_{mt}^2}
 \end{align}
@@
     X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
-    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}})
+    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
+    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}})
 \end{align}
@@
 \begin{align}
-    P(Win|\tau)        =& P(React|\tau) \cdot P(Win|React) \nonumber \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
-    P(Indecision|\tau) =& P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
-    P(Incorrect|\tau)  =& P(React|\tau) \cdot P(Incorrect|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess)
+    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
+    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
+    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess)
 \end{align}
@@
 \begin{align}
-    \mathbb{E}[R|\tau] = &P(Win|\tau) \cdot R_{Win} \nonumber\\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
+    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
 \end{align}
@@
     \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
-\end{equation}
-
-% Switch time included in movement onset times
-\begin{equation}
-    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
-\end{equation}
-\begin{equation}
-    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
-\end{equation}
-
-% Expected switch time 
-\begin{equation}
-    \hat{\mu}_{mo_{guess}} = \tau +  \mu_{nmd} + \hat{\mu}_{switch}
-\end{equation}
-\begin{equation}
-    \hat{\sigma}_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \hat{\sigma}_{switch}^2}
 \end{equation}
@@
 
+% Fit Parameter Table
+{\renewcommand{\arraystretch}{1.2}% for the vertical padding
+\begin{table}[h]
+    \centering
+    \begin{tabular}{l|c|c }
+        % \hline
+                                  & Decision Policy Parameter Value & Model Output Parameter Value \\
+        \hline
+        \textit{No Switch Time Model}      & -                               & -                            \\
+        \hdashline
+        \textit{Known Switch Time Model}   & \begin{tabular}[t]{@{}c@{}}$\mu_{switch}=2.82$ ms \\$\sigma_{switch}=70.95$ ms\end{tabular}   & \begin{tabular}[t]{@{}c@{}}$\mu_{switch}=2.82$ ms \\$\sigma_{switch}=70.95$ ms\end{tabular} \\
+        \hdashline
+        \textit{Unknown Switch Time Model}   & \begin{tabular}[t]{@{}c@{}}$\mu_{switch}=5.31$ ms \\$\sigma_{switch}=14.06$ ms\\$\sigma_{\tau}=2.03$ ms \end{tabular}   & \begin{tabular}[t]{@{}c@{}}$\mu_{switch}=31.17$ ms \\$\sigma_{switch}=115.35$ ms\\$\sigma_{\tau}=77.60$ ms\end{tabular} \\
+        % \hline
+    \end{tabular}
+    \caption[]{Fit values for each of the three models.
+The No Switch Time Model has no fit parameters.
+The Known Switch Time Model fit the switch time mean and uncertainty.
+Additionally, this model required the decision policy parameter value and the model output parameter value to be equal.
+The Unknown Switch Time Model fits the switch time mean, switch time uncertainty, and stopping time uncertainty.
+This model allowed the decision policy parameter value and the model output parameter value to be fit separately.
+Importantly, for the Unknown Switch Time Model, the parameter values used by the decision policy were found to be less than the parameter values that affect the model outputs.
+Since the Unknown Switch Time model had the lowest loss, this result suggests that participants do not account for the delay and uncertainty associated with switching from reacting to guessing.}
+\end{table}
+
 \end{document}
+
+% Expected switch time 
+\begin{equation}
+    \hat{\mu}_{mot_{guess}} = \tau +  \mu_{nmd} + \hat{\mu}_{switch}
+\end{equation}
+\begin{equation}
+    \hat{\sigma}_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \hat{\sigma}_{switch}^2}
+\end{equation}

### 2024-06-27 scripts/optimal_model/generate_model_inputs_and_bootstrap_parameters.py
updated scripts for producing models

@@ -43,8 +43,10 @@ rt_sd = np.nanstd(group.movement_metrics.reaction_times, axis=1)
 mt = np.min(np.nanmean(group.movement_metrics.movement_times("task"), axis=2), axis=1)
 mt_sd = np.min(np.nanstd(group.movement_metrics.movement_times("task"), axis=2), axis=1)
 timing_sd = np.nanstd(group.movement_metrics.coincidence_reach_time, axis=1)
-agent_sds = np.nanmean(np.nanstd(group.raw_data.agent_task_leave_time, axis=2),axis=0)
-agent_means = np.nanmean(np.nanmean(group.raw_data.agent_task_leave_time, axis=2),axis=0)
+agent_sds_calc = np.nanmean(np.nanstd(group.raw_data.agent_task_leave_time, axis=2),axis=0)
+agent_sds = np.array([50.0,150.0,50.0,150.0,50.0,150.0])
+agent_means_calc = np.nanmean(np.nanmean(group.raw_data.agent_task_leave_time, axis=2),axis=0)
+agent_means = np.array([1000.0,100.00,1100.0,1100.0,1200.0,1200.0])
 metrics = [rt,rt_sd,mt,mt_sd,timing_sd,agent_sds,agent_means]
 keys = ["rt","rt_sd","mt","mt_sd","timing_sd","agent_sds","agent_means"]
 model_input_dict = dict(zip(keys,metrics))

### 2024-06-27 scripts/optimal_model/generate_models_for_comparison_bootstrapped.py

@@ -22,10 +22,14 @@ This script can either do the warmstarts (set WARM_START = True)
 It can also bootstrap using the best warmstart initial conditions
 
 Model Options Final
-1. suboptimal_one
+1. optimal
   - THis fits the switch delay and switch sd, but model has knowledge
 2. suboptimal_partial
-  - this fits the switch delay and switch sd expected and true, 
+  - this fits the switch delay and switch sd expected and true
+3. suboptimal_none
+  - THis fits the switch delay and sd true to whatever, while holding the expected equal to 0
+
+NOTE: base_model is run simultaneously as the fit model if STORE_BASE_MODEL = True
 '''
 
 # * Functions
@@ -86,11 +90,11 @@ it = InitialThangs(EXPERIMENT)
 
 #! SET THE SETTINGS BEFORE RUNNING SCRIPT
 print("DID YOU SET THE RIGHT SETTINGS?")
-FIT_PARAMETERS = True
-SAVE = True
-MODEL_TO_FIT = "suboptimal_all" # OPTIONS: "optimal", "suboptimal_partial", "suboptimal_none"
-WARM_START = True # If False, that means I'm bootstrapping with the warmstart initial condition 
-STORE_BASE_MODEL = False
+FIT_PARAMETERS   = True
+SAVE             = True
+MODEL_TO_FIT     = "optimal" # OPTIONS: "optimal", "suboptimal_partial", "suboptimal_none"
+WARM_START       = False # If False, that means I'm bootstrapping with the warmstart initial condition 
+STORE_BASE_MODEL = True
 input_keys = ["rt","rt_sd","mt","mt_sd","timing_sd",]
 print(f" Fit Parameters: {FIT_PARAMETERS}\n Save: {SAVE}\n Model to Fit: {MODEL_TO_FIT}\n Warm Start: {WARM_START}\n Store Base Model: {STORE_BASE_MODEL}")
 print(f" Fitting: {MODEL_TO_FIT}")
@@ -124,14 +128,15 @@ if True:
 if WARM_START:
     print("FINDING INITIAL CONDITIONS")
     if MODEL_TO_FIT != "suboptimal_all":
-        iters = 10000
+        iters = 1000
         #* Randomize for warmstart
         player_inputs = dict(zip(input_keys,true_parameters)) #! This won't change unless we're boostrapping so can pull out of for loop for Warm_Start
         switch_delay_expected_rand = np.random.uniform(0,200,size=iters)
[…]

### 2024-07-29 paper/main.tex
updated figures not sure what
started getting everything into latex

--- 2024-03-29 paper/main.tex
@@
 \usepackage{caption}
+\usepackage{arydshln} % For \hdashline
+\usepackage{lineno}
+\usepackage{setspace}
+
+\definecolor{mydarkblue}{RGB}{0,51,102}
 \graphicspath{ {./figures/} }
-\usepackage[backend=biber]{biblatex}
+
+\usepackage[%
+  autocite  = superscript,
+  backend  = bibtex,
+  sortcites  = false,
+  citestyle = numeric,
+  bibstyle=authoryear,
+  sorting = none,
+  maxbibnames=99,
+  giveninits = true, %initials
+  isbn=false,
+  doi = false,
+  url = false
+]{biblatex}
+
+\addbibresource{Aim1.bib}
+% \bibliography{draft}
+
 \usepackage[paper=letterpaper,
@@
             includemp]{geometry}
-\usepackage{fontspec} %XeLatex
+
+\renewbibmacro{in:}{}
+\DeclareFieldFormat[article]{citetitle}{#1}
+\DeclareFieldFormat[article]{title}{#1}  %
+\DeclareFieldFormat{pages}{#1}% no prefix for the `pages` field in the bibliography
+\DeclareNameAlias{sortname}{family-given} % put last name first
+\DeclareNameAlias{default}{family-given}
+\DeclareFieldFormat{labelnumberwidth}{\textcolor{mydarkblue}{\mkbibbold{#1\adddot}}} %remove brackets in bibliography
+\DeclareFieldFormat{journaltitle}{\mkbibemph{#1}\isdot}
+%\renewcommand{\labelnamepunct}{\addspace}  % remove period after year
+
+% add numbers in front of citations and puts year behind authors
+\defbibenvironment{bibliography}
+  {\list
+     {\printtext[labelnumberwidth]{%
+    \printfield{prefixnumber}%
+    \printfield{labelnumber}}}
+     {\setlength{\labelwidth}{\labelnumberwidth}%
+      \setlength{\leftmargin}{\labelwidth}%
+      \setlength{\labelsep}{\biblabelsep}%
+      \addtolength{\leftmargin}{\labelsep}%
+      \setlength{\itemsep}{\bibitemsep}%
+      \setlength{\parsep}{\bibparsep}}%
+      \renewcommand*{\makelabel}[1]{\hss##1}}
+  {\endlist}
+  {\item}
+
+\usepackage{xpatch}
+\xpatchbibmacro{date+extrayear}{%
+  \printtext[parens]%
+}{%
+  \setunit{\addperiod\space}%
+  \printtext%
+}{}{}
+\AtEveryBibitem{%
+  \clearfield{note}%
+}
+
+% adds comma after journal 
+\renewcommand\bibpagespunct{\ifentrytype{article}{\addcolon}{\addcomma}\space}
+\renewbibmacro*{volume+number+eid}{%
+\setunit*{\addcomma\space}% NEW
+  \printfield{volume}
+  \printfield[parens]{number}{,}%
+  \setunit{\addcomma\space}%
+  \printfield{eid}}
+
+% change and to \& (can also remove)
+\DefineBibliographyExtras{english}{%
+  \renewcommand*{\finalnamedelim}{\addcomma\addspace\&\addspace}%
+  %\renewcommand*{\finalnamedelim}{\addcomma\addspace}%
+}
+
+%\usepackage{hyperref}
+\usepackage{fancyhdr}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrulewidth}{0pt}
+
 \setmainfont{AvenirLTProBook.otf}[
@@
 % \DeclareCaptionLabelFormat{table}{1-2}
-\captionsetup[table]{labelfont=bf,labelsep=period}
-% \captionsetup[figure]{labelfont=bf,labelsep=period}
+% \captionsetup[table]{labelfont=bf, labelsep=period}
+\captionsetup[figure]{labelfont=bf, labelsep=colon, font=footnotesize, justification=justified}
 
-\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
+\DeclareMathOperator*{\argmax}{srg\,max} % thin space, limits underneath in displays
 
-\newcommand{\SethCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
+\newcommand{\SuppCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
 \newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
@@
 
+\abovedisplayskip = 10.0pt plus 2.0pt minus 20.0pt
+\belowdisplayskip = 10.0pt plus 2.0pt minus 20.0pt
+\abovedisplayshortskip = 0.0pt plus 20.0pt
+\belowdisplayshortskip = 9pt plus 3pt minus 20pt
+
+% Condition variables
+% \def\emlv{\emph{early mean low variance}}
+% \def\emhv{\emph{early mean high variance}}
+% \def\mmlv{\emph{middle mean low variance}}
+% \def\mmhv{\emph{middle mean high variance}}
+% \def\lmlv{\emph{late mean low variance}}
+% \def\lmhv{\emph{late mean high variance}}
+
+% \def\em{\emph{early mean}}
+% \def\mm{\emph{middle mean}}
+% \def\lm{\emph{late mean}}
+
 % \definecolor{myudblue}{RGB}{0, 83, 159}
 \begin{document}
-% \SectionHeader{Main Figures}
+%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%
+\pagenumbering{gobble} % No page number for title page
+\begin{center}
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figures/exp1_experimental_design.png}
+    \noindent\textbf{\Large\textcolor{mydarkblue}{Indecisions under time pressure arise from suboptimal switching behaviour
+        }}
+    \vspace{5mm}
+    \\
+    Seth R.
+Sullivan\textsuperscript{1}, \textsuperscript{2} Christopher Peters\textsuperscript{1}, \textsuperscript{2}, Rakshith Lokesh\textsuperscript{1}, Jan A.
+Calalo\textsuperscript{1},\\ Truc Ngo\textsuperscript{3}, John H.
+Buggeln\textsuperscript{5},Isaac Kurtzer\textsuperscript{5},Michael Carter\textsuperscript{5}, Joshua G.A.
+Cashaback\textsuperscript{1},\textsuperscript{2},\textsuperscript{4},\textsuperscript{5}
+    \vspace{2mm}
+    \\
+\end{center}
 
-%     \SethCaption{Figure 1.}{Experimental Design}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
+\textsuperscript{1} Department of Biomedical Engineering, University of Delaware\\
+\textsuperscript{2} Department of Mechanical Engineering, University of Delaware\\
+\textsuperscript{3} Human Performance Lab, University of Calgary\\
+\textsuperscript{4} Biomechanics and Movements Science Program, University of Delaware\\
+\textsuperscript{5} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
+\vspace{15mm}
+\\
+\textcolor{mydarkblue}{\large Abbreviated Title:}
+\vspace{1mm}
+\\
+Indecisive behaviour arises from suboptimal switching
+\\
+\vspace{15mm}
+\\
+\textcolor{mydarkblue}{\large Funding:}
+\vspace{1mm}
+\\
+XXXXXXXXXXXXXXX
+\\
+\vspace{10mm}
+\\
+\textcolor{mydarkblue}{\large Correspondence:}
+\vspace{1mm}
+\\
+Seth Sullivan\\
+Biomedical Engineering\\
+University of Delaware\\
+STAR Campus, Room 122\\
+Newark, DE 19711, U.S.A\\
+Email: sethsullivan99@gmail.com
+\vspace{2mm}
+\\
+Or
+\vspace{2mm}
+\\
+Joshua G. A. Cashaback, PhD\\
+Biomedical Engineering\\
+University of Delaware\\
+STAR Campus, Room 201J\\
+Newark, DE 19711, U.S.A\\
+Email: cashabackjga@gmail.com
 
-%     \SethCaption{Figure 2.}{Data}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
+\newpage
+\doublespace %
+\linenumbers %
+\noindent \textbf{\large\textcolor{mydarkblue}{ABSTRACT}}
+\vspace{2mm}
+\\
+Indecisive behaviour can be catastrophic, leading to car crashes or stock market losses.
+Despite fruitful efforts across several decades to understand decision-making, there has been little research on what leads to indecision.
+Here we examined how indecisions arise under high-pressure deadlines.
+In our first experiment, participants attempted to select a target by either reacting to a stimulus or guessing, when acting under a high pressure time constraint.
+We found that participants were suboptimal, displaying a below chance win percentage due to an excessive number of indecisions.
+Computational modeling suggested that participants were excessively indecisive because they failed to account for a time delay and temporal uncertainty when switching from reacting to guessing, which has not been previously reported in the literature.
+In a followup experiment, we show for the first time the existence of a time delay and temporal uncertainty when switching from reacting to guessing.
+Collectively, our results support the idea that humans are suboptimal and fail to account for a time delay and temporal uncertainty when switching from reacting to guessing, leading to indecisive behaviour.
+\newpage
 
-%     \SethCaption{Figure 3.}{Data}
-% \end{figure}
+\noindent \textbf{\large\textcolor{mydarkblue}{NEW AND NOTEWORTHY}}
+\vspace{2mm}
+\\
+The sensorimotor system has the constant challenge of dealing with the naturally occurring variability in our movements.
+Here we investigated the potential roles of muscular co-contraction and visuomotor feedback responses to regulate movement variability.
+When we visually amplified movements, we found that the sensorimotor system primarily uses muscular co-contraction to regulate movement variability.
+Interestingly, we found that muscular co-contraction was relative to participant-specific visuomotor feedback response, suggesting an interplay between impedance and feedback control.
+\newpage
+%\noindent\textbf{Author Summary}`
+%\vspace{2mm}\\
+%
+%\newpage
+\pagestyle{fancy}
+%\cfoot[]{\textcolor{mydarkblue}{\thepage}}
+\fancyhead[R]{\emph{\textcolor{mydarkblue}{Regulation of Movement Variability via Impedance and Feedback Control
+        }}}
+\fancyfoot[C]{\textcolor{mydarkblue}{\thepage}}
+%\fancyfoot[C]{\emph{\textcolor{mydarkblue}{\thepage}}}
+%\cfoot{\textcolor{myudblue}{\thepage}}
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/model_diagram.png}
+%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagenumbering{arabic} % page numbering starts here
+\noindent\textbf{\large\textcolor{mydarkblue}{INTRODUCTION}}
+\vspace{2mm}
+\\
+Indecisions often arise from failing to decide and act upon sensory information in time, such as a driver failing to brake or hit the gas pedal when a traffic light turns yellow.
+When acting under high pressure time constraints, the ability to accurately time a decision is critical to success.
+Past literature has had very little focus on indecisions.
+The vast majority of decision-making research either does not consider responses made after some time constraint or simply does not permit a non-response, such as in the classic two-alternative forced choice paradigm (Zachsenhouse Robust versus optimal,  Bogacz 2006, Cho et al.
+2002 Mechanisms underlying, Jogan and Stocker 2014 A new two-alternative, Ratcliff et al.
+2018 modeling 2-alternative forced-choice tasks, Tyler and Chen 2000, Ulrich and Miller 2004 Threshold estimation,   ).
+Thus, despite its real-world ubiquity and importance, we have very little understanding of how indecisions arise.
 
-%     \SethCaption{Figure 4.}{Data}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}
+There have only been a handful of papers to examine indecisions, which involve either high (Lokesh et al.
+2022) or low time pressure (Karsilar et al.
+2014, Wu et al.
+2016, Phillastides et al.
+2011, Dambacher and Hubner 2015, Forstmann et al.
+2008).
+We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target (Lokesh et al.
+2022).
+In this competitive scenario, the ‘prey’ attempted to end up in the same target as the ‘predator’ by a time constraint, while the predator attempted to end up in the opposite target as the prey.
+This task had a high time pressure, such that participants were awarded no points if they were indecisive by failing to enter either target within the time constraint.
+The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision.
+Surprisingly, participants displayed a median indecision rate of approximately 25% with an upper range close to 40% indecisions.
+Similar to others (Wu et al.
+2016, Phillastides et al.
+2011, Dambacher and Hubner 2015, Forstmann et al.
+2008), Karsilar and colleagues (2014) used a low time pressure task and found only 1.7% of trials were indecisions.
+Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline.
+Yet the mechanisms that give rise to indecisive behaviour, which is particularly relevant under common high time pressure scenarios, remains unclear.
 
-%     \SethCaption{Figure 5.}{Data w/ models}
-% \end{figure}
+Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response (drugowitsch, balci, bogacz, hudson landy, trommershauser).
+To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system (drugowitsch, bogacz, maybe balci too, hudson landy, acerbi wolpert internal representations, Wolpert/Faisal review, Kording/wolpert bayesian decision theory, wolpert/landy motor control is decision-making).
+Past work has shown that humans will often produce nearly optimal decision times during cognitive (Balci et al.
+2011, Miletic and Van Maanen 2019) and motor tasks (Hudson et al.
+2008, Faisal and Wolpert 2009 Near Optimal Combination).
+Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties (Ota et al.
+2015, drugowitsch computational precision).
+With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/exp2_design.png}
+Building on our past work (Lokesh, 2022), we developed a high pressure task with a time constraint to examine how humans select decision times.
+We tested the idea that humans optimally account for time delays and temporal uncertainties to select a decision time that maximizes reward.
+Alternatively, humans may suboptimally represent time delays and temporal uncertainties, which can lead to an excessive number of indecisions.
+In Experiment 1, we found humans were suboptimal and observed excessive indecisions that led to a below chance win rate.
+Computational modelling work suggested that suboptimality arose by failing to account for the time delay and temporal uncertainty associated with switching from reacting to guessing.
+Experiment 2 showed for the first time, to our knowledge, the existence of an additional time delay and uncertainty when switching from reacting to guessing within a trial.
+Taken together, our work suggests that humans suboptimally represent the time delay and temporal uncertainty associated with switching from reacting to guessing, leading to indecisive behaviour.
 
-%     \SethCaption{Figure 6.}{Experiment 2 Design}
-% \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\noindent\textbf{\large\textcolor{mydarkblue}{RESULTS}}
+\vspace{2mm}
+\\
+\textbf{\textcolor{mydarkblue}{{Experiment 1}}}
+\vspace{2mm}
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/exp2_reaction_panel.png}
+\noindent\textbf{\textcolor{mydarkblue}{{Experimental Design}}}
+\vspace{2mm}
 
-%     \SethCaption{Figure 7.}{React or Guess panel}
-% \end{figure}
+The goal of Experiment 1 was to test how stimulus timing influenced indecisive behaviour.
+Briefly, participants began each trial by moving their cursor into a start position (Fig.
+1A).
+The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles.
+Participants were instructed to reach the same target as the stimulus within a time constraint of 1500 ms.
+The time remaining in each trial was represented visually with a timing bar that decreased in width according to the elapsed time.
+Thus, participants were fully aware of how much time they had left relative to the time constraint.
+A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint (Fig.
+1B).
+A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
+A trial was considered an indecision and the participant received zero points if they failed to reach a target within the time constraint.
 
-% \SectionHeader{Supplementary Figures}
+For each trial within a condition, the stimulus movement onset was drawn from the same normal distribution.
+Using a 3 x 2 within experimental design (Fig.
+1C), in separate blocks we manipulated the stimulus movement onset mean (early mean = 1000 ms, middle mean = 1100 ms, late mean = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms).
+For the purposes of the main manuscript we focus on the results of the low variance conditions, but report the findings for the high variance conditions in Supplementary A.
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/reaction_guess_decisions.png}
+\noindent\textbf{\textcolor{mydarkblue}{{Participant Timing Behaviour}}}
+\vspace{2mm}
 
-%     \SethCaption{Supplementary Figure 1.}{Reaction and Guess Decisions}
-% \end{figure}
+Participant movement onsets for the low variance condition are shown in Fig.
+2A, We found a significant main effect of stimulus movement onset mean (F[1.551,29.475] = 4.36, p = 0.030) and variance (F[1.000,19.000], p = 0.017).
+There was no significant interaction between stimulus movement onset mean and variance (F[1.657,31.474], p = 0.565).
+When collapsed across low and high variance, participant movement onsets were significantly greater in the middle mean conditions compared to the early mean conditions (p = 0.014, $\hat{\theta}$=72.5 \%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
+Again when collapsed across low and high variance, participant movement onset significantly decreased from the middle mean conditions to the late mean conditions (p = 0.018, $\hat{\theta}$=62.5\%).
+Here, an earlier participant movement onset in the late mean condition suggests that participants attempted to wait and react to the stimulus, but ended up guessing.
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/model_losses.png}
+Participant movement onset standard deviation for the low variance conditions are shown in Fig.
+2B.
+There was a main effect of mean (F[1.383, 26.284], p = 0.018) and variance (F[1.000,19.000], p < 0.001) of the stimulus movement onset, and no significant interaction (F[1.978, 37.575], p = 0.097).
+When collapsed across variance, waiting to react and then guessing in the late mean conditions led to a higher standard deviation of participant movement onset relative to the middle mean (p = 0.039, $\hat{\theta}$ = 70.0\%) and early mean (p < 0.001, $\hat{\theta}$ = 77.5\%) conditions.
 
-%     \SethCaption{Supplementary Figure 2.}{Model Loss Comparison}
-% \end{figure}
+\noindent\textbf{\textcolor{mydarkblue}{{Participants are suboptimal and excessively indecisive.}}}
 
-\SectionHeader{Methods}
-\begin{table}[h]
-    \centering
-    \begin{tabular}{|l | c|}
-        \hline
-        Agent Movement Onset Time Mean        & $\mu_{a}$         \\
-        Agent Movement Onset Time Uncertainty & $\sigma_{a}$      \\
-        Reaction Time Mean                    & $\mu_{rt}$        \\
-        Reaction Time Uncertainty             & $\sigma_{rt}$     \\
-        Movement Time Mean                    & $\mu_{mt}$        \\
-        Movement Time Uncertainty             & $\sigma_{mt}$     \\
-        Neuromechanical Delay Mean            & $\mu_{nmd}$       \\
-        Neuromechanical Delay Uncertainty     & $\sigma_{nmd}$    \\
-        Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
-        Switch Time Mean                      & $\mu_{switch}$    \\
-        Switch Time Uncertainty               & $\sigma_{switch}$ \\
-        \hline
-    \end{tabular}
-    \caption[]{Inputs to the model}
-\end{table}
+We calculated the indecisions (Fig.
+2C), wins (Fig.
+2D), and incorrects (Fig.
+2E) for each of the experimental conditions.
+Participants displayed a high proportion of indecisions.
+The median percentage of indecisions was 15.0\% [range: 0.0 - 93.8\%] across all conditions, with the late mean low variance condition having a median percentage of indecisions of 19.4\% [range: 1.2\%, 93.8\%].
+We found a significant interaction between stimulus movement onset and variance for indecisions (F[1.571, 28.781] = 5.58, p = 0.013).
+In low variance conditions, participants made significantly more indecisions in the middle mean condition than the early mean condition (p<0.001, $\hat{\theta}$ = 85.0\%; Fig.
+2C).
+Additionally, participants made significantly more indecisions in the late mean condition compared to the early mean condition (p<0.004, $\hat{\theta}$ = 80.0\%).
 
-\begin{table}[h]
-    \centering
-    \begin{tabular}{|l | c|}
-        \hline
-        Reaction Time             & $\mathcal{N}(\mu_{rt},\sigma_{rt})$         \\
-        Movement Time             & $\mathcal{N}(\mu_{mt},\sigma_{mt})$         \\
-        Neuromechanical Delay     & $\mathcal{N}(\mu_{nmd},\sigma_{nmd})$       \\
-        Switch Time               & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
-        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
-        Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
-        \hline
-    \end{tabular}
-    \caption[]{Inputs to the model}
-\end{table}
+The win percentage across all conditions was 56.25\% (range: 6.2\%, 93.8\%; Fig.
+2D].
+We found a significant interaction between stimulus movement onset mean and variance for wins (F[1.542, 29.296] = 23.73, p<0.001).
+We found that the late mean condition had significantly less wins than the early mean condition (p < 0.001, $\hat{\theta}$ = 95.0\%).
+Interestingly, in the late mean condition we found that the average win percentage was significantly below the 50\% chance level (p<0.001; $\hat{\theta}$=95.0\%), which was true for 19 out of 20 participants.
+Since guessing on every trial would lead to a win percentage of 50\%, the only way participants would be below chance is if they are excessively indecisive.
+The incorrect percentage across all conditions was 26.3\% [range: 0.0\%, 57.5\%; Fig.
+2E].
+We found significant interactions between stimulus movement onset mean and variance for incorrects (F[1.658,31.508]=3.72, p=0.033).
+Participants displayed a greater percentage of incorrect decisions in the late mean condition than the early mean condition (p < 0.001, $\hat{\theta}$ = 92.5\%).
+
+\noindent\textbf{\textcolor{mydarkblue}{{Decision making model.}}}
+
+In our task, participants must make a decision of whether to react to the stimulus or guess.
+For Experiment 1, we tested three different models:  i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (Fig.
+3, left column).
+The decision policy of these models considers the expected value ($\mathbb{E[R|\tau]}$) to determine the time ($\tau$) to transition from reacting to guessing.
+Expected value is defined as
+
+\begin{align}
+    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
+\end{align}
+
+where ($P(Win|\tau)$) is the probability of a win, ($P(Incorrect|\tau)$) probability of an incorrect, and ($P(Indecision|\tau)$) is the probability of an indecision.
+$R_{Win} = 1$, $R_{Incorrect} = 0$, and ($R_{Indecision} = 0$ correspond to the reward structure of the task (Fig.
+1B).
+The decision policy of each model maximized expected reward to determine the optimal time to transition from reacting to guessing, $\tau^*$, according to
+
+\begin{equation}
+    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
+\end{equation}
+
+Each model has varying knowledge of the different parameters (Fig.
+3, left column).
+A model can have full knowledge or partial knowledge of a particular parameter.
+With full knowledge, the decision policy fully utilizes the parameter when selecting the time to transition from reacting to guessing.
+With partial knowledge, the decision policy utilizes its partial and imperfect representation of the parameter.
+Here the idea is that a human may not have a perfect representation of some parameter when determining a transition time, even though that particular parameter will still influence behaviour.
+All model parameter values are shown in Supplementary B.
+
+\noindent\emph{\textcolor{mydarkblue}{{No Switch Time Model}}}
+
+We first considered a model that incorporated various time delays and temporal uncertainties from sources previously identified in the literature: response time, neuromechanical delay, movement time, stimulus movement onset, and timing uncertainty.
+Note, unlike the other models we will address below, this model did not consider a `switch time’ delay and uncertainty because it was not considered in past literature.
+Hence, we termed it the No Switch Time Model.
+
+In the late mean low variance condition, the No Switch Time Model underestimated participant movement onset (Fig.
+2A), underestimated indecisions (Fig.
+2C), and overestimated wins (Fig.
+2D).
+During this condition, participants displayed 19\% indecisions on average and a win percentage significantly below chance.
+One reason that the No Switch Time Model was unable to capture behaviour is because it did not consider the potential delays and uncertainties that might exist when switching from reacting to guessing.
+
+\noindent\emph{\textcolor{mydarkblue}{{Full Switch Time Model}}}
+
+Next we considered a model that additionally incorporated the potential existence of a switch time delay and uncertainty when transitioning from reacting to guessing.
+For this Full Switch Time Model, we assumed that the model had full knowledge of the time delay and uncertainty when switching from reacting to guessing.
+
+Yet, despite including switch time, the Full Switch Time Model also performed poorly when predicting participant movement onset (Fig.
+2A), indecisions (Fig.
+2C), and wins (Fig.
+2D) in the late mean condition.
+An explanation for why this model did not do well to explain indecisions is that humans may not have full knowledge of this potential switch time delay and uncertainty.
+
+\noindent\emph{\textcolor{mydarkblue}{{Full Switch Time Model}}}
+Finally, we considered a model that had only partial knowledge of a potential switch time delay and uncertainty when transitioning from reaching to guessing.
+That is, this model specifically tests whether humans have an imperfect representation of a switch time delay and uncertainty.
+The model also had partial knowledge of timing uncertainty, which the fitting procedure found to further improve model fits.
+The Partial Switch Time Model was able to replicate all aspects of behaviour (Fig.
+2).
+Crucially, it was also able to capture suboptimal behaviour in the late mean condition, where we found that an excessive percentage of indecisions (Fig.
+2C, Fig.
+3) led to a lower than chance win percentage (Fig.
+2D).
+
+\textbf{\textcolor{mydarkblue}{{Experiment 1}}}
+\vspace{2mm}
+
+Our behavioural findings in Experiment 1 demonstrated that participants were suboptimal decision makers.
+Through our modelling efforts, we were able to capture this suboptimal decision making by including a switch time delay and uncertainty when transitioning from reacting to guessing.
+The switch time delay and uncertainty were only partially represented by the Partial Switch Time Model when determining the optimal time to switch from reacting and guessing.
+However, we are not aware of any work that considers the temporal time delays and uncertainty associated with switching from reacting to guessing within a trial.
+Thus, the goal of Experiment 2 was to determine if there is indeed a switch delay and uncertainty that occurs when humans transition from reacting to guessing.
+
+\noindent\textbf{\textcolor{mydarkblue}{{Experimental Design.}}}
+For all conditions, participants controlled a visible cursor that was aligned with their hand position.
+They started each trial by moving their cursor into a start position.
+Trial onset began with the appearance of both the stimulus (yellow cursor) and two targets.
+Participants could experience two trial types: react trials or guess trials.
+In the react trials, participants saw the stimulus move and were instructed to as quickly as possible follow the stimulus to one of the targets (Fig.
+4A).
+In the guess trials, participants saw the stimulus disappear from the start circle.
+They were instructed to guess one of the two targets as quickly as possible (Fig.
+4B).
+Following trial onset, the movement or disappearance of the stimulus was drawn from a normal distribution with a mean of 800ms and a standard deviation of 50ms.
+There were three experimental conditions (Fig.
+4C): the react or guess condition, the only react condition, and the only guess condition.
+In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+Participants were informed that the stimulus would either move to one of the targets or disappear.
+In the only react condition, participants were informed that the stimulus would always move to one of the two targets (50 react trials and 0 guess trials).
+They were also told that the stimulus would not disappear.
+In the only guess condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
+They were also informed that it would not move to one of the two targets.
+
+During the react or guess condition, we reasoned that participants would prefer to react because they would be guaranteed to select the correct target.
+As a result, in the react or guess condition, if the stimulus disappeared the participant would switch from reacting to guessing when selecting a target.
+Conversely, during the only guess condition, if the stimulus disappeared participants would not have to switch from reacting to guessing.
+Thus, if there is a delay when switching from reacting to guessing, we would expect a greater response time for the guess trials in the react or guess condition compared to the guess trials in the guess only condition.
+
+\textbf{Response Time}.
+Average participant response times are shown for react and guess trials for each condition are shown in Fig.
+5A.
+As expected, we found significantly greater response times for guess trials in the react or guess condition when compared to the only guess condition (p < 0.001, $\hat{\theta}$ = XX.X), which was displayed by all participants.
+These comparatively greater response times for guess trials in the react or guess condition supports the idea that there is a switch time delay when transitioning from reacting to guessing.
+
+Likewise, if there was a switch time delay we would also expect a comparatively greater response time difference between guess and react trials in the react or guess condition, compared to the response time difference between only guess trials and only react trials [i.e., guess - react (react or guess condition) > guess - react (guess only and react only conditions)].
+Indeed, we found a greater response time difference between guess and react trials in the react or guess condition, compared to the response time difference between the guess only and react only conditions (p < 0.001, $\hat{\theta}$ = XX.X, Fig.
+5A).
+Moreover this result shows that the response time differences between guess and react trials are not due to any dual tasking (Selst and Jolicoeur 1997) or task switching between trials (Monsell 2003, Kiesel et al.
+2010, Rubinstein 2001), which would not show this relative difference  [i.e., guess - react (react or guess condition) = guess - react (guess only and react only conditions)].
+
+\textbf{Response Time Uncertainty}.
+We also examined participant response time uncertainty, calculated as the standard deviation (Fig.
+5B).
+We found that response time uncertainty on guess trials was significantly greater in the react or guess condition compared to the only guess condition (p < 0.001).
+This result suggests that there is additional uncertainty when participants switch from reacting to guessing.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Discussion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\noindent\textbf{\large\textcolor{mydarkblue}{Discussion}}
+
+We found that participants were suboptimal decision-makers and excessively indecisive, leading to a below chance win rate.
+Computational modelling suggested that excessive indecisions were a result of failing to account for a delay and uncertainty associated with switching from reacting to guessing.
+We then showed empirical evidence of an additional delay and uncertainty when switching from reacting to guessing.
+Taken together, we found that participants were suboptimal decision-makers and excessively indecisive because they did not account for the time delay and temporal uncertainty when switching from reacting to guessing.
+
+In Experiment 1, participants were required to reach the same target as a cursor before a time constraint.
+Within a trial, they could either react to a moving stimulus or guess which of the two targets would be correct.
+We saw that 95\% of participants had a win rate less than chance (50\%) in the late mean condition, which corresponded with an average of 19.4\% indecisions.
+This proportion of indecisions aligns with our recent prior work that examined competitive human-human decision making with a high time pressure (Lokesh et al.
+2022).
+In this competitive task, one participant attempted to reach the same target as their opponent, while the other tried to reach the opposite target within a time constraint.
+It was suggested that the high proportion of indecisions in this competitive human-human task were the result of participants waiting too long to acquire sensory information of their opponent, despite the impending time deadline.
+Likewise, we found a high proportion of indecisions across experimental conditions.
+Our results would also suggest that participants waited to acquire sensory information of when the stimuli would move.
+Moreover, building upon the previous work (Lokesh et al.
+2022), our work also suggests that a key contributor leading to excessive indecisions is failing to account for the time delay and temporal uncertainty when switching from reacting to guessing.
+
+Past work has suggested that humans can nearly optimally account for time delays and temporal uncertainty when performing decision making (Balci Risk assessment in man and mouse, Jazayeri and Shadlen 2010.
+Balci Optimal temporal risk assessment) and movement tasks (Hudson et al.
+2008, Battaglia and Schrater 2007, Dean 2007) when attempting to maximize reward.
+Here we considered two optimal models, the No Switch Time Model and Full Switch Time Model, which both had full knowledge of the inputted time delays and temporal uncertainties.
+Interestingly, both the No Switch Time Model and Full Switch Time Model showed that even when fully accounting for all sensorimotor delays and uncertainties, indecisions were a part of an optimal strategy in all but one of the six conditions.
+In other words, given the inherent delays and uncertainty of our nervous system (Wolpert Faisal), an optimal strategy of earning maximal reward may involve indecisive behaviour on some proportion of trials.
+We are unaware of any work in the literature suggesting that some level of indecisions may be optimal.
+Even though making some indecisions can be optimal, our results in Experiment 1 were in support of the idea that humans are suboptimal.
+Specifically, in the late mean condition, we found that humans were suboptimal since they had a win percentage lower than chance, which arose from an excessive number of indecisions.
+The Partial Switch Time Model was suboptimal, since it had a partial representation of time delays and temporal uncertainties associated with switching from reacting to guessing.
+We found that this model best explained behaviour, including a below chance win percentage and an excessive number of indecisions.
+The Partial Switch Time Model supports the notion that humans suboptimally select decision times when under high time pressures.
+An interesting future direction would be to test whether different reward structures, such as placing a higher reward on wins or punishing indecisions (Kahneman and Tversky 2013, Roth et al.
+2024, Galea et al.
+2015), would provide a means to reduce an excessive number of indecisions.
+The combined empirical evidence of Experiment 1 and computational modelling suggested the existence of time delay and uncertainty when switching from reacting to guessing.
+However, we were unaware of any work in the literature to support this idea.
+In Experiment 2 we tested the notion of a more delayed and uncertain response time when switching from reacting to guessing, compared to guessing by itself.
+Indeed, we found that when participants had to switch from reacting to guessing, their response times were significantly slower and more uncertain than when they only had to guess.
+One possibility for increased time delays and temporal uncertainty could be related to switching between different processing ‘modes’.
+In our task, participants may have switched from a `react mode’ that corresponded to preparing to follow the stimulus, and then switch to a `guess mode’ to randomly select one of the targets.
+
+Dutilh and colleagues (2011) explored the idea of switching between a stimulus controlled (i.e.
+react) mode and a guess mode between trials.
+In their task, participants were required to discriminate between a word stimuli from a non-word stimuli by selecting one of two buttons during a two-alternative forced choice task.
+Between trials, the authors manipulated whether participants received more reward for fast decisions to promote guessing, or more reward for accurate decisions that promoted reacting.
+Participants displayed longer response times when transitioning from more accurate decisions to fast decisions, compared to when transitioning from fast decisions to accurate decisions given the same current reward weighting.
+The authors interpreted these results to represent a resistance, termed hysteresis, when switching between react and guess modes.
+That is, participants are more likely to stay in their current mode than switch modes.
+They also highlighted that classical decision-making models, such as drift-diffusion models (Bogacz, Ratcliff) or more recently the urgency-gating model (Cisek, Thura,derosiere thura cisek duque), do not consider different modes of reacting or guessing.
+Extending upon the findings of Dutilh and colleagues (2011) that examined between trial mode switching, our work suggests that humans switch between react and guess modes within a trial.
+Importantly, we find that not accounting for the time delays and temporal uncertainties when switching from reacting to guessing gives rise to excessive indecisions.
+To our knowledge, it is unknown how different modes would be represented in the nervous system.
+One possibility is that the different modes represent different attractors from a neural dynamical systems perspective (Erlhagen and Schoner 2002, wang 2008 Decision making in recurrent, Churchland et al.
+2012, Shenoy Sahani Churchland 2013), which would be an interesting avenue of investigation.
+
+We found in Experiment 2 that participant response times were more delayed by approximately 75ms during guess trials in the react or guess condition, compared to guess only trials.
+Moreover, the response time difference between guess and react trials in the react or guess condition are significantly greater than the response time difference between the guess only and react only conditions.
+Collectively, these results suggest that participants have an initial preference to react, before having to switch to a guess in the react or guess condition.
+In this experiment the behaviour may be explained by a strong preference to react since it yields a 100\% success probability, as opposed to guessing that on average yields a 50\% success probability.
+It would be interesting for future studies to examine if they can manipulate the magnitude or probability of reward to switch a preference between reacting or guessing, and how this impacts indecisive behaviour.
+
+Indecisions are often not studied since many decision-making tasks do not permit a non-response or simply do not consider responses made after some time constraint.
+A limitation of the commonly used two-alternative forced choice task without a time constraint is that the participant or animal must select one of two potential options, which does not allow for indecisive behaviour.
+For decision making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis (Forstmann et al.
+2008, Diederich a further test of sequential, Phillastides et al.
+2011, Wu et al.
+2016, Dambacher and Hubne 2015s).
+Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions (Karsilar Balci 2014 deadline paper, Farasahi 2015, …s).
+However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
+
+Here we showed in our first experiment that humans are excessively indecisive under time constraints.
+Our computational work and second experiment suggest that indecisive behaviour can occur by not accounting for the time delays and temporal uncertainty associated with switching from reacting to guessing.
+Our experimental and theoretical approach offers a new paradigm to study indecisions, which has received surprisingly little attention despite its ecological relevance.
+Our work advances how indecisive behaviour arises, which is important to understand when attempting to avoid potentially catastrophic events during high time pressure scenarios.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\noindent\textbf{\large\textcolor{mydarkblue}{Methods}}
+
+\noindent\textbf{Participants}
+
+44 participants participated across two experiments: 20 individuals participated in Experiment 1 and 24 individuals participated in Experiment 2.
+All participants reported they were free from musculoskeletal injuries, neurological conditions, or sensory impairments.
+In addition to a base compensation of \$5.00, we informed them they would receive a performance-based compensation of up to \$5.00.
+Participants received the full \$10.00 once they completed the experiment, irrespective of their performance.
+All participants provided written informed consent to participate in the experiment and the procedures were approved by the University of Delaware’s Institutional Review Board.
+
+\noindent\textbf{Apparatus}
+
+For both experiments we used an end point KINARM robot (Fig.
+1A; BKIN Technologies, Kingston, ON).
+Each participant was seated on an adjustable chair in front of one of the end-point robots.
+Each participant grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
+A semi-silvered mirror blocked the vision of the upper limb and displayed virtual images (e.g., targets, cursors) from an LCD screen.
+In all experiments, the cursor was aligned with the position of the hand.
+The semi-silvered mirror occluded the vision of their hand.
+Kinematic data were recorded at 1,000 Hz and stored offline for data analysis.
+
+\noindent\textbf{\large\textcolor{mydarkblue}{Experiment 1 Design}}
+
+The goal of Experiment 1 was to study the influence of stimulus onset on indecisive behaviour.
+To begin the task, the participant moved their cursor (white circle, 1 cm diameter) into a start position (white circle, 1 cm diameter) (Fig.
+1A).
+Then a stimulus (yellow cursor, 1 cm diameter) appeared in the start position.
+After a random time delay (600-2400 ms drawn from a uniform distribution), the participant heard a tone that coincided with two targets (white ring, 8 cm diameter) and a timing bar appearing on the screen.
+The two potential targets were positioned 16.7 cm forward relative to the start position, and either 11.1 cm to the left or right of the start position.
+The timing bar was 10 cm below the start position.
+In each trial, the stimulus would move quickly (150 ms movement time) with a bell-shaped velocity profile into one of the two targets.
+The stimulus selected the left and right targets randomly with equal probability.
+Participants were instructed to reach the same target as the stimulus.
+They had to select a target within the 1500 ms time constraint, relative to trial onset.
+The timing bar decreased in width according to elapsed time and disappeared at 1500 ms.
+Visual feedback of the timing bar provided participants full knowledge of the time remaining in the trial.
+Participants were instructed to stay inside the start position until they decided to select a target.
+Importantly, participants were informed that they could select one of the targets at any time during the trial.
+Thus, they could either wait to react to the stimulus or guess one of the targets.
+Once they decided which target to select, the participant rapidly moved their cursor into the selected target.
+
+Participants were instructed that their goal was to earn as many points as possible.
+A trial was considered a win if they successfully reached the same target as the stimulus within the 1500 ms time constraint.
+A trial was considered incorrect if they reached the opposite target as the stimulus before the time constraint.
+A trial was considered an indecision if they failed to reach a target within the time constraint.
+Participants earned one point for a win, zero points for being incorrect, and zero points for making an indecision (Fig.
+1B).
+
+For each trial within a condition, the stimulus movement onset was drawn from the same normal distribution.
+Using a 3 x 2 within experimental design, we manipulated the stimulus movement onset mean (early mean = 1000 ms, middle mean = 1100 ms, late mean = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms) that resulted in 6 experimental conditions (Fig.
+1C).
+Each condition was performed separately using a block design.
+
+Participants completed 605 total trials.
+They first performed 25 baseline trials, as well as 80 trials per experimental condition that were each separated by 25 washout trials.
+The stimulus movement onset during baseline and washout trials was randomly drawn from a discrete uniform distribution [400, 437.5,…,1300 ms].
+The washout condition was designed to minimize the influence of the stimulus movement onset distribution of the previous condition.
+Condition order was randomized across participants.
+Prior to Experiment 1, participants performed two separate tasks to estimate response time (response time task; Supplementary C) and timing uncertainty (timing uncertainty task; Supplementary D).
+We counterbalanced the order of the response time and timing uncertainty tasks.
+
+\noindent\textbf{\large\textcolor{mydarkblue}{Experiment 2 Design}}
+
+The goal of Experiment 2 was to test whether there is a time delay and uncertainty associated with switching from reacting to guessing.
+To investigate, participants began each trial by moving their cursor into a start position.
+Then, a stimulus cursor appeared in the start position.
+Each trial began with a beep and the two potential targets appeared on the screen.
+Here participants experienced two different types of trials: react trials or guess trials.
+The react trials consisted of the stimulus moving to one of the two targets (Fig.
+4A).
+Participants were instructed to follow the stimulus as quickly as possible.
+The guess trials consisted of the stimulus disappearing from the start position (Fig.
+4B).
+Participants were instructed to select the target they believed the stimulus would end up in as quickly as possible.
+After the participant selected their target, the stimulus cursor appeared in one of the two targets.
+The stimulus movement onset (reaction trials) or disappearance time (guess trials) was drawn from a normal distribution (mean = 800 ms, standard deviation = 50 ms).
+The stimulus randomly selected the left and right targets with equal probability.
+
+Using these react and guess trials, participants performed a within experimental design with three experimental conditions: react or guess condition, only react condition, and only guess condition.
+In the react or guess condition, we pseudorandomly interleaved the 50 react trials and 50 guess trials.
+Participants were informed the stimulus would either move to one of the targets (react trials) or disappear (guess trials).
+The only react condition consisted of 50 react trials.
+Participants were informed that the stimulus would move to one of the two targets and would not disappear.
+The only guess condition consisted of 50 guess trials.
+Participants were informed that the stimulus would only disappear and would not move to one of the two targets.
+The react or guess condition was performed first by participants to avoid any potential carry-over effects of repeatedly performing react or guess trials in the other two conditions.
+After the react or guess condition, the order of the only react condition and only guess condition was counterbalanced.
+
+\noindent\textbf{\large\textcolor{mydarkblue}{Data Analysis}}
+
+Kinematics were filtered using a dual-pass, low pass, second order Butterworth filter with a cutoff frequency of 14 Hz.
+
+\underline{Experiment 1}
+\emph{Participant movement onset}: On each trial, we found when the time point where the participant hand velocity exceeded 0.05 m/s (Gribble 2003 A role for cocontraction, Calalo et al.
+2023).
+The meantime point across all trials within a condition was used to estimate participant movement onset.
+
+\emph{Participant movement onset standard deviation}: Using all trials in a condition, we used the time point where the participant hand velocity exceeded 0.05 m/s to calculate the standard deviation of participant movement onsets for each condition.
+
+\emph{Outcome metrics}: Win (\%): A trial was a win if participants reached the same target as the stimulus before the time constraint.
+Incorrect (\%): A trial was an incorrect if participants reached the opposite target as the stimulus before the time constraint.
+Indecision (\%): A trial was an indecision if participants failed to reach either target before the time constraint.
+We calculated each of the outcome metrics as a percentage of the total trials.
+
+\noindent\underline{Experiment 2}
+
+\emph{Response time}: Response times were calculated as the difference between participant movement onset and either the stimulus movement onset or stimulus disappearance time.
+The mean time difference across all trials within a condition was used to estimate the participant response times.
+Note that any response times greater than 650 ms or less than 150 ms were removed from analysis (3.7\% of trials).
+We calculated response time separately for react and guess trials.
+
+\emph{Response time standard deviation}: We calculated the standard deviation of participant’s response times separately for react and guess trials.
+
+\noindent\textbf{\textcolor{mydarkblue}{Statistics}}
+
+\noindent\emph{Experiment 1 and 2}
+
+We used analysis of variance (ANOVA) as omnibus tests to determine whether there were main effects and interactions.
+We report the Greenhouse-Geiser adjusted p-values and degrees of freedom.
+In Experiment 1 we used a 3 (mean: early, middle, late) x 2 (variance: low, high) repeated measures ANOVA for each dependent variable.
+In Experiment 2 we used a 2 (condition: interleaved react and guess, react or guess only) x 2 (trial type: react trials, guess trials) repeated measures ANOVA for each dependent variable.
+For both Experiments 1 and 2, we performed mean comparisons using nonparametric bootstrap hypothesis tests (n = 1,000,000).
+Mean comparisons were Holm-Bonferonni correct to account for multiple comparisons.
+Significance threshold was set at $\alpha$ = 0.05).
+We also report the common-language effect size ($\hat{\theta}$).
+
+\SectionHeader{Supplementary}
+
+\noindent\textbf{\textcolor{mydarkblue}{Suuplementary B: Optimal Models}}
+
+We tested three different models to investigate the ability of participants to maximize reward during Experiment 1: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (Fig.
+2).
+Each model represents a different hypothesis on how humans time their decisions, which we address further below.
+Intuitively, participants should react to the stimulus on trials where it moved earlier in time and guess on trials where it moved later in time.
+That is, reacting to early stimulus movement onsets ensures they can select the correct target.
+Likewise, guessing on late stimulus movement onsets affords the participant a 50% chance of selecting the correct target.
+However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
+We modelled the time to switch from reacting to guessing as an optimal stopping problem.
+This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim (trommershauser) and reach timing (Hudson, Maloney, Landy 2008).
+Here a model represents a decision-maker that selects a stopping time, $\tau$.
+This stopping time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets.
+The optimal stopping time is determined from a decision policy that maximizes reward, given task constraints (i.e.
+stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.
+
+\emph{Model Parameters}
+
+Here we define the parameters used for the three models.
+Note that not all the parameters are used in each model, which we specify further below and in Fig.
+2.
+The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement.
+Neuromechanical Delay is the mean ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) of the time between a volitional decision to move and movement onset.
+Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target.
+Stimulus Movement onset is knowledge of the mean ($\mu_{A}$) and uncertainty ($\sigma_{A}$) of the stimulus’s movement onset distribution.
+Timing uncertainty ($\sigma_{\tau}$) is the participants uncertainty around the intended stopping time, $\tau$.
+Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing.
+All probability distributions are assumed to be normally distributed with a mean $\mu$ and standard deviation $\sigma$.
+Each of our three models has a different set of known and unknown parameters.
+A model decision policy has full knowledge of known parameters when determining the optimal decision time.
+A model decision policy has no or partial knowledge of unknown parameters when determining the optimal decision time.
+
+\emph{No Switch Time Model}
+
+The No Switch Time Model had the following known parameters: response time mean and uncertainty, movement time mean and uncertainty, neuromechanical delay mean and uncertainty, timing uncertainty, and stimulus movement onset.
+This model had no unknown parameters.
+Importantly, the No Switch Time Model did not include the switch time mean and uncertainty in neither the known nor the unknown parameter sets.
+The No Switch Time Model reflects the hypothesis that there is no additional delay and uncertainty when switching from reacting to guessing.
+
+\emph{Full Switch Time Model}
+
+The Full Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, stimulus movement onset, timing uncertainty, and switch time mean and uncertainty.
+This model did not have any unknown parameters.
+The Full Switch Time Model reflects the hypothesis that participants fully account for a delay and uncertainty associated with switching from reacting to guessing.
+
+\emph{Partial Switch Time Model}
+
+The Partial Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, and stimulus movement onset.
+This model had the following unknown parameters: switch time mean and uncertainty, and timing uncertainty.
+The Partial Switch Time Model reflects our hypothesis that participants do not account for the delay and uncertainties associated with guessing.
+
+\emph{General Formulation for the Models}
+
+We begin by defining the general normal probability density function and cumulative density function:
 
 % Define pdf and cdf
+\begin{equation}
+    X\sim\mathcal{N}(\mu,\sigma)
+\end{equation}
 \begin{equation}
@@
 \begin{equation}
-    P(u\leq X\leq v) = \int_{u}^{v} f_{X}(x; \mu, \sigma)dt
-\end{equation}
-% \begin{equation}
-%     t \in [0,1500]
-% \end{equation}
-\begin{equation}
-    X\sim\mathcal{N}(\mu,\sigma)
+    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
 \end{equation}
 
-% % Define prob react and guess
-% \begin{equation}
-%     P(React|\tau) = P(\tau>\mu_{A}; \sigma_{\tau}, \sigma_{A})
-% \end{equation}
-% \begin{equation}
-%     P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{\tau}, \sigma_{A})
-% \end{equation}
+$X$ is the random variable drawn from a normal distribution $\mathcal{N}$ with some mean and standard deviation.
+$f_{X}(x;\mu,\sigma)$ is the normal probability density function over the variable $x$, with a mean ($\mu$) and standard deviation ($\sigma$).
+$F_{X}(b)$ is the normal cumulative density, which is the integral of the probability density function $f_{X}(x;\mu,\sigma)$ from $-\infty$ to $b$.
+Throughout, capitalized variables denote normally distributed random variables.
+Additionally, lowercase variables such as $x$ refer to the realization of the random variable $X$.
+The lowercase notation simply indicates that the value is known and is not a random variable.
+
+Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions.
+We begin by defining $A$ as the random variable drawn from the stimulus’s movement onset distribution (Eq.
+4) and $T$ as the random variable drawn from the stopping time distribution (Eq.
+5).
 
 % Define random variables A and T
-% Define expected value
-\begin{equation}
-    \mu_{A} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{A}(a)dx
-\end{equation}
-
 \begin{align}
-    A & \sim\mathcal{N}(\mu_{A},\sigma_{A}) \\
+    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
     T & \sim\mathcal{N}(\tau,\sigma_{\tau})
@@
 
-% Define indicator function and the set S
+Consider$a$ and $t$ as the realizations of random variables $A$ and $T$ for a single trial.
+On any specific trial, a decision-maker will react if the stimulus movement onset is before the stopping time (i.e., $a<t$).
+Conversely, the decision-maker will guess at the stopping time if the stimulus has not moved by the stopping time (i.e., $a>t$).
+Thus, the probability that a participant will react or guess depends on the participants choice of a stopping time $\tau$.
+Specifically, the probability that the participant will react is the probability that the random variable A is less than T.
+
+% Define prob react and guess
+\begin{equation}
+    P(React|\tau) = P(\tau>\mu_{S}; \sigma_{\tau}, \sigma_{S})
+\end{equation}
+
+Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.
+
+\begin{equation}
+    P(Guess|\tau) = P(\tau<\mu_{S}; \sigma_{\tau}, \sigma_{S})
+\end{equation}
+
+As a result, a decision-maker only reacts to the portion of the stimulus’s distribution that is prior to their stopping time.
+Thus, the participant reacts to a truncated distribution of the stimulus movement onset.
+The truncated stimulus movement onset distribution is generated from only taking the random variable $A$ if it is less than the random variable $T$.
+We can then define an indicator function ($\mathbbm{1}_{a<t}$), which is equal to one if the realized value $a$ is less than $t$ and zero otherwise:
+
+% Define indicator function 
 \begin{align}
-     & \mathbbm{1}_{a \in S} =
+     & \mathbbm{1}_{s<t} =
     \begin{cases}
-        1, & \text{if } a \in S     \\
-        0, & \text{if }  a \notin S
-    \end{cases}                                                             \\
-     & \text{\emph{where} } S = \{a \mid a < t; \hspace{2pt} a,t \in \mathbb{R}\} \nonumber
+        1 & \text{if } s < t, \\
+        0 & \text{otherwise.}
+    \end{cases}
 \end{align}
+
+The mean of the truncated stimulus movement onset distribution ($\mu_{A_{react}}$) can be calculated by combining the indicator function and the method of moments.
+We start by calculating the expected value of the random variable $A$, which is the integral from $-\infty$ to $\infty$ of the value $a$ multiplied by the probability density function $f_{A}(a)$.
+
+% Define expected value
+\begin{equation}
+    \mu_{S} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{S}(s)da
+\end{equation}
+
+Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution.
+For the truncated stimulus movement onset distribution, we only take values $a$ if they are less than $t$.
+Since the inclusion of $a$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $a$ and $t$.
+Inside the double integral, we multiply the realized value $a$ by its probability density function (i.e., $f_{A}(a)$).
+We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{a<t}$).
+Since this double integral multiplies two gaussian probability density functions and only sums values if $a$ is less than $t$, we must normalize by dividing by the probability that A is less than T.
+The mean (first moment) of the truncated stimulus movement onset distribution is
 
@@
 \begin{equation}
-    \mu_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} a \cdot p(a) \cdot p(t) \cdot \mathbbm{1}_{a \in S} \ dxdt} {P(A<T) }
+    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}
 \end{equation}
 
+Similarly we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
+
 \begin{equation}
-    \sigma^2_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (a - \mu_{A_{react}})^2 \cdot p(a) \cdot p(t_{j}) \cdot \mathbbm{1}_{a \in S} \ dx \ dt}{P(A<T)}
+    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ da \ dt}{P(S<T)}
 \end{equation}
+
+The player’s movement onset distribution consists of a mix between reacting to the truncated stimulus movement onset and guessing.
+Importantly, reacting and guessing have unique delays and uncertainties.
+Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
+The participant mean reaction movement onset ($\mu_{mo_{react}}$; Eq.
+10) is the truncated stimulus movement onset mean ($\mu_{A_{react}}$) plus the participant mean response time ($\mu_{rt}$).
+Likewise, the standard deviation of participant reaction movement onset (($\sigma_{mo_{react}}$; Eq.
+11) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
 
@@
 \begin{equation}
-    \mu_{mo_{react}} = \mu_{A_{react}} + \mu_{rt}
+    \mu_{mot_{react}} = \mu_{S_{react}} + \mu_{rt}
 \end{equation}
 \begin{equation}
-    \sigma_{mo_{react}} = \sqrt{\sigma_{A_{react}}^2 + \sigma_{rt}^2}
+    \sigma_{mot_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
+\end{equation}
+
+Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
+For the no switch time model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, Eq.
+12) is the sum of the participant stopping time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$ .
+The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (Eq.
+13).
+
+\begin{equation}
+    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
 \end{equation}
 \begin{equation}
-    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
+    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
+\end{equation}
+
+Crucially, for the known switch time model and unknown switch time model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
+
+% Switch time included in movement onset times
+\begin{equation}
+    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
 \end{equation}
 \begin{equation}
-    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
+    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
 \end{equation}
 
-% Scores 
-\begin{equation}
-    R_{win} = 1
-\end{equation}
-\begin{equation}
-    R_{indecision} = 0
-\end{equation}
-\begin{equation}
-    R_{incorrect} = 0
-\end{equation}
+For both the known switch time model and unknown switch time models, the switch time mean and uncertainty influence the model outputs.
+However, the decision policy of the Full Switch Time Model has perfect knowledge of the switch time, while the decision policy of the Partial Switch Time Model has imperfect knowledge of the switch time.
+Further below (see Model Fitting), we address how we estimate the amount of imperfect knowledge for the Partial Switch Time Model.
 
-% Prob React and Guess
-\begin{align}
-    P(React)             & = P(A<T) \nonumber                                      \\
-                         & = P(A-T<0) \nonumber                                    \\
-                         & = P(Z<0)                                                \\
-    \text{\emph{where} } & Z\sim \mathcal{N}(\mu_{z}, \sigma_{z})   \nonumber      \\
-                         & \mu_z = \mu_A - \mu_\tau                 \nonumber      \\
-                         & \sigma_z = \sqrt{\sigma_{A}^2 + \sigma_{T}^2} \nonumber
-\end{align}
-
-\begin{align}
-    P(G) = 1 - P(React)
-\end{align}
+We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as
 
@@
 \begin{align}
-    \mu_{reach_{react}} =\mu_{mo_{react}} + \mu_{mt}                      \\
-    \sigma_{reach_{react}} = \sqrt{\sigma_{mo_{react}}^2 + \sigma_{mt}^2} \\
-    \mu_{reach_{guess}} =\mu_{mo_{guess}} + \mu_{mt}                      \\
-    \sigma_{reach_{guess}} = \sqrt{\sigma_{mo_{guess}}^2 + \sigma_{mt}^2}
+    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
+    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
+    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
+    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}
 \end{align}
+
+To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to
+
+% Reach random variables
+\begin{align}
+    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
+    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
+    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}})
+\end{align}
+
+We can then define the probability that the participant will reach one of the two targets before the time constraint of 1500ms given they react ($P(Reach|React)$) or guess ($P(Reach|Guess)$):
 
@@
 \begin{align}
-    P(Reach|React) = P(X_{reach_{react}} < 1500) \\
-    \text{\emph{where} } X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \nonumber
+    P(Reach|React) = P(X_{reach_{react}} < 1500)
 \end{align}
 \begin{align}
-    P(Reach|Guess) = P(X_{reach_{guess}} < 1500) \\
-    \text{\emph{where} } X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \nonumber
+    P(Reach|Guess) = P(X_{reach_{guess}} < 1500)
 \end{align}
+
+We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect.
+The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from Eqs.
+20-21.
+An indecision is simply the probability that the participant reaches the target after the time constraint:
+
+% Probability of indecision sequence 
+\begin{equation}
+    P(Indecision|React) = 1 - P(Reach|React)
+\end{equation}
+\begin{equation}
+    P(Indecision|Guess) = 1 - P(Reach|Guess)
+\end{equation}
+
+To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$).
+The probability of selecting the correct target when the participant reacts is 100\% (Eq.
+24).
+The probability of selecting the correct target when the participant guesses is 50\% (Eq.
+25).
 
@@
 
+The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint and they select the correct target:
+
 % Probability of winning sequence
@@
 \end{equation}
-\begin{equation}
-    P(Win) = P(React) \cdot P(Win|React) + P(Guess) \cdot P(Win|Guess) 
-\end{equation}
+
+The conditional probability the participant is incorrect given they react ($P(Incorrect|React)$) or guess ($P(Incorrect|Guess)$) is the probability that they reach the target within the time constraint and they select the wrong target:
 
@@
 \end{equation}
-\begin{equation}
-    P(Incorrect) = P(React) \cdot P(Incorrect|React) + P(Guess) \cdot P(Incorrect|Guess) 
-\end{equation}
 
-% Probability of incorrect sequence 
-\begin{equation}
-    P(Indecision|React) = 1 - P(Reach|React)
-\end{equation}
-\begin{equation}
-    P(Indecision|Guess) = 1 - P(Reach|Guess)
-\end{equation}
-\begin{equation}
-    P(Indecision) = P(React) \cdot P(Indecision|React) + P(Guess) \cdot P(Indecision|Guess) 
-\end{equation}
+Finally we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (Eq.
+x-x) and the probability of reaching and guessing given a stopping time (Eq.
+x-x), as
+
+\begin{align}
+    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
+    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
+    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess)
+\end{align}
+
+\noindent\emph{Decision Policy}
+
+For each model, the goal of the decision policy is to find the optimal stopping time that maximizes expected reward.
+The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,
 
@@
 
+The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is
+
 \begin{align}
-    \mathbb{E}[R] = & P(Win) \cdot R_{Win} + P(Incorrect) \cdot R_{Incorrect} + P(Indecision) \cdot R_{Indecision}
+    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
 \end{align}
+
+The decision policy uses known parameters to select an optimal stopping time $\tau^*$ that maximizes expected reward:
 
@@
 \begin{equation}
-    \tau = \underset{\tau \in [0,2000]}{argmax}(\mathbb{E}[R])
+    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
 \end{equation}
 
+\noindent\textbf{Model Parameter Estimation and Fitting Procedure}
+
+As a reminder, we had three models: No Switch Time Model, Full Switch Time Model, and Partial Switch Time Model.
+Each of these models had full knowledge of the reaction time mean and standard deviation, neuromechanical delay mean and standard deviation, movement time mean and standard deviation, and the stimulus movement onset distribution.
+These parameter values were estimated from experimental data by bootstrapping the meansfrom the response time experiment ($\mu_{rt}, \sigma_{rt}$), timing experiment ($\sigma_{\tau}$), and Experiment 1 ($\mu_{mt}, \sigma_{mt}$).
+We describe the bootstrap procedure below.
+Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature (Norman and Komi 1979, Bruce et al.
+1985, Rossini and Rossi 1998 ).
+
+We used both a warm-start initialization and bootstrap procedure (see below) to determine the switch time mean ($\mu_{switch}$) and uncertainty ($\sigma_{switch}$), as well as the decision policy’s knowledge of the switch time mean ($\hat{\mu}_{switch}$, switch time uncertainty ($\hat{\sigma}_{switch}$), and timing uncertainty ($\hat{\sigma}_{\tau}$).
+
+\noindent\emph{Warm-Start Initialization}
+
+\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and ($\hat{\sigma}_{\tau}$) (Roth 2023r).
+Here the remaining parameters estimated from experimental data were set as the group level means.
+We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means($Data_{i,j}$) according to
+
+% Loss Equation 
+\begin{equation}
+    \mathcal{L} = \sum_{i = 1}^{6} \sum_{j = 1}^{5} \frac{|Data_{i,j} - Model_{i,j}|}{Data_{i,j}}
+\end{equation}
+
+where, i corresponds to experimental condition and j corresponds to each dependent measure (i.e., movement onset, standard deviation of participant movement onset, wins, indecisions, and incorrects) over the target metrics.
+This fitting procedure was repeated 1,000 times to avoid local minimums.
+From these 1,000 optimizations, we used the set of parameters that resulted in the lowest loss as the initial guess for our bootstrap procedure.
+Model fitting was performed using the Powell algorithm in the Minimize function from the Scipy Python library.
+The parameter set with the lowest loss was used as the initial guess for the bootstrap procedure.
+
+\noindent\emph{Warm-Start Initialization}
+
+\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times (Cashaback 2017, Cashback 2019, Roth 2024, Roth 2023).
+We used the mean of the bootstrapped participant data for each of the parameter values that were estimated from data.
+For each bootstrap iteration, the optimization process selected the free parameters for the Full Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$) and Partial Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{\tau}$, $\hat{\sigma}_{\tau}$) that minimized the loss function (Eq.
+44).
+
+\noindent \textbf{Model Parameters}
+
+\noindent Here we report the mean and 95\% confidence intervals for the bootstrapped model parameters.
+For each parameter, each model had a value that determined the model outputs and a value that the decision policy used to select $\tau$.
+The No Switch Time Model and Full Switch Time Model were both optimal in the sense that they had perfect knowledge of all parameters.
+That is, the value that determined model outputs was equal to the value used by the decision policy.
+Parameter values for reaction time mean, reaction time uncertainty, movement time mean, movement time uncertainty, and timing uncertainty were all calculated from participant data on each bootstrap iteration: reaction time mean (247.4 ms; [239.2, 256.35]), reaction time uncertainty (38.5 ms; [35.7, 41.4]), movement time mean (171.7 ms; [157.6, 197.2]), movement time uncertainty (25.4 ms; [22.2, 28.7]), and timing uncertainty (77.8 ms; [69.4, 86.6]).
+The No Switch Time Model had no parameters to fit and the decision policy had full knowledge of all of these parameters.
+The Full Switch Time Model fit the switch time mean and switch time uncertainty and the decision policy had full knowledge of all parameters.
+The bootstrapped mean of the switch time delay parameter was 0.95 ms with a 95\% confidence interval of [0.21, 2.20].
+The bootstrapped mean of the switch time uncertainty parameter was 103.20 ms with a 95\% confidence interval of [97.77, 115.31].
+
+The Partial Switch Time Model fit the timing uncertainty, switch time mean, switch time uncertainty.
+Critically, this model did not have full knowledge of these parameters, so the value that the decision policy used to select the optimal time was fit separately from the value that was used to determine the model outputs.
+Note that the timing uncertainty value used for model outputs is from experimental data, but this model allowed the knowledge of the timing uncertainty to be a fit parameter.
+The values that were used for model outputs were: timing uncertainty (77.83 ms; [69.4, 86.8]), switch time mean (21.10 ms; [1.46, 63.71]), switch time uncertainty (134.73 ms; [111.22, 155.06].
+The values that were used by the decision policy were: timing uncertainty (1.65 ms;  [0.08, 4.63]), switch time mean (9.0 ms; [0.00, 16.65]), switch time uncertainty (40.4 ms; [34.54, 48.02]).
+Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and stopping time certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.
+
+\SectionHeader{Main Figures}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figures/exp1_experimental_design.png}
+
+%     \caption{\textbf{Experimental Design.} \textbf{S)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
+An LCD projected images (start position, targets) onto a semi-silvered mirror that occluded vision of the hand and upper arm.
+Participants began each trial by moving their cursor (purple) into the start position (solid white circle).
+They then heard a tone and saw two targets (white rings) and a timing bar (white rectangle) appear on the screen.
+During each trial, an stimulus (yellow) would move quickly in a straight line to one of the two targets.
+Participants were instructed to reach the same target as the stimulus within a time constraint of 1500ms.
+This time constraint was visually represented with a timing bar (white rectangle) that decreased in width according to the elapsed time.
+\textbf{B)} A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint.
+A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
+A trial was considered an indecision and the participant received 0 points if they failed to reach a target within the time constraint.
+\textbf{C)} Stimulus movement onset time on each trial was randomly drawn from a specific probability distribution in each condition.
+Using a within experimental design, we manipulated the mean and standard deviation of the stimulus movement onset time probability distribution for each of the following six conditions: 1) early mean low variance, 2) middle mean low variance, 3) late mean low variance, 4) early mean high variance, 5) middle mean high variance, 6) late mean high variance.
+%     }
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
+
+%     \caption{\textbf{Timing Behaviour.} \textbf{S)} Average participant movement onset time (y-axis) for each of the six experimental conditions (x-axis).
+\textbf{B)} Corresponding participant movement onset time (y-axis) for the three different mean onset times (x-axis) when collapsed across variance.
+During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint.
+For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions.
+Waiting longer to react and/or late guessing led to longer movement onset times.
+In the late mean condition participants either guessed early to avoid a late reaction to the stimulus, or waited to react but ended up producing a late guess.
+The combination of early and late guesses led to an early movement onset time compared to the middle mean condition.
+For both the middle mean and late mean conditions, late guessing often led to indecisions (see Fig.
+3A).
+\textbf{C)} Participant movement onset time standard deviation (y-axis) for each of the six experimental conditions (x-axis).
+\textbf{D)} Corresponding participant movement onset time standard deviation (y-axis) for the three different mean onset times (x-axis), when collapsed across variance.
+In the late mean conditions, the combination of early and late guesses led to a larger participant movement onset time standard deviation compared to the early mean and middle mean conditions.
+Box and whisker plots display the 25th, 50th, and 75th percentiles.
+Open gray circles and connecting lines represent individual data.
+}
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
+
+%     \caption{\textbf{Trial Outcomes.} \textbf{S)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition.
+\textbf{S)} We found that the middle mean low variance and late mean low variance conditions had a significantly greater number of indecisions compared to the early mean low variance condition.
+That is, in the middle mean low variance and late mean low variance conditions, participants often waited to react to the stimulus but ended up guessing late.
+These late guesses often led to indecisions.
+\textbf{B)} Interestingly, we also found that the average win percentage (4X.X\%) was significantly below the 50\% chance level (p < 0.001) in the late mean low variance condition, clearly demonstrating suboptimal behaviour.
+Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the stimulus.
+Collectively, these results show that participants were suboptimal decision makers that led to excessively indecisive behaviour.}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/model_diagram.png}
+
+%     \caption{\textbf{Models.} \textbf{S)} Predicted target reach times from three models: No Switch Time Model (light gray), Known Switch Time Model (dark gray), and Unknown Switch Time Model (black).
+Stimulus movement onset time is shown in pink, which corresponds to the late mean low variance condition.
+The time constraint on the task is shown in purple.
+Predicted indecision proportion is the area shown in dark blue.
+The Unknown Switch Time Model (black) is the only model that predicts indecisions for the late mean low variance condition, aligning with the data (see Figure 5C).
+\textbf{B)} Each model has inputs that represent the delays and uncertainties inherent to the sensorimotor system and the stimulus movement onset distribution.
+The decision policy finds the stopping time that maximizes reward.
+Given that the stimulus has not yet moved, the stopping time represents the time that participants transition from reacting to guessing.
+It is important to note that each model will react to the stimulus if it moves prior to the stopping time.
+The decision policy accounts for only the known inputs to determine stopping time.
+The decision policy is unaware of the unknown inputs when determining the stopping time, but these unknown inputs still influence the model outputs.
+The No Switch Time Model (light gray) has knowledge of all its model inputs.
+However, it does not consider the potential delay and uncertainties associated with switching from reaching to guessing, which we term ‘switch time’.
+The Known Switch Time Model (dark gray) has knowledge of all model inputs, including the switch time.
+Finally, the Unknown Switch Time Model (black) has knowledge of several of the model inputs, but is unaware of decision uncertainty and the switch time.
+\textbf{C)} Outputs for each of the models.}
+% \end{figure}
+
+% % Figure 5 Model Outputs
+% \begin{figure}[H]
+%     \begin{minipage}[c]{0.67\textwidth}
+
+%         \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}
+%     \end{minipage}\hfill
+%     \begin{minipage}[c]{0.3\textwidth}
+%         \caption{
+%             Model Outputs: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{S)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
+The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the late mean low variance and late mean high variance conditions.
+Conversely, the Unknown Switch Time Model (black) is able to accurately predict the participant data for all conditions across all metrics.
+As a reminder, the Unknown Switch time Model does not account for the delay and uncertainties associated with switching from reacting to guessing.
+Critically, in \textbf{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the late mean low variance condition, whereas the other two models predict zero indecisions for that condition.
+Further, in \textbf{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the late mean low variance condition.
+Collectively, our findings show that humans are suboptimal and excessively indecisive, which can be captured by a model that does not account  for the delay and uncertainties associated with switching from reacting to guessing.
+%         } 
+%     \end{minipage}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/exp2_design.png}
+
+%     \caption{\textbf{Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1.
+\textbf{S)} Participants responded to two different types of stimuli.
+In the react trials (pink), the stimulus (yellow cursor) would move to one of the two potential targets.
+Participants were instructed to reach the same target as the stimulus as quickly as possible.
+\textbf{B)} In the guess trials (blue), the stimulus disappeared from the start position.
+Once the stimulus disappeared, participants were instructed to guess which target the stimulus would appear in and select that target as quickly as possible.
+After the participant reached the target, the stimulus’s cursor would appear in one of the targets.
+\textbf{C)} We had three experimental conditions.
+In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+Participants were informed that the stimulus would either move to one of the targets or disappear.
+In the only react condition, participants were informed that the stimulus would alway move to one of the two targets (50 react trials and 0 guess trials).
+They were also told that the stimulus would not disappear.
+In the only guess condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
+They were also informed the stimulus would not move.
+}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/exp2_reaction_panel.png}
+
+%     \caption{S) Response time (y-axis) for each of the experimental conditions (x-axis).
+Participants had significantly greater response times for guess trials in the react or guess condition compared to the only guess condition.
+Critically, this result suggests there is an additional delay when participants initially wait to react to the stimulus and then switch to guessing.
+B) Interquartile range (IQR) of response times (y-axis) was used to quantify participants’ response time uncertainty for each of the experimental conditions (x-axis).
+Participants had significantly greater response time uncertainty for guess trials in the react or guess condition than in the only guess condition.
+Similarly, this finding suggests there is additional uncertainty when participants initially wait to react to the stimulus and then switch to guessing.
+Taken together, these results match the predictions of our model in Experiment 1, providing empirical evidence for an additional delay and uncertainty when switching from reacting to guessing.}
+% \end{figure}
+
+% \SectionHeader{Supplementary Figures}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/reaction_guess_decisions.png}
+
+%     \SuppCaption{Supplementary Figure 1.}{Reaction and Guess Decision Percentages for Experiment 1: Estimated percentage of reaction (pink) and guess (blue) decision percentages (y-axis) for each experimental condition (x-axis).
+During Experiment 1 participants were rewarded for successful trials and experienced a time constraint.
+Thus, we would expect participants to have faster reaction times in Experiment 1 than in the Reaction Time task (citation).
+To account for this, we adjusted participants’ reaction times by subtracting 25ms from their median reaction time in the Reaction Time task.
+A trial was a reaction decision if the difference between the stimulus’s movement onset time and participant’s movement onset time was greater than that participant’s adjusted reaction time.
+Conversely, a trial was a guess decision if the difference between the stimulus movement onset time and participant movement onset time was less than that participant’s adjusted reaction time.
+We found that participants guessed significantly more often as the stimulus’s mean movement onset time approached the time constraint.
+}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale = 1]{figures/model_losses.png}
+
+%     \SuppCaption{Supplementary Figure 2.}{Model Loss Comparison}
+% \end{figure}
+
+Hello \autocite{kording_bayesian_2006}
+
+% HEADINGS
+\fancyhead[R]{\emph{\textcolor{mydarkblue}{Indecisions arise from suboptimal switching behaviour}}}
+\fancyhead[L]{}
+\fancyfoot[C]{\textcolor{mydarkblue}{\thepage}}
+\begin{nolinenumbers}
+    \printbibliography[title= \large\textcolor{mydarkblue}{REFERENCES}]
+\end{nolinenumbers}
 \end{document}

### 2024-07-29 src/constants.py
switched model name

@@ -65,7 +65,7 @@ cadet_grey      = "#91A3B0"
 marengo         = "#4C5866"
 pebble          = "#333333"
 model_colors = [cadet_grey, wheel.lighten_color(pebble,0.75), wheel.black]
-model_names = ["No Switch Time Model", "Known Switch Time Model", "Unknown Switch Time Model"]
+model_names = ["No Switch Time Model", "Full Switch Time Model", "Partial Switch Time Model"]
 
 stimulus_color = wheel.lighten_color(wheel.yellow, 1.75)
 player_color = wheel.purple

### 2024-07-29 paper/Cover_letter_Indecisions.tex
supplementary and cover letter added

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%some% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[12pt]{article}
%\RequirePackage[T1]{fontenc}
\usepackage{ragged2e}
% LaTeX will typeset using Computer Modern Roman, which a lot of
% non-mathematicians and non-engineers won't like. Also, a few PDF
% viewers may not render CMR very well. Instead, Times New Roman can
% be used. That's what this package does.
%times 
%\usepackage{times}
\usepackage{fontspec}

% The automated optical recognition software used to digitize resume
% information works best with fonts that do not have serifs. This
% command uses a sans serif font throughout. Uncomment both lines (or at
% least the second) to restore a Roman font (i.e., a font with serifs).
% (NOTE: This requires the times package above)
%\renewcommand{\familydefault}{\sfdefault}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% This package helps LaTeX auto-hyphenate hyphenated words if you use
% special hyphens. For example, bio\-/mimicry will properly hyphenate
% ``mimicry'' if necessary.
\usepackage[shortcuts]{extdash}
\usepackage{graphicx}
\usepackage{fontawesome}
%\usepackage{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx,wrapfig}
%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
	   \pagestyle{empty}

\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0.0pt} % sets line size of header / footer
\renewcommand{\footrulewidth}{0.0pt}

\usepackage{graphicx} 
\usepackage{caption}
\usepackage{mwe}

\definecolor{myudblue}{RGB}{0, 83, 159}
\usepackage[hidelinks]{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\fontsize{12pt}{12pt}\selectfont
%\pagenumbering{gobble}
\pagestyle{fancy}
\cfoot{}
\lfoot{}
\rfoot{\textcolor{myudblue}{1}}
\raggedright
\begin{minipage}[ht]{0.6\textwidth}
\hspace{-10mm}\includegraphics[height=0.9in]{udcoe_logo}
\end{minipage}\hfill
\begin{minipage}[ht]{0.275\textwidth}
\begin{tabular}{lr}
\raggedleft
&\fontsize{10}{10}\selectfont \hspace{+20mm}\textcolor{myudblue}{Joshua Cashaback}\\
&\fontsize{10}{10}\selectfont \textcolor{myudblue}{Assistant Professor}\\
 &{\fontsize{10}{10}\selectfont \textcolor{myudblue}{\faPhone \hspace{1mm} +1.302.784.5986}}\\
 &{\fontsize{10}{10}\selectfont \textcolor{myudblue}{\href{mailto:joshcash@udel.edu}{\faEnvelope \hspace{1mm} joshcash@udel.edu}}}\\
%&{\fontsize{10}{10}\selectfont \textcolor{myudblue}{\faHome joshcashaback.weebly.com}}
%&{\fontsize{10}{10}\selectfont \textcolor{myudblue}{\href{mailto:cashabackjga@gmail.com}{cashabackjga@gmail.com}}}\\
\end{tabular}
\end{minipage}
\\
\vspace{6mm}
\today
\\
\vspace{6mm}
Dear Editor,
\justify
\vspace{1.0mm}
We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{``Indecision under time pressure arises from suboptimal switching behaviour''}}, for publication in \emph{Current Biology}.
\vspace{1.0mm}
\\
Indecisions can be catastrophic, preventing a life-saving response or leading to a loss of large sums of money.  Despite their importance and high prevalence, indecisions have been surprisingly ignored in the literature. The main culprit is that the field of decision-making leans heavily on the classic two-alternative forced choice task---where a human or animal \emph{must} select one of two potential options---which simply does not permit a non-response past some deadline (i.e., indecision). Of the few papers that have considered a deadline, indecisions are usually only mentioned in passing and, more often, simply removed from analyses and discarded from model fitting. \textbf{The field has consequently overlooked a common and hallmark feature of human and animal behaviour---indecisions.}
\vspace{3mm}
\\
Here we designed a novel paradigm to study high pressure scenarios that lead to indecisions. We found a median indecision rate of approximately 20\%, \textbf{with some participants even displaying over 50\% indecisions despite having plenty of time to make a guess.} Our computational modelling suggested that these indecisions arose by not accounting for the time delay and uncertainty associated when switching from reacting to guessing. In a second experiment, we show for the first time there is an inherent and functionally relevant time delay when switching from reacting to guessing, a phenomenon previously unreported in the literature. \textbf{Our paper novelly provides a mechanism to explain how indecisions arise.}
\vspace{3mm}
\\
We fully expect that our work will broadly draw interest from fields as diverse as Decision-Making, Economics, and Sports Science, which are all interested in the role of decision-making on behaviour.
Thank you for your time and consideration.
\vspace{3mm}
\\
Sincerely, 
\vspace{3mm}
\\
\includegraphics[height=0.75in]{signature}
\\
\vspace{-3.5mm}
\\
Joshua G. A. Cashaback, Ph.D.
\thispagestyle{fancy}
\rfoot{\textcolor{myudblue}{\thepage}}
\lfoot{\textcolor{myudblue}{\textbf{\fontsize{10}{10}\selectfont Biomedical Engineering | College of Engineering | University of Delaware} }
\\
\fontsize{10}{10}\selectfont \textcolor{myudblue}{STAR Health Sciences Complex, Rm 201J | 540 South College Avenue | Newark, DE., 19713}}
\newpage
\noindent \textcolor{myudblue}{REVIEWER SUGGESTIONS}
\\
\\
Michael S Landy, New York University, landy@nyu.edu
\\
\\
Han L.J. van der Maas, University of Amsterdam, H.L.J.vanderMaas@uva.nl 
\\
\\
Tony Carlsen, University of Ottawa, University of Ottawa
\\
\\
Martin Wiener, George Mason University, mwiener@gmu.edu
%\\
%\\
%Laurence T. Maloney, New York University, laurence.maloney@nyu.edu
%\\
%\\
%Jan Drugowitsch, Harvard Medical School, jan_drugowitsch@hms.harvard.edu
%\\
%\\
%Taraz G. Lee, University of Michigan, tarazlee@umich.edu
%\\
%\\
%Tony Carlsen, University of Ottawa, University of Ottawa
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------%
% The following is copyright and licensing information for
% redistribution of this LaTeX source code; it also includes a liability
% statement. If this source code is not being redistributed to others,
% it may be omitted. It has no effect on the function of the above code.
%----------------------------------------------------------------------%
% Copyright (c) 2007, 2008, 2009, 2010, 2011 by Theodore P. Pavlic
%
% Unless otherwise expressly stated, this work is licensed under the
% Creative Commons Attribution-Noncommercial 3.0 United States License. To
% view a copy of this license, visit
% http://creativecommons.org/licenses/by-nc/3.0/us/ or send a letter to
% Creative Commons, 171 Second Street, Suite 300, San Francisco,
% California, 94105, USA.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS
% OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
% MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
% IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY
% CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
% TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
% SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
%----------------------------------------------------------------------%

### 2024-07-29 paper/main.tex
supplementary and cover letter added

@@
      {\printtext[labelnumberwidth]{%
-    \printfield{prefixnumber}%
+    \printfield{labelprefix}%
     \printfield{labelnumber}}}
@@
 % \captionsetup[table]{labelfont=bf, labelsep=period}
+\DeclareCaptionLabelFormat{supp}{1-2}
 \captionsetup[figure]{labelfont=bf, labelsep=colon, font=footnotesize, justification=justified}
 
-\DeclareMathOperator*{\argmax}{srg\,max} % thin space, limits underneath in displays
+\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
 
-\newcommand{\SuppCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
+\newcommand{\SuppCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}\footnotesize}
 \newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
@@
 %\cfoot[]{\textcolor{mydarkblue}{\thepage}}
-\fancyhead[R]{\emph{\textcolor{mydarkblue}{Regulation of Movement Variability via Impedance and Feedback Control
+\fancyhead[R]{\emph{\textcolor{mydarkblue}{Indecision arises from suboptimal switching behaviour
         }}}
@@
 The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision.
-Surprisingly, participants displayed a median indecision rate of approximately 25% with an upper range close to 40% indecisions.
+Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions.
 Similar to others (Wu et al.
@@
 2011, Dambacher and Hubner 2015, Forstmann et al.
-2008), Karsilar and colleagues (2014) used a low time pressure task and found only 1.7% of trials were indecisions.
+2008), Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions.
 Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline.
@@
 Participant movement onsets for the low variance condition are shown in Fig.
-2A, We found a significant main effect of stimulus movement onset mean (F[1.551,29.475] = 4.36, p = 0.030) and variance (F[1.000,19.000], p = 0.017).
-There was no significant interaction between stimulus movement onset mean and variance (F[1.657,31.474], p = 0.565).
+2A, We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
+There was no significant interaction between stimulus movement onset mean and variance (F[1.66,31.47], p = 0.565).
 When collapsed across low and high variance, participant movement onsets were significantly greater in the middle mean conditions compared to the early mean conditions (p = 0.014, $\hat{\theta}$=72.5 \%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
@@
 2B.
-There was a main effect of mean (F[1.383, 26.284], p = 0.018) and variance (F[1.000,19.000], p < 0.001) of the stimulus movement onset, and no significant interaction (F[1.978, 37.575], p = 0.097).
+There was a main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) of the stimulus movement onset, and no significant interaction (F[1.98, 37.58], p = 0.097).
 When collapsed across variance, waiting to react and then guessing in the late mean conditions led to a higher standard deviation of participant movement onset relative to the middle mean (p = 0.039, $\hat{\theta}$ = 70.0\%) and early mean (p < 0.001, $\hat{\theta}$ = 77.5\%) conditions.
@@
 
-\SectionHeader{Supplementary}
-
-\noindent\textbf{\textcolor{mydarkblue}{Suuplementary B: Optimal Models}}
-
-We tested three different models to investigate the ability of participants to maximize reward during Experiment 1: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (Fig.
-2).
-Each model represents a different hypothesis on how humans time their decisions, which we address further below.
-Intuitively, participants should react to the stimulus on trials where it moved earlier in time and guess on trials where it moved later in time.
-That is, reacting to early stimulus movement onsets ensures they can select the correct target.
-Likewise, guessing on late stimulus movement onsets affords the participant a 50% chance of selecting the correct target.
-However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
-We modelled the time to switch from reacting to guessing as an optimal stopping problem.
-This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim (trommershauser) and reach timing (Hudson, Maloney, Landy 2008).
-Here a model represents a decision-maker that selects a stopping time, $\tau$.
-This stopping time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets.
-The optimal stopping time is determined from a decision policy that maximizes reward, given task constraints (i.e.
-stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.
-
-\emph{Model Parameters}
-
-Here we define the parameters used for the three models.
-Note that not all the parameters are used in each model, which we specify further below and in Fig.
-2.
-The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement.
-Neuromechanical Delay is the mean ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) of the time between a volitional decision to move and movement onset.
-Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target.
-Stimulus Movement onset is knowledge of the mean ($\mu_{A}$) and uncertainty ($\sigma_{A}$) of the stimulus’s movement onset distribution.
-Timing uncertainty ($\sigma_{\tau}$) is the participants uncertainty around the intended stopping time, $\tau$.
-Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing.
-All probability distributions are assumed to be normally distributed with a mean $\mu$ and standard deviation $\sigma$.
-Each of our three models has a different set of known and unknown parameters.
-A model decision policy has full knowledge of known parameters when determining the optimal decision time.
-A model decision policy has no or partial knowledge of unknown parameters when determining the optimal decision time.
-
-\emph{No Switch Time Model}
-
-The No Switch Time Model had the following known parameters: response time mean and uncertainty, movement time mean and uncertainty, neuromechanical delay mean and uncertainty, timing uncertainty, and stimulus movement onset.
-This model had no unknown parameters.
-Importantly, the No Switch Time Model did not include the switch time mean and uncertainty in neither the known nor the unknown parameter sets.
-The No Switch Time Model reflects the hypothesis that there is no additional delay and uncertainty when switching from reacting to guessing.
-
-\emph{Full Switch Time Model}
-
-The Full Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, stimulus movement onset, timing uncertainty, and switch time mean and uncertainty.
-This model did not have any unknown parameters.
-The Full Switch Time Model reflects the hypothesis that participants fully account for a delay and uncertainty associated with switching from reacting to guessing.
-
-\emph{Partial Switch Time Model}
-
-The Partial Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, and stimulus movement onset.
-This model had the following unknown parameters: switch time mean and uncertainty, and timing uncertainty.
-The Partial Switch Time Model reflects our hypothesis that participants do not account for the delay and uncertainties associated with guessing.
-
-\emph{General Formulation for the Models}
-
-We begin by defining the general normal probability density function and cumulative density function:
-
-% Define pdf and cdf
-\begin{equation}
-    X\sim\mathcal{N}(\mu,\sigma)
-\end{equation}
-\begin{equation}
-    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
-\end{equation}
-\begin{equation}
-    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
-\end{equation}
-
-$X$ is the random variable drawn from a normal distribution $\mathcal{N}$ with some mean and standard deviation.
-$f_{X}(x;\mu,\sigma)$ is the normal probability density function over the variable $x$, with a mean ($\mu$) and standard deviation ($\sigma$).
-$F_{X}(b)$ is the normal cumulative density, which is the integral of the probability density function $f_{X}(x;\mu,\sigma)$ from $-\infty$ to $b$.
-Throughout, capitalized variables denote normally distributed random variables.
-Additionally, lowercase variables such as $x$ refer to the realization of the random variable $X$.
-The lowercase notation simply indicates that the value is known and is not a random variable.
-
-Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions.
-We begin by defining $A$ as the random variable drawn from the stimulus’s movement onset distribution (Eq.
-4) and $T$ as the random variable drawn from the stopping time distribution (Eq.
-5).
-
-% Define random variables A and T
-\begin{align}
-    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
-    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
-\end{align}
-
-Consider$a$ and $t$ as the realizations of random variables $A$ and $T$ for a single trial.
-On any specific trial, a decision-maker will react if the stimulus movement onset is before the stopping time (i.e., $a<t$).
-Conversely, the decision-maker will guess at the stopping time if the stimulus has not moved by the stopping time (i.e., $a>t$).
-Thus, the probability that a participant will react or guess depends on the participants choice of a stopping time $\tau$.
-Specifically, the probability that the participant will react is the probability that the random variable A is less than T.
-
-% Define prob react and guess
-\begin{equation}
-    P(React|\tau) = P(\tau>\mu_{S}; \sigma_{\tau}, \sigma_{S})
-\end{equation}
-
-Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.
-
-\begin{equation}
-    P(Guess|\tau) = P(\tau<\mu_{S}; \sigma_{\tau}, \sigma_{S})
-\end{equation}
-
-As a result, a decision-maker only reacts to the portion of the stimulus’s distribution that is prior to their stopping time.
-Thus, the participant reacts to a truncated distribution of the stimulus movement onset.
-The truncated stimulus movement onset distribution is generated from only taking the random variable $A$ if it is less than the random variable $T$.
-We can then define an indicator function ($\mathbbm{1}_{a<t}$), which is equal to one if the realized value $a$ is less than $t$ and zero otherwise:
-
-% Define indicator function 
-\begin{align}
-     & \mathbbm{1}_{s<t} =
-    \begin{cases}
-        1 & \text{if } s < t, \\
-        0 & \text{otherwise.}
-    \end{cases}
-\end{align}
-
-The mean of the truncated stimulus movement onset distribution ($\mu_{A_{react}}$) can be calculated by combining the indicator function and the method of moments.
-We start by calculating the expected value of the random variable $A$, which is the integral from $-\infty$ to $\infty$ of the value $a$ multiplied by the probability density function $f_{A}(a)$.
-
-% Define expected value
-\begin{equation}
-    \mu_{S} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{S}(s)da
-\end{equation}
-
-Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution.
-For the truncated stimulus movement onset distribution, we only take values $a$ if they are less than $t$.
-Since the inclusion of $a$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $a$ and $t$.
-Inside the double integral, we multiply the realized value $a$ by its probability density function (i.e., $f_{A}(a)$).
-We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{a<t}$).
-Since this double integral multiplies two gaussian probability density functions and only sums values if $a$ is less than $t$, we must normalize by dividing by the probability that A is less than T.
-The mean (first moment) of the truncated stimulus movement onset distribution is
-
-% Define Cutoff react mean 
-\begin{equation}
-    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}
-\end{equation}
-
-Similarly we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
-
-\begin{equation}
-    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ da \ dt}{P(S<T)}
-\end{equation}
-
-The player’s movement onset distribution consists of a mix between reacting to the truncated stimulus movement onset and guessing.
-Importantly, reacting and guessing have unique delays and uncertainties.
-Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
-The participant mean reaction movement onset ($\mu_{mo_{react}}$; Eq.
-10) is the truncated stimulus movement onset mean ($\mu_{A_{react}}$) plus the participant mean response time ($\mu_{rt}$).
-Likewise, the standard deviation of participant reaction movement onset (($\sigma_{mo_{react}}$; Eq.
-11) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
-
-% Movement Onset times
-\begin{equation}
-    \mu_{mot_{react}} = \mu_{S_{react}} + \mu_{rt}
-\end{equation}
-\begin{equation}
-    \sigma_{mot_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
-\end{equation}
-
-Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
-For the no switch time model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, Eq.
-12) is the sum of the participant stopping time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$ .
-The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (Eq.
-13).
-
-\begin{equation}
-    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
-\end{equation}
-\begin{equation}
-    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
-\end{equation}
-
-Crucially, for the known switch time model and unknown switch time model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
-
-% Switch time included in movement onset times
-\begin{equation}
-    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
-\end{equation}
-\begin{equation}
-    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
-\end{equation}
-
-For both the known switch time model and unknown switch time models, the switch time mean and uncertainty influence the model outputs.
-However, the decision policy of the Full Switch Time Model has perfect knowledge of the switch time, while the decision policy of the Partial Switch Time Model has imperfect knowledge of the switch time.
-Further below (see Model Fitting), we address how we estimate the amount of imperfect knowledge for the Partial Switch Time Model.
-
-We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as
-
-% Target Reach Time 
-\begin{align}
-    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
-    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
-    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
-    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}
-\end{align}
-
-To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to
-
-% Reach random variables
-\begin{align}
-    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
-    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
-    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}})
-\end{align}
-
-We can then define the probability that the participant will reach one of the two targets before the time constraint of 1500ms given they react ($P(Reach|React)$) or guess ($P(Reach|Guess)$):
-
-% Probability of Reaching Target
-\begin{align}
-    P(Reach|React) = P(X_{reach_{react}} < 1500)
-\end{align}
-\begin{align}
-    P(Reach|Guess) = P(X_{reach_{guess}} < 1500)
-\end{align}
-
-We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect.
-The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from Eqs.
-20-21.
-An indecision is simply the probability that the participant reaches the target after the time constraint:
-
-% Probability of indecision sequence 
-\begin{equation}
-    P(Indecision|React) = 1 - P(Reach|React)
-\end{equation}
-\begin{equation}
-    P(Indecision|Guess) = 1 - P(Reach|Guess)
-\end{equation}
-
-To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$).
-The probability of selecting the correct target when the participant reacts is 100\% (Eq.
-24).
-The probability of selecting the correct target when the participant guesses is 50\% (Eq.
-25).
-
-% Probability of being correct
-\begin{equation}
-    P(Correct|React) = 1.0
-\end{equation}
-\begin{equation}
-    P(Correct|Guess) = 0.5
-\end{equation}
-
-The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint and they select the correct target:
-
-% Probability of winning sequence
-\begin{equation}
-    P(Win|React) = P(Reach|React) \cdot P(Correct|React)
-\end{equation}
-\begin{equation}
-    P(Win|Guess) = P(Reach|Guess) \cdot P(Correct|Guess)
-\end{equation}
-
-The conditional probability the participant is incorrect given they react ($P(Incorrect|React)$) or guess ($P(Incorrect|Guess)$) is the probability that they reach the target within the time constraint and they select the wrong target:
-
-% Probability of incorrect sequence 
-\begin{equation}
-    P(Incorrect|React) = P(Reach|React) \cdot (1 - P(Correct|React))
-\end{equation}
-\begin{equation}
-    P(Incorrect|Guess) = P(Reach|Guess) \cdot (1 - P(Correct|Guess))
-\end{equation}
-
-Finally we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (Eq.
-x-x) and the probability of reaching and guessing given a stopping time (Eq.
-x-x), as
-
-\begin{align}
-    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
-    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
-    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess)
-\end{align}
-
-\noindent\emph{Decision Policy}
-
-For each model, the goal of the decision policy is to find the optimal stopping time that maximizes expected reward.
-The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,
-
-% Expected Reward
-\begin{equation}
-    R_{win} = 1
-\end{equation}
-\begin{equation}
-    R_{indecision} = 0
-\end{equation}
-\begin{equation}
-    R_{incorrect} = 0
-\end{equation}
-
-The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is
-
-\begin{align}
-    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
-\end{align}
-
-The decision policy uses known parameters to select an optimal stopping time $\tau^*$ that maximizes expected reward:
-
-% Maximize expected reward with tau
-\begin{equation}
-    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
-\end{equation}
-
-\noindent\textbf{Model Parameter Estimation and Fitting Procedure}
-
-As a reminder, we had three models: No Switch Time Model, Full Switch Time Model, and Partial Switch Time Model.
-Each of these models had full knowledge of the reaction time mean and standard deviation, neuromechanical delay mean and standard deviation, movement time mean and standard deviation, and the stimulus movement onset distribution.
-These parameter values were estimated from experimental data by bootstrapping the meansfrom the response time experiment ($\mu_{rt}, \sigma_{rt}$), timing experiment ($\sigma_{\tau}$), and Experiment 1 ($\mu_{mt}, \sigma_{mt}$).
-We describe the bootstrap procedure below.
-Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature (Norman and Komi 1979, Bruce et al.
-1985, Rossini and Rossi 1998 ).
-
-We used both a warm-start initialization and bootstrap procedure (see below) to determine the switch time mean ($\mu_{switch}$) and uncertainty ($\sigma_{switch}$), as well as the decision policy’s knowledge of the switch time mean ($\hat{\mu}_{switch}$, switch time uncertainty ($\hat{\sigma}_{switch}$), and timing uncertainty ($\hat{\sigma}_{\tau}$).
-
-\noindent\emph{Warm-Start Initialization}
-
-\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and ($\hat{\sigma}_{\tau}$) (Roth 2023r).
-Here the remaining parameters estimated from experimental data were set as the group level means.
-We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means($Data_{i,j}$) according to
-
-% Loss Equation 
-\begin{equation}
-    \mathcal{L} = \sum_{i = 1}^{6} \sum_{j = 1}^{5} \frac{|Data_{i,j} - Model_{i,j}|}{Data_{i,j}}
-\end{equation}
-
-where, i corresponds to experimental condition and j corresponds to each dependent measure (i.e., movement onset, standard deviation of participant movement onset, wins, indecisions, and incorrects) over the target metrics.
-This fitting procedure was repeated 1,000 times to avoid local minimums.
-From these 1,000 optimizations, we used the set of parameters that resulted in the lowest loss as the initial guess for our bootstrap procedure.
-Model fitting was performed using the Powell algorithm in the Minimize function from the Scipy Python library.
-The parameter set with the lowest loss was used as the initial guess for the bootstrap procedure.
-
-\noindent\emph{Warm-Start Initialization}
-
-\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times (Cashaback 2017, Cashback 2019, Roth 2024, Roth 2023).
-We used the mean of the bootstrapped participant data for each of the parameter values that were estimated from data.
-For each bootstrap iteration, the optimization process selected the free parameters for the Full Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$) and Partial Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{\tau}$, $\hat{\sigma}_{\tau}$) that minimized the loss function (Eq.
-44).
-
-\noindent \textbf{Model Parameters}
-
-\noindent Here we report the mean and 95\% confidence intervals for the bootstrapped model parameters.
-For each parameter, each model had a value that determined the model outputs and a value that the decision policy used to select $\tau$.
-The No Switch Time Model and Full Switch Time Model were both optimal in the sense that they had perfect knowledge of all parameters.
-That is, the value that determined model outputs was equal to the value used by the decision policy.
-Parameter values for reaction time mean, reaction time uncertainty, movement time mean, movement time uncertainty, and timing uncertainty were all calculated from participant data on each bootstrap iteration: reaction time mean (247.4 ms; [239.2, 256.35]), reaction time uncertainty (38.5 ms; [35.7, 41.4]), movement time mean (171.7 ms; [157.6, 197.2]), movement time uncertainty (25.4 ms; [22.2, 28.7]), and timing uncertainty (77.8 ms; [69.4, 86.6]).
-The No Switch Time Model had no parameters to fit and the decision policy had full knowledge of all of these parameters.
-The Full Switch Time Model fit the switch time mean and switch time uncertainty and the decision policy had full knowledge of all parameters.
-The bootstrapped mean of the switch time delay parameter was 0.95 ms with a 95\% confidence interval of [0.21, 2.20].
-The bootstrapped mean of the switch time uncertainty parameter was 103.20 ms with a 95\% confidence interval of [97.77, 115.31].
-
-The Partial Switch Time Model fit the timing uncertainty, switch time mean, switch time uncertainty.
-Critically, this model did not have full knowledge of these parameters, so the value that the decision policy used to select the optimal time was fit separately from the value that was used to determine the model outputs.
-Note that the timing uncertainty value used for model outputs is from experimental data, but this model allowed the knowledge of the timing uncertainty to be a fit parameter.
-The values that were used for model outputs were: timing uncertainty (77.83 ms; [69.4, 86.8]), switch time mean (21.10 ms; [1.46, 63.71]), switch time uncertainty (134.73 ms; [111.22, 155.06].
-The values that were used by the decision policy were: timing uncertainty (1.65 ms;  [0.08, 4.63]), switch time mean (9.0 ms; [0.00, 16.65]), switch time uncertainty (40.4 ms; [34.54, 48.02]).
-Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and stopping time certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.
-
 \SectionHeader{Main Figures}
@@
 
-%     \caption{\textbf{Experimental Design.} \textbf{S)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
+%     \caption{\textbf{Experimental Design.} \textbf{A)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
 An LCD projected images (start position, targets) onto a semi-silvered mirror that occluded vision of the hand and upper arm.
@@
 
-%     \caption{\textbf{Timing Behaviour.} \textbf{S)} Average participant movement onset time (y-axis) for each of the six experimental conditions (x-axis).
+%     \caption{\textbf{Timing Behaviour.} \textbf{A)} Average participant movement onset time (y-axis) for each of the six experimental conditions (x-axis).
 \textbf{B)} Corresponding participant movement onset time (y-axis) for the three different mean onset times (x-axis) when collapsed across variance.
@@
 
-%     \caption{\textbf{Trial Outcomes.} \textbf{S)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition.
-\textbf{S)} We found that the middle mean low variance and late mean low variance conditions had a significantly greater number of indecisions compared to the early mean low variance condition.
+%     \caption{\textbf{Trial Outcomes.} \textbf{A)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition.
+\textbf{A)} We found that the middle mean low variance and late mean low variance conditions had a significantly greater number of indecisions compared to the early mean low variance condition.
 That is, in the middle mean low variance and late mean low variance conditions, participants often waited to react to the stimulus but ended up guessing late.
@@
 
-%     \caption{\textbf{Models.} \textbf{S)} Predicted target reach times from three models: No Switch Time Model (light gray), Known Switch Time Model (dark gray), and Unknown Switch Time Model (black).
+%     \caption{\textbf{Models.} \textbf{A)} Predicted target reach times from three models: No Switch Time Model (light gray), Known Switch Time Model (dark gray), and Unknown Switch Time Model (black).
 Stimulus movement onset time is shown in pink, which corresponds to the late mean low variance condition.
@@
 %         \caption{
-%             Model Outputs: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{S)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
+%             Model Outputs: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{A)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
 The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the late mean low variance and late mean high variance conditions.
@@
 %     \caption{\textbf{Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1.
-\textbf{S)} Participants responded to two different types of stimuli.
+\textbf{A)} Participants responded to two different types of stimuli.
 In the react trials (pink), the stimulus (yellow cursor) would move to one of the two potential targets.

### 2024-07-29 paper/supplementary.tex
supplementary and cover letter added

\documentclass[12pt,letterpaper]{article}
\usepackage{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{arydshln} % For \hdashline
\usepackage{lineno}
\usepackage{setspace}

\definecolor{mydarkblue}{RGB}{0,51,102}
\graphicspath{ {./figures/} }

\usepackage[%
  autocite  = superscript,
  backend  = bibtex,
  sortcites  = false,
  citestyle = numeric,
  bibstyle=authoryear,
  sorting = none,
  maxbibnames=99,
  giveninits = true, %initials
  isbn=false,
  doi = false,
  url = false
]{biblatex}

\addbibresource{Aim1.bib}
% \bibliography{draft}

\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}

\renewbibmacro{in:}{}
\DeclareFieldFormat[article]{citetitle}{#1}
\DeclareFieldFormat[article]{title}{#1}  %
\DeclareFieldFormat{pages}{#1}% no prefix for the `pages` field in the bibliography
\DeclareNameAlias{sortname}{family-given} % put last name first
\DeclareNameAlias{default}{family-given}
\DeclareFieldFormat{labelnumberwidth}{\textcolor{mydarkblue}{\mkbibbold{#1\adddot}}} %remove brackets in bibliography
\DeclareFieldFormat{journaltitle}{\mkbibemph{#1}\isdot}
%\renewcommand{\labelnamepunct}{\addspace}  % remove period after year

% add numbers in front of citations and puts year behind authors
\defbibenvironment{bibliography}
  {\list
     {\printtext[labelnumberwidth]{%
    \printfield{labelprefix}%
    \printfield{labelnumber}}}
     {\setlength{\labelwidth}{\labelnumberwidth}%
      \setlength{\leftmargin}{\labelwidth}%
      \setlength{\labelsep}{\biblabelsep}%
      \addtolength{\leftmargin}{\labelsep}%
      \setlength{\itemsep}{\bibitemsep}%
      \setlength{\parsep}{\bibparsep}}%
      \renewcommand*{\makelabel}[1]{\hss##1}}
  {\endlist}
  {\item}

\usepackage{xpatch}
\xpatchbibmacro{date+extrayear}{%
  \printtext[parens]%
}{%
  \setunit{\addperiod\space}%
  \printtext%
}{}{}
\AtEveryBibitem{%
  \clearfield{note}%
}

% adds comma after journal 
\renewcommand\bibpagespunct{\ifentrytype{article}{\addcolon}{\addcomma}\space}
\renewbibmacro*{volume+number+eid}{%
\setunit*{\addcomma\space}% NEW
  \printfield{volume}
  \printfield[parens]{number}{,}%
  \setunit{\addcomma\space}%
  \printfield{eid}}

% change and to \& (can also remove)
\DefineBibliographyExtras{english}{%
  \renewcommand*{\finalnamedelim}{\addcomma\addspace\&\addspace}%
  %\renewcommand*{\finalnamedelim}{\addcomma\addspace}%
}

%\usepackage{hyperref}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
% Set caption styles
% \DeclareCaptionLabelFormat{table}{1-2}
% \captionsetup[table]{labelfont=bf, labelsep=period}
\DeclareCaptionLabelFormat{supp}{1-2}
\captionsetup[figure]{labelfont=bf, labelsep=colon, font=footnotesize, justification=justified}

\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays

\newcommand{\SuppCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}\footnotesize}
\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{black}{#1}}\normalsize }

\abovedisplayskip = 10.0pt plus 2.0pt minus 20.0pt
\belowdisplayskip = 10.0pt plus 2.0pt minus 20.0pt
\abovedisplayshortskip = 0.0pt plus 20.0pt
\belowdisplayshortskip = 9pt plus 3pt minus 20pt

% Condition variables
% \def\emlv{\emph{early mean low variance}}
% \def\emhv{\emph{early mean high variance}}
% \def\mmlv{\emph{middle mean low variance}}
% \def\mmhv{\emph{middle mean high variance}}
% \def\lmlv{\emph{late mean low variance}}
% \def\lmhv{\emph{late mean high variance}}

% \def\em{\emph{early mean}}
% \def\mm{\emph{middle mean}}
% \def\lm{\emph{late mean}}

% \definecolor{myudblue}{RGB}{0, 83, 159}
\begin{document}
\SectionHeader{Supplementary}

\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary A: High Variance Results}}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
    \renewcommand\figurename{Supplementary Figure}
    \caption{\textbf{Timing Behaviour.} A) Average participant movement onset (y-axis) for each experimental condition (x-axis). We found a significant main effect of stimulus movement onset mean (F[1.551,29.475] = 4.36, p = 0.030) and variance (F[1.000,19.000], p = 0.017)) on participant movement onset. There was no significant interaction (F[1.657,31.474], p = 0.565) B) Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance. During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint. For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions. Waiting longer to react and/or late guessing led to later movement onset. In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see Supplementary Figure 6). The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition. For both the middle mean and late mean conditions, late guessing often led to indecisions (see Fig. 2). C) Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis). We found a significant main effect of mean (F[1.383, 26.284], p = 0.018) and variance (F[1.000,19.000], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.978, 37.575], p = 0.097) D) Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance. In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions. Box and whisker plots display the 25th, 50th, and 75th percentiles. Open gray circles and connecting lines represent individual data.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
    \renewcommand\figurename{Supplementary Figure}

    \caption{\textbf{Trial Outcomes.} \textbf{A)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition. \textbf{A)} We found that the middle mean low variance and late mean low variance conditions had a significantly greater number of indecisions compared to the early mean low variance condition. That is, in the middle mean low variance and late mean low variance conditions, participants often waited to react to the stimulus but ended up guessing late. These late guesses often led to indecisions. \textbf{B)} Interestingly, we also found that the average win percentage (4X.X\%) was significantly below the 50\% chance level (p < 0.001) in the late mean low variance condition, clearly demonstrating suboptimal behaviour. Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the stimulus. Collectively, these results show that participants were suboptimal decision makers that led to excessively indecisive behaviour.}
\end{figure}

\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary B: Optimal Models}}

We tested three different models to investigate the ability of participants to maximize reward during Experiment 1: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (Fig. 2). Each model represents a different hypothesis on how humans time their decisions, which we address further below. Intuitively, participants should react to the stimulus on trials where it moved earlier in time and guess on trials where it moved later in time. That is, reacting to early stimulus movement onsets ensures they can select the correct target. Likewise, guessing on late stimulus movement onsets affords the participant a 50\% chance of selecting the correct target. However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
We modelled the time to switch from reacting to guessing as an optimal stopping problem. This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim (trommershauser) and reach timing (Hudson, Maloney, Landy 2008). Here a model represents a decision-maker that selects a stopping time, $\tau$. This stopping time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets. The optimal stopping time is determined from a decision policy that maximizes reward, given task constraints (i.e. stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.

\noindent \emph{Model Parameters}

\noindent Here we define the parameters used for the three models. Note that not all the parameters are used in each model, which we specify further below and in Fig. 2. The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement. Neuromechanical Delay is the mean ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) of the time between a volitional decision to move and movement onset. Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target. Stimulus Movement onset is knowledge of the mean ($\mu_{A}$) and uncertainty ($\sigma_{A}$) of the stimulus’s movement onset distribution. Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended stopping time, $\tau$. Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing. All probability distributions are assumed to be normally distributed with a mean $\mu$ and standard deviation $\sigma$.  Each of our three models has a different set of known and unknown parameters. A model decision policy has full knowledge of known parameters when determining the optimal decision time. A model decision policy has no or partial knowledge of unknown parameters when determining the optimal decision time.

\noindent \emph{No Switch Time Model}

\noindent The No Switch Time Model had the following known parameters: response time mean and uncertainty, movement time mean and uncertainty, neuromechanical delay mean and uncertainty, timing uncertainty, and stimulus movement onset. This model had no unknown parameters. Importantly, the No Switch Time Model did not include the switch time mean and uncertainty in neither the known nor the unknown parameter sets. The No Switch Time Model reflects the hypothesis that there is no additional delay and uncertainty when switching from reacting to guessing.

\noindent \emph{Full Switch Time Model}

\noindent The Full Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, stimulus movement onset, timing uncertainty, and switch time mean and uncertainty. This model did not have any unknown parameters. The Full Switch Time Model reflects the hypothesis that participants fully account for a delay and uncertainty associated with switching from reacting to guessing.

\noindent \emph{Partial Switch Time Model}

\noindent The Partial Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, and stimulus movement onset. This model had the following unknown parameters: switch time mean and uncertainty, and timing uncertainty. The Partial Switch Time Model reflects our hypothesis that participants do not account for the delay and uncertainties associated with guessing.

\noindent \emph{General Formulation for the Models}

\noindent We begin by defining the general normal probability density function and cumulative density function:

% Define pdf and cdf
\begin{equation}
    X\sim\mathcal{N}(\mu,\sigma)
\end{equation}
\begin{equation}
    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
\end{equation}

$X$ is the random variable drawn from a normal distribution $\mathcal{N}$ with some mean and standard deviation. $f_{X}(x;\mu,\sigma)$ is the normal probability density function over the variable $x$, with a mean ($\mu$) and standard deviation ($\sigma$). $F_{X}(b)$ is the normal cumulative density, which is the integral of the probability density function $f_{X}(x;\mu,\sigma)$ from $-\infty$ to $b$. Throughout, capitalized variables denote normally distributed random variables. Additionally, lowercase variables such as $x$ refer to the realization of the random variable $X$. The lowercase notation simply indicates that the value is known and is not a random variable.

Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions. We begin by defining $A$ as the random variable drawn from the stimulus’s movement onset distribution (Eq. 4) and $T$ as the random variable drawn from the stopping time distribution (Eq. 5).

% Define random variables A and T
\begin{align}
    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}

Consider$a$ and $t$ as the realizations of random variables $A$ and $T$ for a single trial. On any specific trial, a decision-maker will react if the stimulus movement onset is before the stopping time (i.e., $a<t$). Conversely, the decision-maker will guess at the stopping time if the stimulus has not moved by the stopping time (i.e., $a>t$). Thus, the probability that a participant will react or guess depends on the participants choice of a stopping time $\tau$. Specifically, the probability that the participant will react is the probability that the random variable A is less than T.

% Define prob react and guess
\begin{equation}
    P(React|\tau) = P(\tau>\mu_{S}; \sigma_{\tau}, \sigma_{S})
\end{equation}

Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.

\begin{equation}
    P(Guess|\tau) = P(\tau<\mu_{S}; \sigma_{\tau}, \sigma_{S})
\end{equation}

As a result, a decision-maker only reacts to the portion of the stimulus’s distribution that is prior to their stopping time. Thus, the participant reacts to a truncated distribution of the stimulus movement onset.
The truncated stimulus movement onset distribution is generated from only taking the random variable $A$ if it is less than the random variable $T$. We can then define an indicator function ($\mathbbm{1}_{a<t}$), which is equal to one if the realized value $a$ is less than $t$ and zero otherwise:

% Define indicator function 
\begin{align}
     & \mathbbm{1}_{s<t} =
    \begin{cases}
        1 & \text{if } s < t, \\
        0 & \text{otherwise.}
    \end{cases}
\end{align}

The mean of the truncated stimulus movement onset distribution ($\mu_{A_{react}}$) can be calculated by combining the indicator function and the method of moments. We start by calculating the expected value of the random variable $A$, which is the integral from $-\infty$ to $\infty$ of the value $a$ multiplied by the probability density function $f_{A}(a)$.

% Define expected value
\begin{equation}
    \mu_{S} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{S}(s)da
\end{equation}

Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution. For the truncated stimulus movement onset distribution, we only take values $a$ if they are less than $t$. Since the inclusion of $a$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $a$ and $t$. Inside the double integral, we multiply the realized value $a$ by its probability density function (i.e., $f_{A}(a)$). We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{a<t}$). Since this double integral multiplies two gaussian probability density functions and only sums values if $a$ is less than $t$, we must normalize by dividing by the probability that A is less than T. The mean (first moment) of the truncated stimulus movement onset distribution is

% Define Cutoff react mean 
\begin{equation}
    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}
\end{equation}

Similarly we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:

\begin{equation}
    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ da \ dt}{P(S<T)}
\end{equation}

The player’s movement onset distribution consists of a mix between reacting to the truncated stimulus movement onset and guessing. Importantly, reacting and guessing have unique delays and uncertainties. Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
The participant mean reaction movement onset ($\mu_{mo_{react}}$; Eq. 10) is the truncated stimulus movement onset mean ($\mu_{A_{react}}$) plus the participant mean response time ($\mu_{rt}$). Likewise, the standard deviation of participant reaction movement onset (($\sigma_{mo_{react}}$; Eq. 11) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).

% Movement Onset times
\begin{equation}
    \mu_{mot_{react}} = \mu_{S_{react}} + \mu_{rt}
\end{equation}
\begin{equation}
    \sigma_{mot_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
\end{equation}

Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
For the no switch time model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, Eq. 12) is the sum of the participant stopping time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$ . The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (Eq. 13).

\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
\end{equation}

Crucially, for the known switch time model and unknown switch time model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,

% Switch time included in movement onset times
\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
\end{equation}

For both the known switch time model and unknown switch time models, the switch time mean and uncertainty influence the model outputs. However, the decision policy of the Full Switch Time Model has perfect knowledge of the switch time, while the decision policy of the Partial Switch Time Model has imperfect knowledge of the switch time. Further below (see Model Fitting), we address how we estimate the amount of imperfect knowledge for the Partial Switch Time Model.

We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as

% Target Reach Time 
\begin{align}
    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}
\end{align}

To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to

% Reach random variables
\begin{align}
    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}})
\end{align}

We can then define the probability that the participant will reach one of the two targets before the time constraint of 1500ms given they react ($P(Reach|React)$) or guess ($P(Reach|Guess)$):

% Probability of Reaching Target
\begin{align}
    P(Reach|React) = P(X_{reach_{react}} < 1500)
\end{align}
\begin{align}
    P(Reach|Guess) = P(X_{reach_{guess}} < 1500)
\end{align}

We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect. The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from Eqs. 20-21. An indecision is simply the probability that the participant reaches the target after the time constraint:

% Probability of indecision sequence 
\begin{equation}
    P(Indecision|React) = 1 - P(Reach|React)
\end{equation}
\begin{equation}
    P(Indecision|Guess) = 1 - P(Reach|Guess)
\end{equation}

To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$). The probability of selecting the correct target when the participant reacts is 100\% (Eq. 24). The probability of selecting the correct target when the participant guesses is 50\% (Eq. 25).

% Probability of being correct
\begin{equation}
    P(Correct|React) = 1.0
\end{equation}
\begin{equation}
    P(Correct|Guess) = 0.5
\end{equation}

The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint and they select the correct target:

% Probability of winning sequence
\begin{equation}
    P(Win|React) = P(Reach|React) \cdot P(Correct|React)
\end{equation}
\begin{equation}
    P(Win|Guess) = P(Reach|Guess) \cdot P(Correct|Guess)
\end{equation}

The conditional probability the participant is incorrect given they react ($P(Incorrect|React)$) or guess ($P(Incorrect|Guess)$) is the probability that they reach the target within the time constraint and they select the wrong target:

% Probability of incorrect sequence 
\begin{equation}
    P(Incorrect|React) = P(Reach|React) \cdot (1 - P(Correct|React))
\end{equation}
\begin{equation}
    P(Incorrect|Guess) = P(Reach|Guess) \cdot (1 - P(Correct|Guess))
\end{equation}

Finally we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (Eq. x-x) and the probability of reaching and guessing given a stopping time (Eq. x-x), as

\begin{align}
    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess)
\end{align}

\noindent\emph{Decision Policy}

For each model, the goal of the decision policy is to find the optimal stopping time that maximizes expected reward. The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,

% Expected Reward
\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}

The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is

\begin{align}
    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
\end{align}

The decision policy uses known parameters to select an optimal stopping time $\tau^*$ that maximizes expected reward:

% Maximize expected reward with tau
\begin{equation}
    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
\end{equation}

\noindent\textbf{Model Parameter Estimation and Fitting Procedure}

\noindent As a reminder, we had three models: No Switch Time Model, Full Switch Time Model, and Partial Switch Time Model. Each of these models had full knowledge of the reaction time mean and standard deviation, neuromechanical delay mean and standard deviation, movement time mean and standard deviation, and the stimulus movement onset distribution. These parameter values were estimated from experimental data by bootstrapping the meansfrom the response time experiment ($\mu_{rt}, \sigma_{rt}$), timing experiment ($\sigma_{\tau}$), and Experiment 1 ($\mu_{mt}, \sigma_{mt}$). We describe the bootstrap procedure below. Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature (Norman and Komi 1979, Bruce et al. 1985, Rossini and Rossi 1998 ).

We used both a warm-start initialization and bootstrap procedure (see below) to determine the switch time mean ($\mu_{switch}$) and uncertainty ($\sigma_{switch}$), as well as the decision policy’s knowledge of the switch time mean ($\hat{\mu}_{switch}$, switch time uncertainty ($\hat{\sigma}_{switch}$), and timing uncertainty ($\hat{\sigma}_{\tau}$).

\noindent\emph{Warm-Start Initialization}

\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and ($\hat{\sigma}_{\tau}$) (Roth 2023r).  Here the remaining parameters estimated from experimental data were set as the group level means. We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means($Data_{i,j}$) according to

% Loss Equation 
\begin{equation}
    \mathcal{L} = \sum_{i = 1}^{6} \sum_{j = 1}^{5} \frac{|Data_{i,j} - Model_{i,j}|}{Data_{i,j}},
\end{equation}
where $i$ corresponds to experimental condition and $j$ corresponds to each dependent measure (i.e., movement onset, standard deviation of participant movement onset, wins, indecisions, and incorrects) over the target metrics. This fitting procedure was repeated 1,000 times to avoid local minimums. From these 1,000 optimizations, we used the set of parameters that resulted in the lowest loss as the initial guess for our bootstrap procedure. Model fitting was performed using the Powell algorithm in the Minimize function from the Scipy Python library. The parameter set with the lowest loss was used as the initial guess for the bootstrap procedure.

\noindent\emph{Warm-Start Initialization}

\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times (Cashaback 2017, Cashback 2019, Roth 2024, Roth 2023). We used the mean of the bootstrapped participant data for each of the parameter values that were estimated from data. For each bootstrap iteration, the optimization process selected the free parameters for the Full Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$) and Partial Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{\tau}$, $\hat{\sigma}_{\tau}$) that minimized the loss function (Eq. 44).

\noindent \textbf{Model Parameters}

\noindent Here we report the mean and 95\% confidence intervals for the bootstrapped model parameters. For each parameter, each model had a value that determined the model outputs and a value that the decision policy used to select $\tau$. The No Switch Time Model and Full Switch Time Model were both optimal in the sense that they had perfect knowledge of all parameters. That is, the value that determined model outputs was equal to the value used by the decision policy. Parameter values for reaction time mean, reaction time uncertainty, movement time mean, movement time uncertainty, and timing uncertainty were all calculated from participant data on each bootstrap iteration: reaction time mean (247.4 ms; [239.2, 256.35]), reaction time uncertainty (38.5 ms; [35.7, 41.4]), movement time mean (171.7 ms; [157.6, 197.2]), movement time uncertainty (25.4 ms; [22.2, 28.7]), and timing uncertainty (77.8 ms; [69.4, 86.6]). The No Switch Time Model had no parameters to fit, and the decision policy had full knowledge of all of these parameters. The Full Switch Time Model fit the switch time mean and switch time uncertainty and the decision policy had full knowledge of all parameters. The bootstrapped mean of the switch time delay parameter was 0.95 ms with a 95\% confidence interval of [0.21, 2.20]. The bootstrapped mean of the switch time uncertainty parameter was 103.20 ms with a 95\% confidence interval of [97.77, 115.31].

The Partial Switch Time Model fit the timing uncertainty, switch time mean, switch time uncertainty. Critically, this model did not have full knowledge of these parameters, so the value that the decision policy used to select the optimal time was fit separately from the value that was used to determine the model outputs. Note that the timing uncertainty value used for model outputs is from experimental data, but this model allowed the knowledge of the timing uncertainty to be a fit parameter. The values that were used for model outputs were: timing uncertainty (77.83 ms; [69.4, 86.8]), switch time mean (21.10 ms; [1.46, 63.71]), switch time uncertainty (134.73 ms; [111.22, 155.06]. The values that were used by the decision policy were: timing uncertainty (1.65 ms;  [0.08, 4.63]), switch time mean (9.0 ms; [0.00, 16.65]), switch time uncertainty (40.4 ms; [34.54, 48.02]). Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and stopping time certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.

\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary C: Model Results}}

% Figure 5 Model Outputs All Conditions
\begin{figure}[H]
    \renewcommand\figurename{Supplementary Figure}

    \begin{minipage}[c]{0.64\textwidth}
        \includegraphics[scale = 0.95]{figures/exp1_data_panel_with_models_all_conditions.png}
    \end{minipage}\hfill
    \begin{minipage}[c]{0.3\textwidth}
        \caption{
            Model Outputs: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{A)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition. The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the late mean low variance and late mean high variance conditions. Conversely, the Unknown Switch Time Model (black) is able to accurately predict the participant data for all conditions across all metrics. As a reminder, the Unknown Switch time Model does not account for the delay and uncertainties associated with switching from reacting to guessing. Critically, in \textbf{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the late mean low variance condition, whereas the other two models predict zero indecisions for that condition. Further, in \textbf{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the late mean low variance condition. Collectively, our findings show that humans are suboptimal and excessively indecisive, which can be captured by a model that does not account  for the delay and uncertainties associated with switching from reacting to guessing.
        } 
    \end{minipage}
\end{figure}

\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary D: Response Time Task}}
\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp1_response_time_experimental_design.png}

    \caption{Response Time Experiment: One of two potential targets (dashed white rings; not visible to participants) would appear on the screen. Once a target appeared (solid white ring), participants were instructed to rapidly move their cursor to hit the displayed target. We used the mean and standard deviation of response times as model parameters in the optimal stopping models.}
\end{figure}

\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary E: Timing Uncertainty Task}}

\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary F: Guess Decisions}}

\end{document}

### 2024-07-29 paper/main.tex
almost done!

@@
-\documentclass[12pt,letterpaper]{article}
+\documentclass[12pt]{article}
 \usepackage{inputenc}
@@
 \definecolor{mydarkblue}{RGB}{0,51,102}
+\definecolor{MYDARKBLUE}{RGB}{0,51,102}
+
 \graphicspath{ {./figures/} }
@@
 
-\newcommand{\SuppCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}\footnotesize}
-\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
-\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{black}{#1}}\normalsize }
+\newcommand\boldblue[1]{\textcolor{mydarkblue}{\textbf{#1}}}
+
+\newcommand{\SuppCaption}[2]{\noindent\boldblue{{#1}} {#2}\footnotesize}
+\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large\textcolor{mydarkblue}{#1}}\normalsize }
+\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{mydarkblue}{#1}}\normalsize }
 
@@
 
-    \noindent\textbf{\Large\textcolor{mydarkblue}{Indecisions under time pressure arise from suboptimal switching behaviour
+    \noindent\boldblue{\Large\textcolor{mydarkblue}{Indecisions under time pressure arise from suboptimal switching behaviour
         }}
@@
     Seth R.
-Sullivan\textsuperscript{1}, \textsuperscript{2} Christopher Peters\textsuperscript{1}, \textsuperscript{2}, Rakshith Lokesh\textsuperscript{1}, Jan A.
-Calalo\textsuperscript{1},\\ Truc Ngo\textsuperscript{3}, John H.
-Buggeln\textsuperscript{5},Isaac Kurtzer\textsuperscript{5},Michael Carter\textsuperscript{5}, Joshua G.A.
-Cashaback\textsuperscript{1},\textsuperscript{2},\textsuperscript{4},\textsuperscript{5}
+Sullivan\textsuperscript{1}, Rakshith Lokesh\textsuperscript{4}, Jan A.
+Calalo\textsuperscript{1,2}, Truc Ngo\textsuperscript{1}, John H.
+Buggeln\textsuperscript{3},Christopher Peters\textsuperscript{1}, Isaac Kurtzer\textsuperscript{5}, Michael Carter\textsuperscript{6}, Joshua G.A.
+Cashaback\textsuperscript{1,2,3,7}
     \vspace{2mm}
@@
 
-\textsuperscript{1} Department of Biomedical Engineering, University of Delaware\\
+\noindent \textsuperscript{1} Department of Biomedical Engineering, University of Delaware\\
 \textsuperscript{2} Department of Mechanical Engineering, University of Delaware\\
-\textsuperscript{3} Human Performance Lab, University of Calgary\\
-\textsuperscript{4} Biomechanics and Movements Science Program, University of Delaware\\
-\textsuperscript{5} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
+\textsuperscript{3} Biomechanics and Movements Science Program, University of Delaware\\
+\textsuperscript{4} Action Lab, Northeastern University\\
+\textsuperscript{5} College of Osteopathic Medicine, New York Institute of Technology\\
+\textsuperscript{6} Action, Cognition, and Metascience Lab, McMaster University\\
+\textsuperscript{7} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
 \vspace{15mm}
@@
 \\
-XXXXXXXXXXXXXXX
+NSF2146888
 \\
@@
 \linenumbers %
-\noindent \textbf{\large\textcolor{mydarkblue}{ABSTRACT}}
-\vspace{2mm}
+\SectionHeader{ABSTRACT}
 \\
@@
 Here we examined how indecisions arise under high-pressure deadlines.
-In our first experiment, participants attempted to select a target by either reacting to a stimulus or guessing, when acting under a high pressure time constraint.
+In our first experiment participants attempted to select a target by either reacting to a stimulus or guessing, when acting under a high pressure time constraint.
 We found that participants were suboptimal, displaying a below chance win percentage due to an excessive number of indecisions.
-Computational modeling suggested that participants were excessively indecisive because they failed to account for a time delay and temporal uncertainty when switching from reacting to guessing, which has not been previously reported in the literature.
-In a followup experiment, we show for the first time the existence of a time delay and temporal uncertainty when switching from reacting to guessing.
-Collectively, our results support the idea that humans are suboptimal and fail to account for a time delay and temporal uncertainty when switching from reacting to guessing, leading to indecisive behaviour.
+Computational modeling suggested that participants were excessively indecisive because they failed to account for a time delay and temporal uncertainty when switching from reacting to guessing, a phenomenon previously unreported in the literature.
+In a followup experiment we provide direct evidence for functionally relevant time delay and temporal uncertainty when switching from reacting to guessing.
+Collectively, our results demonstrate that humans are suboptimal and fail to account for a time delay and temporal uncertainty when switching from reacting to guessing, leading to indecisive behaviour.
+
 \newpage
 
-\noindent \textbf{\large\textcolor{mydarkblue}{NEW AND NOTEWORTHY}}
-\vspace{2mm}
-\\
-The sensorimotor system has the constant challenge of dealing with the naturally occurring variability in our movements.
-Here we investigated the potential roles of muscular co-contraction and visuomotor feedback responses to regulate movement variability.
-When we visually amplified movements, we found that the sensorimotor system primarily uses muscular co-contraction to regulate movement variability.
-Interestingly, we found that muscular co-contraction was relative to participant-specific visuomotor feedback response, suggesting an interplay between impedance and feedback control.
-\newpage
-%\noindent\textbf{Author Summary}`
-%\vspace{2mm}\\
-%
-%\newpage
 \pagestyle{fancy}
@@
 
-%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \pagenumbering{arabic} % page numbering starts here
-\noindent\textbf{\large\textcolor{mydarkblue}{INTRODUCTION}}
+\vspace{2mm}
+\SectionHeader{INTRODUCTION}
 \vspace{2mm}
 \\
-Indecisions often arise from failing to decide and act upon sensory information in time, such as a driver failing to brake or hit the gas pedal when a traffic light turns yellow.
+\noindent Indecisions arise from failing to decide and act upon sensory information in time, such as a driver failing to brake or hit the gas pedal when a traffic light turns yellow.
 When acting under high pressure time constraints, the ability to accurately time a decision is critical to success.
 Past literature has had very little focus on indecisions.
-The vast majority of decision-making research either does not consider responses made after some time constraint or simply does not permit a non-response, such as in the classic two-alternative forced choice paradigm (Zachsenhouse Robust versus optimal,  Bogacz 2006, Cho et al.
-2002 Mechanisms underlying, Jogan and Stocker 2014 A new two-alternative, Ratcliff et al.
-2018 modeling 2-alternative forced-choice tasks, Tyler and Chen 2000, Ulrich and Miller 2004 Threshold estimation,   ).
+The vast majority of decision-making research either does not consider responses made after some time constraint or simply does not permit a non-response, such as in the classic two-alternative forced choice paradigm\autocite{zacksenhouse_robust_2010,bogacz_physics_2006,cho_mechanisms_2002,jogan_new_2014,ratcliff_diffusion_2008,ulrich_threshold_2004,tyler_signal_2000}.
 Thus, despite its real-world ubiquity and importance, we have very little understanding of how indecisions arise.
 
-There have only been a handful of papers to examine indecisions, which involve either high (Lokesh et al.
-2022) or low time pressure (Karsilar et al.
-2014, Wu et al.
-2016, Phillastides et al.
-2011, Dambacher and Hubner 2015, Forstmann et al.
-2008).
-We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target (Lokesh et al.
-2022).
+There have only been a handful of papers to examine indecisions, which involve either high \autocite{lokesh_humans_2022} or low time pressure \autocite{karsilar_speed_2014,wu_capacity_2016,philiastides_causal_2011,dambacher_time_2015,forstmann_striatum_2008}.
+We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokesh_humans_2022}.
 In this competitive scenario, the ‘prey’ attempted to end up in the same target as the ‘predator’ by a time constraint, while the predator attempted to end up in the opposite target as the prey.
@@
 Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions.
-Similar to others (Wu et al.
-2016, Phillastides et al.
-2011, Dambacher and Hubner 2015, Forstmann et al.
-2008), Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions.
+Similar to others \autocite{karsilar_speed_2014,wu_capacity_2016,philiastides_causal_2011,dambacher_time_2015,forstmann_striatum_2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions.
 Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline.
@@
 
-Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response (drugowitsch, balci, bogacz, hudson landy, trommershauser).
-To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system (drugowitsch, bogacz, maybe balci too, hudson landy, acerbi wolpert internal representations, Wolpert/Faisal review, Kording/wolpert bayesian decision theory, wolpert/landy motor control is decision-making).
-Past work has shown that humans will often produce nearly optimal decision times during cognitive (Balci et al.
-2011, Miletic and Van Maanen 2019) and motor tasks (Hudson et al.
-2008, Faisal and Wolpert 2009 Near Optimal Combination).
-Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties (Ota et al.
-2015, drugowitsch computational precision).
+Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response \autocite{drugowitsch_optimal_2014,balci_optimal_2011,bogacz_physics_2006,hudson_optimal_2008,trommershauser_humans_2006}.
+To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system (\autocite{drugowitsch_tuning_2015, balci_optimal_2011,hudson_optimal_2008,acerbi_internal_2012,faisal_noise_2008,kording_bayesian_2006,wolpert_motor_2012,tanis_accuracy_2023,lokesh_visual_2023}.
+Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite{balci_optimal_2011,miletic_caution_2019} and motor tasks\autocite{hudson_optimal_2008,faisal_near_2009}.
+Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties \autocite{ota_motor_2015,drugowitsch_computational_2016}.
 With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.
-
-Building on our past work (Lokesh, 2022), we developed a high pressure task with a time constraint to examine how humans select decision times.
+Building on our past work\autocite{lokesh_humans_2022}, we developed a high pressure task with a time constraint to examine how humans select decision times.
 We tested the idea that humans optimally account for time delays and temporal uncertainties to select a decision time that maximizes reward.
 Alternatively, humans may suboptimally represent time delays and temporal uncertainties, which can lead to an excessive number of indecisions.
-In Experiment 1, we found humans were suboptimal and observed excessive indecisions that led to a below chance win rate.
+In \boldblue{Experiment 1}, we found humans were suboptimal and observed excessive indecisions that led to a below chance win rate.
 Computational modelling work suggested that suboptimality arose by failing to account for the time delay and temporal uncertainty associated with switching from reacting to guessing.
-Experiment 2 showed for the first time, to our knowledge, the existence of an additional time delay and uncertainty when switching from reacting to guessing within a trial.
+\boldblue{Experiment 2} showed for the first time, to our knowledge, the existence of an additional time delay and uncertainty when switching from reacting to guessing within a trial.
 Taken together, our work suggests that humans suboptimally represent the time delay and temporal uncertainty associated with switching from reacting to guessing, leading to indecisive behaviour.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\noindent\textbf{\large\textcolor{mydarkblue}{RESULTS}}
 \vspace{2mm}
-\\
-\textbf{\textcolor{mydarkblue}{{Experiment 1}}}
-\vspace{2mm}
+\SectionHeader{RESULTS}
 
-\noindent\textbf{\textcolor{mydarkblue}{{Experimental Design}}}
-\vspace{2mm}
+\SubSectionHeader{Experiment 1}
 
-The goal of Experiment 1 was to test how stimulus timing influenced indecisive behaviour.
-Briefly, participants began each trial by moving their cursor into a start position (Fig.
-1A).
+\noindent\boldblue{Experimental Design.}
+The goal of \boldblue{Experiment 1} was to test how stimulus timing influenced indecisive behaviour.
+Briefly, participants began each trial by moving their cursor into a start position (\boldblue{Fig.
+1A}).
 The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles.
@@
 Thus, participants were fully aware of how much time they had left relative to the time constraint.
-A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint (Fig.
-1B).
+A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint (\boldblue{Fig.
+1B}).
 A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale =1]{figures/exp1_experimental_design_v2.png}
+  \caption{\textbf{Experimental Design.} \textbf{A)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
+An LCD projected images (start position, targets) onto a semi-silvered mirror.
+Participants began each trial by moving their cursor (purple) into the start position (solid white circle).
+At the start of the trial (0 ms), they heard a tone and saw two targets (white rings) and a timing bar (white rectangle) appear on the screen.
+During each trial, a stimulus (yellow cursor) would move quickly in a straight line to one of the two targets.
+Participants were instructed to reach the same target as the stimulus within a time constraint of 1500ms.
+This time constraint was visually represented with a timing bar (white rectangle) that decreased in width according to the elapsed time.
+\textbf{B)} A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint.
+A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
+A trial was considered an indecision and the participant received 0 points if they failed to reach a target within the time constraint.
+\textbf{C)} Stimulus movement onset on each trial was randomly drawn from a specific probability distribution in each condition.
+Using a within experimental design, we manipulated the mean (early, middle, late) and standard deviation (low, high) of the stimulus movement onset probability distribution.
+For the main manuscript we focus on results for the low variance conditions, with high variance conditions results shown in \boldblue{Supplementary A.}}
+\end{figure}
+
 For each trial within a condition, the stimulus movement onset was drawn from the same normal distribution.
-Using a 3 x 2 within experimental design (Fig.
-1C), in separate blocks we manipulated the stimulus movement onset mean (early mean = 1000 ms, middle mean = 1100 ms, late mean = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms).
-For the purposes of the main manuscript we focus on the results of the low variance conditions, but report the findings for the high variance conditions in Supplementary A.
+Using a 3 x 2 within experimental design (\boldblue{Fig.
+1C}), in separate blocks we manipulated the stimulus movement onset mean (early mean = 1000 ms, middle mean = 1100 ms, late mean = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms).
+For the purposes of the main manuscript we focus on the results of the low variance conditions, but report the findings for the high variance conditions in \boldblue{Supplementary A}.
 
-\noindent\textbf{\textcolor{mydarkblue}{{Participant Timing Behaviour}}}
-\vspace{2mm}
-
-Participant movement onsets for the low variance condition are shown in Fig.
-2A, We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
+\textbf{{{Participant timing behaviour.}}}
+Participant movement onsets for the low variance condition are shown in \boldblue{Fig.
+2A}, We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
 There was no significant interaction between stimulus movement onset mean and variance (F[1.66,31.47], p = 0.565).
-When collapsed across low and high variance, participant movement onsets were significantly greater in the middle mean conditions compared to the early mean conditions (p = 0.014, $\hat{\theta}$=72.5 \%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
-Again when collapsed across low and high variance, participant movement onset significantly decreased from the middle mean conditions to the late mean conditions (p = 0.018, $\hat{\theta}$=62.5\%).
+When collapsed across low and high variance, participant movement onsets were significantly greater in the middle mean conditions compared to the early mean conditions (p = 0.014, $\hat{\theta}$ = 72.5 \%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
+Again when collapsed across low and high variance, participant movement onset significantly decreased from the middle mean conditions to the late mean conditions (p = 0.018, $\hat{\theta}$ = 62.5\%).
 Here, an earlier participant movement onset in the late mean condition suggests that participants attempted to wait and react to the stimulus, but ended up guessing.
 
-Participant movement onset standard deviation for the low variance conditions are shown in Fig.
-2B.
+Participant movement onset standard deviation for the low variance conditions are shown in \boldblue{Fig.
+2B}.
 There was a main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) of the stimulus movement onset, and no significant interaction (F[1.98, 37.58], p = 0.097).
@@
 
-\noindent\textbf{\textcolor{mydarkblue}{{Participants are suboptimal and excessively indecisive.}}}
+% Figure 3 Model Outputs and Data
+\begin{figure}[H]
+    \begin{minipage}[c][\pdfpageheight][t]{0.5\textwidth}
 
-We calculated the indecisions (Fig.
-2C), wins (Fig.
-2D), and incorrects (Fig.
-2E) for each of the experimental conditions.
-Participants displayed a high proportion of indecisions.
+        \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}
+    \end{minipage}\hfill
+    \begin{minipage}[c][\pdfpageheight][t]{0.5\textwidth}
+        \caption{
+          \textbf{Behaviour Results}: \textbf{A)} Participant movement onset, \textbf{B)} participant movement onset standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects are shown for each condition.
+In our high time pressure task, participants made a high proportion of indecisions.
+Open circles are individual participant data.
+Filled icons are the predicted behavior of the three models, see legend for detail.
+Interestingly, we also found that the average win percentage (41.25\%) was significantly below the 50\% chance level (p < 0.001) in the late mean condition, clearly demonstrating suboptimal behaviour.
+Critically, participants would have earned more points if they had simply guessed earlier on all trials, rather than attempting to react to the stimulus.
+Model Results: Only the Partial Switch Time Model, which had only a partial representation of the time delay and uncertainty when switching from reacting to guessing, was able to predict the indecisions and a suboptimal win rate (below 50\%) in the late mean condition.
+See \boldblue{Fig.
+3} for the time varying model predictions for the late mean condition.
+Collectively, our findings show that humans are suboptimal and excessively indecisive.}
+    \end{minipage}
+\end{figure}
+
+\textbf{{{Participants are suboptimal and excessively indecisive.}}}
+We calculated the indecisions (\boldblue{Fig.
+2C}), wins (\boldblue{Fig.
+2D}), and incorrect decisions (\boldblue{Fig.
+2E}) for each of the experimental conditions.
+Participants displayed a substantial number of indecisions.
 The median percentage of indecisions was 15.0\% [range: 0.0 - 93.8\%] across all conditions, with the late mean low variance condition having a median percentage of indecisions of 19.4\% [range: 1.2\%, 93.8\%].
-We found a significant interaction between stimulus movement onset and variance for indecisions (F[1.571, 28.781] = 5.58, p = 0.013).
-In low variance conditions, participants made significantly more indecisions in the middle mean condition than the early mean condition (p<0.001, $\hat{\theta}$ = 85.0\%; Fig.
-2C).
+We found a significant interaction between stimulus movement onset and variance for indecisions (F[1.57, 28.78] = 5.58, p = 0.013).
+In low variance conditions, participants made significantly more indecisions in the middle mean condition than the early mean condition (p<0.001, $\hat{\theta}$ = 85.0\%; \boldblue{Fig.
+2C}).
 Additionally, participants made significantly more indecisions in the late mean condition compared to the early mean condition (p<0.004, $\hat{\theta}$ = 80.0\%).
 
-The win percentage across all conditions was 56.25\% (range: 6.2\%, 93.8\%; Fig.
-2D].
-We found a significant interaction between stimulus movement onset mean and variance for wins (F[1.542, 29.296] = 23.73, p<0.001).
-We found that the late mean condition had significantly less wins than the early mean condition (p < 0.001, $\hat{\theta}$ = 95.0\%).
-Interestingly, in the late mean condition we found that the average win percentage was significantly below the 50\% chance level (p<0.001; $\hat{\theta}$=95.0\%), which was true for 19 out of 20 participants.
+The win percentage across all conditions was 56.25\% (range: 6.2\%, 93.8\%; \boldblue{Fig.
+2D}).
+We found a significant interaction between stimulus movement onset mean and variance for wins (F[1.54, 29.30] = 23.73, p<0.001).
+The late mean condition had significantly less wins than the early mean condition (p < 0.001, $\hat{\theta}$ = 95.0\%).
+Interestingly, in the late mean condition we found that the average win percentage was significantly below the 50\% chance level (p<0.001; $\hat{\theta}$ = 95.0\%), which was true for 19 out of 20 participants.
 Since guessing on every trial would lead to a win percentage of 50\%, the only way participants would be below chance is if they are excessively indecisive.
-The incorrect percentage across all conditions was 26.3\% [range: 0.0\%, 57.5\%; Fig.
-2E].
-We found significant interactions between stimulus movement onset mean and variance for incorrects (F[1.658,31.508]=3.72, p=0.033).
+The incorrect percentage across all conditions was 26.3\% [range: 0.0\%, 57.5\%; \boldblue{Fig.
+2E}].
+We found significant interactions between stimulus movement onset mean and variance for incorrect decisions (F[1.66,31.51]=3.72, p=0.033).
 Participants displayed a greater percentage of incorrect decisions in the late mean condition than the early mean condition (p < 0.001, $\hat{\theta}$ = 92.5\%).
 
-\noindent\textbf{\textcolor{mydarkblue}{{Decision making model.}}}
-
+\noindent\textbf{{{Decision-making model.}}}
 In our task, participants must make a decision of whether to react to the stimulus or guess.
-For Experiment 1, we tested three different models:  i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (Fig.
-3, left column).
-The decision policy of these models considers the expected value ($\mathbb{E[R|\tau]}$) to determine the time ($\tau$) to transition from reacting to guessing.
+For \boldblue{Experiment 1}, we tested three different models:  i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
+3}, left column).
+The decision policy of all models considers the expected value ($\mathbb{E}[R|\tau]$) to determine the time ($\tau$) to transition from reacting to guessing.
 Expected value is defined as
@@
 \begin{align}
-    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
+    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision},
 \end{align}
 
-where ($P(Win|\tau)$) is the probability of a win, ($P(Incorrect|\tau)$) probability of an incorrect, and ($P(Indecision|\tau)$) is the probability of an indecision.
-$R_{Win} = 1$, $R_{Incorrect} = 0$, and ($R_{Indecision} = 0$ correspond to the reward structure of the task (Fig.
-1B).
-The decision policy of each model maximized expected reward to determine the optimal time to transition from reacting to guessing, $\tau^*$, according to
+\noindent where $P(Win|\tau)$ is the probability of a win, $P(Incorrect|\tau)$ is the probability of an incorrect, and $P(Indecision|\tau)$ is the probability of an indecision.
+$R_{Win} = 1$, $R_{Incorrect} = 0$, and ($R_{Indecision} = 0$ correspond to the reward structure of the task (\boldblue{Fig.
+1B}).
+The decision policy of each model maximized expected reward to determine the optimal time to transition from reacting to guessing ($\tau^*$) according to
 
 \begin{equation}
-    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
+    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)].
 \end{equation}
 
-Each model has varying knowledge of the different parameters (Fig.
-3, left column).
+Each model has varying knowledge of the different parameters (\boldblue{Fig.
+3}, left column).
 A model can have full knowledge or partial knowledge of a particular parameter.
@@
 With partial knowledge, the decision policy utilizes its partial and imperfect representation of the parameter.
-Here the idea is that a human may not have a perfect representation of some parameter when determining a transition time, even though that particular parameter will still influence behaviour.
-All model parameter values are shown in Supplementary B.
+Here the idea is that a human may have an imperfect representation of some parameter when determining a transition time, even though that particular parameter will still influence behaviour.
+As an example, one could plan for only some portion of a time delay, but then end up deciding too late because they did not fully account for the entire time delay.
+All model parameter values are shown in \boldblue{Supplementary B}.
 
-\noindent\emph{\textcolor{mydarkblue}{{No Switch Time Model}}}
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 1]{figures/model_diagram.png}
 
-We first considered a model that incorporated various time delays and temporal uncertainties from sources previously identified in the literature: response time, neuromechanical delay, movement time, stimulus movement onset, and timing uncertainty.
+  \caption{%
+    \boldblue{Models.} No Switch Time Model (\textbf{top row}, light grey), Full Switch Time Model (\textbf{middle row}, dark grey), and Partial Switch Time Model (\textbf{bottom row}, black).
+Each decision policy maximizes reward to select a time to transition from reacting to guessing.
+The decision policy of each model has different knowledge, full or partial, of the delays and uncertainties associated with the various parameters (e.g., response time, switch time).
+\textbf{Top Row)} The No Switch Time Model (light grey) has full knowledge of all its model parameters.
+However, it does not include the potential delay and uncertainty when switching from reaching to guessing, which we term ‘switch time’.
+\textbf{Middle Row}) The Full Switch Time Model (dark gray) has knowledge of all model parameters, including switch time (bright green).
+\textbf{Bottom Row)} Finally, the Partial Switch Time Model (black) has knowledge of several of the model parameters, but is only partially aware of the stopping time uncertainty and the switch time (delay and uncertainty).
+Only the Partial Switch Time Model is able to capture the participant target reach times (pink) in the late mean condition (stimulus movement onset; blue), allowing it to explain indecisions (\boldblue{Fig.
+2C}) and suboptimal win rates (\boldblue{Fig.
+2D}).
+    }
+\end{figure}
+
+\noindent\emph{{No Switch Time Model}}
+
+\noindent We first considered a model that incorporated various time delays and temporal uncertainties from sources previously identified in the literature: response time, neuromechanical delay, movement time, stimulus movement onset, and timing uncertainty.
 Note, unlike the other models we will address below, this model did not consider a `switch time’ delay and uncertainty because it was not considered in past literature.
@@
 
-In the late mean low variance condition, the No Switch Time Model underestimated participant movement onset (Fig.
-2A), underestimated indecisions (Fig.
-2C), and overestimated wins (Fig.
-2D).
+In the late mean low variance condition, the No Switch Time Model underestimated participant movement onset (\boldblue{Fig.
+2A}), underestimated indecisions (\boldblue{Fig.
+2C}), and overestimated wins (\boldblue{Fig.
+2D}).
 During this condition, participants displayed 19\% indecisions on average and a win percentage significantly below chance.
@@
 
-\noindent\emph{\textcolor{mydarkblue}{{Full Switch Time Model}}}
+\noindent\emph{{{Full Switch Time Model}}}
 
-Next we considered a model that additionally incorporated the potential existence of a switch time delay and uncertainty when transitioning from reacting to guessing.
+\noindent Next we considered a model that additionally incorporated the potential existence of a switch time delay and uncertainty when transitioning from reacting to guessing.
 For this Full Switch Time Model, we assumed that the model had full knowledge of the time delay and uncertainty when switching from reacting to guessing.
 
-Yet, despite including switch time, the Full Switch Time Model also performed poorly when predicting participant movement onset (Fig.
-2A), indecisions (Fig.
-2C), and wins (Fig.
-2D) in the late mean condition.
+Yet, despite including switch time, the Full Switch Time Model also performed poorly in the late mean condition by under-predicting participant movement onset (\boldblue{Fig.
+2A}), being unable to predict indecisions (\boldblue{Fig.
+2C}), and not being able to predict less than 50\% wins (\boldblue{Fig.
+2D}).
 An explanation for why this model did not do well to explain indecisions is that humans may not have full knowledge of this potential switch time delay and uncertainty.
 
-\noindent\emph{\textcolor{mydarkblue}{{Full Switch Time Model}}}
-Finally, we considered a model that had only partial knowledge of a potential switch time delay and uncertainty when transitioning from reaching to guessing.
+\noindent\emph{{{Partial Switch Time Model}}}
+
+\noindent Finally, we considered a model that had only partial knowledge of a potential switch time delay and uncertainty when transitioning from reaching to guessing.
 That is, this model specifically tests whether humans have an imperfect representation of a switch time delay and uncertainty.
 The model also had partial knowledge of timing uncertainty, which the fitting procedure found to further improve model fits.
-The Partial Switch Time Model was able to replicate all aspects of behaviour (Fig.
-2).
-Crucially, it was also able to capture suboptimal behaviour in the late mean condition, where we found that an excessive percentage of indecisions (Fig.
-2C, Fig.
-3) led to a lower than chance win percentage (Fig.
-2D).
+The Partial Switch Time Model was able to replicate all aspects of behaviour (\boldblue{Fig.
+2}).
+Crucially, it was able to capture suboptimal behaviour in the late mean condition, where we found that an excessive percentage of indecisions (\boldblue{Fig.
+2C}, \boldblue{Fig.
+3}) led to a lower than chance win percentage (\boldblue{Fig.
+2D}).
 
-\textbf{\textcolor{mydarkblue}{{Experiment 1}}}
 \vspace{2mm}
+\SubSectionHeader{Experiment 2}
 
-Our behavioural findings in Experiment 1 demonstrated that participants were suboptimal decision makers.
-Through our modelling efforts, we were able to capture this suboptimal decision making by including a switch time delay and uncertainty when transitioning from reacting to guessing.
+\noindent Our behavioural findings in \boldblue{Experiment 1} demonstrated that participants were suboptimal decision makers.
+Through our modelling efforts, we were able to capture this suboptimal decision-making by including a switch time delay and uncertainty when transitioning from reacting to guessing.
 The switch time delay and uncertainty were only partially represented by the Partial Switch Time Model when determining the optimal time to switch from reacting and guessing.
 However, we are not aware of any work that considers the temporal time delays and uncertainty associated with switching from reacting to guessing within a trial.
-Thus, the goal of Experiment 2 was to determine if there is indeed a switch delay and uncertainty that occurs when humans transition from reacting to guessing.
+The goal of \boldblue{Experiment 2} was to determine if there is indeed a switch delay and uncertainty that occurs when humans transition from reacting to guessing.
 
-\noindent\textbf{\textcolor{mydarkblue}{{Experimental Design.}}}
+\textbf{Experimental Design}.
 For all conditions, participants controlled a visible cursor that was aligned with their hand position.
@@
 Participants could experience two trial types: react trials or guess trials.
-In the react trials, participants saw the stimulus move and were instructed to as quickly as possible follow the stimulus to one of the targets (Fig.
-4A).
+In the react trials, participants saw the stimulus move and were instructed to as quickly as possible follow the stimulus to one of the targets (\boldblue{Fig.
+4A}).
 In the guess trials, participants saw the stimulus disappear from the start circle.
-They were instructed to guess one of the two targets as quickly as possible (Fig.
-4B).
+They were instructed to guess one of the two targets as quickly as possible (\boldblue{Fig.
+4B}).
 Following trial onset, the movement or disappearance of the stimulus was drawn from a normal distribution with a mean of 800ms and a standard deviation of 50ms.
-There were three experimental conditions (Fig.
-4C): the react or guess condition, the only react condition, and the only guess condition.
+There were three experimental conditions (\boldblue{Fig.
+4C}): the react or guess condition, the only react condition, and the only guess condition.
 In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 1]{figures/exp2_design.png}
+
+  \caption{\boldblue{Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1.
+\textbf{A)} Participants responded to two different types of stimuli.
+In the react trials (pink), the stimulus (yellow cursor) would move to one of the two potential targets.
+Participants were instructed to reach the same target as the stimulus as quickly as possible.
+\textbf{B)} In the guess trials (blue), the stimulus disappeared from the start position.
+Once the stimulus disappeared, participants were instructed to guess which target the stimulus would appear in and select that target as quickly as possible.
+After the participant reached the target, the stimulus’s cursor would appear in one of the targets.
+\textbf{C)} We had three experimental conditions.
+In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+Participants were informed that the stimulus would either move to one of the targets or disappear.
+In the only react condition, participants were informed that the stimulus would alway move to one of the two targets (50 react trials and 0 guess trials).
+They were also told that the stimulus would not disappear.
+In the only guess condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
+They were also informed the stimulus would not move.
+}
+\end{figure}
+
 \textbf{Response Time}.
-Average participant response times are shown for react and guess trials for each condition are shown in Fig.
-5A.
-As expected, we found significantly greater response times for guess trials in the react or guess condition when compared to the only guess condition (p < 0.001, $\hat{\theta}$ = XX.X), which was displayed by all participants.
+Average participant response times are shown for react and guess trials for each condition are shown in \boldblue{Fig.
+5A}.
+As expected, we found significantly greater response times for guess trials in the react or guess condition when compared to the only guess condition (p < 0.001, $\hat{\theta}$ = 100.0\%), which was displayed by all participants.
 These comparatively greater response times for guess trials in the react or guess condition supports the idea that there is a switch time delay when transitioning from reacting to guessing.
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/exp2_reaction_panel_mean_sd.png}
+    \caption{\textbf{A)} Response time (y-axis) for each of the experimental conditions (x-axis).
+Participants had significantly greater response times for guess trials in the react or guess condition compared to the only guess condition.
+Critically, this result suggests there is an additional delay when participants initially wait to react to the stimulus and then switch to guessing.
+\textbf{B)} Standard deviation of response times (y-axis) was used to quantify participant response time uncertainty for each of the experimental conditions (x-axis).
+Participants had significantly greater response time uncertainty for guess trials in the react or guess condition than in the only guess condition.
+Similarly, this finding suggests there is additional uncertainty when participants initially wait to react to the stimulus and then switch to guessing.
+These results provide empirical evidence for an additional time delay and temporal uncertainty when switching from reacting to guessing.}
+\end{figure}
+
 Likewise, if there was a switch time delay we would also expect a comparatively greater response time difference between guess and react trials in the react or guess condition, compared to the response time difference between only guess trials and only react trials [i.e., guess - react (react or guess condition) > guess - react (guess only and react only conditions)].
-Indeed, we found a greater response time difference between guess and react trials in the react or guess condition, compared to the response time difference between the guess only and react only conditions (p < 0.001, $\hat{\theta}$ = XX.X, Fig.
-5A).
-Moreover this result shows that the response time differences between guess and react trials are not due to any dual tasking (Selst and Jolicoeur 1997) or task switching between trials (Monsell 2003, Kiesel et al.
-2010, Rubinstein 2001), which would not show this relative difference  [i.e., guess - react (react or guess condition) = guess - react (guess only and react only conditions)].
+Indeed, we found a greater response time difference between guess and react trials in the react or guess condition, compared to the response time difference between the guess only and react only conditions (p < 0.001, $\hat{\theta}$ = 66.7\%; \boldblue{Fig.
+5A}).
+This result shows that the response time differences between guess and react trials are not due to dual tasking \autocite{van_selst_decision_1997} or task switching between trials \autocite{monsell_task_2003,kiesel_control_2010,rubinstein_executive_2001}, which would not show this relative difference  [i.e., guess - react (react or guess condition) = guess - react (guess only and react only conditions)].
 
 \textbf{Response Time Uncertainty}.
-We also examined participant response time uncertainty, calculated as the standard deviation (Fig.
-5B).
-We found that response time uncertainty on guess trials was significantly greater in the react or guess condition compared to the only guess condition (p < 0.001).
+We also examined participant response time uncertainty, calculated as the standard deviation (\boldblue{Fig.
+5B}).
+Response time uncertainty on guess trials was significantly greater in the react or guess condition compared to the only guess condition (p < 0.001).
 This result suggests that there is additional uncertainty when participants switch from reacting to guessing.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Discussion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\noindent\textbf{\large\textcolor{mydarkblue}{Discussion}}
+\vspace{2mm}
+\SectionHeader{Discussion}
 
-We found that participants were suboptimal decision-makers and excessively indecisive, leading to a below chance win rate.
+\noindent Participants were suboptimal decision-makers and excessively indecisive in a high time pressure task.
 Computational modelling suggested that excessive indecisions were a result of failing to account for a delay and uncertainty associated with switching from reacting to guessing.
@@
 
-In Experiment 1, participants were required to reach the same target as a cursor before a time constraint.
+In \boldblue{Experiment 1}, participants were required to reach the same target as a cursor before a time constraint.
 Within a trial, they could either react to a moving stimulus or guess which of the two targets would be correct.
 We saw that 95\% of participants had a win rate less than chance (50\%) in the late mean condition, which corresponded with an average of 19.4\% indecisions.
-This proportion of indecisions aligns with our recent prior work that examined competitive human-human decision making with a high time pressure (Lokesh et al.
-2022).
+This proportion of indecisions aligns with our recent prior work that examined competitive human-human decision-making with a high time pressure\autocite{lokesh_humans_2022}.
 In this competitive task, one participant attempted to reach the same target as their opponent, while the other tried to reach the opposite target within a time constraint.
@@
 Our results would also suggest that participants waited to acquire sensory information of when the stimuli would move.
-Moreover, building upon the previous work (Lokesh et al.
-2022), our work also suggests that a key contributor leading to excessive indecisions is failing to account for the time delay and temporal uncertainty when switching from reacting to guessing.
+Moreover, building upon Lokesh and colleagues (2022), our work also suggests that a key contributor leading to excessive indecisions is failing to account for the time delay and temporal uncertainty when switching from reacting to guessing.
 
-Past work has suggested that humans can nearly optimally account for time delays and temporal uncertainty when performing decision making (Balci Risk assessment in man and mouse, Jazayeri and Shadlen 2010.
-Balci Optimal temporal risk assessment) and movement tasks (Hudson et al.
-2008, Battaglia and Schrater 2007, Dean 2007) when attempting to maximize reward.
-Here we considered two optimal models, the No Switch Time Model and Full Switch Time Model, which both had full knowledge of the inputted time delays and temporal uncertainties.
+Past work has suggested that humans can nearly optimally account for time delays and temporal uncertainty when performing decision-making \autocite{balci_risk_2009,jazayeri_temporal_2010,balci_optimal_2011} and movement tasks \autocite*{hudson_optimal_2008,battaglia_humans_2007,dean_trading_2007} when attempting to maximize reward.
+Here we considered two optimal models, the No Switch Time Model and Full Switch Time Model, which both had full knowledge of all available time delays and temporal uncertainties.
 Interestingly, both the No Switch Time Model and Full Switch Time Model showed that even when fully accounting for all sensorimotor delays and uncertainties, indecisions were a part of an optimal strategy in all but one of the six conditions.
-In other words, given the inherent delays and uncertainty of our nervous system (Wolpert Faisal), an optimal strategy of earning maximal reward may involve indecisive behaviour on some proportion of trials.
+In other words, given the inherent delays and uncertainty of our nervous system\autocite{faisal_noise_2008}, an optimal strategy of earning maximal reward may involve indecisive behaviour on some proportion of trials.
 We are unaware of any work in the literature suggesting that some level of indecisions may be optimal.
-Even though making some indecisions can be optimal, our results in Experiment 1 were in support of the idea that humans are suboptimal.
+Even though making some indecisions can be optimal, our results in \boldblue{Experiment 1} were in support of the idea that humans are suboptimal.
 Specifically, in the late mean condition, we found that humans were suboptimal since they had a win percentage lower than chance, which arose from an excessive number of indecisions.
@@
 The Partial Switch Time Model supports the notion that humans suboptimally select decision times when under high time pressures.
-An interesting future direction would be to test whether different reward structures, such as placing a higher reward on wins or punishing indecisions (Kahneman and Tversky 2013, Roth et al.
-2024, Galea et al.
-2015), would provide a means to reduce an excessive number of indecisions.
-The combined empirical evidence of Experiment 1 and computational modelling suggested the existence of time delay and uncertainty when switching from reacting to guessing.
+An interesting future direction would be to test whether different reward structures, such as placing a higher reward on wins or punishing indecisions \autocite{kahneman_prospect_2013,roth_reinforcement-based_2023,roth_punishment_2024, galea_dissociable_2015}, would provide a means to reduce an excessive number of indecisions.
+
+The combined empirical evidence of \boldblue{Experiment 1} and computational modelling suggested the existence of time delay and uncertainty when switching from reacting to guessing.
 However, we were unaware of any work in the literature to support this idea.
-In Experiment 2 we tested the notion of a more delayed and uncertain response time when switching from reacting to guessing, compared to guessing by itself.
+In \boldblue{Experiment 2} we tested the notion of a more delayed and uncertain response time when switching from reacting to guessing, compared to guessing by itself.
 Indeed, we found that when participants had to switch from reacting to guessing, their response times were significantly slower and more uncertain than when they only had to guess.
@@
 Dutilh and colleagues (2011) explored the idea of switching between a stimulus controlled (i.e.
-react) mode and a guess mode between trials.
+react) mode and a guess mode between trials \autocite{dutilh_phase_2011}.
 In their task, participants were required to discriminate between a word stimuli from a non-word stimuli by selecting one of two buttons during a two-alternative forced choice task.
@@
 That is, participants are more likely to stay in their current mode than switch modes.
-They also highlighted that classical decision-making models, such as drift-diffusion models (Bogacz, Ratcliff) or more recently the urgency-gating model (Cisek, Thura,derosiere thura cisek duque), do not consider different modes of reacting or guessing.
+They also highlighted that classical decision-making models, such as drift-diffusion models \autocite{ratcliff_modeling_2018} or more recently the urgency-gating model \autocite{cisek_decisions_2009,derosiere_trading_2021,thura_decision_2012} do not consider different modes of reacting or guessing.
 Extending upon the findings of Dutilh and colleagues (2011) that examined between trial mode switching, our work suggests that humans switch between react and guess modes within a trial.
@@
 To our knowledge, it is unknown how different modes would be represented in the nervous system.
-One possibility is that the different modes represent different attractors from a neural dynamical systems perspective (Erlhagen and Schoner 2002, wang 2008 Decision making in recurrent, Churchland et al.
-2012, Shenoy Sahani Churchland 2013), which would be an interesting avenue of investigation.
+One possibility is that the different modes represent different attractors from a neural dynamical systems perspective \autocite{erlhagen_dynamic_2002,wang_decision_2008,churchland_neural_2012,shenoy_cortical_2013}, which would be an interesting avenue of investigation.
 
-We found in Experiment 2 that participant response times were more delayed by approximately 75ms during guess trials in the react or guess condition, compared to guess only trials.
+We found in \boldblue{Experiment 2} that participant response times were more delayed by approximately 75ms during guess trials in the react or guess condition, compared to guess only trials.
 Moreover, the response time difference between guess and react trials in the react or guess condition are significantly greater than the response time difference between the guess only and react only conditions.
 Collectively, these results suggest that participants have an initial preference to react, before having to switch to a guess in the react or guess condition.
-In this experiment the behaviour may be explained by a strong preference to react since it yields a 100\% success probability, as opposed to guessing that on average yields a 50\% success probability.
+In this experiment behaviour may be explained by a strong preference to react since it yields a 100\% success probability, as opposed to guessing that on average yields a 50\% success probability.
 It would be interesting for future studies to examine if they can manipulate the magnitude or probability of reward to switch a preference between reacting or guessing, and how this impacts indecisive behaviour.
@@
 A limitation of the commonly used two-alternative forced choice task without a time constraint is that the participant or animal must select one of two potential options, which does not allow for indecisive behaviour.
-For decision making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis (Forstmann et al.
-2008, Diederich a further test of sequential, Phillastides et al.
-2011, Wu et al.
-2016, Dambacher and Hubne 2015s).
-Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions (Karsilar Balci 2014 deadline paper, Farasahi 2015, …s).
+For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis \autocite{forstmann_striatum_2008,diederich_further_2008,wu_capacity_2016,dambacher_time_2015}.
+Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite{karsilar_speed_2014,farashahi_dynamic_2018}.
 However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
 
-Here we showed in our first experiment that humans are excessively indecisive under time constraints.
-Our computational work and second experiment suggest that indecisive behaviour can occur by not accounting for the time delays and temporal uncertainty associated with switching from reacting to guessing.
+Here we showed in our first experiment humans are excessively indecisive under time constraints.
+Computational work and second experiment suggest that indecisive behaviour can occur by not accounting for the time delays and temporal uncertainty associated with switching from reacting to guessing.
 Our experimental and theoretical approach offers a new paradigm to study indecisions, which has received surprisingly little attention despite its ecological relevance.
-Our work advances how indecisive behaviour arises, which is important to understand when attempting to avoid potentially catastrophic events during high time pressure scenarios.
+This work advances how indecisive behaviour arises, which is important to understand when attempting to avoid potentially catastrophic events during high time pressure scenarios.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\noindent\textbf{\large\textcolor{mydarkblue}{Methods}}
+\vspace{2mm}
+\SectionHeader{Methods}
 
@@
 
-44 participants participated across two experiments: 20 individuals participated in Experiment 1 and 24 individuals participated in Experiment 2.
+\noindent 44 participants participated across two experiments 20 individuals participated in \boldblue{Experiment 1} and 24 individuals participated in \boldblue{Experiment 2}.
 All participants reported they were free from musculoskeletal injuries, neurological conditions, or sensory impairments.
 In addition to a base compensation of \$5.00, we informed them they would receive a performance-based compensation of up to \$5.00.
-Participants received the full \$10.00 once they completed the experiment, irrespective of their performance.
+Participants received the full \$10.00 once they completed the experiment irrespective of their performance.
 All participants provided written informed consent to participate in the experiment and the procedures were approved by the University of Delaware’s Institutional Review Board.
@@
 
-For both experiments we used an end point KINARM robot (Fig.
-1A; BKIN Technologies, Kingston, ON).
+\noindent For both experiments we used an end point KINARM robot (\boldblue{Fig.
+1A}; BKIN Technologies, Kingston, ON).
 Each participant was seated on an adjustable chair in front of one of the end-point robots.
@@
 A semi-silvered mirror blocked the vision of the upper limb and displayed virtual images (e.g., targets, cursors) from an LCD screen.
-In all experiments, the cursor was aligned with the position of the hand.
+In all experiments the cursor was aligned with the position of the hand.
 The semi-silvered mirror occluded the vision of their hand.
@@
 
-\noindent\textbf{\large\textcolor{mydarkblue}{Experiment 1 Design}}
+\vspace{2mm}
+\noindent\textbf{\large\textcolor{mydarkblue}Experiment 1 Design}
 
-The goal of Experiment 1 was to study the influence of stimulus onset on indecisive behaviour.
-To begin the task, the participant moved their cursor (white circle, 1 cm diameter) into a start position (white circle, 1 cm diameter) (Fig.
-1A).
+\noindent The goal of \boldblue{Experiment 1} was to study the influence of stimulus onset on indecisive behaviour.
+To begin the task, the participant moved their cursor (white circle, 1 cm diameter) into a start position (white circle, 1 cm diameter) (\boldblue{Fig.
+1A}).
 Then a stimulus (yellow cursor, 1 cm diameter) appeared in the start position.
@@
 A trial was considered an indecision if they failed to reach a target within the time constraint.
-Participants earned one point for a win, zero points for being incorrect, and zero points for making an indecision (Fig.
-1B).
+Participants earned one point for a win, zero points for being incorrect, and zero points for making an indecision (\boldblue{Fig.
+1B}).
 
 For each trial within a condition, the stimulus movement onset was drawn from the same normal distribution.
-Using a 3 x 2 within experimental design, we manipulated the stimulus movement onset mean (early mean = 1000 ms, middle mean = 1100 ms, late mean = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms) that resulted in 6 experimental conditions (Fig.
-1C).
+Using a 3 x 2 within experimental design, we manipulated the stimulus movement onset mean (early mean = 1000 ms, middle mean = 1100 ms, late mean = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms) that resulted in 6 experimental conditions (\boldblue{Fig.
+1C}).
 Each condition was performed separately using a block design.
@@
 Condition order was randomized across participants.
-Prior to Experiment 1, participants performed two separate tasks to estimate response time (response time task; Supplementary C) and timing uncertainty (timing uncertainty task; Supplementary D).
+
+Prior to \boldblue{Experiment 1}, participants performed two separate tasks to estimate response time (response time task; \boldblue{Supplementary C}) and timing uncertainty (timing uncertainty task; \boldblue{Supplementary D}).
 We counterbalanced the order of the response time and timing uncertainty tasks.
 
-\noindent\textbf{\large\textcolor{mydarkblue}{Experiment 2 Design}}
+\vspace{2mm}
+\noindent\textbf{\large\textcolor{mydarkblue} Experiment 2 Design}
 
-The goal of Experiment 2 was to test whether there is a time delay and uncertainty associated with switching from reacting to guessing.
+\noindent The goal of \boldblue{Experiment 2} was to test whether there is a time delay and uncertainty associated with switching from reacting to guessing.
 To investigate, participants began each trial by moving their cursor into a start position.
@@
 Here participants experienced two different types of trials: react trials or guess trials.
-The react trials consisted of the stimulus moving to one of the two targets (Fig.
-4A).
+The react trials consisted of the stimulus moving to one of the two targets (\boldblue{Fig.
+4A}).
 Participants were instructed to follow the stimulus as quickly as possible.
-The guess trials consisted of the stimulus disappearing from the start position (Fig.
-4B).
+The guess trials consisted of the stimulus disappearing from the start position (\boldblue{Fig.
+4B}).
 Participants were instructed to select the target they believed the stimulus would end up in as quickly as possible.
@@
 
-Using these react and guess trials, participants performed a within experimental design with three experimental conditions: react or guess condition, only react condition, and only guess condition.
+Using these react and guess trials, participants performed a within experimental design with three conditions: react or guess condition, only react condition, and only guess condition.
 In the react or guess condition, we pseudorandomly interleaved the 50 react trials and 50 guess trials.
@@
 
-\noindent\textbf{\large\textcolor{mydarkblue}{Data Analysis}}
+\vspace{2mm}
+\noindent\boldblue{\large{Data Analysis}}
 
-Kinematics were filtered using a dual-pass, low pass, second order Butterworth filter with a cutoff frequency of 14 Hz.
+\noindent Kinematics were filtered using a dual-pass, low pass, second order Butterworth filter with a cutoff frequency of 14 Hz.
 
-\underline{Experiment 1}
-\emph{Participant movement onset}: On each trial, we found when the time point where the participant hand velocity exceeded 0.05 m/s (Gribble 2003 A role for cocontraction, Calalo et al.
-2023).
+\noindent \boldblue{Experiment 1}
+
+\noindent \emph{Participant movement onset}: On each trial, we found when the time point where the participant hand velocity exceeded 0.05 m/s \autocite{gribble_role_2003,calalo_sensorimotor_2023}.
 The meantime point across all trials within a condition was used to estimate participant movement onset.
 
-\emph{Participant movement onset standard deviation}: Using all trials in a condition, we used the time point where the participant hand velocity exceeded 0.05 m/s to calculate the standard deviation of participant movement onsets for each condition.
+\noindent \emph{Participant movement onset standard deviation}: Using all trials in a condition, we used the time point where the participant hand velocity exceeded 0.05 m/s to calculate the standard deviation of participant movement onsets for each condition.
 
-\emph{Outcome metrics}: Win (\%): A trial was a win if participants reached the same target as the stimulus before the time constraint.
+\noindent \emph{Outcome metrics}: Win (\%): A trial was a win if participants reached the same target as the stimulus before the time constraint.
 Incorrect (\%): A trial was an incorrect if participants reached the opposite target as the stimulus before the time constraint.
@@
 
-\noindent\underline{Experiment 2}
+\noindent \boldblue{ Experiment 2}
 
-\emph{Response time}: Response times were calculated as the difference between participant movement onset and either the stimulus movement onset or stimulus disappearance time.
+\noindent \emph{Response time}: Response times were calculated as the difference between participant movement onset and either the stimulus movement onset or stimulus disappearance time.
 The mean time difference across all trials within a condition was used to estimate the participant response times.
@@
 
-\emph{Response time standard deviation}: We calculated the standard deviation of participant’s response times separately for react and guess trials.
+\noindent \emph{Response time standard deviation}: We calculated the standard deviation of participant’s response times separately for react and guess trials.
 
-\noindent\textbf{\textcolor{mydarkblue}{Statistics}}
+\noindent\boldblue{\large\textcolor{mydarkblue}{Statistics}}
 
-\noindent\emph{Experiment 1 and 2}
+\noindent{\boldblue{Experiment 1 and 2}}
 
-We used analysis of variance (ANOVA) as omnibus tests to determine whether there were main effects and interactions.
+\noindent We used analysis of variance (ANOVA) as omnibus tests to determine whether there were main effects and interactions.
 We report the Greenhouse-Geiser adjusted p-values and degrees of freedom.
-In Experiment 1 we used a 3 (mean: early, middle, late) x 2 (variance: low, high) repeated measures ANOVA for each dependent variable.
-In Experiment 2 we used a 2 (condition: interleaved react and guess, react or guess only) x 2 (trial type: react trials, guess trials) repeated measures ANOVA for each dependent variable.
-For both Experiments 1 and 2, we performed mean comparisons using nonparametric bootstrap hypothesis tests (n = 1,000,000).
+In \boldblue{Experiment 1} we used a 3 (mean: early, middle, late) x 2 (variance: low, high) repeated measures ANOVA for each dependent variable.
+In \boldblue{Experiment 2} we used a 2 (condition: interleaved react and guess, react or guess only) x 2 (trial type: react trials, guess trials) repeated measures ANOVA for each dependent variable.
+For both \boldblue{Experiment 1} and \boldblue{2}, we performed mean comparisons using nonparametric bootstrap hypothesis tests (n = 1,000,000) \autocite{hesterberg_bootstrap_2011,cashaback_dissociating_2017, cashaback_gradient_2019}.
 Mean comparisons were Holm-Bonferonni correct to account for multiple comparisons.
@@
 
-\SectionHeader{Main Figures}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figures/exp1_experimental_design.png}
+\fancyhead[L]{} % Need this because print bibliography is dumb and puts a REFERENCES in the left header
+\begin{nolinenumbers}
+    \definecolor{mydarkblue}{RGB}{0,51,102}
 
-%     \caption{\textbf{Experimental Design.} \textbf{A)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
-An LCD projected images (start position, targets) onto a semi-silvered mirror that occluded vision of the hand and upper arm.
-Participants began each trial by moving their cursor (purple) into the start position (solid white circle).
-They then heard a tone and saw two targets (white rings) and a timing bar (white rectangle) appear on the screen.
-During each trial, an stimulus (yellow) would move quickly in a straight line to one of the two targets.
-Participants were instructed to reach the same target as the stimulus within a time constraint of 1500ms.
-This time constraint was visually represented with a timing bar (white rectangle) that decreased in width according to the elapsed time.
-\textbf{B)} A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint.
-A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
-A trial was considered an indecision and the participant received 0 points if they failed to reach a target within the time constraint.
-\textbf{C)} Stimulus movement onset time on each trial was randomly drawn from a specific probability distribution in each condition.
-Using a within experimental design, we manipulated the mean and standard deviation of the stimulus movement onset time probability distribution for each of the following six conditions: 1) early mean low variance, 2) middle mean low variance, 3) late mean low variance, 4) early mean high variance, 5) middle mean high variance, 6) late mean high variance.
-%     }
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
+    \printbibliography[title=\LARGE\textcolor{mydarkblue}{References}]
+\end{nolinenumbers}
 
-%     \caption{\textbf{Timing Behaviour.} \textbf{A)} Average participant movement onset time (y-axis) for each of the six experimental conditions (x-axis).
-\textbf{B)} Corresponding participant movement onset time (y-axis) for the three different mean onset times (x-axis) when collapsed across variance.
-During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint.
-For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions.
-Waiting longer to react and/or late guessing led to longer movement onset times.
-In the late mean condition participants either guessed early to avoid a late reaction to the stimulus, or waited to react but ended up producing a late guess.
-The combination of early and late guesses led to an early movement onset time compared to the middle mean condition.
-For both the middle mean and late mean conditions, late guessing often led to indecisions (see Fig.
-3A).
-\textbf{C)} Participant movement onset time standard deviation (y-axis) for each of the six experimental conditions (x-axis).
-\textbf{D)} Corresponding participant movement onset time standard deviation (y-axis) for the three different mean onset times (x-axis), when collapsed across variance.
-In the late mean conditions, the combination of early and late guesses led to a larger participant movement onset time standard deviation compared to the early mean and middle mean conditions.
-Box and whisker plots display the 25th, 50th, and 75th percentiles.
-Open gray circles and connecting lines represent individual data.
-}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
-
-%     \caption{\textbf{Trial Outcomes.} \textbf{A)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition.
-\textbf{A)} We found that the middle mean low variance and late mean low variance conditions had a significantly greater number of indecisions compared to the early mean low variance condition.
-That is, in the middle mean low variance and late mean low variance conditions, participants often waited to react to the stimulus but ended up guessing late.
-These late guesses often led to indecisions.
-\textbf{B)} Interestingly, we also found that the average win percentage (4X.X\%) was significantly below the 50\% chance level (p < 0.001) in the late mean low variance condition, clearly demonstrating suboptimal behaviour.
-Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the stimulus.
-Collectively, these results show that participants were suboptimal decision makers that led to excessively indecisive behaviour.}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/model_diagram.png}
-
-%     \caption{\textbf{Models.} \textbf{A)} Predicted target reach times from three models: No Switch Time Model (light gray), Known Switch Time Model (dark gray), and Unknown Switch Time Model (black).
-Stimulus movement onset time is shown in pink, which corresponds to the late mean low variance condition.
-The time constraint on the task is shown in purple.
-Predicted indecision proportion is the area shown in dark blue.
-The Unknown Switch Time Model (black) is the only model that predicts indecisions for the late mean low variance condition, aligning with the data (see Figure 5C).
-\textbf{B)} Each model has inputs that represent the delays and uncertainties inherent to the sensorimotor system and the stimulus movement onset distribution.
-The decision policy finds the stopping time that maximizes reward.
-Given that the stimulus has not yet moved, the stopping time represents the time that participants transition from reacting to guessing.
-It is important to note that each model will react to the stimulus if it moves prior to the stopping time.
-The decision policy accounts for only the known inputs to determine stopping time.
-The decision policy is unaware of the unknown inputs when determining the stopping time, but these unknown inputs still influence the model outputs.
-The No Switch Time Model (light gray) has knowledge of all its model inputs.
-However, it does not consider the potential delay and uncertainties associated with switching from reaching to guessing, which we term ‘switch time’.
-The Known Switch Time Model (dark gray) has knowledge of all model inputs, including the switch time.
-Finally, the Unknown Switch Time Model (black) has knowledge of several of the model inputs, but is unaware of decision uncertainty and the switch time.
-\textbf{C)} Outputs for each of the models.}
-% \end{figure}
-
-% % Figure 5 Model Outputs
-% \begin{figure}[H]
-%     \begin{minipage}[c]{0.67\textwidth}
-
-%         \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}
-%     \end{minipage}\hfill
-%     \begin{minipage}[c]{0.3\textwidth}
-%         \caption{
-%             Model Outputs: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{A)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
-The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the late mean low variance and late mean high variance conditions.
-Conversely, the Unknown Switch Time Model (black) is able to accurately predict the participant data for all conditions across all metrics.
-As a reminder, the Unknown Switch time Model does not account for the delay and uncertainties associated with switching from reacting to guessing.
-Critically, in \textbf{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the late mean low variance condition, whereas the other two models predict zero indecisions for that condition.
-Further, in \textbf{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the late mean low variance condition.
-Collectively, our findings show that humans are suboptimal and excessively indecisive, which can be captured by a model that does not account  for the delay and uncertainties associated with switching from reacting to guessing.
-%         } 
-%     \end{minipage}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/exp2_design.png}
-
-%     \caption{\textbf{Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1.
-\textbf{A)} Participants responded to two different types of stimuli.
-In the react trials (pink), the stimulus (yellow cursor) would move to one of the two potential targets.
-Participants were instructed to reach the same target as the stimulus as quickly as possible.
-\textbf{B)} In the guess trials (blue), the stimulus disappeared from the start position.
-Once the stimulus disappeared, participants were instructed to guess which target the stimulus would appear in and select that target as quickly as possible.
-After the participant reached the target, the stimulus’s cursor would appear in one of the targets.
-\textbf{C)} We had three experimental conditions.
-In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
-Participants were informed that the stimulus would either move to one of the targets or disappear.
-In the only react condition, participants were informed that the stimulus would alway move to one of the two targets (50 react trials and 0 guess trials).
-They were also told that the stimulus would not disappear.
-In the only guess condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
-They were also informed the stimulus would not move.
-}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/exp2_reaction_panel.png}
-
-%     \caption{S) Response time (y-axis) for each of the experimental conditions (x-axis).
-Participants had significantly greater response times for guess trials in the react or guess condition compared to the only guess condition.
-Critically, this result suggests there is an additional delay when participants initially wait to react to the stimulus and then switch to guessing.
-B) Interquartile range (IQR) of response times (y-axis) was used to quantify participants’ response time uncertainty for each of the experimental conditions (x-axis).
-Participants had significantly greater response time uncertainty for guess trials in the react or guess condition than in the only guess condition.
-Similarly, this finding suggests there is additional uncertainty when participants initially wait to react to the stimulus and then switch to guessing.
-Taken together, these results match the predictions of our model in Experiment 1, providing empirical evidence for an additional delay and uncertainty when switching from reacting to guessing.}
-% \end{figure}
-
-% \SectionHeader{Supplementary Figures}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/reaction_guess_decisions.png}
-
-%     \SuppCaption{Supplementary Figure 1.}{Reaction and Guess Decision Percentages for Experiment 1: Estimated percentage of reaction (pink) and guess (blue) decision percentages (y-axis) for each experimental condition (x-axis).
-During Experiment 1 participants were rewarded for successful trials and experienced a time constraint.
-Thus, we would expect participants to have faster reaction times in Experiment 1 than in the Reaction Time task (citation).
-To account for this, we adjusted participants’ reaction times by subtracting 25ms from their median reaction time in the Reaction Time task.
-A trial was a reaction decision if the difference between the stimulus’s movement onset time and participant’s movement onset time was greater than that participant’s adjusted reaction time.
-Conversely, a trial was a guess decision if the difference between the stimulus movement onset time and participant movement onset time was less than that participant’s adjusted reaction time.
-We found that participants guessed significantly more often as the stimulus’s mean movement onset time approached the time constraint.
-}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale = 1]{figures/model_losses.png}
-
-%     \SuppCaption{Supplementary Figure 2.}{Model Loss Comparison}
-% \end{figure}
-
-Hello \autocite{kording_bayesian_2006}
-
-% HEADINGS
-\fancyhead[R]{\emph{\textcolor{mydarkblue}{Indecisions arise from suboptimal switching behaviour}}}
-\fancyhead[L]{}
-\fancyfoot[C]{\textcolor{mydarkblue}{\thepage}}
-\begin{nolinenumbers}
-    \printbibliography[title= \large\textcolor{mydarkblue}{REFERENCES}]
-\end{nolinenumbers}
 \end{document}

### 2024-07-29 paper/supplementary.tex
almost done!

@@
 
-\newcommand{\SuppCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}\footnotesize}
-\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
-\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{black}{#1}}\normalsize }
+\newcommand\boldblue[1]{\textcolor{mydarkblue}{\textbf{#1}}}
+
+\newcommand{\SuppCaption}[2]{\noindent\boldblue{{#1}} {#2}\footnotesize}
+\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large\textcolor{mydarkblue}{#1}}\normalsize }
+\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{mydarkblue}{#1}}\normalsize }
+
+\renewcommand{\figurename}{Supplementary Figure}
 
@@
 % Condition variables
-% \def\emlv{\emph{early mean low variance}}
+% \def\emlv{\emph{\emph{early mean low variance}}}
 % \def\emhv{\emph{early mean high variance}}
@@
 % \def\mmhv{\emph{middle mean high variance}}
-% \def\lmlv{\emph{late mean low variance}}
+% \def\lmlv{\emph{\emph{late mean low variance}}}
 % \def\lmhv{\emph{late mean high variance}}
@@
     \caption{\textbf{Timing Behaviour.} A) Average participant movement onset (y-axis) for each experimental condition (x-axis).
-We found a significant main effect of stimulus movement onset mean (F[1.551,29.475] = 4.36, p = 0.030) and variance (F[1.000,19.000], p = 0.017)) on participant movement onset.
-There was no significant interaction (F[1.657,31.474], p = 0.565) B) Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance.
+We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset.
+There was no significant interaction (F[1.66,31.47], p = 0.565) B) Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance.
 During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint.
@@
 The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition.
-For both the middle mean and late mean conditions, late guessing often led to indecisions (see Fig.
-2).
+For both the middle mean and late mean conditions, late guessing often led to indecisions (see \boldblue{Fig.
+2}).
 C) Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis).
-We found a significant main effect of mean (F[1.383, 26.284], p = 0.018) and variance (F[1.000,19.000], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.978, 37.575], p = 0.097) D) Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance.
+We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) D) Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance.
 In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions.
@@
     \caption{\textbf{Trial Outcomes.} \textbf{A)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition.
-\textbf{A)} We found that the middle mean low variance and late mean low variance conditions had a significantly greater number of indecisions compared to the early mean low variance condition.
-That is, in the middle mean low variance and late mean low variance conditions, participants often waited to react to the stimulus but ended up guessing late.
+\textbf{A)} We found that the middle mean low variance and \emph{late mean low variance} condition had a significantly greater number of indecisions compared to the \emph{early mean low variance} condition.
+That is, in the middle mean low variance and \emph{late mean low variance} conditions, participants often waited to react to the stimulus but ended up guessing late.
 These late guesses often led to indecisions.
-\textbf{B)} Interestingly, we also found that the average win percentage (4X.X\%) was significantly below the 50\% chance level (p < 0.001) in the late mean low variance condition, clearly demonstrating suboptimal behaviour.
+\textbf{B)} Interestingly, we also found that the average win percentage (41\%) was significantly below the 50\% chance level (p < 0.001) in the \emph{late mean low variance} condition, clearly demonstrating suboptimal behaviour.
 Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the stimulus.
@@
 
+\vspace{2mm}
 \noindent\textbf{\large\textcolor{mydarkblue}{Supplementary B: Optimal Models}}
 
-We tested three different models to investigate the ability of participants to maximize reward during Experiment 1: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (Fig.
-2).
+We tested three different models to investigate the ability of participants to maximize reward during \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
+2}).
 Each model represents a different hypothesis on how humans time their decisions, which we address further below.
@@
 However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
-We modelled the time to switch from reacting to guessing as an optimal stopping problem.
-This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim (trommershauser) and reach timing (Hudson, Maloney, Landy 2008).
-Here a model represents a decision-maker that selects a stopping time, $\tau$.
-This stopping time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets.
-The optimal stopping time is determined from a decision policy that maximizes reward, given task constraints (i.e.
+We modelled the time to switch from reacting to guessing as an optimal transition problem.
+This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim \autocite{trommershauser_statistical_2003} and reach timing \autocite{hudson_optimal_2008}.
+Here a model represents a decision-maker that selects a transition time, $\tau$.
+This transition time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets.
+The optimal transition time is determined from a decision policy that maximizes reward, given task constraints (i.e.
 stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.
 
+\vspace{2mm}
 \noindent \emph{Model Parameters}
@@
 \noindent Here we define the parameters used for the three models.
-Note that not all the parameters are used in each model, which we specify further below and in Fig.
-2.
+Note that not all the parameters are used in each model, which we specify further below and in \boldblue{Fig.
+2}.
 The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement.
@@
 Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target.
-Stimulus Movement onset is knowledge of the mean ($\mu_{A}$) and uncertainty ($\sigma_{A}$) of the stimulus’s movement onset distribution.
-Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended stopping time, $\tau$.
+Stimulus Movement onset is knowledge of the mean ($\mu_{S}$) and uncertainty ($\sigma_{A}$) of the stimulus’s movement onset distribution.
+Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended transition time, $\tau$.
 Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing.
@@
 
+\vspace{2mm}
 \noindent \emph{No Switch Time Model}
@@
 
+\vspace*{2mm}
 \noindent \emph{Full Switch Time Model}
@@
 
+\vspace{2mm}
 \noindent \emph{Partial Switch Time Model}
@@
 
-\noindent \emph{General Formulation for the Models}
+\vspace{2mm}
+\noindent \textbf{General Formulation for the Models}
 
@@
 Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions.
-We begin by defining $A$ as the random variable drawn from the stimulus’s movement onset distribution (Eq.
-4) and $T$ as the random variable drawn from the stopping time distribution (Eq.
-5).
+We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\textbf{Eq.
+4}) and $T$ as the random variable drawn from the transition time distribution (\textbf{Eq.
+5}).
 
-% Define random variables A and T
+% Define random variables S and T
 \begin{align}
@@
 
-Consider$a$ and $t$ as the realizations of random variables $A$ and $T$ for a single trial.
-On any specific trial, a decision-maker will react if the stimulus movement onset is before the stopping time (i.e., $a<t$).
-Conversely, the decision-maker will guess at the stopping time if the stimulus has not moved by the stopping time (i.e., $a>t$).
-Thus, the probability that a participant will react or guess depends on the participants choice of a stopping time $\tau$.
+Consider $s$ and $t$ as the realizations of random variables $S$ and $T$ for a single trial.
+On any specific trial, a decision-maker will react if the stimulus movement onset is before the transition time (i.e., $s<t$).
+Conversely, the decision-maker will guess at the transition time if the stimulus has not moved by the transition time (i.e., $s>t$).
+Thus, the probability that a participant will react or guess depends on the participants choice of a transition time $\tau$.
 Specifically, the probability that the participant will react is the probability that the random variable A is less than T.
@@
 \begin{equation}
-    P(React|\tau) = P(\tau>\mu_{S}; \sigma_{\tau}, \sigma_{S})
+    P(React|\tau) = P(T>S)
 \end{equation}
@@
 \begin{equation}
-    P(Guess|\tau) = P(\tau<\mu_{S}; \sigma_{\tau}, \sigma_{S})
+    P(Guess|\tau) = P(T<S)
 \end{equation}
 
-As a result, a decision-maker only reacts to the portion of the stimulus’s distribution that is prior to their stopping time.
+As a result, a decision-maker only reacts to the portion of the stimulus’s distribution that is prior to their transition time.
 Thus, the participant reacts to a truncated distribution of the stimulus movement onset.
-The truncated stimulus movement onset distribution is generated from only taking the random variable $A$ if it is less than the random variable $T$.
-We can then define an indicator function ($\mathbbm{1}_{a<t}$), which is equal to one if the realized value $a$ is less than $t$ and zero otherwise:
+The truncated stimulus movement onset distribution is generated from only taking the random variable $S$ if it is less than the random variable $T$.
+We can then define an indicator function ($\mathbbm{1}_{s<t}$), which is equal to one if the realized value $s$ is less than $t$ and zero otherwise:
 
@@
 
-The mean of the truncated stimulus movement onset distribution ($\mu_{A_{react}}$) can be calculated by combining the indicator function and the method of moments.
-We start by calculating the expected value of the random variable $A$, which is the integral from $-\infty$ to $\infty$ of the value $a$ multiplied by the probability density function $f_{A}(a)$.
+The mean of the truncated stimulus movement onset distribution ($\mu_{S_{react}}$) can be calculated by combining the indicator function and the method of moments.
+We start by calculating the expected value of the random variable $S$, which is the integral from $-\infty$ to $\infty$ of the value $s$ multiplied by the probability density function $f_{S}(s)$.
 
@@
 \begin{equation}
-    \mu_{S} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{S}(s)da
+    \mu_{S} = \mathbb{E}[S] = \int_{-\infty}^{\infty}s \cdot f_{S}(s)ds
 \end{equation}
@@
 Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution.
-For the truncated stimulus movement onset distribution, we only take values $a$ if they are less than $t$.
-Since the inclusion of $a$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $a$ and $t$.
-Inside the double integral, we multiply the realized value $a$ by its probability density function (i.e., $f_{A}(a)$).
-We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{a<t}$).
-Since this double integral multiplies two gaussian probability density functions and only sums values if $a$ is less than $t$, we must normalize by dividing by the probability that A is less than T.
+For the truncated stimulus movement onset distribution, we only take values $s$ if they are less than $t$.
+Since the inclusion of $s$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $s$ and $t$.
+Inside the double integral, we multiply the realized value $s$ by its probability density function (i.e., $f_{S}(s)$).
+We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{s<t}$).
+Since this double integral multiplies two gaussian probability density functions and only sums values if $s$ is less than $t$, we must normalize by dividing by the probability that A is less than T.
 The mean (first moment) of the truncated stimulus movement onset distribution is
@@
 
-Similarly we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
+Similarly, we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
 
 \begin{equation}
-    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ da \ dt}{P(S<T)}
+    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ ds \ dt}{P(S<T)}
 \end{equation}
@@
 Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
-The participant mean reaction movement onset ($\mu_{mo_{react}}$; Eq.
-10) is the truncated stimulus movement onset mean ($\mu_{A_{react}}$) plus the participant mean response time ($\mu_{rt}$).
-Likewise, the standard deviation of participant reaction movement onset (($\sigma_{mo_{react}}$; Eq.
-11) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
+The participant mean reaction movement onset ($\mu_{mo_{react}}$, \textbf{Eq.
+12}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$).
+Likewise, the standard deviation of participant reaction movement onset (($\sigma_{mo_{react}}$, \textbf{Eq.
+13}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
 
@@
 Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
-For the no switch time model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, Eq.
-12) is the sum of the participant stopping time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$ .
-The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (Eq.
-13).
+For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, \textbf{Eq.
+14}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$.
+The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\textbf{Eq.
+15}).
 
@@
 
-Crucially, for the known switch time model and unknown switch time model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
+Crucially, for the Known Switch Time Model and Unknown Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
 
@@
     \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
-    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}
+    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}.
 \end{align}
@@
     X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
-    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}})
+    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}}).
 \end{align}
@@
 To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$).
-The probability of selecting the correct target when the participant reacts is 100\% (Eq.
-24).
-The probability of selecting the correct target when the participant guesses is 50\% (Eq.
-25).
+The probability of selecting the correct target when the participant reacts is 100\% (\textbf{Eq.
+24}).
+The probability of selecting the correct target when the participant guesses is 50\% (\textbf{Eq.
+25}).
 
@@
 
-The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint and they select the correct target:
+The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint, and they select the correct target:
 
@@
 
-Finally we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (Eq.
-x-x) and the probability of reaching and guessing given a stopping time (Eq.
-x-x), as
+Finally we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\textbf{Eq.
+27-34}) and the probability of reaching and guessing given a transition time ($\tau$), as
 
@@
     P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
-    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess)
+    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess).
 \end{align}
 
+\vspace{2mm}
 \noindent\emph{Decision Policy}
 
-For each model, the goal of the decision policy is to find the optimal stopping time that maximizes expected reward.
+\noindent For each model, the goal of the decision policy is to find the optimal transition time that maximizes expected reward.
 The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,
@@
 
-The decision policy uses known parameters to select an optimal stopping time $\tau^*$ that maximizes expected reward:
+The decision policy uses known parameters to select an optimal transition time $\tau^*$ that maximizes expected reward:
 
@@
 
+\vspace{2mm}
 \noindent\textbf{Model Parameter Estimation and Fitting Procedure}
@@
 Each of these models had full knowledge of the reaction time mean and standard deviation, neuromechanical delay mean and standard deviation, movement time mean and standard deviation, and the stimulus movement onset distribution.
-These parameter values were estimated from experimental data by bootstrapping the meansfrom the response time experiment ($\mu_{rt}, \sigma_{rt}$), timing experiment ($\sigma_{\tau}$), and Experiment 1 ($\mu_{mt}, \sigma_{mt}$).
+These parameter values were estimated from experimental data by bootstrapping the meansfrom the response time experiment ($\mu_{rt}, \sigma_{rt}$), timing experiment ($\sigma_{\tau}$), and \boldblue{Experiment 1} ($\mu_{mt}, \sigma_{mt}$).
 We describe the bootstrap procedure below.
-Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature (Norman and Komi 1979, Bruce et al.
-1985, Rossini and Rossi 1998 ).
+Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature \autocite{norman_electromechanical_1979,rossini_clinical_1998,bruce_primate_1985}.
 
@@
 
+\vspace{2mm}
 \noindent\emph{Warm-Start Initialization}
 
-\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and ($\hat{\sigma}_{\tau}$) (Roth 2023r).
+\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ (\autocite*{roth_reinforcement-based_2023,roth_punishment_2024}.
 Here the remaining parameters estimated from experimental data were set as the group level means.
-We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means($Data_{i,j}$) according to
+We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means ($Data_{i,j}$) according to
 
@@
 
-\noindent\emph{Warm-Start Initialization}
+\vspace{2mm}
+\noindent\emph{Bootstrap Procedure}
 
-\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times (Cashaback 2017, Cashback 2019, Roth 2024, Roth 2023).
+\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times \autocite*{cashaback_dissociating_2017,cashaback_gradient_2019,roth_reinforcement-based_2023,roth_punishment_2024}.
 We used the mean of the bootstrapped participant data for each of the parameter values that were estimated from data.
-For each bootstrap iteration, the optimization process selected the free parameters for the Full Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$) and Partial Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{\tau}$, $\hat{\sigma}_{\tau}$) that minimized the loss function (Eq.
-44).
+For each bootstrap iteration, the optimization process selected the free parameters for the Full Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$) and Partial Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{\tau}$, $\hat{\sigma}_{\tau}$) that minimized the loss function (\textbf{Eq.
+44}).
 
-\noindent \textbf{Model Parameters}
+\vspace{2mm}
+\noindent \textbf{Model Parameter Values}
 
@@
 The values that were used by the decision policy were: timing uncertainty (1.65 ms;  [0.08, 4.63]), switch time mean (9.0 ms; [0.00, 16.65]), switch time uncertainty (40.4 ms; [34.54, 48.02]).
-Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and stopping time certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.
+Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and transition time certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.
 
+\newpage
 \noindent\textbf{\large\textcolor{mydarkblue}{Supplementary C: Model Results}}
@@
         \caption{
-            Model Outputs: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{A)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
-The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the late mean low variance and late mean high variance conditions.
+            \textbf{Model Outputs}: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{A)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
+The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the \emph{late mean low variance} and late mean high variance conditions.
 Conversely, the Unknown Switch Time Model (black) is able to accurately predict the participant data for all conditions across all metrics.
 As a reminder, the Unknown Switch time Model does not account for the delay and uncertainties associated with switching from reacting to guessing.
-Critically, in \textbf{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the late mean low variance condition, whereas the other two models predict zero indecisions for that condition.
-Further, in \textbf{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the late mean low variance condition.
+Critically, in \textbf{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the \emph{late mean low variance} condition, whereas the other two models predict zero indecisions for that condition.
+Further, in \textbf{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the \emph{late mean low variance} condition.
 Collectively, our findings show that humans are suboptimal and excessively indecisive, which can be captured by a model that does not account  for the delay and uncertainties associated with switching from reacting to guessing.
@@
 \noindent\textbf{\large\textcolor{mydarkblue}{Supplementary D: Response Time Task}}
+
+\noindent For the response time task (\boldblue{Supplementary Figure 1}), participants began each trial by moving their cursor (yellow circle, 1 cm diameter) into a start position (white circle, 1.5 cm diameter).
+Following a randomized time period (600-2400 ms drawn from a uniform distribution), one of two potential targets (white rings, 8 cm diameter) appeared on the screen.
+The two potential targets were positioned 16.7 cm forward relative to the start position, and either 11.1 cm to the left or right of the start position.
+As soon as one of the two potential targets appeared, the participant reached as fast as possible to the displayed target.
+Participants experienced 25 left target trials and 25 right target trials in a randomized order.
 \begin{figure}[H]
@@
 
-    \caption{Response Time Experiment: One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
+    \caption{\textbf{Response Time Experiment}.
+One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
 Once a target appeared (solid white ring), participants were instructed to rapidly move their cursor to hit the displayed target.
-We used the mean and standard deviation of response times as model parameters in the optimal stopping models.}
+We used the mean and standard deviation of response times as model parameters in the optimal transition models.}
 \end{figure}
@@
 
+\noindent To capture timing uncertainty, participants were instructed to reach into a target at a specified time of 1500 ms.
+Each trial began with a participant moving their cursor into a start position (white circle, 1.5 cm diameter).
+Following a randomized time delay (600-2400 ms drawn from a uniform distribution), they would hear a beep, a target (white ring, 8 cm diameter) appeared 17 cm forward relative to the start position, and a timing bar was displayed 10 cm below the start position.
+After the initial beep, participants were instructed to wait in the start position until they decided to hit the target.
+They were then told to make a smooth and quick movement to hit the target with their cursor at 1500 ms.
+They would then hear a beep at the desired time of 1500 ms.
+Participants performed a block of 50 trials for the timing uncertainty task with a timing bar and another block of 50 trials without a timing bar.
+The timing bar decreased in width over time and consequently disappeared at 1500 ms.
+Thus, during the trials with a timing bar the participants would have better knowledge of when they were required to hit the target.
+We used the data during this condition for the timing uncertainty parameter in each model, which aligned with the experimental design of \boldblue{Experiment 1}.
+Trials where there was no timing bar were not used for subsequent analyses.
+We counterbalanced the blocks of trials that did or did not have the timing bar.
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/exp1_timing_experimental_design.png}
+
+    \caption{\textbf{Timing Uncertainty Experiment}.
+One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
+Once a target appeared (solid white ring), participants were instructed to rapidly move their cursor to hit the displayed target.
+We used the mean and standard deviation of response times as model parameters in the optimal transition models.}
+\end{figure}
+
 \noindent\textbf{\large\textcolor{mydarkblue}{Supplementary F: Guess Decisions}}
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/guess_decisions.png}
+
+    \caption{\textbf{Reaction and Guess Decision Percentages for Experiment 1}.
+Estimated percentage of reaction (pink) and guess (blue) decision percentages (y-axis) for each experimental condition (x-axis).
+During \boldblue{Experiment 1} participants were rewarded for successful trials and experienced a time constraint.
+Thus, we would expect participants to have faster response times in \boldblue{Experiment 1} than in the Response Time task \autocite{milstein_influence_2007,shadmehr_movement_2019}.
+To account for this, we adjusted participant response times by subtracting 25ms from their median response time in the Response Time task.
+A trial was a reaction decision if the difference between the stimulus’s movement onset and participant’s movement onset was greater than that participant’s adjusted response time.
+Conversely, a trial was a guess decision if the difference between the stimulus movement onset and participant movement onset was less than that participant’s adjusted response time.
+We found that participants guessed significantly more often as the stimulus’s mean movement onset approached the time constraint.}
+\end{figure}
+
+\newpage
+\fancyhead[L]{} % Need this because print bibliography is dumb and puts a REFERENCES in the left header
+\begin{nolinenumbers}
+    \definecolor{mydarkblue}{RGB}{0,51,102}
+
+    \printbibliography[title=\LARGE\textcolor{mydarkblue}{Supplementary References}]
+\end{nolinenumbers}
+
 \end{document}

### 2024-07-30 paper/main.tex
submitted

@@
 \usepackage{setspace}
+\usepackage{docmute} % For putting one tex into another tex using \input
 
@@
   backend  = bibtex,
-  sortcites  = false,
+  sortcites  = true, % Sort citations that are grouped together by number (not date, unsure how to do this)
   citestyle = numeric,
@@
   doi = false,
-  url = false
+  url = false, 
+  date=year, % Removes everything but year (i.e. month day) from citations
 ]{biblatex}
@@
     \printfield{labelprefix}%
-    \printfield{labelnumber}}}
+    \printfield{labelnumber}}}%
      {\setlength{\labelwidth}{\labelnumberwidth}%
@@
 \DeclareCaptionLabelFormat{supp}{1-2}
+% \DeclareCaptionFont{myblue}{\color{mydarkblue}}
 \captionsetup[figure]{labelfont=bf, labelsep=colon, font=footnotesize, justification=justified}
@@
 \newcommand{\SuppCaption}[2]{\noindent\boldblue{{#1}} {#2}\footnotesize}
-\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large\textcolor{mydarkblue}{#1}}\normalsize }
+\newcommand{\SectionHeader}[1]{\noindent\boldblue{\Large{#1}}\normalsize }
 \newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{mydarkblue}{#1}}\normalsize }
@@
 % Condition variables
-% \def\emlv{\emph{early mean low variance}}
-% \def\emhv{\emph{early mean high variance}}
-% \def\mmlv{\emph{middle mean low variance}}
-% \def\mmhv{\emph{middle mean high variance}}
-% \def\lmlv{\emph{late mean low variance}}
-% \def\lmhv{\emph{late mean high variance}}
+% \def\emlv{\emph{\emph{early mean} low variance}}
+% \def\emhv{\emph{\emph{early mean} high variance}}
+% \def\mmlv{\emph{\emph{middle mean} low variance}}
+% \def\mmhv{\emph{\emph{middle mean} high variance}}
+% \def\lmlv{\emph{\emph{late mean} low variance}}
+% \def\lmhv{\emph{\emph{late mean} high variance}}
 
-% \def\em{\emph{early mean}}
-% \def\mm{\emph{middle mean}}
-% \def\lm{\emph{late mean}}
+% \def\em{\emph{\emph{early mean}}}
+% \def\mm{\emph{\emph{middle mean}}}
+% \def\lm{\emph{\emph{late mean}}}
 
@@
 \begin{document}
+% MUST BE IN DOCUMENT FOR EQUATION SPACING
 %%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%
@@
 
-    \noindent\boldblue{\Large\textcolor{mydarkblue}{Indecisions under time pressure arise from suboptimal switching behaviour
+    \noindent\boldblue{\Large{Indecision under time pressure arises from suboptimal switching behaviour
         }}
@@
 Sullivan\textsuperscript{1}, Rakshith Lokesh\textsuperscript{4}, Jan A.
-Calalo\textsuperscript{1,2}, Truc Ngo\textsuperscript{1}, John H.
-Buggeln\textsuperscript{3},Christopher Peters\textsuperscript{1}, Isaac Kurtzer\textsuperscript{5}, Michael Carter\textsuperscript{6}, Joshua G.A.
-Cashaback\textsuperscript{1,2,3,7}
+Calalo\textsuperscript{2}, Truc Ngo\textsuperscript{1}, John H.
+Buggeln\textsuperscript{3}, Adam M.
+Roth\textsuperscript{2}, Christopher Peters\textsuperscript{1}, Isaac Kurtzer\textsuperscript{5}, Michael J.
+Carter\textsuperscript{6}, Joshua G.A.
+Cashaback\textsuperscript{1,2,3,6,7}
     \vspace{2mm}
@@
 \textsuperscript{3} Biomechanics and Movements Science Program, University of Delaware\\
-\textsuperscript{4} Action Lab, Northeastern University\\
+\textsuperscript{4} Department of Electrical and Computer Engineering, Northeastern University\\
 \textsuperscript{5} College of Osteopathic Medicine, New York Institute of Technology\\
-\textsuperscript{6} Action, Cognition, and Metascience Lab, McMaster University\\
+\textsuperscript{6} Department of Kinesiology, McMaster University\\
 \textsuperscript{7} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
-\vspace{15mm}
+\vspace{4mm}
 \\
@@
 \\
-Indecisive behaviour arises from suboptimal switching
+Indecision arises from suboptimal switching
 \\
-\vspace{15mm}
+\vspace{4mm}
 \\
@@
 \\
-NSF2146888
+National Science Foundation (NSF \#2146888) awarded to JGAC
 \\
-\vspace{10mm}
+National Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589) awarded to MJC
+\\
+\vspace{4mm}
+\\
+\textcolor{mydarkblue}{\large Declaration of Interests:}
+\vspace{1mm}
+\\
+The authors declare no competing interests.
+\vspace{5mm}
 \\
@@
 Past literature has had very little focus on indecisions.
-The vast majority of decision-making research either does not consider responses made after some time constraint or simply does not permit a non-response, such as in the classic two-alternative forced choice paradigm\autocite{zacksenhouse_robust_2010,bogacz_physics_2006,cho_mechanisms_2002,jogan_new_2014,ratcliff_diffusion_2008,ulrich_threshold_2004,tyler_signal_2000}.
+The vast majority of decision-making research either does not consider responses made after some time constraint or simply does not permit a non-response, such as in the classic two-alternative forced choice paradigm \autocite{zacksenhouseRobustOptimalStrategies2010, bogaczPhysicsOptimalDecision2006, choMechanismsUnderlyingDependencies2002, joganNewTwoalternativeForced2014, ratcliffDiffusionDecisionModel2008,ulrichThresholdEstimationTwoalternative2004,tylerSignalDetectionTheory2000}.
 Thus, despite its real-world ubiquity and importance, we have very little understanding of how indecisions arise.
 
-There have only been a handful of papers to examine indecisions, which involve either high \autocite{lokesh_humans_2022} or low time pressure \autocite{karsilar_speed_2014,wu_capacity_2016,philiastides_causal_2011,dambacher_time_2015,forstmann_striatum_2008}.
-We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokesh_humans_2022}.
+There have only been a handful of papers to examine indecisions, which involve either high \autocite{lokeshHumansUtilizeSensory2022} or low time pressure \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016,philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}.
+We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokeshHumansUtilizeSensory2022}.
 In this competitive scenario, the ‘prey’ attempted to end up in the same target as the ‘predator’ by a time constraint, while the predator attempted to end up in the opposite target as the prey.
@@
 Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions.
-Similar to others \autocite{karsilar_speed_2014,wu_capacity_2016,philiastides_causal_2011,dambacher_time_2015,forstmann_striatum_2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions.
+Similar to others \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016, philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions.
 Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline.
@@
 
-Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response \autocite{drugowitsch_optimal_2014,balci_optimal_2011,bogacz_physics_2006,hudson_optimal_2008,trommershauser_humans_2006}.
-To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system (\autocite{drugowitsch_tuning_2015, balci_optimal_2011,hudson_optimal_2008,acerbi_internal_2012,faisal_noise_2008,kording_bayesian_2006,wolpert_motor_2012,tanis_accuracy_2023,lokesh_visual_2023}.
-Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite{balci_optimal_2011,miletic_caution_2019} and motor tasks\autocite{hudson_optimal_2008,faisal_near_2009}.
-Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties \autocite{ota_motor_2015,drugowitsch_computational_2016}.
+Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response\autocite*{drugowitschOptimalDecisionmakingTimevarying2014,balciOptimalTemporalRisk2011,bogaczPhysicsOptimalDecision2006,hudsonOptimalCompensationTemporal2008,trommershauserHumansRapidlyEstimate2006}.
+To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system \autocite*{drugowitschTuningSpeedaccuracyTradeoff2015,balciOptimalTemporalRisk2011,hudsonOptimalCompensationTemporal2008,acerbiInternalRepresentationsTemporal2012,faisalNoiseNervousSystem2008,kordingBayesianDecisionTheory2006,wolpertMotorControlDecisionmaking2012,tanisAccuracyEffortCosts2023,lokeshVisualAccuracyDominates2023}.
+Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite*{balciOptimalTemporalRisk2011,mileticCautionDecisionmakingTime2019} and motor tasks\autocite*{hudsonOptimalCompensationTemporal2008,faisalOptimalCombinationSensory2009}.
+Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016}.
 With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.
-Building on our past work\autocite{lokesh_humans_2022}, we developed a high pressure task with a time constraint to examine how humans select decision times.
+
+Building on our past work\autocite{lokeshHumansUtilizeSensory2022}, we developed a high pressure task with a time constraint to examine how humans select decision times.
 We tested the idea that humans optimally account for time delays and temporal uncertainties to select a decision time that maximizes reward.
@@
 \SectionHeader{RESULTS}
+\vspace{-1mm}
 
 \SubSectionHeader{Experiment 1}
+\vspace{-1mm}
 
 \noindent\boldblue{Experimental Design.}
-The goal of \boldblue{Experiment 1} was to test how stimulus timing influenced indecisive behaviour.
+
+\noindent The goal of \boldblue{Experiment 1} was to test how stimulus timing influenced indecisive behaviour.
 Briefly, participants began each trial by moving their cursor into a start position (\boldblue{Fig.
 1A}).
-The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale =1]{figures/exp1_experimental_design_v2.png}
+  \caption*{\boldblue{Figure 1: Experimental Design.} \boldblue{A)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
+An LCD projected images (start position, targets) onto a semi-silvered mirror.
+Participants began each trial by moving their cursor (purple) into the start position (solid white circle).
+At the start of the trial (0 ms), they heard a tone and saw two targets (white rings) and a timing bar (white rectangle) appear on the screen.
+During each trial, a stimulus (yellow cursor) would move quickly in a straight line to one of the two targets.
+Participants were instructed to reach the same target as the stimulus within a time constraint of 1500ms.
+This time constraint was visually represented with a timing bar (white rectangle) that decreased in width according to the elapsed time.
+\boldblue{B)} A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint.
+A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
+A trial was considered an indecision and the participant received 0 points if they failed to reach a target within the time constraint.
+\boldblue{C)} Stimulus movement onset on each trial was randomly drawn from a specific probability distribution in each condition.
+Using a within experimental design, we manipulated the mean (early, middle, late) and standard deviation (low, high) of the stimulus movement onset probability distribution.
+For the main manuscript we focus on results for the low variance conditions, with high variance conditions results shown in \boldblue{Supplementary A.}}
+\end{figure}
+
+\noindent The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles.
 Participants were instructed to reach the same target as the stimulus within a time constraint of 1500 ms.
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[scale =1]{figures/exp1_experimental_design_v2.png}
-  \caption{\textbf{Experimental Design.} \textbf{A)} Participants grasped the handle of a robotic manipulandum and made reaching movements in the horizontal plane.
-An LCD projected images (start position, targets) onto a semi-silvered mirror.
-Participants began each trial by moving their cursor (purple) into the start position (solid white circle).
-At the start of the trial (0 ms), they heard a tone and saw two targets (white rings) and a timing bar (white rectangle) appear on the screen.
-During each trial, a stimulus (yellow cursor) would move quickly in a straight line to one of the two targets.
-Participants were instructed to reach the same target as the stimulus within a time constraint of 1500ms.
-This time constraint was visually represented with a timing bar (white rectangle) that decreased in width according to the elapsed time.
-\textbf{B)} A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint.
-A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
-A trial was considered an indecision and the participant received 0 points if they failed to reach a target within the time constraint.
-\textbf{C)} Stimulus movement onset on each trial was randomly drawn from a specific probability distribution in each condition.
-Using a within experimental design, we manipulated the mean (early, middle, late) and standard deviation (low, high) of the stimulus movement onset probability distribution.
-For the main manuscript we focus on results for the low variance conditions, with high variance conditions results shown in \boldblue{Supplementary A.}}
-\end{figure}
-
 For each trial within a condition, the stimulus movement onset was drawn from the same normal distribution.
@@
 
-\textbf{{{Participant timing behaviour.}}}
-Participant movement onsets for the low variance condition are shown in \boldblue{Fig.
+\vspace*{2mm}
+\noindent \boldblue{{{Participant timing behaviour.}}}
+
+\noindent Participant movement onsets for the low variance conditions are shown in \boldblue{Fig.
 2A}, We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
 There was no significant interaction between stimulus movement onset mean and variance (F[1.66,31.47], p = 0.565).
-When collapsed across low and high variance, participant movement onsets were significantly greater in the middle mean conditions compared to the early mean conditions (p = 0.014, $\hat{\theta}$ = 72.5 \%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
-Again when collapsed across low and high variance, participant movement onset significantly decreased from the middle mean conditions to the late mean conditions (p = 0.018, $\hat{\theta}$ = 62.5\%).
-Here, an earlier participant movement onset in the late mean condition suggests that participants attempted to wait and react to the stimulus, but ended up guessing.
+When collapsed across low and high variance, participant movement onsets were significantly greater in the \emph{middle mean} conditions compared to the \emph{early mean} conditions (p = 0.014, $\hat{\theta}$ = 72.5 \%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
+Again when collapsed across low and high variance, participant movement onset significantly decreased from the \emph{middle mean} conditions to the \emph{late mean} conditions (p = 0.018, $\hat{\theta}$ = 62.5\%).
+Here, an earlier participant movement onset in the \emph{late mean} condition suggests that participants attempted to wait and react to the stimulus, but ended up guessing.
 
@@
 There was a main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) of the stimulus movement onset, and no significant interaction (F[1.98, 37.58], p = 0.097).
-When collapsed across variance, waiting to react and then guessing in the late mean conditions led to a higher standard deviation of participant movement onset relative to the middle mean (p = 0.039, $\hat{\theta}$ = 70.0\%) and early mean (p < 0.001, $\hat{\theta}$ = 77.5\%) conditions.
 
@@
   \begin{minipage}[c][\pdfpageheight][t]{0.5\textwidth}
-        \caption{
-          \textbf{Behaviour Results}: \textbf{A)} Participant movement onset, \textbf{B)} participant movement onset standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects are shown for each condition.
+      \caption*{
+        \boldblue{Figure 2: Behaviour Results}.
+\boldblue{A)} Participant movement onset, \boldblue{B)} participant movement onset standard deviation, \boldblue{C)} indecisions, \boldblue{D)} wins, and \boldblue{E)} incorrects are shown for each condition.
 In our high time pressure task, participants made a high proportion of indecisions.
@@
 Filled icons are the predicted behavior of the three models, see legend for detail.
-Interestingly, we also found that the average win percentage (41.25\%) was significantly below the 50\% chance level (p < 0.001) in the late mean condition, clearly demonstrating suboptimal behaviour.
+Interestingly, we also found that the average win percentage (41.25\%) was significantly below the 50\% chance level (p < 0.001) in the \emph{late mean} condition, clearly demonstrating suboptimal behaviour.
 Critically, participants would have earned more points if they had simply guessed earlier on all trials, rather than attempting to react to the stimulus.
-Model Results: Only the Partial Switch Time Model, which had only a partial representation of the time delay and uncertainty when switching from reacting to guessing, was able to predict the indecisions and a suboptimal win rate (below 50\%) in the late mean condition.
+Model Results: Only the Partial Switch Time Model, which had only a partial representation of the time delay and uncertainty when switching from reacting to guessing, was able to predict the indecisions and a suboptimal win rate (below 50\%) in the \emph{late mean} condition.
 See \boldblue{Fig.
-3} for the time varying model predictions for the late mean condition.
+3} for the time varying model predictions for the \emph{late mean} condition.
 Collectively, our findings show that humans are suboptimal and excessively indecisive.}
@@
 
-\textbf{{{Participants are suboptimal and excessively indecisive.}}}
-We calculated the indecisions (\boldblue{Fig.
+\noindent When collapsed across variance, waiting to react and then guessing in the \emph{late mean} conditions led to a higher standard deviation of participant movement onset relative to the \emph{middle mean} (p = 0.039, $\hat{\theta}$ = 70.0\%) and \emph{early mean} (p < 0.001, $\hat{\theta}$ = 77.5\%) conditions.
+
+\vspace*{2mm}
+\noindent \boldblue{{{Participants are suboptimal and excessively indecisive.}}}
+
+\noindent We calculated the indecisions (\boldblue{Fig.
 2C}), wins (\boldblue{Fig.
@@
 Participants displayed a substantial number of indecisions.
-The median percentage of indecisions was 15.0\% [range: 0.0 - 93.8\%] across all conditions, with the late mean low variance condition having a median percentage of indecisions of 19.4\% [range: 1.2\%, 93.8\%].
+The median percentage of indecisions was 15.0\% [range: 0.0 - 93.8\%] across all conditions, with the \emph{late mean} condition having a median percentage of indecisions of 19.4\% [range: 1.2\%, 93.8\%].
 We found a significant interaction between stimulus movement onset and variance for indecisions (F[1.57, 28.78] = 5.58, p = 0.013).
-In low variance conditions, participants made significantly more indecisions in the middle mean condition than the early mean condition (p<0.001, $\hat{\theta}$ = 85.0\%; \boldblue{Fig.
+In low variance conditions, participants made significantly more indecisions in the \emph{middle mean} condition than the \emph{early mean} condition (p<0.001, $\hat{\theta}$ = 85.0\%; \boldblue{Fig.
 2C}).
-Additionally, participants made significantly more indecisions in the late mean condition compared to the early mean condition (p<0.004, $\hat{\theta}$ = 80.0\%).
+Additionally, participants made significantly more indecisions in the \emph{late mean} condition compared to the \emph{early mean} condition (p<0.004, $\hat{\theta}$ = 80.0\%).
 
@@
 We found a significant interaction between stimulus movement onset mean and variance for wins (F[1.54, 29.30] = 23.73, p<0.001).
-The late mean condition had significantly less wins than the early mean condition (p < 0.001, $\hat{\theta}$ = 95.0\%).
-Interestingly, in the late mean condition we found that the average win percentage was significantly below the 50\% chance level (p<0.001; $\hat{\theta}$ = 95.0\%), which was true for 19 out of 20 participants.
+The \emph{late mean} condition had significantly less wins than the \emph{early mean} condition (p < 0.001, $\hat{\theta}$ = 95.0\%).
+Interestingly, in the \emph{late mean} condition we found that the average win percentage was significantly below the 50\% chance level (p<0.001; $\hat{\theta}$ = 95.0\%), which was true for 19 out of 20 participants.
 Since guessing on every trial would lead to a win percentage of 50\%, the only way participants would be below chance is if they are excessively indecisive.
@@
 We found significant interactions between stimulus movement onset mean and variance for incorrect decisions (F[1.66,31.51]=3.72, p=0.033).
-Participants displayed a greater percentage of incorrect decisions in the late mean condition than the early mean condition (p < 0.001, $\hat{\theta}$ = 92.5\%).
+Participants displayed a greater percentage of incorrect decisions in the \emph{late mean} condition than the \emph{early mean} condition (p < 0.001, $\hat{\theta}$ = 92.5\%).
 
-\noindent\textbf{{{Decision-making model.}}}
-In our task, participants must make a decision of whether to react to the stimulus or guess.
+\vspace{10mm}
+\noindent \boldblue{{{Decision-Making Models}}}
+
+\noindent In our task, participants must make a decision of whether to react to the stimulus or guess.
 For \boldblue{Experiment 1}, we tested three different models:  i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
@@
 Expected value is defined as
-
+\setlength{\belowdisplayskip}{4pt} \setlength{\belowdisplayshortskip}{4pt} % THIS MUST BE HERE FOR EQUATIONS SPACING
+\setlength{\abovedisplayskip}{4pt} \setlength{\abovedisplayshortskip}{4pt}
 \begin{align}
@@
 \noindent where $P(Win|\tau)$ is the probability of a win, $P(Incorrect|\tau)$ is the probability of an incorrect, and $P(Indecision|\tau)$ is the probability of an indecision.
-$R_{Win} = 1$, $R_{Incorrect} = 0$, and ($R_{Indecision} = 0$ correspond to the reward structure of the task (\boldblue{Fig.
+$R_{Win} = 1$, $R_{Incorrect} = 0$, and $R_{Indecision} = 0$ correspond to the reward structure of the task (\boldblue{Fig.
 1B}).
 The decision policy of each model maximized expected reward to determine the optimal time to transition from reacting to guessing ($\tau^*$) according to
-
 \begin{equation}
@@
 As an example, one could plan for only some portion of a time delay, but then end up deciding too late because they did not fully account for the entire time delay.
-All model parameter values are shown in \boldblue{Supplementary B}.
+All model parameter values are described in \boldblue{Supplementary B}.
 
@@
 
-  \caption{%
-    \boldblue{Models.} No Switch Time Model (\textbf{top row}, light grey), Full Switch Time Model (\textbf{middle row}, dark grey), and Partial Switch Time Model (\textbf{bottom row}, black).
+  \caption*{%
+    \boldblue{Figure 3: Models.} No Switch Time Model (\boldblue{top row}, light grey), Full Switch Time Model (\boldblue{middle row}, dark grey), and Partial Switch Time Model (\boldblue{bottom row}, black).
 Each decision policy maximizes reward to select a time to transition from reacting to guessing.
 The decision policy of each model has different knowledge, full or partial, of the delays and uncertainties associated with the various parameters (e.g., response time, switch time).
-\textbf{Top Row)} The No Switch Time Model (light grey) has full knowledge of all its model parameters.
+\boldblue{Top Row)} The No Switch Time Model (light grey) has full knowledge of all its model parameters.
 However, it does not include the potential delay and uncertainty when switching from reaching to guessing, which we term ‘switch time’.
-\textbf{Middle Row}) The Full Switch Time Model (dark gray) has knowledge of all model parameters, including switch time (bright green).
-\textbf{Bottom Row)} Finally, the Partial Switch Time Model (black) has knowledge of several of the model parameters, but is only partially aware of the stopping time uncertainty and the switch time (delay and uncertainty).
-Only the Partial Switch Time Model is able to capture the participant target reach times (pink) in the late mean condition (stimulus movement onset; blue), allowing it to explain indecisions (\boldblue{Fig.
+\boldblue{Middle Row}) The Full Switch Time Model (dark gray) has knowledge of all model parameters, including switch time (bright green).
+\boldblue{Bottom Row)} Finally, the Partial Switch Time Model (black) has knowledge of several of the model parameters, but is only partially aware of the stopping time uncertainty and the switch time (delay and uncertainty).
+Only the Partial Switch Time Model is able to capture the participant target reach times (pink) in the \emph{late mean} condition (stimulus movement onset; blue), allowing it to explain indecisions (\boldblue{Fig.
 2C}) and suboptimal win rates (\boldblue{Fig.
@@
 
+% \vspace*{2mm}
 \noindent\emph{{No Switch Time Model}}
@@
 
-In the late mean low variance condition, the No Switch Time Model underestimated participant movement onset (\boldblue{Fig.
+In the \emph{late mean} condition, the No Switch Time Model underestimated participant movement onset (\boldblue{Fig.
 2A}), underestimated indecisions (\boldblue{Fig.
@@
 
+\vspace*{2mm}
 \noindent\emph{{{Full Switch Time Model}}}
@@
 
-Yet, despite including switch time, the Full Switch Time Model also performed poorly in the late mean condition by under-predicting participant movement onset (\boldblue{Fig.
+Yet, despite including switch time, the Full Switch Time Model also performed poorly in the \emph{late mean} condition by under-predicting participant movement onset (\boldblue{Fig.
 2A}), being unable to predict indecisions (\boldblue{Fig.
@@
 
+\vspace*{2mm}
 \noindent\emph{{{Partial Switch Time Model}}}
@@
 2}).
-Crucially, it was able to capture suboptimal behaviour in the late mean condition, where we found that an excessive percentage of indecisions (\boldblue{Fig.
+Crucially, it was able to capture suboptimal behaviour in the \emph{late mean} condition, where we found that an excessive percentage of indecisions (\boldblue{Fig.
 2C}, \boldblue{Fig.
@@
 
-\textbf{Experimental Design}.
-For all conditions, participants controlled a visible cursor that was aligned with their hand position.
+\noindent \boldblue{Experimental Design}
+
+\noindent For all conditions, participants controlled a visible cursor that was aligned with their hand position.
 They started each trial by moving their cursor into a start position.
@@
 There were three experimental conditions (\boldblue{Fig.
-4C}): the react or guess condition, the only react condition, and the only guess condition.
-In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
-Participants were informed that the stimulus would either move to one of the targets or disappear.
-In the only react condition, participants were informed that the stimulus would always move to one of the two targets (50 react trials and 0 guess trials).
-They were also told that the stimulus would not disappear.
-In the only guess condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
-They were also informed that it would not move to one of the two targets.
-
-During the react or guess condition, we reasoned that participants would prefer to react because they would be guaranteed to select the correct target.
-As a result, in the react or guess condition, if the stimulus disappeared the participant would switch from reacting to guessing when selecting a target.
-Conversely, during the only guess condition, if the stimulus disappeared participants would not have to switch from reacting to guessing.
-Thus, if there is a delay when switching from reacting to guessing, we would expect a greater response time for the guess trials in the react or guess condition compared to the guess trials in the guess only condition.
+4C}): the \emph{react or guess} condition, the \emph{only react} condition, and the \emph{only guess} condition.
 
@@
 
-  \caption{\boldblue{Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1.
-\textbf{A)} Participants responded to two different types of stimuli.
+  \caption*{\boldblue{Figure 4: Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1.
+\boldblue{A)} Participants responded to two different types of stimuli.
 In the react trials (pink), the stimulus (yellow cursor) would move to one of the two potential targets.
 Participants were instructed to reach the same target as the stimulus as quickly as possible.
-\textbf{B)} In the guess trials (blue), the stimulus disappeared from the start position.
+\boldblue{B)} In the guess trials (blue), the stimulus disappeared from the start position.
 Once the stimulus disappeared, participants were instructed to guess which target the stimulus would appear in and select that target as quickly as possible.
 After the participant reached the target, the stimulus’s cursor would appear in one of the targets.
-\textbf{C)} We had three experimental conditions.
-In the react or guess condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+\boldblue{C)} We had three experimental conditions.
+In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
 Participants were informed that the stimulus would either move to one of the targets or disappear.
-In the only react condition, participants were informed that the stimulus would alway move to one of the two targets (50 react trials and 0 guess trials).
+In the \emph{only react} condition, participants were informed that the stimulus would alway move to one of the two targets (50 react trials and 0 guess trials).
 They were also told that the stimulus would not disappear.
-In the only guess condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
+In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
 They were also informed the stimulus would not move.
@@
 
-\textbf{Response Time}.
-Average participant response times are shown for react and guess trials for each condition are shown in \boldblue{Fig.
+\noindent In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+Participants were informed that the stimulus would either move to one of the targets or disappear.
+In the \emph{only react} condition, participants were informed that the stimulus would always move to one of the two targets (50 react trials and 0 guess trials).
+They were also told that the stimulus would not disappear.
+In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
+They were also informed that it would not move to one of the two targets.
+
+During the \emph{react or guess} condition, we reasoned that participants would prefer to react because they would be guaranteed to select the correct target.
+As a result, in the \emph{react or guess} condition, if the stimulus disappeared the participant would switch from reacting to guessing when selecting a target.
+Conversely, during the \emph{only guess} condition, if the stimulus disappeared participants would not have to switch from reacting to guessing.
+Thus, if there is a delay when switching from reacting to guessing, we would expect a greater response time for the guess trials in the \emph{react or guess} condition compared to the guess trials in the guess only condition.
+
+\noindent \boldblue{Response Time}
+
+\noindent Average participant response times are shown for react and guess trials for each condition are shown in \boldblue{Fig.
 5A}.
-As expected, we found significantly greater response times for guess trials in the react or guess condition when compared to the only guess condition (p < 0.001, $\hat{\theta}$ = 100.0\%), which was displayed by all participants.
-These comparatively greater response times for guess trials in the react or guess condition supports the idea that there is a switch time delay when transitioning from reacting to guessing.
+As expected, we found significantly greater response times for guess trials in the \emph{react or guess} condition when compared to the \emph{only guess} condition (p < 0.001, $\hat{\theta}$ = 100.0\%), which was displayed by all participants.
+These comparatively greater response times for guess trials in the \emph{react or guess} condition supports the idea that there is a switch time delay when transitioning from reacting to guessing.
 
@@
     \includegraphics[scale = 1]{figures/exp2_reaction_panel_mean_sd.png}
-    \caption{\textbf{A)} Response time (y-axis) for each of the experimental conditions (x-axis).
-Participants had significantly greater response times for guess trials in the react or guess condition compared to the only guess condition.
+    \caption*{\boldblue{Figure 5: Response Times.
+A)} Response time (y-axis) for each of the experimental conditions (x-axis).
+Participants had significantly greater response times for guess trials in the \emph{react or guess} condition compared to the \emph{only guess} condition.
 Critically, this result suggests there is an additional delay when participants initially wait to react to the stimulus and then switch to guessing.
-\textbf{B)} Standard deviation of response times (y-axis) was used to quantify participant response time uncertainty for each of the experimental conditions (x-axis).
-Participants had significantly greater response time uncertainty for guess trials in the react or guess condition than in the only guess condition.
+\boldblue{B)} Standard deviation of response times (y-axis) was used to quantify participant response time uncertainty for each of the experimental conditions (x-axis).
+Participants had significantly greater response time uncertainty for guess trials in the \emph{react or guess} condition than in the \emph{only guess} condition.
 Similarly, this finding suggests there is additional uncertainty when participants initially wait to react to the stimulus and then switch to guessing.
@@
 
-Likewise, if there was a switch time delay we would also expect a comparatively greater response time difference between guess and react trials in the react or guess condition, compared to the response time difference between only guess trials and only react trials [i.e., guess - react (react or guess condition) > guess - react (guess only and react only conditions)].
-Indeed, we found a greater response time difference between guess and react trials in the react or guess condition, compared to the response time difference between the guess only and react only conditions (p < 0.001, $\hat{\theta}$ = 66.7\%; \boldblue{Fig.
+Likewise, if there was a switch time delay we would also expect a comparatively greater response time difference between guess and react trials in the \emph{react or guess} condition, compared to the response time difference between \emph{only guess} trials and \emph{only react} trials [i.e., guess - react (\emph{react or guess} condition) > guess - react (guess only and react only conditions)].
+Indeed, we found a greater response time difference between guess and react trials in the \emph{react or guess} condition, compared to the response time difference between the guess only and react only conditions (p < 0.001, $\hat{\theta}$ = 66.7\%; \boldblue{Fig.
 5A}).
-This result shows that the response time differences between guess and react trials are not due to dual tasking \autocite{van_selst_decision_1997} or task switching between trials \autocite{monsell_task_2003,kiesel_control_2010,rubinstein_executive_2001}, which would not show this relative difference  [i.e., guess - react (react or guess condition) = guess - react (guess only and react only conditions)].
+This result shows that the response time differences between guess and react trials are not due to dual tasking \autocite{vanselstDecisionResponseDualTask1997} or task switching between trials \autocite*{monsellTaskSwitching2003,kieselControlInterferenceTask2010a,rubinsteinExecutiveControlCognitive2001}, which would not show this relative difference  [i.e., guess - react (\emph{react or guess} condition) = guess - react (guess only and react only conditions)].
 
-\textbf{Response Time Uncertainty}.
-We also examined participant response time uncertainty, calculated as the standard deviation (\boldblue{Fig.
+\vspace{10mm}
+\noindent \boldblue{Response Time Uncertainty}
+
+\noindent We also examined participant response time uncertainty, calculated as the standard deviation (\boldblue{Fig.
 5B}).
-Response time uncertainty on guess trials was significantly greater in the react or guess condition compared to the only guess condition (p < 0.001).
+Response time uncertainty on guess trials was significantly greater in the \emph{react or guess} condition compared to the \emph{only guess} condition (p < 0.001).
 This result suggests that there is additional uncertainty when participants switch from reacting to guessing.
@@
 Within a trial, they could either react to a moving stimulus or guess which of the two targets would be correct.
-We saw that 95\% of participants had a win rate less than chance (50\%) in the late mean condition, which corresponded with an average of 19.4\% indecisions.
-This proportion of indecisions aligns with our recent prior work that examined competitive human-human decision-making with a high time pressure\autocite{lokesh_humans_2022}.
+We saw that 95\% of participants had a win rate less than chance (50\%) in the \emph{late mean} condition, which corresponded with an average of 19.4\% indecisions.
+This proportion of indecisions aligns with our recent prior work that examined competitive human-human decision-making with a high time pressure\autocite{lokeshHumansUtilizeSensory2022}.
 In this competitive task, one participant attempted to reach the same target as their opponent, while the other tried to reach the opposite target within a time constraint.
@@
 Our results would also suggest that participants waited to acquire sensory information of when the stimuli would move.
-Moreover, building upon Lokesh and colleagues (2022), our work also suggests that a key contributor leading to excessive indecisions is failing to account for the time delay and temporal uncertainty when switching from reacting to guessing.
+Moreover, building upon Lokesh and colleagues (2022), our work suggests that a key contributor leading to excessive indecisions is failing to account for the time delay and temporal uncertainty when switching from reacting to guessing.
 
-Past work has suggested that humans can nearly optimally account for time delays and temporal uncertainty when performing decision-making \autocite{balci_risk_2009,jazayeri_temporal_2010,balci_optimal_2011} and movement tasks \autocite*{hudson_optimal_2008,battaglia_humans_2007,dean_trading_2007} when attempting to maximize reward.
+Past work has suggested that humans can nearly optimally account for time delays and temporal uncertainty when performing decision-making \autocite*{balciRiskAssessmentMan2009,jazayeriTemporalContextCalibrates2010,balciOptimalTemporalRisk2011} and movement tasks \autocite*{hudsonOptimalCompensationTemporal2008,deanTradingSpeedAccuracy2007} when attempting to maximize reward.
 Here we considered two optimal models, the No Switch Time Model and Full Switch Time Model, which both had full knowledge of all available time delays and temporal uncertainties.
 Interestingly, both the No Switch Time Model and Full Switch Time Model showed that even when fully accounting for all sensorimotor delays and uncertainties, indecisions were a part of an optimal strategy in all but one of the six conditions.
-In other words, given the inherent delays and uncertainty of our nervous system\autocite{faisal_noise_2008}, an optimal strategy of earning maximal reward may involve indecisive behaviour on some proportion of trials.
+In other words, given the inherent delays and uncertainty of our nervous system\autocite{faisalNoiseNervousSystem2008}, an optimal strategy of earning maximal reward may involve indecisive behaviour on some proportion of trials.
 We are unaware of any work in the literature suggesting that some level of indecisions may be optimal.
 Even though making some indecisions can be optimal, our results in \boldblue{Experiment 1} were in support of the idea that humans are suboptimal.
-Specifically, in the late mean condition, we found that humans were suboptimal since they had a win percentage lower than chance, which arose from an excessive number of indecisions.
+Specifically, in the \emph{late mean} condition, we found that humans were suboptimal since they had a win percentage lower than chance, which arose from an excessive number of indecisions.
 The Partial Switch Time Model was suboptimal, since it had a partial representation of time delays and temporal uncertainties associated with switching from reacting to guessing.
@@
 The Partial Switch Time Model supports the notion that humans suboptimally select decision times when under high time pressures.
-An interesting future direction would be to test whether different reward structures, such as placing a higher reward on wins or punishing indecisions \autocite{kahneman_prospect_2013,roth_reinforcement-based_2023,roth_punishment_2024, galea_dissociable_2015}, would provide a means to reduce an excessive number of indecisions.
+An interesting future direction would be to test whether different reward structures, such as placing a higher reward on wins or punishing indecisions\autocite*{kahnemanProspectTheoryAnalysis2013,rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024,galeaDissociableEffectsPunishment2015}, would provide a means to reduce an excessive number of indecisions.
 
@@
 Dutilh and colleagues (2011) explored the idea of switching between a stimulus controlled (i.e.
-react) mode and a guess mode between trials \autocite{dutilh_phase_2011}.
+react) mode and a guess mode between trials \autocite{dutilhPhaseTransitionModel2011}.
 In their task, participants were required to discriminate between a word stimuli from a non-word stimuli by selecting one of two buttons during a two-alternative forced choice task.
@@
 That is, participants are more likely to stay in their current mode than switch modes.
-They also highlighted that classical decision-making models, such as drift-diffusion models \autocite{ratcliff_modeling_2018} or more recently the urgency-gating model \autocite{cisek_decisions_2009,derosiere_trading_2021,thura_decision_2012} do not consider different modes of reacting or guessing.
+They also highlighted that classical decision-making models, such as drift-diffusion models \autocite{ratcliffModeling2alternativeForcedchoice2018} or more recently the urgency-gating model \autocite*{cisekDecisionsChangingConditions2009,derosiereTradingAccuracySpeed2021,thuraDecisionMakingUrgency2012} do not consider different modes of reacting or guessing.
 Extending upon the findings of Dutilh and colleagues (2011) that examined between trial mode switching, our work suggests that humans switch between react and guess modes within a trial.
@@
 To our knowledge, it is unknown how different modes would be represented in the nervous system.
-One possibility is that the different modes represent different attractors from a neural dynamical systems perspective \autocite{erlhagen_dynamic_2002,wang_decision_2008,churchland_neural_2012,shenoy_cortical_2013}, which would be an interesting avenue of investigation.
+One possibility is that the different modes represent different attractors from a neural dynamical systems perspective \autocite*{erlhagenDynamicFieldTheory2002,wangDecisionMakingRecurrent2008,churchlandNeuralPopulationDynamics2012,shenoyCorticalControlArm2013}, which would be an interesting avenue of investigation.
 
-We found in \boldblue{Experiment 2} that participant response times were more delayed by approximately 75ms during guess trials in the react or guess condition, compared to guess only trials.
-Moreover, the response time difference between guess and react trials in the react or guess condition are significantly greater than the response time difference between the guess only and react only conditions.
-Collectively, these results suggest that participants have an initial preference to react, before having to switch to a guess in the react or guess condition.
+We found in \boldblue{Experiment 2} that participant response times were more delayed by approximately 75ms during guess trials in the \emph{react or guess} condition, compared to guess only trials.
+Moreover, the response time difference between guess and react trials in the \emph{react or guess} condition are significantly greater than the response time difference between the guess only and react only conditions.
+Collectively, these results suggest that participants have an initial preference to react, before having to switch to a guess in the \emph{react or guess} condition.
 In this experiment behaviour may be explained by a strong preference to react since it yields a 100\% success probability, as opposed to guessing that on average yields a 50\% success probability.
@@
 A limitation of the commonly used two-alternative forced choice task without a time constraint is that the participant or animal must select one of two potential options, which does not allow for indecisive behaviour.
-For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis \autocite{forstmann_striatum_2008,diederich_further_2008,wu_capacity_2016,dambacher_time_2015}.
-Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite{karsilar_speed_2014,farashahi_dynamic_2018}.
+For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis\autocite*{forstmannStriatumPreSMAFacilitate2008,diederichFurtherTestSequentialsampling2008,wuCapacityCognitiveControl2016,dambacherTimePressureAffects2015}.
+Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.
 However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
@@
 
-\noindent\textbf{Participants}
+\noindent\boldblue{Participants}
 
@@
 
-\noindent\textbf{Apparatus}
+\noindent\boldblue{Apparatus}
 
@@
 \vspace{2mm}
-\noindent\textbf{\large\textcolor{mydarkblue}Experiment 1 Design}
+\noindent\boldblue{\large Experiment 1 Design}
 
@@
 For each trial within a condition, the stimulus movement onset was drawn from the same normal distribution.
-Using a 3 x 2 within experimental design, we manipulated the stimulus movement onset mean (early mean = 1000 ms, middle mean = 1100 ms, late mean = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms) that resulted in 6 experimental conditions (\boldblue{Fig.
+Using a 3 x 2 within experimental design, we manipulated the stimulus movement onset mean (\emph{early mean} = 1000 ms, \emph{middle mean} = 1100 ms, \emph{late mean} = 1200 ms) and standard deviation (low variance = 50 ms, high variance = 150 ms) that resulted in 6 experimental conditions (\boldblue{Fig.
 1C}).
@@
 
-Prior to \boldblue{Experiment 1}, participants performed two separate tasks to estimate response time (response time task; \boldblue{Supplementary C}) and timing uncertainty (timing uncertainty task; \boldblue{Supplementary D}).
+Prior to \boldblue{Experiment 1}, participants performed two separate tasks to estimate response time (response time task; \boldblue{Supplementary D}) and timing uncertainty (timing uncertainty task; \boldblue{Supplementary E}).
 We counterbalanced the order of the response time and timing uncertainty tasks.
@@
 \vspace{2mm}
-\noindent\textbf{\large\textcolor{mydarkblue} Experiment 2 Design}
+\noindent\boldblue{\large Experiment 2 Design}
 
@@
 
-Using these react and guess trials, participants performed a within experimental design with three conditions: react or guess condition, only react condition, and only guess condition.
-In the react or guess condition, we pseudorandomly interleaved the 50 react trials and 50 guess trials.
+Using these react and guess trials, participants performed a within experimental design with three conditions: \emph{react or guess} condition, \emph{only react} condition, and \emph{only guess} condition.
+In the \emph{react or guess} condition, we pseudorandomly interleaved the 50 react trials and 50 guess trials.
 Participants were informed the stimulus would either move to one of the targets (react trials) or disappear (guess trials).
-The only react condition consisted of 50 react trials.
+The \emph{only react} condition consisted of 50 react trials.
 Participants were informed that the stimulus would move to one of the two targets and would not disappear.
-The only guess condition consisted of 50 guess trials.
+The \emph{only guess} condition consisted of 50 guess trials.
 Participants were informed that the stimulus would only disappear and would not move to one of the two targets.
-The react or guess condition was performed first by participants to avoid any potential carry-over effects of repeatedly performing react or guess trials in the other two conditions.
-After the react or guess condition, the order of the only react condition and only guess condition was counterbalanced.
+The \emph{react or guess} condition was performed first by participants to avoid any potential carry-over effects of repeatedly performing \emph{react or guess} trials in the other two conditions.
+After the \emph{react or guess} condition, the order of the \emph{only react} condition and \emph{only guess} condition was counterbalanced.
 
@@
 
-\noindent \emph{Participant movement onset}: On each trial, we found when the time point where the participant hand velocity exceeded 0.05 m/s \autocite{gribble_role_2003,calalo_sensorimotor_2023}.
+\noindent \emph{Participant movement onset}: On each trial, we found when the time point where the participant hand velocity exceeded 0.05 m/s \autocite{gribbleRoleCocontractionArm2003,calaloSensorimotorSystemModulates2023}.
 The meantime point across all trials within a condition was used to estimate participant movement onset.
@@
 In \boldblue{Experiment 1} we used a 3 (mean: early, middle, late) x 2 (variance: low, high) repeated measures ANOVA for each dependent variable.
-In \boldblue{Experiment 2} we used a 2 (condition: interleaved react and guess, react or guess only) x 2 (trial type: react trials, guess trials) repeated measures ANOVA for each dependent variable.
-For both \boldblue{Experiment 1} and \boldblue{2}, we performed mean comparisons using nonparametric bootstrap hypothesis tests (n = 1,000,000) \autocite{hesterberg_bootstrap_2011,cashaback_dissociating_2017, cashaback_gradient_2019}.
+In \boldblue{Experiment 2} we used a 2 (condition: interleaved react and guess, \emph{react or guess} only) x 2 (trial type: react trials, guess trials) repeated measures ANOVA for each dependent variable.
+For both \boldblue{Experiment 1} and \boldblue{2}, we performed mean comparisons using nonparametric bootstrap hypothesis tests (n = 1,000,000) \autocite*{hesterbergBootstrap2011,cashabackDissociatingErrorbasedReinforcementbased2017,cashabackGradientReinforcementLandscape2019a}.
 Mean comparisons were Holm-Bonferonni correct to account for multiple comparisons.
@@
 
+\newpage
+\input{supplementary}
+
 \end{document}

### 2024-07-30 paper/supplementary.tex
submitted

@@
 
-\newcommand{\SuppCaption}[2]{\noindent\boldblue{{#1}} {#2}\footnotesize}
+\newcommand{\SuppCaption}[2]{\noindent\textbf{{#1}} {#2}\footnotesize}
 \newcommand{\SectionHeader}[1]{\noindent\textbf{\Large\textcolor{mydarkblue}{#1}}\normalsize }
@@
 \renewcommand{\figurename}{Supplementary Figure}
-
-\abovedisplayskip = 10.0pt plus 2.0pt minus 20.0pt
-\belowdisplayskip = 10.0pt plus 2.0pt minus 20.0pt
-\abovedisplayshortskip = 0.0pt plus 20.0pt
-\belowdisplayshortskip = 9pt plus 3pt minus 20pt
 
@@
 
-\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary A: High Variance Results}}
+\noindent\boldblue{\large{Supplementary A: High Variance Results}}
 \begin{figure}[H]
@@
     \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
-    \renewcommand\figurename{Supplementary Figure}
-    \caption{\textbf{Timing Behaviour.} A) Average participant movement onset (y-axis) for each experimental condition (x-axis).
+    \caption*{\boldblue{Supplementary Figure 1: Timing Behaviour.} \boldblue{A)} Average participant movement onset (y-axis) for each experimental condition (x-axis).
 We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset.
-There was no significant interaction (F[1.66,31.47], p = 0.565) B) Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance.
+There was no significant interaction (F[1.66,31.47], p = 0.565) \boldblue{B)} Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance.
 During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint.
@@
 2}).
-C) Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis).
-We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) D) Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance.
+\boldblue{C)} Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis).
+We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) \boldblue{D)} Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance.
 In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions.
@@
     \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
-    \renewcommand\figurename{Supplementary Figure}
 
-    \caption{\textbf{Trial Outcomes.} \textbf{A)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition.
-\textbf{A)} We found that the middle mean low variance and \emph{late mean low variance} condition had a significantly greater number of indecisions compared to the \emph{early mean low variance} condition.
+    \caption*{\boldblue{Supplementary Figure 2: Trial Outcomes.} \boldblue{A)} Indecisions (\%) \boldblue{B)} Wins (\%), and \boldblue{C)} Incorrects (\%) for each condition.
+\boldblue{A)} We found that the middle mean low variance and \emph{late mean low variance} condition had a significantly greater number of indecisions compared to the \emph{early mean low variance} condition.
 That is, in the middle mean low variance and \emph{late mean low variance} conditions, participants often waited to react to the stimulus but ended up guessing late.
 These late guesses often led to indecisions.
-\textbf{B)} Interestingly, we also found that the average win percentage (41\%) was significantly below the 50\% chance level (p < 0.001) in the \emph{late mean low variance} condition, clearly demonstrating suboptimal behaviour.
+\boldblue{B)} Interestingly, we also found that the average win percentage (41\%) was significantly below the 50\% chance level (p < 0.001) in the \emph{late mean low variance} condition, clearly demonstrating suboptimal behaviour.
 Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the stimulus.
@@
 
-\vspace{2mm}
-\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary B: Optimal Models}}
+\newpage
+\noindent\boldblue{\large{Supplementary B: Optimal Models}}
 
@@
 We modelled the time to switch from reacting to guessing as an optimal transition problem.
-This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim \autocite{trommershauser_statistical_2003} and reach timing \autocite{hudson_optimal_2008}.
+This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim \autocite{trommershauserStatisticalDecisionTheory2003} and reach timing \autocite{hudsonOptimalCompensationTemporal2008}.
 Here a model represents a decision-maker that selects a transition time, $\tau$.
@@
 \vspace{2mm}
-\noindent \textbf{General Formulation for the Models}
+\noindent \boldblue{General Formulation for the Models}
 
 \noindent We begin by defining the general normal probability density function and cumulative density function:
-
+\setlength{\belowdisplayskip}{4pt} \setlength{\belowdisplayshortskip}{4pt} % THIS MUST BE HERE FOR EQUATIONS SPACING
+\setlength{\abovedisplayskip}{4pt} \setlength{\abovedisplayshortskip}{4pt}
 % Define pdf and cdf
@@
 Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions.
-We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\textbf{Eq.
-4}) and $T$ as the random variable drawn from the transition time distribution (\textbf{Eq.
-5}).
-
+We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\boldblue{Eq.
+5}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq.
+6}).
 % Define random variables S and T
@@
 Specifically, the probability that the participant will react is the probability that the random variable A is less than T.
-
 % Define prob react and guess
@@
 Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.
-
 \begin{equation}
@@
 We can then define an indicator function ($\mathbbm{1}_{s<t}$), which is equal to one if the realized value $s$ is less than $t$ and zero otherwise:
-
 % Define indicator function 
@@
 We start by calculating the expected value of the random variable $S$, which is the integral from $-\infty$ to $\infty$ of the value $s$ multiplied by the probability density function $f_{S}(s)$.
-
 % Define expected value
@@
 The mean (first moment) of the truncated stimulus movement onset distribution is
-
 % Define Cutoff react mean 
@@
 Similarly, we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
-
+%
 \begin{equation}
@@
 Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
-The participant mean reaction movement onset ($\mu_{mo_{react}}$, \textbf{Eq.
-12}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$).
-Likewise, the standard deviation of participant reaction movement onset (($\sigma_{mo_{react}}$, \textbf{Eq.
-13}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
-
+The participant mean reaction movement onset ($\mu_{mo_{react}}$, \boldblue{Eq.
+14}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$).
+Likewise, the standard deviation of participant reaction movement onset ($\sigma_{mo_{react}}$, \boldblue{Eq.
+15}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
 % Movement Onset times
@@
 Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
-For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, \textbf{Eq.
-14}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$.
-The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\textbf{Eq.
-15}).
-
+For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, \boldblue{Eq.
+16}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$.
+The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\boldblue{Eq.
+17}).
+%
 \begin{equation}
@@
 Crucially, for the Known Switch Time Model and Unknown Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
-
 % Switch time included in movement onset times
@@
 We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as
-
 % Target Reach Time 
@@
 To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to
-
 % Reach random variables
@@
 We can then define the probability that the participant will reach one of the two targets before the time constraint of 1500ms given they react ($P(Reach|React)$) or guess ($P(Reach|Guess)$):
-
 % Probability of Reaching Target
@@
 An indecision is simply the probability that the participant reaches the target after the time constraint:
-
 % Probability of indecision sequence 
@@
 To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$).
-The probability of selecting the correct target when the participant reacts is 100\% (\textbf{Eq.
+The probability of selecting the correct target when the participant reacts is 100\% (\boldblue{Eq.
 24}).
-The probability of selecting the correct target when the participant guesses is 50\% (\textbf{Eq.
+The probability of selecting the correct target when the participant guesses is 50\% (\boldblue{Eq.
 25}).
-
 % Probability of being correct
@@
 The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint, and they select the correct target:
-
 % Probability of winning sequence
@@
 The conditional probability the participant is incorrect given they react ($P(Incorrect|React)$) or guess ($P(Incorrect|Guess)$) is the probability that they reach the target within the time constraint and they select the wrong target:
-
 % Probability of incorrect sequence 
@@
 
-Finally we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\textbf{Eq.
+Finally, we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\boldblue{Eq.
 27-34}) and the probability of reaching and guessing given a transition time ($\tau$), as
-
 \begin{align}
@@
 The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,
-
 % Expected Reward
@@
 The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is
-
+%
 \begin{align}
@@
 The decision policy uses known parameters to select an optimal transition time $\tau^*$ that maximizes expected reward:
-
 % Maximize expected reward with tau
@@
 \vspace{2mm}
-\noindent\textbf{Model Parameter Estimation and Fitting Procedure}
+\noindent\boldblue{Model Parameter Estimation and Fitting Procedure}
 
@@
 We describe the bootstrap procedure below.
-Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature \autocite{norman_electromechanical_1979,rossini_clinical_1998,bruce_primate_1985}.
+Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature\autocite*{normanElectromechanicalDelaySkeletal1979,rossiniClinicalApplicationsMotor1998,brucePrimateFrontalEye1985}.
 
@@
 
-\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ (\autocite*{roth_reinforcement-based_2023,roth_punishment_2024}.
+\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ (\autocite*{rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
 Here the remaining parameters estimated from experimental data were set as the group level means.
 We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means ($Data_{i,j}$) according to
-
 % Loss Equation 
@@
 
-\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times \autocite*{cashaback_dissociating_2017,cashaback_gradient_2019,roth_reinforcement-based_2023,roth_punishment_2024}.
+\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times\autocite*{cashabackGradientReinforcementLandscape2019a, cashabackDissociatingErrorbasedReinforcementbased2017,rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
 We used the mean of the bootstrapped participant data for each of the parameter values that were estimated from data.
-For each bootstrap iteration, the optimization process selected the free parameters for the Full Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$) and Partial Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{\tau}$, $\hat{\sigma}_{\tau}$) that minimized the loss function (\textbf{Eq.
+For each bootstrap iteration, the optimization process selected the free parameters for the Full Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$) and Partial Switch Time Model ($\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{\tau}$, $\hat{\sigma}_{\tau}$) that minimized the loss function (\boldblue{Eq.
 44}).
@@
 \vspace{2mm}
-\noindent \textbf{Model Parameter Values}
+\noindent \boldblue{Model Parameter Values}
 
@@
 \newpage
-\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary C: Model Results}}
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary C: Model Results}}
 
@@
 \begin{figure}[H]
-    \renewcommand\figurename{Supplementary Figure}
-
-    \begin{minipage}[c]{0.64\textwidth}
+    \begin{minipage}[c]{0.6\textwidth}
         \includegraphics[scale = 0.95]{figures/exp1_data_panel_with_models_all_conditions.png}
@@
     \begin{minipage}[c]{0.3\textwidth}
-        \caption{
-            \textbf{Model Outputs}: Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \textbf{A)} participant movement onset time, \textbf{B)} participant movement onset time standard deviation, \textbf{C)} indecisions, \textbf{D)} wins, and \textbf{E)} incorrects for each condition.
+        \caption*{
+            \boldblue{Supplementary Figure 3: Model Outputs}.
+Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \boldblue{A)} participant movement onset time, \boldblue{B)} participant movement onset time standard deviation, \boldblue{C)} indecisions, \boldblue{D)} wins, and \boldblue{E)} incorrects for each condition.
 The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the \emph{late mean low variance} and late mean high variance conditions.
@@
 As a reminder, the Unknown Switch time Model does not account for the delay and uncertainties associated with switching from reacting to guessing.
-Critically, in \textbf{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the \emph{late mean low variance} condition, whereas the other two models predict zero indecisions for that condition.
-Further, in \textbf{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the \emph{late mean low variance} condition.
+Critically, in \boldblue{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the \emph{late mean low variance} condition, whereas the other two models predict zero indecisions for that condition.
+Further, in \boldblue{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the \emph{late mean low variance} condition.
 Collectively, our findings show that humans are suboptimal and excessively indecisive, which can be captured by a model that does not account  for the delay and uncertainties associated with switching from reacting to guessing.
@@
 
-\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary D: Response Time Task}}
+\begin{figure}[H]
+    \centering 
+    \includegraphics[scale = 1]{figures/model_losses.png}
 
-\noindent For the response time task (\boldblue{Supplementary Figure 1}), participants began each trial by moving their cursor (yellow circle, 1 cm diameter) into a start position (white circle, 1.5 cm diameter).
+        \caption*{
+            \boldblue{Supplementary Figure 4: Model Losses}.
+Here we show histograms of each of our model’s bootstrapped losses.
+Loss was calculated as the normalized mean absolute error between the model prediction and experimental data for each of the following metrics: movement onset, movement onset standard deviation, indecisions, wins, and incorrects.
+The median loss is shown by the red line.
+The Partial Switch Time Model has the lowest loss out of the three models, suggesting that participants do not account for a delay and uncertainty when switching from reacting to guessing.
+        } 
+\end{figure}
+
+\newpage
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary D: Response Time Task}}
+
+\noindent For the response time task (\boldblue{Supplementary Figure 5}), participants began each trial by moving their cursor (yellow circle, 1 cm diameter) into a start position (white circle, 1.5 cm diameter).
 Following a randomized time period (600-2400 ms drawn from a uniform distribution), one of two potential targets (white rings, 8 cm diameter) appeared on the screen.
@@
 
-    \caption{\textbf{Response Time Experiment}.
+    \caption*{\boldblue{Supplementary Figure 5: Response Time Experiment}.
 One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
@@
 
-\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary E: Timing Uncertainty Task}}
+\newpage
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary E: Timing Uncertainty Task}}
 
@@
     \centering
-    \includegraphics[scale = 1]{figures/exp1_timing_experimental_design.png}
+    \includegraphics[scale = 0.7]{figures/exp1_timing_experimental_design.png}
 
-    \caption{\textbf{Timing Uncertainty Experiment}.
+    \caption*{\boldblue{Supplementary Figure 6: Timing Uncertainty Experiment}.
 One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
@@
 
-\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary F: Guess Decisions}}
+\newpage
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary F: Guess Decisions}}
 
@@
 
-    \caption{\textbf{Reaction and Guess Decision Percentages for Experiment 1}.
-Estimated percentage of reaction (pink) and guess (blue) decision percentages (y-axis) for each experimental condition (x-axis).
+    \caption*{\boldblue{Supplementary Figure 7: Guess Decision Percentages for Experiment 1}. 
+    Estimated percentage of guess decision percentages (y-axis) for each experimental condition (x-axis).
 During \boldblue{Experiment 1} participants were rewarded for successful trials and experienced a time constraint.
-Thus, we would expect participants to have faster response times in \boldblue{Experiment 1} than in the Response Time task \autocite{milstein_influence_2007,shadmehr_movement_2019}.
+Thus, we would expect participants to have faster response times in Experiment 1 than in the Response Time task \autocite*{milsteinInfluenceExpectedValue2007,shadmehrMovementVigorReflection2019a}.
 To account for this, we adjusted participant response times by subtracting 25ms from their median response time in the Response Time task.
-A trial was a reaction decision if the difference between the stimulus’s movement onset and participant’s movement onset was greater than that participant’s adjusted response time.
-Conversely, a trial was a guess decision if the difference between the stimulus movement onset and participant movement onset was less than that participant’s adjusted response time.
+A trial was a guess decision if the difference between the stimulus movement onset and participant movement onset was less than that participant’s adjusted response time.
 We found that participants guessed significantly more often as the stimulus’s mean movement onset approached the time constraint.}
@@
 
-\newpage
-\fancyhead[L]{} % Need this because print bibliography is dumb and puts a REFERENCES in the left header
-\begin{nolinenumbers}
-    \definecolor{mydarkblue}{RGB}{0,51,102}
+% \newpage
+% \fancyhead[L]{} % Need this because print bibliography is dumb and puts a REFERENCES in the left header
+% \begin{nolinenumbers}
+%     \definecolor{mydarkblue}{RGB}{0,51,102}
 
-    \printbibliography[title=\LARGE\textcolor{mydarkblue}{Supplementary References}]
-\end{nolinenumbers}
+%     \printbibliography[title=\LARGE\textcolor{mydarkblue}{Supplementary References}]
+% \end{nolinenumbers}
 

### 2024-08-01 paper/Cover_letter_Indecisions.tex
submitted
updated cover letter

@@
 \vspace{1.0mm}
-We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{``Indecision under time pressure arises from suboptimal switching behaviour''}}, for publication in \emph{Current Biology}.
-\vspace{1.0mm}
+We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{``Indecision under time pressure arises from suboptimal switching behaviour''}}, for publication in \emph{Proceedings of the National Academy of Sciences}.
+\vspace{3.0mm}
 \\
@@
 \\
-Tony Carlsen, University of Ottawa, University of Ottawa
+Tony Carlsen, University of Ottawa, acarlsen@uottawa.ca
 \\
@@
 %\\
-%Tony Carlsen, University of Ottawa, University of Ottawa
 \end{document}

### 2024-08-01 paper/main.tex
added significance statement to main doc for PNAS

@@
         }}
-    \vspace{5mm}
+    \vspace{4mm}
     \\
@@
 Cashaback\textsuperscript{1,2,3,6,7}
-    \vspace{2mm}
+    \vspace{1mm}
     \\
@@
 \textsuperscript{7} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
-\vspace{4mm}
+\vspace{1mm}
 \\
@@
 \\
-\vspace{4mm}
+\vspace{1mm}
+\\
+\textcolor{mydarkblue}{\large Significance Statement:}
+\vspace{1mm}
+\\
+Indecisive behaviour is highly prevalent in many aspects of daily life.
+Despite its ubiquity, there has been very little focus and a lack of explanation for why indecisions occur.
+Here we find under high time pressure scenarios that indecisions arise by misrepresenting additional time delays and temporal uncertainties associated when attempting to switch from reacting to guessing.
+Our novel paradigm presents a new way to elucidate and study indecisions.
+\\
 \\
@@
 \\
-\vspace{4mm}
-\\
-\textcolor{mydarkblue}{\large Declaration of Interests:}
 \vspace{1mm}
 \\
-The authors declare no competing interests.
-\vspace{5mm}
-\\
 \textcolor{mydarkblue}{\large Correspondence:}
-\vspace{1mm}
 \\
@@
 University of Delaware\\
-STAR Campus, Room 122\\
 Newark, DE 19711, U.S.A\\
 Email: sethsullivan99@gmail.com
-\vspace{2mm}
 \\
-Or
-\vspace{2mm}
 \\

### 2024-08-01 paper/main.tex
final cleanup

@@
 Computational modeling suggested that participants were excessively indecisive because they failed to account for a time delay and temporal uncertainty when switching from reacting to guessing, a phenomenon previously unreported in the literature.
-In a followup experiment we provide direct evidence for functionally relevant time delay and temporal uncertainty when switching from reacting to guessing.
+In a followup experiment we provide direct evidence for a functionally relevant time delay and temporal uncertainty when switching from reacting to guessing.
 Collectively, our results demonstrate that humans are suboptimal and fail to account for a time delay and temporal uncertainty when switching from reacting to guessing, leading to indecisive behaviour.
@@
 During each trial, a stimulus (yellow cursor) would move quickly in a straight line to one of the two targets.
-Participants were instructed to reach the same target as the stimulus within a time constraint of 1500ms.
+Participants were instructed to reach the same target as the stimulus within a time constraint of 1500 ms.
 This time constraint was visually represented with a timing bar (white rectangle) that decreased in width according to the elapsed time.
@@
 
-\noindent Participant movement onsets for the low variance conditions are shown in \boldblue{Fig.
-2A}, We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
+\noindent Participant movement onset for the low variance conditions is shown in \boldblue{Fig.
+2A}.
+We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
 There was no significant interaction between stimulus movement onset mean and variance (F[1.66,31.47], p = 0.565).
-When collapsed across low and high variance, participant movement onsets were significantly greater in the \emph{middle mean} conditions compared to the \emph{early mean} conditions (p = 0.014, $\hat{\theta}$ = 72.5 \%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
-Again when collapsed across low and high variance, participant movement onset significantly decreased from the \emph{middle mean} conditions to the \emph{late mean} conditions (p = 0.018, $\hat{\theta}$ = 62.5\%).
+When collapsed across low and high variance, participant movement onsets were significantly greater in the \emph{middle mean} conditions compared to the \emph{early mean} conditions (p = 0.014, $\hat{\theta}$ = 72.5\%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
+Again, when collapsed across low and high variance, participant movement onset significantly decreased from the \emph{middle mean} conditions to the \emph{late mean} conditions (p = 0.018, $\hat{\theta}$ = 62.5\%).
 Here, an earlier participant movement onset in the \emph{late mean} condition suggests that participants attempted to wait and react to the stimulus, but ended up guessing.
 
-Participant movement onset standard deviation for the low variance conditions are shown in \boldblue{Fig.
+Participant movement onset standard deviation for the low variance conditions is shown in \boldblue{Fig.
 2B}.
@@
 Critically, participants would have earned more points if they had simply guessed earlier on all trials, rather than attempting to react to the stimulus.
-Model Results: Only the Partial Switch Time Model, which had only a partial representation of the time delay and uncertainty when switching from reacting to guessing, was able to predict the indecisions and a suboptimal win rate (below 50\%) in the \emph{late mean} condition.
+\boldblue{Model Results}: Only the Partial Switch Time Model, which had only a partial representation of the time delay and uncertainty when switching from reacting to guessing, was able to predict the indecisions and a suboptimal win rate (below 50\%) in the \emph{late mean} condition.
 See \boldblue{Fig.
@@
 Interestingly, in the \emph{late mean} condition we found that the average win percentage was significantly below the 50\% chance level (p<0.001; $\hat{\theta}$ = 95.0\%), which was true for 19 out of 20 participants.
-Since guessing on every trial would lead to a win percentage of 50\%, the only way participants would be below chance is if they are excessively indecisive.
+Since guessing on every trial would lead to a win percentage of 50\%, the only way participants would be below chance is if they were excessively indecisive.
 The incorrect percentage across all conditions was 26.3\% [range: 0.0\%, 57.5\%; \boldblue{Fig.
 2E}].
-We found significant interactions between stimulus movement onset mean and variance for incorrect decisions (F[1.66,31.51]=3.72, p=0.033).
+We found significant interactions between stimulus movement onset mean and variance for incorrect decisions (F[1.66,31.51] = 3.72, p = 0.033).
 Participants displayed a greater percentage of incorrect decisions in the \emph{late mean} condition than the \emph{early mean} condition (p < 0.001, $\hat{\theta}$ = 92.5\%).
@@
 The switch time delay and uncertainty were only partially represented by the Partial Switch Time Model when determining the optimal time to switch from reacting and guessing.
-However, we are not aware of any work that considers the temporal time delays and uncertainty associated with switching from reacting to guessing within a trial.
+However, we are not aware of any work that considers a delay and uncertainty associated with switching from reacting to guessing within a trial.
 The goal of \boldblue{Experiment 2} was to determine if there is indeed a switch delay and uncertainty that occurs when humans transition from reacting to guessing.
@@
 Once the stimulus disappeared, participants were instructed to guess which target the stimulus would appear in and select that target as quickly as possible.
-After the participant reached the target, the stimulus’s cursor would appear in one of the targets.
+After the participant reached the target, the stimulus cursor would appear in one of the targets.
 \boldblue{C)} We had three experimental conditions.
@@
 In this competitive task, one participant attempted to reach the same target as their opponent, while the other tried to reach the opposite target within a time constraint.
-It was suggested that the high proportion of indecisions in this competitive human-human task were the result of participants waiting too long to acquire sensory information of their opponent, despite the impending time deadline.
+It was suggested that the high proportion of indecisions were the result of participants waiting too long to acquire sensory information of their opponent, despite the impending time deadline.
 Likewise, we found a high proportion of indecisions across experimental conditions.
@@
 Specifically, in the \emph{late mean} condition, we found that humans were suboptimal since they had a win percentage lower than chance, which arose from an excessive number of indecisions.
-The Partial Switch Time Model was suboptimal, since it had a partial representation of time delays and temporal uncertainties associated with switching from reacting to guessing.
+The Partial Switch Time Model was suboptimal, since it had a partial representation of the time delay and temporal uncertainties associated with switching from reacting to guessing.
 We found that this model best explained behaviour, including a below chance win percentage and an excessive number of indecisions.
@@
 
-The combined empirical evidence of \boldblue{Experiment 1} and computational modelling suggested the existence of time delay and uncertainty when switching from reacting to guessing.
+The combined empirical evidence of \boldblue{Experiment 1} and computational modelling suggested the existence of a time delay and uncertainty when switching from reacting to guessing.
 However, we were unaware of any work in the literature to support this idea.
@@
 One possibility for increased time delays and temporal uncertainty could be related to switching between different processing ‘modes’.
-In our task, participants may have switched from a `react mode’ that corresponded to preparing to follow the stimulus, and then switch to a `guess mode’ to randomly select one of the targets.
+In our task, participants may have switched from a `react mode’ that corresponded to preparing to follow the stimulus, to a `guess mode’ to randomly select one of the targets.
 
@@
 In their task, participants were required to discriminate between a word stimuli from a non-word stimuli by selecting one of two buttons during a two-alternative forced choice task.
-Between trials, the authors manipulated whether participants received more reward for fast decisions to promote guessing, or more reward for accurate decisions that promoted reacting.
+Between trials, the authors manipulated whether participants received more reward for accurate decisions to promote reacting, or more reward for fast decisions that promoted guessing.
 Participants displayed longer response times when transitioning from more accurate decisions to fast decisions, compared to when transitioning from fast decisions to accurate decisions given the same current reward weighting.
@@
 That is, participants are more likely to stay in their current mode than switch modes.
-They also highlighted that classical decision-making models, such as drift-diffusion models \autocite{ratcliffModeling2alternativeForcedchoice2018} or more recently the urgency-gating model \autocite*{cisekDecisionsChangingConditions2009,derosiereTradingAccuracySpeed2021,thuraDecisionMakingUrgency2012} do not consider different modes of reacting or guessing.
-Extending upon the findings of Dutilh and colleagues (2011) that examined between trial mode switching, our work suggests that humans switch between react and guess modes within a trial.
+They also highlighted that classical decision-making models, such as drift-diffusion models \autocite{ratcliffModeling2alternativeForcedchoice2018} or more recently the urgency-gating model \autocite*{cisekDecisionsChangingConditions2009,derosiereTradingAccuracySpeed2021,thuraDecisionMakingUrgency2012}, do not consider different modes of reacting or guessing.
+Extending upon the findings of Dutilh and colleagues (2011) that examined between trial mode switching, our work suggests that humans switch react and guess modes within a trial.
 Importantly, we find that not accounting for the time delays and temporal uncertainties when switching from reacting to guessing gives rise to excessive indecisions.
@@
 
-We found in \boldblue{Experiment 2} that participant response times were more delayed by approximately 75ms during guess trials in the \emph{react or guess} condition, compared to guess only trials.
-Moreover, the response time difference between guess and react trials in the \emph{react or guess} condition are significantly greater than the response time difference between the guess only and react only conditions.
-Collectively, these results suggest that participants have an initial preference to react, before having to switch to a guess in the \emph{react or guess} condition.
+We found in \boldblue{Experiment 2} that participant response times were more delayed by approximately 75 ms during guess trials in the \emph{react or guess} condition, compared to guess only trials.
+Moreover, the response time difference between guess and react trials in the \emph{react or guess} condition are significantly greater than the response time difference between the \emph{guess only} and \emph{react only} conditions.
+Collectively, these results suggest that participants have an initial preference to react, before having to switch to a guess.
 In this experiment behaviour may be explained by a strong preference to react since it yields a 100\% success probability, as opposed to guessing that on average yields a 50\% success probability.
@@
 
-Here we showed in our first experiment humans are excessively indecisive under time constraints.
-Computational work and second experiment suggest that indecisive behaviour can occur by not accounting for the time delays and temporal uncertainty associated with switching from reacting to guessing.
+Here we showed in our first experiment that humans are excessively indecisive under time constraints.
+Computational work and a second experiment suggested that indecisive behaviour can occur by not accounting for the time delay and temporal uncertainty associated with switching from reacting to guessing.
 Our experimental and theoretical approach offers a new paradigm to study indecisions, which has received surprisingly little attention despite its ecological relevance.
@@
 
-\vspace{2mm}
+\vspace{5mm}
 \noindent\boldblue{\large Experiment 1 Design}
@@
 
-\noindent The goal of \boldblue{Experiment 2} was to test whether there is a time delay and uncertainty associated with switching from reacting to guessing.
+\noindent The goal of \boldblue{Experiment 2} was to test whether there is a time delay and uncertainty when switching from reacting to guessing.
 To investigate, participants began each trial by moving their cursor into a start position.
@@
 \noindent \emph{Participant movement onset}: On each trial, we found when the time point where the participant hand velocity exceeded 0.05 m/s \autocite{gribbleRoleCocontractionArm2003,calaloSensorimotorSystemModulates2023}.
-The meantime point across all trials within a condition was used to estimate participant movement onset.
+The mean time point across all trials within a condition was used to estimate participant movement onset.
 

### 2024-08-01 paper/supplementary.tex
final cleanup

@@
     \centering
-    \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
+    \includegraphics[scale =1]{figures/exp1_movement_onset_panel_all_conditions.png}
     \caption*{\boldblue{Supplementary Figure 1: Timing Behaviour.} \boldblue{A)} Average participant movement onset (y-axis) for each experimental condition (x-axis).
@@
 Waiting longer to react and/or late guessing led to later movement onset.
-In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see Supplementary Figure 6).
+In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see \boldblue{Supplementary Figure 6}).
 The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition.
@@
 Box and whisker plots display the 25th, 50th, and 75th percentiles.
-Open gray circles and connecting lines represent individual data.}
+Open circles and connecting lines represent individual data.}
 \end{figure}
@@
 Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target.
-Stimulus Movement onset is knowledge of the mean ($\mu_{S}$) and uncertainty ($\sigma_{A}$) of the stimulus’s movement onset distribution.
+Stimulus Movement onset is knowledge of the mean ($\mu_{S}$) and uncertainty ($\sigma_{S}$) of the stimulus’s movement onset distribution.
 Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended transition time, $\tau$.
@@
 This model had the following unknown parameters: switch time mean and uncertainty, and timing uncertainty.
-The Partial Switch Time Model reflects our hypothesis that participants do not account for the delay and uncertainties associated with guessing.
+The Partial Switch Time Model reflects our hypothesis that participants can only partially account for the delay and uncertainties associated with guessing.
 
@@
 \setlength{\abovedisplayskip}{4pt} \setlength{\abovedisplayshortskip}{4pt}
+
+\setcounter{equation}{0}
+
 % Define pdf and cdf
@@
 We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\boldblue{Eq.
-5}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq.
-6}).
+4}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq.
+5}).
 % Define random variables S and T
@@
 Conversely, the decision-maker will guess at the transition time if the stimulus has not moved by the transition time (i.e., $s>t$).
-Thus, the probability that a participant will react or guess depends on the participants choice of a transition time $\tau$.
-Specifically, the probability that the participant will react is the probability that the random variable A is less than T.
+Thus, the probability that a participant will react or guess depends on the participants choice of a transition time mean ($\tau$).
+Specifically, the probability that the participant will react is the probability that the random variable T is greater than S.
 % Define prob react and guess
 \begin{equation}
-    P(React|\tau) = P(T>S)
+    P(React|\tau) = P(T>S).
 \end{equation}
 
-Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.
+The probability that the participant will guess is the probability that the random variable T is less than S.
 \begin{equation}
-    P(Guess|\tau) = P(T<S)
+    P(Guess|\tau) = P(T<S).
 \end{equation}
@@
 \begin{equation}
-    \mu_{S} = \mathbb{E}[S] = \int_{-\infty}^{\infty}s \cdot f_{S}(s)ds
+    \mu_{S} = \mathbb{E}[S] = \int_{-\infty}^{\infty}s \cdot f_{S}(s).ds
 \end{equation}
@@
 We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{s<t}$).
-Since this double integral multiplies two gaussian probability density functions and only sums values if $s$ is less than $t$, we must normalize by dividing by the probability that A is less than T.
+Since this double integral multiplies two gaussian probability density functions and only sums values if $s$ is less than $t$, we must normalize by dividing by the probability that S is less than T.
 The mean (first moment) of the truncated stimulus movement onset distribution is
@@
 \begin{equation}
-    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}
+    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}.
 \end{equation}
@@
 \begin{equation}
-    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ ds \ dt}{P(S<T)}
+    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ ds \ dt}{P(S<T)}.
 \end{equation}
@@
 The participant mean reaction movement onset ($\mu_{mo_{react}}$, \boldblue{Eq.
-14}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$).
+12}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$).
 Likewise, the standard deviation of participant reaction movement onset ($\sigma_{mo_{react}}$, \boldblue{Eq.
-15}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
+13}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{S_{react}}^2$) plus the participant response time variance ($\sigma_{rt}^2$).
 % Movement Onset times
 \begin{equation}
-    \mu_{mot_{react}} = \mu_{S_{react}} + \mu_{rt}
+    \mu_{mo_{react}} = \mu_{S_{react}} + \mu_{rt}
 \end{equation}
 \begin{equation}
-    \sigma_{mot_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
+    \sigma_{mo_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
 \end{equation}
@@
 Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
-For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, \boldblue{Eq.
-16}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$.
-The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\boldblue{Eq.
-17}).
+For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mo_{guess}}$, \boldblue{Eq.
+14}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$.
+The participant standard deviation guess movement onset ($\sigma_{mo_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\boldblue{Eq.
+15}).
 %
 \begin{equation}
-    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
+    \mu_{mo_{guess}} = \tau +  \mu_{nmd}
 \end{equation}
 \begin{equation}
-    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
+    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
 \end{equation}
 
-Crucially, for the Known Switch Time Model and Unknown Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
+Crucially, for the Full Switch Time Model and Partial Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
 % Switch time included in movement onset times
 \begin{equation}
-    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
+    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
 \end{equation}
 \begin{equation}
-    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
+    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
 \end{equation}
 
-For both the known switch time model and unknown switch time models, the switch time mean and uncertainty influence the model outputs.
+For both the Full Switch Time Model and Partial Switch Time Model, the switch time mean and uncertainty influence the model outputs.
 However, the decision policy of the Full Switch Time Model has perfect knowledge of the switch time, while the decision policy of the Partial Switch Time Model has imperfect knowledge of the switch time.
@@
 
-We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as
+We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach_{guess}}$) and standard deviation ($\sigma_{reach_{guess}}$) as
 % Target Reach Time 
 \begin{align}
-    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
-    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
-    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
-    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}.
+    \mu_{reach_{react}} =\mu_{mo_{react}} + \mu_{mt}                      \\
+    \sigma_{reach_{react}} = \sqrt{\sigma_{mo_{react}}^2 + \sigma_{mt}^2} \\
+    \mu_{reach_{guess}} =\mu_{mo_{guess}} + \mu_{mt}                      \\
+    \sigma_{reach_{guess}} = \sqrt{\sigma_{mo_{guess}}^2 + \sigma_{mt}^2}.
 \end{align}
@@
     X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
-    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
-    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}}).
+    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}})
+    % \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}}).
 \end{align}
@@
 We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect.
-The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from Eqs.
-20-21.
-An indecision is simply the probability that the participant reaches the target after the time constraint:
+The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from \boldblue{Eqs.
+24-25}.
+An indecision is simply the probability that the participant does not reach the target within the time constraint:
 % Probability of indecision sequence 
@@
 The probability of selecting the correct target when the participant reacts is 100\% (\boldblue{Eq.
-24}).
+28}).
 The probability of selecting the correct target when the participant guesses is 50\% (\boldblue{Eq.
-25}).
+29}).
 % Probability of being correct
@@
 Finally, we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\boldblue{Eq.
-27-34}) and the probability of reaching and guessing given a transition time ($\tau$), as
+26-33}) and the probability of reaching and guessing given a transition time ($\tau$), as
 \begin{align}
@@
 \begin{equation}
-    R_{incorrect} = 0
+    R_{incorrect} = 0.
 \end{equation}
@@
 \begin{align}
-    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
+    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}.
 \end{align}
@@
 \begin{equation}
-    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
+    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)].
 \end{equation}
@@
 
-We used both a warm-start initialization and bootstrap procedure (see below) to determine the switch time mean ($\mu_{switch}$) and uncertainty ($\sigma_{switch}$), as well as the decision policy’s knowledge of the switch time mean ($\hat{\mu}_{switch}$, switch time uncertainty ($\hat{\sigma}_{switch}$), and timing uncertainty ($\hat{\sigma}_{\tau}$).
+We used both a warm-start initialization and bootstrap procedure (see below) to determine the switch time mean ($\mu_{switch}$) and uncertainty ($\sigma_{switch}$), as well as the decision policy’s knowledge of the switch time mean ($\hat{\mu}_{switch}$), switch time uncertainty ($\hat{\sigma}_{switch}$), and timing uncertainty ($\hat{\sigma}_{\tau}$).
 
@@
 
-\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ (\autocite*{rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
+\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ \autocite*{rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
 Here the remaining parameters estimated from experimental data were set as the group level means.
@@
 \end{equation}
-where $i$ corresponds to experimental condition and $j$ corresponds to each dependent measure (i.e., movement onset, standard deviation of participant movement onset, wins, indecisions, and incorrects) over the target metrics.
-This fitting procedure was repeated 1,000 times to avoid local minimums.
+where $i$ corresponds to experimental condition and $j$ corresponds to each dependent measure (i.e., movement onset, standard deviation of participant movement onset, wins, indecisions, and incorrects).
+The fitting procedure was repeated 1,000 times to avoid local minimums.
 From these 1,000 optimizations, we used the set of parameters that resulted in the lowest loss as the initial guess for our bootstrap procedure.
 Model fitting was performed using the Powell algorithm in the Minimize function from the Scipy Python library.
-The parameter set with the lowest loss was used as the initial guess for the bootstrap procedure.
 
@@
 The values that were used by the decision policy were: timing uncertainty (1.65 ms;  [0.08, 4.63]), switch time mean (9.0 ms; [0.00, 16.65]), switch time uncertainty (40.4 ms; [34.54, 48.02]).
-Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and transition time certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.
+Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and timing certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.
 
@@
             \boldblue{Supplementary Figure 3: Model Outputs}.
-Here we show model fits for the No Switch Time Model (light gray circles), Known Switch Time Model (dark gray circles), and the Unknown Switch Time Model (black circles) for \boldblue{A)} participant movement onset time, \boldblue{B)} participant movement onset time standard deviation, \boldblue{C)} indecisions, \boldblue{D)} wins, and \boldblue{E)} incorrects for each condition.
-The No Switch Time Model and Known Switch Time Model poorly predict the participant data across all five metrics for the \emph{late mean low variance} and late mean high variance conditions.
-Conversely, the Unknown Switch Time Model (black) is able to accurately predict the participant data for all conditions across all metrics.
-As a reminder, the Unknown Switch time Model does not account for the delay and uncertainties associated with switching from reacting to guessing.
-Critically, in \boldblue{C)} the Unknown Switch Time Model (black) predicts participant indecisions in the \emph{late mean low variance} condition, whereas the other two models predict zero indecisions for that condition.
-Further, in \boldblue{D)} the Unknown Switch Time Model (black) is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the \emph{late mean low variance} condition.
+Here we show model fits for the No Switch Time Model (light gray circles), Full Switch Time Model (dark gray squares), and the Partial Switch Time Model (black diamonds) for \boldblue{A)} participant movement onset time, \boldblue{B)} participant movement onset time standard deviation, \boldblue{C)} indecisions, \boldblue{D)} wins, and \boldblue{E)} incorrects for each condition.
+The No Switch Time Model and Full Switch Time Model poorly predict the participant data across all five metrics for the \emph{late mean low variance} and late mean high variance conditions.
+Conversely, the Partial Switch Time Model (black diamond) is able to accurately predict the participant data for all conditions across all metrics.
+As a reminder, the Partial Switch Time Model does not account for the delay and uncertainties associated with switching from reacting to guessing.
+Critically, in \boldblue{C)} the Partial Switch Time Model predicts participant indecisions in the \emph{late mean low variance} condition, whereas the other two models predict zero indecisions for that condition.
+Further, in \boldblue{D)} the Partial Switch Time Model is the only model that aligns with the finding that participants are suboptimal and win less than 50\% of trials in the \emph{late mean low variance} condition.
 Collectively, our findings show that humans are suboptimal and excessively indecisive, which can be captured by a model that does not account  for the delay and uncertainties associated with switching from reacting to guessing.
@@
 During \boldblue{Experiment 1} participants were rewarded for successful trials and experienced a time constraint.
-Thus, we would expect participants to have faster response times in Experiment 1 than in the Response Time task \autocite*{milsteinInfluenceExpectedValue2007,shadmehrMovementVigorReflection2019a}.
+Thus, we would expect participants to have faster response times in \boldblue{Experiment 1} than in the Response Time task \autocite*{milsteinInfluenceExpectedValue2007,shadmehrMovementVigorReflection2019a}.
 To account for this, we adjusted participant response times by subtracting 25ms from their median response time in the Response Time task.

### 2024-08-12 paper/main.tex
final adjustments to paper before preprint, pending one more change

@@
 \\
-\textcolor{mydarkblue}{\large Significance Statement:}
-\vspace{1mm}
-\\
-Indecisive behaviour is highly prevalent in many aspects of daily life.
+% \textcolor{mydarkblue}{\large Significance Statement:}
+% \vspace{1mm}
+% \\
+% Indecisive behaviour is highly prevalent in many aspects of daily life.
 Despite its ubiquity, there has been very little focus and a lack of explanation for why indecisions occur.
@@
 Our novel paradigm presents a new way to elucidate and study indecisions.
-\\
+% \\
 \\
@@
 When acting under high pressure time constraints, the ability to accurately time a decision is critical to success.
-Past literature has had very little focus on indecisions.
 The vast majority of decision-making research either does not consider responses made after some time constraint or simply does not permit a non-response, such as in the classic two-alternative forced choice paradigm \autocite{zacksenhouseRobustOptimalStrategies2010, bogaczPhysicsOptimalDecision2006, choMechanismsUnderlyingDependencies2002, joganNewTwoalternativeForced2014, ratcliffDiffusionDecisionModel2008,ulrichThresholdEstimationTwoalternative2004,tylerSignalDetectionTheory2000}.

### 2024-08-13 paper/supplementary.tex
final adjustments to paper before preprint, pending one more change
fixed typo and indent

@@
 
-\noindent\boldblue{\large{Supplementary A: High Variance Results}}
+\noindent\boldblue{\large{Supplementary A: Low and High Variance Results}}
 \begin{figure}[H]
@@
 \noindent\boldblue{\large{Supplementary B: Optimal Models}}
+\vspace{-1mm}
 
-We tested three different models to investigate the ability of participants to maximize reward during \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
+\noindent We tested three different models to investigate the ability of participants to maximize reward during \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
 2}).
@@
 Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions.
-We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\boldblue{Eq.
+We begin by defining $S$ as the random variable drawn from the stimulus movement onset distribution (\boldblue{Eq.
 4}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq.

### 2024-08-15 paper/main.tex
my version of adding in the new paragraph after PNAS review

@@
 A trial was considered an indecision and the participant received zero points if they failed to reach a target within the time constraint.
+That is, we considered an indecision to be not reaching a target within the time constraint and thus failing to make a decision in time.
 
@@
 For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis\autocite*{forstmannStriatumPreSMAFacilitate2008,diederichFurtherTestSequentialsampling2008,wuCapacityCognitiveControl2016,dambacherTimePressureAffects2015}.
-Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.
+These studies tend to focus on  response times and response time distributions of correct and incorrect decisions.
 However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
+
+Two different frameworks to model human decision-making are decision theoretic models (Berger 1985) and  drift-diffusion models (Ratcliff 2016 review)\autocite*{ratcliffDiffusionDecisionModel2008}.
+Decision theoretic models use knowledge of sensorimotor delays and uncertanties to select decisions that maximize reward (more citations)\autocite*{hudsonOptimalCompensationTemporal2008, otaMotorPlanningTemporal2015}.
+Drift-diffusion models characterize the decision-making process through a noisy decision variable that reaches some threshold to make a decision.
+However, unlike decision theoretic models, drift-diffusion models do not explicitly represent sensorimotor delays and uncertainties (e.g.
+reaction time, movement time, timing uncertainty, switch time), which is a critical factor when selecting optimal decisions.
+
+Drift-diffusion models can capture indecisions through the decision variable failing to cross a threshold within a time constraint.
+Yet, prior work using these models for decision-making tasks under time constraints do not model indecisions\autocite*{karsilarSpeedAccuracyTradeoff2014, farashahiDynamicCombinationSensory2018}.
+Further, drift-diffusion models would indicate a guess decision through a noisy decision variable crossing a threshold at random.
+However, these models do not consider guessing as a separate process from reacting to a stimulus (i.e.
+a person consciously deciding when to guess).
+This notion of guessing being a separate process has been proposed by Yellot and colleaugues (1970, ADD TO BIB) in their fast-guess model.
+However, like drift-diffusion models, their modeling framweork also did not consider a representation of sensorimotor delays and uncertainties for optimal decision-making, which decision theoretic models have shown to be important for explaining human behaviour.
+In \boldblue{Experiment 1}, participants were required to account for sensorimotor delays and uncertainties to decide when to switch from waiting to react to making a guess.
+Thus, our modeling approach can be considered as a complementary blend between the decision-theoretic and fast-guess models.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace{2mm}
@@
 
-\noindent 44 participants participated across two experiments 20 individuals participated in \boldblue{Experiment 1} and 24 individuals participated in \boldblue{Experiment 2}.
+\noindent 44 participants participated across two experiments.
+20 individuals participated in \boldblue{Experiment 1} and 24 individuals participated in \boldblue{Experiment 2}.
 All participants reported they were free from musculoskeletal injuries, neurological conditions, or sensory impairments.

### 2024-08-19 paper/main.tex
josh edits on new paragraph and added onagawa and yellot citations

--- 2024-08-12 paper/main.tex
@@
 \\
-Indecision arises from suboptimal switching
+Indecision arises from suboptimal switching behaviour
 \\
@@
 We found that participants were suboptimal, displaying a below chance win percentage due to an excessive number of indecisions.
-Computational modeling suggested that participants were excessively indecisive because they failed to account for a time delay and temporal uncertainty when switching from reacting to guessing, a phenomenon previously unreported in the literature.
+Computational modelling suggested that participants were excessively indecisive because they failed to account for a time delay and temporal uncertainty when switching from reacting to guessing, a phenomenon previously unreported in the literature.
 In a followup experiment we provide direct evidence for a functionally relevant time delay and temporal uncertainty when switching from reacting to guessing.
@@
 Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite*{balciOptimalTemporalRisk2011,mileticCautionDecisionmakingTime2019} and motor tasks\autocite*{hudsonOptimalCompensationTemporal2008,faisalOptimalCombinationSensory2009}.
-Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016}.
+Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016, onagawaSensorimotorStrategySelection2021, onagawaRiskAversion2019}.
 With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.
@@
 
+\vspace{-5mm}
 \noindent The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles.
@@
 
+\vspace*{-4mm}
 Likewise, if there was a switch time delay we would also expect a comparatively greater response time difference between guess and react trials in the \emph{react or guess} condition, compared to the response time difference between \emph{only guess} trials and \emph{only react} trials [i.e., guess - react (\emph{react or guess} condition) > guess - react (guess only and react only conditions)].
@@
 
+Decision theoretic and drift-diffusion models are two common frameworks used to model decision-making.
+Decision theoretic models use knowledge of sensorimotor delays and uncertainties to select decision times that maximize reward\autocite*{mileticCautionDecisionmakingTime2019,balciRiskAssessmentMan2009, onagawaRiskAversionAdjustment2019,battagliaHumansTradeViewing2007}.
+Drift-diffusion models characterize the decision-making process through a decision variable that crosses a threshold to decide\autocite*{ratcliffModeling2alternativeForcedchoice2018,ratcliffDiffusionDecisionModel2008}.
+Unlike decision theoretic models, drift-diffusion models do not explicitly represent several potential sources of sensorimotor delays and uncertainties (e.g.
+reaction time, movement time, timing uncertainty, switch time), which is an important factor when determining the optimal decision time.
+Drift-diffusion models can capture indecisions through the decision variable failing to cross a decision threshold within a time constraint.
+Prior work using these models for decision-making tasks under time constraints have ignored indecisions\autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.
+Further, drift-diffusion models indicate a guess decision when the noisy decision variable randomly crosses some threshold but do not consider guessing as a separate process from reacting to evidence (i.e., a person consciously deciding when to guess).
+The notion of guessing being a separate process from reacting was proposed by Yellot in a fast-guess model\autocite*{yellottCorrectionFastGuessing1971}.
+However, like drift-diffusion models, their modelling framework also did not consider a representation of sensorimotor delays and uncertainties.
+Thus, our modelling approach can be considered as a complementary blend between the decision-theoretic and fast-guess models.
+
 The combined empirical evidence of \boldblue{Experiment 1} and computational modelling suggested the existence of a time delay and uncertainty when switching from reacting to guessing.
@@
 For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis\autocite*{forstmannStriatumPreSMAFacilitate2008,diederichFurtherTestSequentialsampling2008,wuCapacityCognitiveControl2016,dambacherTimePressureAffects2015}.
-Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.
-However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
+These studies tend to focus on  response times and response time distributions of correct and incorrect decisions Furthermore, previous modelling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
 
@@
 
+\newpage
 \fancyhead[L]{} % Need this because print bibliography is dumb and puts a REFERENCES in the left header

### 2024-08-19 paper/main.tex
spacing fixes
fixed citation, submitting to plos biology

@@
 Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite*{balciOptimalTemporalRisk2011,mileticCautionDecisionmakingTime2019} and motor tasks\autocite*{hudsonOptimalCompensationTemporal2008,faisalOptimalCombinationSensory2009}.
-Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016, onagawaSensorimotorStrategySelection2021, onagawaRiskAversion2019}.
+Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016, onagawaSensorimotorStrategySelection2021,onagawaRiskAversionAdjustment2019}.
 With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.
@@
 
-\vspace{10mm}
+% \vspace{10mm}
 \noindent \boldblue{Response Time Uncertainty}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{2mm}
+\newpage
 \SectionHeader{Methods}

### 2024-08-27 paper/Cover_letter_Indecisions.tex
changes for plos comp bio

@@
 \vspace{1.0mm}
-We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{``Indecision under time pressure arises from suboptimal switching behaviour''}}, for publication in \emph{Proceedings of the National Academy of Sciences}.
+We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{PLOS Computational Biology}.
 \vspace{3.0mm}

### 2024-08-27 paper/main.tex
changes for plos comp bio

@@
 \\
-% \textcolor{mydarkblue}{\large Significance Statement:}
-% \vspace{1mm}
-% \\
-% Indecisive behaviour is highly prevalent in many aspects of daily life.
+\textcolor{mydarkblue}{\large Author Summary:}
+\vspace{1mm}
+\\
+Indecisive behaviour is highly prevalent in many aspects of daily life.
 Despite its ubiquity, there has been very little focus and a lack of explanation for why indecisions occur.
@@
 Our novel paradigm presents a new way to elucidate and study indecisions.
-% \\
+\\
 \\
@@
 We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokeshHumansUtilizeSensory2022}.
-In this competitive scenario, the ‘prey’ attempted to end up in the same target as the ‘predator’ by a time constraint, while the predator attempted to end up in the opposite target as the prey.
-This task had a high time pressure, such that participants were awarded no points if they were indecisive by failing to enter either target within the time constraint.
+In this competitive scenario, the ‘predator’ attempted to end up in the same target as the ‘prey’ by a time constraint, while the prey attempted to end up in the opposite target as the predator.
+This task had a high time pressure, such that participants were award ed no points if they were indecisive by failing to enter either target within the time constraint.
 The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision.

### 2024-08-27 paper/main.tex
fixed typo

@@
 In this competitive scenario, the ‘predator’ attempted to end up in the same target as the ‘prey’ by a time constraint, while the prey attempted to end up in the opposite target as the predator.
-This task had a high time pressure, such that participants were award ed no points if they were indecisive by failing to enter either target within the time constraint.
+This task had a high time pressure, such that participants were awarded no points if they were indecisive by failing to enter either target within the time constraint.
 The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision.

### 2024-10-02 scripts/generate_df_for_stats.py
exp1 trial by trial df condition repeats and tiles were not correct

@@ -128,8 +128,8 @@ def generate_exp1_trial_dataframe(group, EXPERIMENT="Exp1", DROP_SUBJECT_NUM=Non
     trial_number = np.tile(np.arange(1,it.num_trials + 1, 1, dtype=int), it.num_subjects*it.num_blocks)
     # alt_condition = np.tile(['1000 (50)','1000 (150)','1100 (50)','1100 (150)', '1200 (50)', '1200 (150)'],it.num_subjects).tolist()
     if EXPERIMENT == "Exp1":
-        factor1 = np.repeat(["1000", "1000", "1100", "1100", "1200", "1200"], it.num_subjects*it.num_trials)
-        factor2 = np.repeat(["50","50","50", "150", "150","150"], it.num_subjects*it.num_trials)
+        factor1 = np.tile(np.repeat(["1000", "1000", "1100", "1100", "1200", "1200"], it.num_trials), it.num_subjects)
+        factor2 = np.tile(np.repeat(["50", "150", "50", "150", "50", "150"], it.num_trials), it.num_subjects)
         points = np.full_like(win, 0)
     else:
         factor1 = np.tile(["0 Inc", "-1 Inc", "0 Inc", "-1 Inc"], it.num_subjects)

### 2024-10-02 src/plot_functions.py
added functionality to plot_stats_v2 to use dict or dataframe for pvals

@@ -611,7 +611,10 @@ def plot_stats_v2(ax, pvals:list[dict],cles, combos:list[str],
             kwargs.update({'cles':cles.iloc[0][combos[i]]})
         else:
             kwargs.update({'cles':None})
-        pval = pvals.iloc[0][combos[i]]
+        if isinstance(pvals, dict):
+            pval = pvals[combos[i]]
+        else:
+            pval = pvals.iloc[0][combos[i]]
         if pval>1.0:
             pval = 1.0
         dv.stat_annotation(ax,xlocs[i][0],xlocs[i][1],y=ypos[i],

### 2024-10-03 paper/supplementary.tex
added in supplementary for learning first half second half

@@
 \newpage
-\noindent\boldblue{\large{Supplementary B: Optimal Models}}
+\noindent\boldblue{\large{Supplementary B: First Half and Second Half Data Trends}}
+\vspace{-1mm}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 1]{figures/exp1_data_panel_first_half.png}
+    \caption*{
+        \boldblue{Supplementary Figure 3: Outcome Metrics for First Half of Trials}.
+\boldblue{A)} Indecisions (\%) \boldblue{B)} Wins (\%), and \boldblue{C)} Incorrects (\%) for the first half of trials for each condition.
+        Here we show that analyzing only the first half of trials in each condition displays the same significant differences as the analysis done on all of the trials.         
+        This result indicates that participants determined their timing strategy early on in each condition there was a negligible effect of learning on participant's strategies throughout the experiment.
+    } 
+\end{figure}
+
+\begin{figure}[H]
+\begin{minipage}[c]{0.6\textwidth}
+    \includegraphics[scale = 1]{figures/exp1_data_panel_second_half.png}
+\end{minipage}\hfill
+\begin{minipage}[c]{0.3\textwidth}
+    \caption*{
+        \boldblue{Supplementary Figure 3: Outcome Metrics for Second Half of Trials} Blah. 
+    } 
+\end{minipage}
+\end{figure}
+
+\newpage
+\noindent\boldblue{\large{Supplementary C: Optimal Models}}
 \vspace{-1mm}
@@
 Each of our three models has a different set of known and unknown parameters.
-A model decision policy has full knowledge of known parameters when determining the optimal decision time.
-A model decision policy has no or partial knowledge of unknown parameters when determining the optimal decision time.
+A model decision policy has full knowledge of known parameters, and no or partial knowledge of unknown parameters when determining the optimal decision time.
 
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary C: Model Results}}
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary D: Model Results}}
 
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary D: Response Time Task}}
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary E: Response Time Task}}
 
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary E: Timing Uncertainty Task}}
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary F: Timing Uncertainty Task}}
 
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary F: Guess Decisions}}
+\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary G: Guess Decisions}}
 

### 2024-10-03 paper/main.tex
last commit before going to apa7

@@
 \usepackage{docmute} % For putting one tex into another tex using \input
-
-\definecolor{mydarkblue}{RGB}{0,51,102}
-\definecolor{MYDARKBLUE}{RGB}{0,51,102}
-
-\graphicspath{ {./figures/} }
-
+\usepackage[paper=letterpaper,
+            %includefoot, % Uncomment to put page number above margin
+            marginparwidth=0.0in,     % Length of section titles
+            marginparsep=.05in,       % Space between titles and text
+            margin=1.0in,               % 1 inch margins
+            includemp]{geometry}
 \usepackage[%
@@
   ]{biblatex}
+\usepackage{fancyhdr}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrulewidth}{0pt}
+\usepackage{xpatch}
+\xpatchbibmacro{date+extrayear}{%
+    \printtext[parens]%
+  }{%
+    \setunit{\addperiod\space}%
+    \printtext%
+  }{}{}
+  \AtEveryBibitem{%
+    \clearfield{note}%
+  }
+
+\definecolor{mydarkblue}{RGB}{0,51,102}
+\definecolor{MYDARKBLUE}{RGB}{0,51,102}
+
+\graphicspath{ {./figures/} }
 
 \addbibresource{Aim1.bib}
-% \bibliography{draft}
-
-\usepackage[paper=letterpaper,
-            %includefoot, % Uncomment to put page number above margin
-            marginparwidth=0.0in,     % Length of section titles
-            marginparsep=.05in,       % Space between titles and text
-            margin=1.0in,               % 1 inch margins
-            includemp]{geometry}
 
@@
 \DeclareFieldFormat{journaltitle}{\mkbibemph{#1}\isdot}
-%\renewcommand{\labelnamepunct}{\addspace}  % remove period after year
 
@@
 
-\usepackage{xpatch}
-\xpatchbibmacro{date+extrayear}{%
-  \printtext[parens]%
-}{%
-  \setunit{\addperiod\space}%
-  \printtext%
-}{}{}
-\AtEveryBibitem{%
-  \clearfield{note}%
-}
-
 % adds comma after journal 
@@
 %\usepackage{hyperref}
-\usepackage{fancyhdr}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrulewidth}{0pt}
 
@@
 
-% Condition variables
-% \def\emlv{\emph{\emph{early mean} low variance}}
-% \def\emhv{\emph{\emph{early mean} high variance}}
-% \def\mmlv{\emph{\emph{middle mean} low variance}}
-% \def\mmhv{\emph{\emph{middle mean} high variance}}
-% \def\lmlv{\emph{\emph{late mean} low variance}}
-% \def\lmhv{\emph{\emph{late mean} high variance}}
-
-% \def\em{\emph{\emph{early mean}}}
-% \def\mm{\emph{\emph{middle mean}}}
-% \def\lm{\emph{\emph{late mean}}}
-
-% \definecolor{myudblue}{RGB}{0, 83, 159}
 \begin{document}
@@
 \boldblue{A)} Participant movement onset, \boldblue{B)} participant movement onset standard deviation, \boldblue{C)} indecisions, \boldblue{D)} wins, and \boldblue{E)} incorrects are shown for each condition.
-In our high time pressure task, participants made a high proportion of indecisions.
 Open circles are individual participant data.
 Filled icons are the predicted behavior of the three models, see legend for detail.
+In our high time pressure task, participants made a high proportion of indecisions.
 Interestingly, we also found that the average win percentage (41.25\%) was significantly below the 50\% chance level (p < 0.001) in the \emph{late mean} condition, clearly demonstrating suboptimal behaviour.
@@
 Since guessing on every trial would lead to a win percentage of 50\%, the only way participants would be below chance is if they were excessively indecisive.
+
 The incorrect percentage across all conditions was 26.3\% [range: 0.0\%, 57.5\%; \boldblue{Fig.
@@
 Participants displayed a greater percentage of incorrect decisions in the \emph{late mean} condition than the \emph{early mean} condition (p < 0.001, $\hat{\theta}$ = 92.5\%).
+For indecisions, wins, and incorrects we also found the same significant differences between conditions when separately analyzing the first half and second half of trials (\boldblue{Supplementary C}).
+That is, the same trends for the first and second half of trials shows that participants determined their decision-timing strategy early on in each condition and there was a negligible influence of learning.
 
@@
 \noindent In our task, participants must make a decision of whether to react to the stimulus or guess.
-For \boldblue{Experiment 1}, we tested three different models:  i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
+Building on the mathematical framework of statistical decision theory\autocite*{trommershauserStatisticalDecisionTheory2003}, we tested three different models for \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
 3}, left column).
@@
 As an example, one could plan for only some portion of a time delay, but then end up deciding too late because they did not fully account for the entire time delay.
-All model parameter values are described in \boldblue{Supplementary B}.
+All model parameter values and the fitting procedure are described in \boldblue{Supplementary C}.
 
@@
 
-Prior to \boldblue{Experiment 1}, participants performed two separate tasks to estimate response time (response time task; \boldblue{Supplementary D}) and timing uncertainty (timing uncertainty task; \boldblue{Supplementary E}).
+Prior to \boldblue{Experiment 1}, participants performed two separate tasks to estimate response time (response time task; \boldblue{Supplementary E}) and timing uncertainty (timing uncertainty task; \boldblue{Supplementary F}).
 We counterbalanced the order of the response time and timing uncertainty tasks.

### 2024-10-03 paper/supplementary.tex
last commit before going to apa7

@@
         \boldblue{Supplementary Figure 3: Outcome Metrics for First Half of Trials}.
-\boldblue{A)} Indecisions (\%) \boldblue{B)} Wins (\%), and \boldblue{C)} Incorrects (\%) for the first half of trials for each condition.
-        Here we show that analyzing only the first half of trials in each condition displays the same significant differences as the analysis done on all of the trials.         
-        This result indicates that participants determined their timing strategy early on in each condition there was a negligible effect of learning on participant's strategies throughout the experiment.
+\boldblue{A)} Indecisions (\%) \boldblue{B)} Wins (\%), and \boldblue{C)} Incorrects (\%) for the first half of trials.
+        Here we show that the significant differences between conditions are the same for the first and second half of trials (\boldblue{Supplementary Figure 4}).         
+        The same trends for the first half and second half of trials indicates that participants determined their timing strategy early on in each condition and there was a negligible effect of learning.
     } 
@@
     \caption*{
-        \boldblue{Supplementary Figure 3: Outcome Metrics for Second Half of Trials} Blah. 
+        \boldblue{Supplementary Figure 4: Outcome Metrics for Second Half of Trials} \boldblue{A)} Indecisions (\%) \boldblue{B)} Wins (\%), and \boldblue{C)} Incorrects (\%) for the second half of trials.
+        Here we show that the significant differences between conditions are the same for the first half (\boldblue{Supplementary Figure 3}) and second half of trials.         
+        The same trends for the first half and second half of trials indicates that participants determined their timing strategy early on in each condition and there was a negligible effect of learning.
     } 
@@
         \caption*{
-            \boldblue{Supplementary Figure 3: Model Outputs}.
+            \boldblue{Supplementary Figure 5: Model Outputs}.
 Here we show model fits for the No Switch Time Model (light gray circles), Full Switch Time Model (dark gray squares), and the Partial Switch Time Model (black diamonds) for \boldblue{A)} participant movement onset time, \boldblue{B)} participant movement onset time standard deviation, \boldblue{C)} indecisions, \boldblue{D)} wins, and \boldblue{E)} incorrects for each condition.
@@
         \caption*{
-            \boldblue{Supplementary Figure 4: Model Losses}.
+            \boldblue{Supplementary Figure 6: Model Losses}.
 Here we show histograms of each of our model’s bootstrapped losses.
@@
 
-\noindent For the response time task (\boldblue{Supplementary Figure 5}), participants began each trial by moving their cursor (yellow circle, 1 cm diameter) into a start position (white circle, 1.5 cm diameter).
+\noindent For the response time task (\boldblue{Supplementary Figure 7}), participants began each trial by moving their cursor (yellow circle, 1 cm diameter) into a start position (white circle, 1.5 cm diameter).
 Following a randomized time period (600-2400 ms drawn from a uniform distribution), one of two potential targets (white rings, 8 cm diameter) appeared on the screen.
@@
 
-    \caption*{\boldblue{Supplementary Figure 5: Response Time Experiment}.
+    \caption*{\boldblue{Supplementary Figure 8: Response Time Experiment}.
 One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
@@
 
-    \caption*{\boldblue{Supplementary Figure 6: Timing Uncertainty Experiment}.
+    \caption*{\boldblue{Supplementary Figure 9: Timing Uncertainty Experiment}.
 One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
@@
 
-    \caption*{\boldblue{Supplementary Figure 7: Guess Decision Percentages for Experiment 1}. 
+    \caption*{\boldblue{Supplementary Figure 10: Guess Decision Percentages for Experiment 1}. 
     Estimated percentage of guess decision percentages (y-axis) for each experimental condition (x-axis).

### 2024-10-03 paper_apa/main.tex
apa formatted

--- 2024-10-03 paper/main.tex
@@
-\documentclass[12pt]{article}
-\usepackage{inputenc}
+\documentclass[man,donotrepeattitle,floatsintext,letterpaper,12pt]{apa7}
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\raggedbottom
+
+\usepackage{fontspec} % For setmainfont
+\usepackage{docmute} % For putting one tex into another tex using \input
+\usepackage{bbm} % Needed for supplementary
+
+\usepackage{csquotes}
+\MakeOuterQuote{"}
+
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{setspace}
+\captionsetup[figure]{font=doublespacing,justification=justified}
+% \captionsetup[table]{font=doublespacing}
+
+\usepackage{hyperref}
+\hypersetup{hidelinks,colorlinks=false}
+\urlstyle{same}
+\usepackage{lineno}
+\linenumbers
+
 \usepackage{amsmath}
@@
 \usepackage{amssymb}
-\usepackage{bbm}
-\usepackage{fontspec} %XeLatex
-\usepackage{soul,xcolor}
-\usepackage{graphicx,wrapfig}
-\usepackage{float}
-\usepackage{caption}
-\usepackage{arydshln} % For \hdashline
-\usepackage{lineno}
-\usepackage{setspace}
-\usepackage{docmute} % For putting one tex into another tex using \input
-\usepackage[paper=letterpaper,
-            %includefoot, % Uncomment to put page number above margin
-            marginparwidth=0.0in,     % Length of section titles
-            marginparsep=.05in,       % Space between titles and text
-            margin=1.0in,               % 1 inch margins
-            includemp]{geometry}
-\usepackage[%
-  autocite  = superscript,
-  backend  = bibtex,
-  sortcites  = true, % Sort citations that are grouped together by number (not date, unsure how to do this)
-  citestyle = numeric,
-  bibstyle=authoryear,
-  sorting = none,
-  maxbibnames=99,
-  giveninits = true, %initials
-  isbn=false,
-  doi = false,
-  url = false, 
-  date=year, % Removes everything but year (i.e. month day) from citations
+
+\usepackage{sectsty}
+\definecolor{mydarkblue}{RGB}{0,51,102}
+\definecolor{MYDARKBLUE}{RGB}{0,51,102}
+\newcommand\boldblue[1]{\textcolor{mydarkblue}{\textbf{#1}}}
+\newcommand\bolditalicblue[1]{\textcolor{mydarkblue}{\textit{\textbf{#1}}}}
+\newcommand\italicblue[1]{\textcolor{mydarkblue}{\textit{#1}}}
+
+\sectionfont{\centering\normalfont\normalsize\boldblue}
+\subsectionfont{\noindent\normalfont\normalsize\bolditalicblue}
+\subsubsectionfont{\noindent\normalfont\normalsize\italicblue}
+
+\usepackage[
+  autocite=inline,
+  style=apa,
+  sortcites=true,
+  sorting=nyt,
+  backend=biber
   ]{biblatex}
-\usepackage{fancyhdr}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrulewidth}{0pt}
-\usepackage{xpatch}
-\xpatchbibmacro{date+extrayear}{%
-    \printtext[parens]%
-  }{%
-    \setunit{\addperiod\space}%
-    \printtext%
-  }{}{}
-  \AtEveryBibitem{%
-    \clearfield{note}%
+  \addbibresource{Aim1.bib}
+
+\DeclareBibliographyCategory{asterisk}
+\renewbibmacro*{begentry}{%
+    \ifcategory{asterisk}%
+    {*}%
+    {}%
+}
+\newcommand*{\nocitemeta}[1]{%
+    \nocite{#1}%
+    \addtocategory{asterisk}{#1}%
 }
 
-\definecolor{mydarkblue}{RGB}{0,51,102}
-\definecolor{MYDARKBLUE}{RGB}{0,51,102}
+\renewcommand{\postnotedelim}{\space}
+
+\usepackage{comment}
+
+%% MY DEFINITIONS --------------------------------------
 
 \graphicspath{ {./figures/} }
-
-\addbibresource{Aim1.bib}
 
@@
 \DeclareFieldFormat{journaltitle}{\mkbibemph{#1}\isdot}
-
-% add numbers in front of citations and puts year behind authors
-\defbibenvironment{bibliography}
-  {\list
-     {\printtext[labelnumberwidth]{%
-    \printfield{labelprefix}%
-    \printfield{labelnumber}}}%
-     {\setlength{\labelwidth}{\labelnumberwidth}%
-      \setlength{\leftmargin}{\labelwidth}%
-      \setlength{\labelsep}{\biblabelsep}%
-      \addtolength{\leftmargin}{\labelsep}%
-      \setlength{\itemsep}{\bibitemsep}%
-      \setlength{\parsep}{\bibparsep}}%
-      \renewcommand*{\makelabel}[1]{\hss##1}}
-  {\endlist}
-  {\item}
-
-% adds comma after journal 
-\renewcommand\bibpagespunct{\ifentrytype{article}{\addcolon}{\addcomma}\space}
-\renewbibmacro*{volume+number+eid}{%
-\setunit*{\addcomma\space}% NEW
-  \printfield{volume}
-  \printfield[parens]{number}{,}%
-  \setunit{\addcomma\space}%
-  \printfield{eid}}
-
-% change and to \& (can also remove)
-\DefineBibliographyExtras{english}{%
-  \renewcommand*{\finalnamedelim}{\addcomma\addspace\&\addspace}%
-  %\renewcommand*{\finalnamedelim}{\addcomma\addspace}%
-}
-
-%\usepackage{hyperref}
 
@@
 
-\newcommand\boldblue[1]{\textcolor{mydarkblue}{\textbf{#1}}}
-
-\newcommand{\SuppCaption}[2]{\noindent\boldblue{{#1}} {#2}\footnotesize}
-\newcommand{\SectionHeader}[1]{\noindent\boldblue{\Large{#1}}\normalsize }
-\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{mydarkblue}{#1}}\normalsize }
-
 \abovedisplayskip = 10.0pt plus 2.0pt minus 20.0pt
@@
 
-\begin{document}
-% MUST BE IN DOCUMENT FOR EQUATION SPACING
 %%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%  
-\pagenumbering{gobble} % No page number for title page
-\begin{center}
+\title{Indecision under time pressure arises from suboptimal switching behaviour}
+\shorttitle{Indecision arises from suboptimal switching behaviour}
+\renewcommand\author[1]{}
+\renewcommand\affiliation[1]{}
 
-    \noindent\boldblue{\Large{Indecision under time pressure arises from suboptimal switching behaviour
-        }}
-    \vspace{4mm}
-    \\
-    Seth R.
-Sullivan\textsuperscript{1}, Rakshith Lokesh\textsuperscript{4}, Jan A.
-Calalo\textsuperscript{2}, Truc Ngo\textsuperscript{1}, John H.
-Buggeln\textsuperscript{3}, Adam M.
-Roth\textsuperscript{2}, Christopher Peters\textsuperscript{1}, Isaac Kurtzer\textsuperscript{5}, Michael J.
-Carter\textsuperscript{6}, Joshua G.A.
-Cashaback\textsuperscript{1,2,3,6,7}
-    \vspace{1mm}
-    \\
-\end{center}
+\authorsnames[1,4,2,1,3,2,1,6,7,{1,2,3,7}]{Seth R.
+Sullivan, Rakshith Lokesh, Jan A.
+Calalo, Truc Ngo, John H.
+Buggeln, Adam M.
+Roth, Christopher Peters, Isaac Kurtzer, Michael J.
+Carter, Joshua G.A.
+Cashaback \vspace{2ex}}
 
-\noindent \textsuperscript{1} Department of Biomedical Engineering, University of Delaware\\
-\textsuperscript{2} Department of Mechanical Engineering, University of Delaware\\
-\textsuperscript{3} Biomechanics and Movements Science Program, University of Delaware\\
-\textsuperscript{4} Department of Electrical and Computer Engineering, Northeastern University\\
-\textsuperscript{5} College of Osteopathic Medicine, New York Institute of Technology\\
-\textsuperscript{6} Department of Kinesiology, McMaster University\\
-\textsuperscript{7} Interdisciplinary Neuroscience Graduate Program, University of Delaware\\
-\vspace{1mm}
-\\
-\textcolor{mydarkblue}{\large Abbreviated Title:}
-\vspace{1mm}
-\\
-Indecision arises from suboptimal switching behaviour
-\\
-\vspace{1mm}
-\\
-\textcolor{mydarkblue}{\large Author Summary:}
-\vspace{1mm}
-\\
-Indecisive behaviour is highly prevalent in many aspects of daily life.
-Despite its ubiquity, there has been very little focus and a lack of explanation for why indecisions occur.
-Here we find under high time pressure scenarios that indecisions arise by misrepresenting additional time delays and temporal uncertainties associated when attempting to switch from reacting to guessing.
-Our novel paradigm presents a new way to elucidate and study indecisions.
-\\
-\\
-\textcolor{mydarkblue}{\large Funding:}
-\vspace{1mm}
-\\
-National Science Foundation (NSF \#2146888) awarded to JGAC
-\\
-National Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589) awarded to MJC
-\\
-\vspace{1mm}
-\\
-\textcolor{mydarkblue}{\large Correspondence:}
-\\
-Seth Sullivan\\
-Biomedical Engineering\\
-University of Delaware\\
-Newark, DE 19711, U.S.A\\
-Email: sethsullivan99@gmail.com
-\\
-\\
-Joshua G. A. Cashaback, PhD\\
-Biomedical Engineering\\
-University of Delaware\\
-STAR Campus, Room 201J\\
-Newark, DE 19711, U.S.A\\
-Email: cashabackjga@gmail.com
+\authorsaffiliations{
+  {Department of Biomedical Engineering, University of Delaware},
+  {Department of Mechanical Engineering, University of Delaware}, 
+  {Biomechanics and Movements Science Program, University of Delaware},
+  {Department of Electrical and Computer Engineering, Northeastern University}, 
+  {College of Osteopathic Medicine, New York Institute of Technology}, 
+  {Department of Kinesiology, McMaster University},
+  {Interdisciplinary Neuroscience Graduate Program, University of Delaware}
+}
 
-\newpage
-\doublespace %
-\linenumbers %
-\SectionHeader{ABSTRACT}
-\\
-Indecisive behaviour can be catastrophic, leading to car crashes or stock market losses.
+\abstract{Indecisive behaviour can be catastrophic, leading to car crashes or stock market losses.
 Despite fruitful efforts across several decades to understand decision-making, there has been little research on what leads to indecision.
@@
 Collectively, our results demonstrate that humans are suboptimal and fail to account for a time delay and temporal uncertainty when switching from reacting to guessing, leading to indecisive behaviour.
+}
 
-\newpage
+\authornote{Correspondence concering this article should be addressed to Joshua G.A. Cashaback, Department of Biomedical Engineering, University of Delaware. Email: cashabackjga@gmail.com
+}
 
-\pagestyle{fancy}
+% \pagestyle{fancy}
 %\cfoot[]{\textcolor{mydarkblue}{\thepage}}
-\fancyhead[R]{\emph{\textcolor{mydarkblue}{Indecision arises from suboptimal switching behaviour
-        }}}
-\fancyfoot[C]{\textcolor{mydarkblue}{\thepage}}
+% \fancyhead[R]{\emph{\textcolor{mydarkblue}{Indecision arises from suboptimal switching behaviour
+% }}}
+% \fancyfoot[C]{\textcolor{mydarkblue}{\thepage}}
 %\fancyfoot[C]{\emph{\textcolor{mydarkblue}{\thepage}}}
@@
 
-\pagenumbering{arabic} % page numbering starts here
+\begin{document}
+\maketitle
+\noindent \textbf{\emph{Public Significance Statement}}
+\\
+\noindent Indecisive behaviour is highly prevalent in many aspects of daily life.
+Despite its ubiquity, there has been very little focus and a lack of explanation for why indecisions occur.
+Here we find under high time pressure scenarios that indecisions arise by misrepresenting additional time delays and temporal uncertainties associated with attempting to switch from reacting to guessing.
+Our novel paradigm presents a new way to elucidate and study indecisions.
+
+\newpage
+% \pagenumbering{arabic} % page numbering starts here
 \vspace{2mm}
-\SectionHeader{INTRODUCTION}
+\section{Introduction}
 \vspace{2mm}
-\\
 \noindent Indecisions arise from failing to decide and act upon sensory information in time, such as a driver failing to brake or hit the gas pedal when a traffic light turns yellow.
@@
 Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions.
-Similar to others \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016, philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions.
+Similar to others \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016, philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015, forstmannStriatumPreSMAFacilitate2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions.
 Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline.
@@
 
-Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response\autocite*{drugowitschOptimalDecisionmakingTimevarying2014,balciOptimalTemporalRisk2011,bogaczPhysicsOptimalDecision2006,hudsonOptimalCompensationTemporal2008,trommershauserHumansRapidlyEstimate2006}.
-To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system \autocite*{drugowitschTuningSpeedaccuracyTradeoff2015,balciOptimalTemporalRisk2011,hudsonOptimalCompensationTemporal2008,acerbiInternalRepresentationsTemporal2012,faisalNoiseNervousSystem2008,kordingBayesianDecisionTheory2006,wolpertMotorControlDecisionmaking2012,tanisAccuracyEffortCosts2023,lokeshVisualAccuracyDominates2023}.
-Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite*{balciOptimalTemporalRisk2011,mileticCautionDecisionmakingTime2019} and motor tasks\autocite*{hudsonOptimalCompensationTemporal2008,faisalOptimalCombinationSensory2009}.
-Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016, onagawaSensorimotorStrategySelection2021,onagawaRiskAversionAdjustment2019}.
+Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response \autocite{drugowitschOptimalDecisionmakingTimevarying2014, balciOptimalTemporalRisk2011, bogaczPhysicsOptimalDecision2006,hudsonOptimalCompensationTemporal2008, trommershauserHumansRapidlyEstimate2006}.
+To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system \autocite{drugowitschTuningSpeedaccuracyTradeoff2015,balciOptimalTemporalRisk2011,hudsonOptimalCompensationTemporal2008,acerbiInternalRepresentationsTemporal2012,faisalNoiseNervousSystem2008,kordingBayesianDecisionTheory2006,wolpertMotorControlDecisionmaking2012,tanisAccuracyEffortCosts2023,lokeshVisualAccuracyDominates2023}.
+Past work has shown that humans will often produce nearly optimal decision times during cognitive \autocite{balciOptimalTemporalRisk2011,mileticCautionDecisionmakingTime2019} and motor tasks \autocite{hudsonOptimalCompensationTemporal2008,faisalOptimalCombinationSensory2009}.
+Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties \autocite{otaMotorPlanningTemporal2015, drugowitschComputationalPrecisionMental2016, onagawaSensorimotorStrategySelection2021, onagawaRiskAversionAdjustment2019}.
 With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.
 
-Building on our past work\autocite{lokeshHumansUtilizeSensory2022}, we developed a high pressure task with a time constraint to examine how humans select decision times.
+Building on our past work \autocite{lokeshHumansUtilizeSensory2022}, we developed a high pressure task with a time constraint to examine how humans select decision times.
 We tested the idea that humans optimally account for time delays and temporal uncertainties to select a decision time that maximizes reward.
@@
 \vspace{2mm}
-\SectionHeader{RESULTS}
+\section{Results}
 \vspace{-1mm}
 
-\SubSectionHeader{Experiment 1}
+\subsection{Experiment 1}
 \vspace{-1mm}
 
-\noindent\boldblue{Experimental Design.}
+\subsubsection{Experimental Design.}
 
@@
 1A}).
+The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles.
+Participants were instructed to reach the same target as the stimulus within a time constraint of 1500 ms.
+The time remaining in each trial was represented visually with a timing bar that decreased in width according to the elapsed time.
+Thus, participants were fully aware of how much time they had left relative to the time constraint.
+A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint (\boldblue{Fig.
+1B}).
+A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
+A trial was considered an indecision and the participant received zero points if they failed to reach a target within the time constraint.
+That is, we considered an indecision to be not reaching a target within the time constraint and thus failing to make a decision in time.
 
@@
 
-\vspace{-5mm}
-\noindent The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles.
-Participants were instructed to reach the same target as the stimulus within a time constraint of 1500 ms.
-The time remaining in each trial was represented visually with a timing bar that decreased in width according to the elapsed time.
-Thus, participants were fully aware of how much time they had left relative to the time constraint.
-A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint (\boldblue{Fig.
-1B}).
-A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint.
-A trial was considered an indecision and the participant received zero points if they failed to reach a target within the time constraint.
-That is, we considered an indecision to be not reaching a target within the time constraint and thus failing to make a decision in time.
-
 For each trial within a condition, the stimulus movement onset was drawn from the same normal distribution.
@@
 
-\vspace*{2mm}
-\noindent \boldblue{{{Participant timing behaviour.}}}
-
-\noindent Participant movement onset for the low variance conditions is shown in \boldblue{Fig.
-2A}.
-We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
-There was no significant interaction between stimulus movement onset mean and variance (F[1.66,31.47], p = 0.565).
-When collapsed across low and high variance, participant movement onsets were significantly greater in the \emph{middle mean} conditions compared to the \emph{early mean} conditions (p = 0.014, $\hat{\theta}$ = 72.5\%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
-Again, when collapsed across low and high variance, participant movement onset significantly decreased from the \emph{middle mean} conditions to the \emph{late mean} conditions (p = 0.018, $\hat{\theta}$ = 62.5\%).
-Here, an earlier participant movement onset in the \emph{late mean} condition suggests that participants attempted to wait and react to the stimulus, but ended up guessing.
-
-Participant movement onset standard deviation for the low variance conditions is shown in \boldblue{Fig.
-2B}.
-There was a main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) of the stimulus movement onset, and no significant interaction (F[1.98, 37.58], p = 0.097).
-
-% Figure 3 Model Outputs and Data
 \begin{figure}[H]
@@
 
+\subsubsection{Participant timing behaviour}
+
+\noindent Participant movement onset for the low variance conditions is shown in \boldblue{Fig.
+2A}.
+We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017).
+There was no significant interaction between stimulus movement onset mean and variance (F[1.66,31.47], p = 0.565).
+When collapsed across low and high variance, participant movement onsets were significantly greater in the \emph{middle mean} conditions compared to the \emph{early mean} conditions (p = 0.014, $\hat{\theta}$ = 72.5\%), suggesting that participants waited longer to react to the stimulus movement and guessed later in time.
+Again, when collapsed across low and high variance, participant movement onset significantly decreased from the \emph{middle mean} conditions to the \emph{late mean} conditions (p = 0.018, $\hat{\theta}$ = 62.5\%).
+Here, an earlier participant movement onset in the \emph{late mean} condition suggests that participants attempted to wait and react to the stimulus, but ended up guessing.
+
+Participant movement onset standard deviation for the low variance conditions is shown in \boldblue{Fig.
+2B}.
+There was a main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) of the stimulus movement onset, and no significant interaction (F[1.98, 37.58], p = 0.097).
+
+% Figure 3 Model Outputs and Data
+
 \noindent When collapsed across variance, waiting to react and then guessing in the \emph{late mean} conditions led to a higher standard deviation of participant movement onset relative to the \emph{middle mean} (p = 0.039, $\hat{\theta}$ = 70.0\%) and \emph{early mean} (p < 0.001, $\hat{\theta}$ = 77.5\%) conditions.
 
-\vspace*{2mm}
-\noindent \boldblue{{{Participants are suboptimal and excessively indecisive.}}}
+\subsubsection{Participants are suboptimal and excessively indecisive}
 
@@
 
-\vspace{10mm}
-\noindent \boldblue{{{Decision-Making Models}}}
+\vspace{2mm}
+\subsubsection{Decision-Making Models}
 
 \noindent In our task, participants must make a decision of whether to react to the stimulus or guess.
-Building on the mathematical framework of statistical decision theory\autocite*{trommershauserStatisticalDecisionTheory2003}, we tested three different models for \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
+Building on the mathematical framework of statistical decision theory \autocite{trommershauserStatisticalDecisionTheory2003}, we tested three different models for \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig.
 3}, left column).
 The decision policy of all models considers the expected value ($\mathbb{E}[R|\tau]$) to determine the time ($\tau$) to transition from reacting to guessing.
-Expected value is defined as
+\\
+\noindent Expected value is defined as
 \setlength{\belowdisplayskip}{4pt} \setlength{\belowdisplayshortskip}{4pt} % THIS MUST BE HERE FOR EQUATIONS SPACING
@@
 
-% \vspace*{2mm}
 \noindent\emph{{No Switch Time Model}}
@@
 
-\vspace{2mm}
-\SubSectionHeader{Experiment 2}
+\subsection{Experiment 2}
 
@@
 
-\noindent \boldblue{Experimental Design}
+\subsubsection{Experimental Design}
 
@@
 4A}).
-In the guess trials, participants saw the stimulus disappear from the start circle.
-They were instructed to guess one of the two targets as quickly as possible (\boldblue{Fig.
-4B}).
-Following trial onset, the movement or disappearance of the stimulus was drawn from a normal distribution with a mean of 800ms and a standard deviation of 50ms.
-There were three experimental conditions (\boldblue{Fig.
-4C}): the \emph{react or guess} condition, the \emph{only react} condition, and the \emph{only guess} condition.
 
@@
 
-\noindent In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+\noindent In the guess trials, participants saw the stimulus disappear from the start circle.
+They were instructed to guess one of the two targets as quickly as possible (\boldblue{Fig.
+4B}).
+Following trial onset, the movement or disappearance of the stimulus was drawn from a normal distribution with a mean of 800ms and a standard deviation of 50ms.
+There were three experimental conditions (\boldblue{Fig.
+4C}): the \emph{react or guess} condition, the \emph{only react} condition, and the \emph{only guess} condition.
+In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
 Participants were informed that the stimulus would either move to one of the targets or disappear.
@@
 
-\noindent \boldblue{Response Time}
+\subsubsection{Response Time}
 
@@
 5A}).
-This result shows that the response time differences between guess and react trials are not due to dual tasking \autocite{vanselstDecisionResponseDualTask1997} or task switching between trials \autocite*{monsellTaskSwitching2003,kieselControlInterferenceTask2010a,rubinsteinExecutiveControlCognitive2001}, which would not show this relative difference  [i.e., guess - react (\emph{react or guess} condition) = guess - react (guess only and react only conditions)].
+This result shows that the response time differences between guess and react trials are not due to dual tasking \autocite{vanselstDecisionResponseDualTask1997} or task switching between trials \autocite{monsellTaskSwitching2003,kieselControlInterferenceTask2010a,rubinsteinExecutiveControlCognitive2001}, which would not show this relative difference  [i.e., guess - react (\emph{react or guess} condition) = guess - react (guess only and react only conditions)].
 
 % \vspace{10mm}
-\noindent \boldblue{Response Time Uncertainty}
+\subsubsection{Response Time Uncertainty}
 
@@
 
-\vspace{2mm}
-\SectionHeader{Discussion}
+\section{Discussion}
 
@@
 We saw that 95\% of participants had a win rate less than chance (50\%) in the \emph{late mean} condition, which corresponded with an average of 19.4\% indecisions.
-This proportion of indecisions aligns with our recent prior work that examined competitive human-human decision-making with a high time pressure\autocite{lokeshHumansUtilizeSensory2022}.
+This proportion of indecisions aligns with our recent prior work that examined competitive human-human decision-making with a high time pressure \autocite{lokeshHumansUtilizeSensory2022}.
 In this competitive task, one participant attempted to reach the same target as their opponent, while the other tried to reach the opposite target within a time constraint.
@@
 
-Past work has suggested that humans can nearly optimally account for time delays and temporal uncertainty when performing decision-making \autocite*{balciRiskAssessmentMan2009,jazayeriTemporalContextCalibrates2010,balciOptimalTemporalRisk2011} and movement tasks \autocite*{hudsonOptimalCompensationTemporal2008,deanTradingSpeedAccuracy2007} when attempting to maximize reward.
+Past work has suggested that humans can nearly optimally account for time delays and temporal uncertainty when performing decision-making \autocite{balciRiskAssessmentMan2009,jazayeriTemporalContextCalibrates2010,balciOptimalTemporalRisk2011} and movement tasks \autocite{hudsonOptimalCompensationTemporal2008,deanTradingSpeedAccuracy2007} when attempting to maximize reward.
 Here we considered two optimal models, the No Switch Time Model and Full Switch Time Model, which both had full knowledge of all available time delays and temporal uncertainties.
 Interestingly, both the No Switch Time Model and Full Switch Time Model showed that even when fully accounting for all sensorimotor delays and uncertainties, indecisions were a part of an optimal strategy in all but one of the six conditions.
-In other words, given the inherent delays and uncertainty of our nervous system\autocite{faisalNoiseNervousSystem2008}, an optimal strategy of earning maximal reward may involve indecisive behaviour on some proportion of trials.
+In other words, given the inherent delays and uncertainty of our nervous system \autocite{faisalNoiseNervousSystem2008}, an optimal strategy of earning maximal reward may involve indecisive behaviour on some proportion of trials.
 We are unaware of any work in the literature suggesting that some level of indecisions may be optimal.
@@
 The Partial Switch Time Model supports the notion that humans suboptimally select decision times when under high time pressures.
-An interesting future direction would be to test whether different reward structures, such as placing a higher reward on wins or punishing indecisions\autocite*{kahnemanProspectTheoryAnalysis2013,rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024,galeaDissociableEffectsPunishment2015}, would provide a means to reduce an excessive number of indecisions.
+An interesting future direction would be to test whether different reward structures, such as placing a higher reward on wins or punishing indecisions \autocite{kahnemanProspectTheoryAnalysis2013,rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024,galeaDissociableEffectsPunishment2015}, would provide a means to reduce an excessive number of indecisions.
 
 Decision theoretic and drift-diffusion models are two common frameworks used to model decision-making.
-Decision theoretic models use knowledge of sensorimotor delays and uncertainties to select decision times that maximize reward\autocite*{mileticCautionDecisionmakingTime2019,balciRiskAssessmentMan2009, onagawaRiskAversionAdjustment2019,battagliaHumansTradeViewing2007}.
-Drift-diffusion models characterize the decision-making process through a decision variable that crosses a threshold to decide\autocite*{ratcliffModeling2alternativeForcedchoice2018,ratcliffDiffusionDecisionModel2008}.
+Decision theoretic models use knowledge of sensorimotor delays and uncertainties to select decision times that maximize reward \autocite{mileticCautionDecisionmakingTime2019,balciRiskAssessmentMan2009, onagawaRiskAversionAdjustment2019,battagliaHumansTradeViewing2007}.
+Drift-diffusion models characterize the decision-making process through a decision variable that crosses a threshold to decide \autocite{ratcliffModeling2alternativeForcedchoice2018,ratcliffDiffusionDecisionModel2008}.
 Unlike decision theoretic models, drift-diffusion models do not explicitly represent several potential sources of sensorimotor delays and uncertainties (e.g.
@@
 Drift-diffusion models can capture indecisions through the decision variable failing to cross a decision threshold within a time constraint.
-Prior work using these models for decision-making tasks under time constraints have ignored indecisions\autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.
+Prior work using these models for decision-making tasks under time constraints have ignored indecisions \autocite{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.
 Further, drift-diffusion models indicate a guess decision when the noisy decision variable randomly crosses some threshold but do not consider guessing as a separate process from reacting to evidence (i.e., a person consciously deciding when to guess).
-The notion of guessing being a separate process from reacting was proposed by Yellot in a fast-guess model\autocite*{yellottCorrectionFastGuessing1971}.
+The notion of guessing being a separate process from reacting was proposed by Yellot in a fast-guess model \autocite{yellottCorrectionFastGuessing1971}.
 However, like drift-diffusion models, their modelling framework also did not consider a representation of sensorimotor delays and uncertainties.
@@
 That is, participants are more likely to stay in their current mode than switch modes.
-They also highlighted that classical decision-making models, such as drift-diffusion models \autocite{ratcliffModeling2alternativeForcedchoice2018} or more recently the urgency-gating model \autocite*{cisekDecisionsChangingConditions2009,derosiereTradingAccuracySpeed2021,thuraDecisionMakingUrgency2012}, do not consider different modes of reacting or guessing.
+They also highlighted that classical decision-making models, such as drift-diffusion models \autocite{ratcliffModeling2alternativeForcedchoice2018} or more recently the urgency-gating model \autocite{cisekDecisionsChangingConditions2009,derosiereTradingAccuracySpeed2021,thuraDecisionMakingUrgency2012}, do not consider different modes of reacting or guessing.
 Extending upon the findings of Dutilh and colleagues (2011) that examined between trial mode switching, our work suggests that humans switch react and guess modes within a trial.
@@
 To our knowledge, it is unknown how different modes would be represented in the nervous system.
-One possibility is that the different modes represent different attractors from a neural dynamical systems perspective \autocite*{erlhagenDynamicFieldTheory2002,wangDecisionMakingRecurrent2008,churchlandNeuralPopulationDynamics2012,shenoyCorticalControlArm2013}, which would be an interesting avenue of investigation.
+One possibility is that the different modes represent different attractors from a neural dynamical systems perspective \autocite{erlhagenDynamicFieldTheory2002,wangDecisionMakingRecurrent2008,churchlandNeuralPopulationDynamics2012,shenoyCorticalControlArm2013}, which would be an interesting avenue of investigation.
 
@@
 A limitation of the commonly used two-alternative forced choice task without a time constraint is that the participant or animal must select one of two potential options, which does not allow for indecisive behaviour.
-For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis\autocite*{forstmannStriatumPreSMAFacilitate2008,diederichFurtherTestSequentialsampling2008,wuCapacityCognitiveControl2016,dambacherTimePressureAffects2015}.
-These studies tend to focus on  response times and response time distributions of correct and incorrect decisions Furthermore, previous modelling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
+For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis \autocite{forstmannStriatumPreSMAFacilitate2008,diederichFurtherTestSequentialsampling2008,wuCapacityCognitiveControl2016,dambacherTimePressureAffects2015}.
+These studies tend to focus on  response times and response time distributions of correct and incorrect decisions Furthermore, previous modelling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}.However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.
 
@@
 \newpage
-\SectionHeader{Methods}
+\section{Methods}
 
-\noindent\boldblue{Participants}
+\subsection{Participants}
 
@@
 
-\noindent\boldblue{Apparatus}
+\subsection{Apparatus}
 
@@
 \vspace{5mm}
-\noindent\boldblue{\large Experiment 1 Design}
+\subsection{Experiment 1 Design}
 
@@
 \vspace{2mm}
-\noindent\boldblue{\large Experiment 2 Design}
+\subsection{Experiment 2 Design}
 
@@
 \vspace{2mm}
-\noindent\boldblue{\large{Data Analysis}}
+\subsection{Data Analysis}
 
@@
 
-\noindent \boldblue{Experiment 1}
+\subsubsection{Experiment 1}
 
@@
 
-\noindent \boldblue{ Experiment 2}
+\subsubsection{Experiment 2}
 
@@
 
-\noindent\boldblue{\large\textcolor{mydarkblue}{Statistics}}
+\subsection{Statistics}
 
-\noindent{\boldblue{Experiment 1 and 2}}
+\subsubsection{Experiment 1 and 2}
 
@@
 In \boldblue{Experiment 2} we used a 2 (condition: interleaved react and guess, \emph{react or guess} only) x 2 (trial type: react trials, guess trials) repeated measures ANOVA for each dependent variable.
-For both \boldblue{Experiment 1} and \boldblue{2}, we performed mean comparisons using nonparametric bootstrap hypothesis tests (n = 1,000,000) \autocite*{hesterbergBootstrap2011,cashabackDissociatingErrorbasedReinforcementbased2017,cashabackGradientReinforcementLandscape2019a}.
+For both \boldblue{Experiment 1} and \boldblue{2}, we performed mean comparisons using nonparametric bootstrap hypothesis tests (n = 1,000,000) \autocite{hesterbergBootstrap2011,cashabackDissociatingErrorbasedReinforcementbased2017,cashabackGradientReinforcementLandscape2019a}.
 Mean comparisons were Holm-Bonferonni correct to account for multiple comparisons.
@@
 \newpage
-\fancyhead[L]{} % Need this because print bibliography is dumb and puts a REFERENCES in the left header
 \begin{nolinenumbers}
-    \definecolor{mydarkblue}{RGB}{0,51,102}
 
-    \printbibliography[title=\LARGE\textcolor{mydarkblue}{References}]
+    \printbibliography[title=\textcolor{mydarkblue}{References}]
+
 \end{nolinenumbers}
 
-\newpage
-\input{supplementary}
+% \newpage
+% \input{supplementary}
 

### 2024-10-03 paper/Cover_letter_Indecisions.tex
submitted to jep general

@@
 \vspace{1.0mm}
-We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{PLOS Computational Biology}.
+We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{Journal of Experimental Psychology: General}.
 \vspace{3.0mm}
@@
 \\
-Michael S Landy, New York University, landy@nyu.edu
+Laurence Maloney, New York University, laurence.maloney@nyu.edu
+
+Expert in statistical decision theory and computational modeling of decisions
 \\
 \\
-Han L.J. van der Maas, University of Amsterdam, H.L.J.vanderMaas@uva.nl 
+Michael S Landy, New York University, landy@nyu.edu
+
+Expert in statistical decision theory and computational modeling of decisions
 \\
 \\
-Tony Carlsen, University of Ottawa, acarlsen@uottawa.ca
+Heather Neyedli, Dalhouse University, hneyedli@dal.ca
+
+Expert in decision-making under risk and optimal decision-making
 \\
 \\
-Martin Wiener, George Mason University, mwiener@gmu.edu
+Todd Hudson, New York University, Todd.Hudson@nyulangone.org
+
+Expert in optimal timing and decision-making
 %\\
@@
 %\\
+\\
+\\
+\noindent \textcolor{myudblue}{EDITOR SUGGESTIONS}
+\\
+\\
+Joo-Hyun Song
+\\
+\\
+Jared Medina  
 \end{document}

### 2024-10-03 paper_apa/main.tex
submitted to jep general

@@
 % \pagenumbering{arabic} % page numbering starts here
-\vspace{2mm}
+Word count: 7114
 \section{Introduction}
@@
 Participants displayed a greater percentage of incorrect decisions in the \emph{late mean} condition than the \emph{early mean} condition (p < 0.001, $\hat{\theta}$ = 92.5\%).
-For indecisions, wins, and incorrects we also found the same significant differences between conditions when separately analyzing the first half and second half of trials (\boldblue{Supplementary C}).
+For indecisions, wins, and incorrects we also found the same significant differences between conditions when separately analyzing the first half and second half of trials (\boldblue{Supplementary B}).
 That is, the same trends for the first and second half of trials shows that participants determined their decision-timing strategy early on in each condition and there was a negligible influence of learning.
@@
 
-\vspace{5mm}
 \subsection{Experiment 1 Design}
@@
 
-\vspace{2mm}
 \subsection{Experiment 2 Design}
@@
 
-\vspace{2mm}
 \subsection{Data Analysis}
@@
 
-% \newpage
-% \input{supplementary}
+\newpage
+\input{supplementary}
 

### 2024-10-03 paper_apa/supplementary.tex
apa formatted
submitted to jep general

--- 2024-10-03 paper/supplementary.tex
@@
 \begin{document}
-\SectionHeader{Supplementary}
+\section{Supplementary}
 
-\noindent\boldblue{\large{Supplementary A: Low and High Variance Results}}
+\section{Supplementary A: Low and High Variance Results}
 \begin{figure}[H]
@@
 \newpage
-\noindent\boldblue{\large{Supplementary B: First Half and Second Half Data Trends}}
+\section{Supplementary B: First Half and Second Half Data Trends}
 \vspace{-1mm}
@@
 \begin{figure}[H]
-\begin{minipage}[c]{0.6\textwidth}
+    \centering
     \includegraphics[scale = 1]{figures/exp1_data_panel_second_half.png}
-\end{minipage}\hfill
-\begin{minipage}[c]{0.3\textwidth}
+
     \caption*{
@@
     } 
-\end{minipage}
 \end{figure}
@@
 \newpage
-\noindent\boldblue{\large{Supplementary C: Optimal Models}}
+\section{Supplementary C: Optimal Models}
 \vspace{-1mm}
@@
 \vspace{2mm}
-\noindent \boldblue{General Formulation for the Models}
+\subsection{General Formulation for the Models}
 
@@
 \vspace{2mm}
-\noindent\boldblue{Model Parameter Estimation and Fitting Procedure}
+\subsection{Model Parameter Estimation and Fitting Procedure}
 
@@
 \vspace{2mm}
-\noindent \boldblue{Model Parameter Values}
+\subsection{Model Parameter Values}
 
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary D: Model Results}}
+\section{Supplementary D: Model Results}
 
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary E: Response Time Task}}
+\section{Supplementary E: Response Time Task}
 
@@
 
-    \caption*{\boldblue{Supplementary Figure 8: Response Time Experiment}.
+    \caption*{\boldblue{Supplementary Figure 7: Response Time Experiment}.
 One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary F: Timing Uncertainty Task}}
+\section{Supplementary F: Timing Uncertainty Task}
 
@@
 
-    \caption*{\boldblue{Supplementary Figure 9: Timing Uncertainty Experiment}.
+    \caption*{\boldblue{Supplementary Figure 8: Timing Uncertainty Experiment}.
 One of two potential targets (dashed white rings; not visible to participants) would appear on the screen.
@@
 \newpage
-\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary G: Guess Decisions}}
+\section{Supplementary G: Guess Decisions}
 
@@
 
-    \caption*{\boldblue{Supplementary Figure 10: Guess Decision Percentages for Experiment 1}. 
+    \caption*{\boldblue{Supplementary Figure 9: Guess Decision Percentages for Experiment 1}. 
     Estimated percentage of guess decision percentages (y-axis) for each experimental condition (x-axis).

### 2024-10-07 paper_apa/supplementary.tex
removed supplementary from main pdf, and had to adjust things for the supp itself to get it to run

@@
-\documentclass[12pt]{article}
-\usepackage{inputenc}
+\documentclass[man,floatsintext,letterpaper,12pt]{apa7}
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\raggedbottom
+
+\usepackage{fontspec} % For setmainfont
+% \usepackage{docmute} % For putting one tex into another tex using \input
+\usepackage{bbm} % Needed for supplementary
+
+\usepackage{csquotes}
+\MakeOuterQuote{"}
+
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{setspace}
+\captionsetup[figure]{font=doublespacing,justification=justified}
+% \captionsetup[table]{font=doublespacing}
+
+\usepackage{hyperref}
+\hypersetup{hidelinks,colorlinks=false}
+\urlstyle{same}
+\usepackage{lineno}
+\linenumbers
+
 \usepackage{amsmath}
@@
 \usepackage{amssymb}
-\usepackage{bbm}
-\usepackage{fontspec} %XeLatex
-\usepackage{soul,xcolor}
-\usepackage{graphicx,wrapfig}
-\usepackage{float}
-\usepackage{caption}
-\usepackage{arydshln} % For \hdashline
-\usepackage{lineno}
-\usepackage{setspace}
 
+\usepackage{sectsty}
 \definecolor{mydarkblue}{RGB}{0,51,102}
 \definecolor{MYDARKBLUE}{RGB}{0,51,102}
+\newcommand\boldblue[1]{\textcolor{mydarkblue}{\textbf{#1}}}
+\newcommand\bolditalicblue[1]{\textcolor{mydarkblue}{\textit{\textbf{#1}}}}
+\newcommand\italicblue[1]{\textcolor{mydarkblue}{\textit{#1}}}
+
+\sectionfont{\centering\normalfont\normalsize\boldblue}
+\subsectionfont{\noindent\normalfont\normalsize\bolditalicblue}
+\subsubsectionfont{\noindent\normalfont\normalsize\italicblue}
+
+\usepackage[
+  autocite=inline,
+  style=apa,
+  sortcites=true,
+  sorting=nyt,
+  backend=biber
+  ]{biblatex}
+  \addbibresource{Aim1.bib}
+
+\DeclareBibliographyCategory{asterisk}
+\renewbibmacro*{begentry}{%
+    \ifcategory{asterisk}%
+    {*}%
+    {}%
+}
+\newcommand*{\nocitemeta}[1]{%
+    \nocite{#1}%
+    \addtocategory{asterisk}{#1}%
+}
+
+\renewcommand{\postnotedelim}{\space}
+
+\usepackage{comment}
+
+%% MY DEFINITIONS --------------------------------------
 
 \graphicspath{ {./figures/} }
-
-\usepackage[%
-  autocite  = superscript,
-  backend  = bibtex,
-  sortcites  = false,
-  citestyle = numeric,
-  bibstyle=authoryear,
-  sorting = none,
-  maxbibnames=99,
-  giveninits = true, %initials
-  isbn=false,
-  doi = false,
-  url = false
-]{biblatex}
-
-\addbibresource{Aim1.bib}
-% \bibliography{draft}
-
-\usepackage[paper=letterpaper,
-            %includefoot, % Uncomment to put page number above margin
-            marginparwidth=0.0in,     % Length of section titles
-            marginparsep=.05in,       % Space between titles and text
-            margin=1.0in,               % 1 inch margins
-            includemp]{geometry}
 
@@
 \DeclareFieldFormat{journaltitle}{\mkbibemph{#1}\isdot}
-%\renewcommand{\labelnamepunct}{\addspace}  % remove period after year
-
-% add numbers in front of citations and puts year behind authors
-\defbibenvironment{bibliography}
-  {\list
-     {\printtext[labelnumberwidth]{%
-    \printfield{labelprefix}%
-    \printfield{labelnumber}}}
-     {\setlength{\labelwidth}{\labelnumberwidth}%
-      \setlength{\leftmargin}{\labelwidth}%
-      \setlength{\labelsep}{\biblabelsep}%
-      \addtolength{\leftmargin}{\labelsep}%
-      \setlength{\itemsep}{\bibitemsep}%
-      \setlength{\parsep}{\bibparsep}}%
-      \renewcommand*{\makelabel}[1]{\hss##1}}
-  {\endlist}
-  {\item}
-
-\usepackage{xpatch}
-\xpatchbibmacro{date+extrayear}{%
-  \printtext[parens]%
-}{%
-  \setunit{\addperiod\space}%
-  \printtext%
-}{}{}
-\AtEveryBibitem{%
-  \clearfield{note}%
-}
-
-% adds comma after journal 
-\renewcommand\bibpagespunct{\ifentrytype{article}{\addcolon}{\addcomma}\space}
-\renewbibmacro*{volume+number+eid}{%
-\setunit*{\addcomma\space}% NEW
-  \printfield{volume}
-  \printfield[parens]{number}{,}%
-  \setunit{\addcomma\space}%
-  \printfield{eid}}
-
-% change and to \& (can also remove)
-\DefineBibliographyExtras{english}{%
-  \renewcommand*{\finalnamedelim}{\addcomma\addspace\&\addspace}%
-  %\renewcommand*{\finalnamedelim}{\addcomma\addspace}%
-}
-
-%\usepackage{hyperref}
-\usepackage{fancyhdr}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrulewidth}{0pt}
 
@@
 
-\newcommand\boldblue[1]{\textcolor{mydarkblue}{\textbf{#1}}}
+\abovedisplayskip = 10.0pt plus 2.0pt minus 20.0pt
+\belowdisplayskip = 10.0pt plus 2.0pt minus 20.0pt
+\abovedisplayshortskip = 0.0pt plus 20.0pt
+\belowdisplayshortskip = 9pt plus 3pt minus 20pt
 
-\newcommand{\SuppCaption}[2]{\noindent\textbf{{#1}} {#2}\footnotesize}
-\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large\textcolor{mydarkblue}{#1}}\normalsize }
-\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{mydarkblue}{#1}}\normalsize }
+%%%%%%%%%%%%%%%%%%%
+\title{Supplementary Information}
+\shorttitle{}
+\authorsnames{}
+\authorsaffiliations{}
 
-\renewcommand{\figurename}{Supplementary Figure}
-
-% Condition variables
-% \def\emlv{\emph{\emph{early mean low variance}}}
-% \def\emhv{\emph{early mean high variance}}
-% \def\mmlv{\emph{middle mean low variance}}
-% \def\mmhv{\emph{middle mean high variance}}
-% \def\lmlv{\emph{\emph{late mean low variance}}}
-% \def\lmhv{\emph{late mean high variance}}
-
-% \def\em{\emph{early mean}}
-% \def\mm{\emph{middle mean}}
-% \def\lm{\emph{late mean}}
-
-% \definecolor{myudblue}{RGB}{0, 83, 159}
 \begin{document}
+% \maketitle
 \section{Supplementary}
-
 \section{Supplementary A: Low and High Variance Results}
@@
 \end{figure}
-
 \newpage
@@
 \vspace{-1mm}
-
 \begin{figure}[H]
@@
 We describe the bootstrap procedure below.
-Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature\autocite*{normanElectromechanicalDelaySkeletal1979,rossiniClinicalApplicationsMotor1998,brucePrimateFrontalEye1985}.
+Neuromechanical delay ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) were estimated from prior literature\autocite{normanElectromechanicalDelaySkeletal1979,rossiniClinicalApplicationsMotor1998,brucePrimateFrontalEye1985}.
 
@@
 
-\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ \autocite*{rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
+\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ \autocite{rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
 Here the remaining parameters estimated from experimental data were set as the group level means.
@@
 
-\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times\autocite*{cashabackGradientReinforcementLandscape2019a, cashabackDissociatingErrorbasedReinforcementbased2017,rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
+\noindent In the bootstrap procedure we randomly sampled participants with replacement 10,000 times\autocite{cashabackGradientReinforcementLandscape2019a, cashabackDissociatingErrorbasedReinforcementbased2017,rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.
 We used the mean of the bootstrapped participant data for each of the parameter values that were estimated from data.
@@
 
-\newpage
+% \newpage
 \section{Supplementary G: Guess Decisions}
@@
 During \boldblue{Experiment 1} participants were rewarded for successful trials and experienced a time constraint.
-Thus, we would expect participants to have faster response times in \boldblue{Experiment 1} than in the Response Time task \autocite*{milsteinInfluenceExpectedValue2007,shadmehrMovementVigorReflection2019a}.
+Thus, we would expect participants to have faster response times in \boldblue{Experiment 1} than in the Response Time task \autocite{milsteinInfluenceExpectedValue2007,shadmehrMovementVigorReflection2019a}.
 To account for this, we adjusted participant response times by subtracting 25ms from their median response time in the Response Time task.
@@
 
-% \newpage
-% \fancyhead[L]{} % Need this because print bibliography is dumb and puts a REFERENCES in the left header
-% \begin{nolinenumbers}
+\newpage
+\begin{nolinenumbers}
 %     \definecolor{mydarkblue}{RGB}{0,51,102}
-
-%     \printbibliography[title=\LARGE\textcolor{mydarkblue}{Supplementary References}]
-% \end{nolinenumbers}
+    \printbibliography[title={Supplementary References}]
+\end{nolinenumbers}
 

### 2024-11-05 paper/Cover_letter_Indecisions.tex
updated for jep human perception and performance

@@
 \vspace{1.0mm}
-We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{Journal of Experimental Psychology: General}.
+We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{Journal of Experimental Psychology: Human Perception and Performance}.
 \vspace{3.0mm}

### 2024-11-05 paper_apa/main.tex
removed supplementary from main pdf, and had to adjust things for the supp itself to get it to run
Update spacing
updated for jep human perception and performance

@@
 % \pagenumbering{arabic} % page numbering starts here
-Word count: 7114
 \section{Introduction}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  RESULTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{2mm}
+% \vspace{2mm}
 \section{Results}
-\vspace{-1mm}
+\vspace{-2mm}
 
 \subsection{Experiment 1}
-\vspace{-1mm}
+\vspace{-2mm}
 
@@
 
-\noindent 44 participants participated across two experiments.
-20 individuals participated in \boldblue{Experiment 1} and 24 individuals participated in \boldblue{Experiment 2}.
+\noindent 44 participants participated across two experiments (collected in 2023).
+20 individuals participated in \boldblue{Experiment 1} (mean age = 25.7, 8 female) and 24 individuals participated in \boldblue{Experiment 2} (mean age = 25.1, 9 female).
 All participants reported they were free from musculoskeletal injuries, neurological conditions, or sensory impairments.
@@
 
+\subsection{Power Analysis}
+For \boldblue{Experiment 1}, we performed a power analysis on the interaction term of a 3 x 2 repeated measures ANOVA ($\alpha$ = 0.05, $\beta$ = 0.2 [80\% power], f = 0.34).
+This yielded a sample size of 14, but we collected 20 participants.
+For \boldblue{Experiment 2}, we performed a power analysis on the interaction term of a 2 x 2 repeated measures ANOVA ($\alpha$ = 0.05, $\beta$ = 0.2 [80\% power], f = 0.41).
+This yielded a sample size of 15, but we collected 24 participants.
 \subsection{Apparatus}
@@
 We also report the common-language effect size ($\hat{\theta}$).
+\subsection{Transparency and Openness}
+Data, analysis scripts, and computational modeling scripts are available on github (https://github.com/CashabackLab). This study and the subsequent analyses were not preregistered.
 
@@
 
-\newpage
-\input{supplementary}
+% \newpage
+% \input{supplementary}
 

### 2024-11-05 src/constants.py
some updates made for proposal figures

@@ -65,7 +65,7 @@ cadet_grey      = "#91A3B0"
 marengo         = "#4C5866"
 pebble          = "#333333"
 model_colors = [cadet_grey, wheel.lighten_color(pebble,0.75), wheel.black]
-model_colors_dark = [cadet_grey, wheel.lighten_color(pebble,0.75), wheel.white]
+model_colors_dark = [wheel.lighten_color(pebble,0.75), cadet_grey,  wheel.white]
 model_names = ["No Switch Time Model", "Full Switch Time Model", "Partial Switch Time Model"]
 
 stimulus_color = wheel.lighten_color(wheel.yellow, 1.75)

### 2024-11-25 paper/main.tex
redid everything for submission to jnp

@@
 
-\vspace{10mm}
+\vspace{1mm}
 \noindent \boldblue{{{Decision-Making Models}}}
@@
 With partial knowledge, the decision policy utilizes its partial and imperfect representation of the parameter.
-Here the idea is that a human may have an imperfect representation of some parameter when determining a transition time, even though that particular parameter will still influence behaviour.
-As an example, one could plan for only some portion of a time delay, but then end up deciding too late because they did not fully account for the entire time delay.
-All model parameter values and the fitting procedure are described in \boldblue{Supplementary C}.
 
@@
 
-% \vspace*{2mm}
+\noindent Here the idea is that a human may have an imperfect representation of some parameter when determining a transition time, even though that particular parameter will still influence behaviour.
+As an example, one could plan for only some portion of a time delay, but then end up deciding too late because they did not fully account for the entire time delay.
+All model parameter values and the fitting procedure are described in \boldblue{Supplementary C}.
+
+\vspace*{1mm}
 \noindent\emph{{No Switch Time Model}}
@@
 
-\vspace*{2mm}
+\vspace*{1mm}
 \noindent\emph{{{Full Switch Time Model}}}
@@
 
-\vspace*{2mm}
+\vspace*{1mm}
 \noindent\emph{{{Partial Switch Time Model}}}
@@
 4C}): the \emph{react or guess} condition, the \emph{only react} condition, and the \emph{only guess} condition.
+In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
+Participants were informed that the stimulus would either move to one of the targets or disappear.
+In the \emph{only react} condition, participants were informed that the stimulus would always move to one of the two targets (50 react trials and 0 guess trials).
+They were also told that the stimulus would not disappear.
+In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
+They were also informed that it would not move to one of the two targets.
 
+During the \emph{react or guess} condition, we reasoned that participants would prefer to react because they would be guaranteed to select the correct target.
+As a result, in the \emph{react or guess} condition, if the stimulus disappeared the participant would switch from reacting to guessing when selecting a target.
+Conversely, during the \emph{only guess} condition, if the stimulus disappeared participants would not have to switch from reacting to guessing.
+Thus, if there is a delay when switching from reacting to guessing, we would expect a greater response time for the guess trials in the \emph{react or guess} condition compared to the guess trials in the guess only condition.
 \begin{figure}[H]
@@
 \end{figure}
-
-\noindent In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials).
-Participants were informed that the stimulus would either move to one of the targets or disappear.
-In the \emph{only react} condition, participants were informed that the stimulus would always move to one of the two targets (50 react trials and 0 guess trials).
-They were also told that the stimulus would not disappear.
-In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials).
-They were also informed that it would not move to one of the two targets.
-
-During the \emph{react or guess} condition, we reasoned that participants would prefer to react because they would be guaranteed to select the correct target.
-As a result, in the \emph{react or guess} condition, if the stimulus disappeared the participant would switch from reacting to guessing when selecting a target.
-Conversely, during the \emph{only guess} condition, if the stimulus disappeared participants would not have to switch from reacting to guessing.
-Thus, if there is a delay when switching from reacting to guessing, we would expect a greater response time for the guess trials in the \emph{react or guess} condition compared to the guess trials in the guess only condition.
-
 \noindent \boldblue{Response Time}

### 2024-11-25 paper/Cover_letter_Indecisions.tex
final changes for JNP

--- 2024-08-27 paper/Cover_letter_Indecisions.tex
@@
 \vspace{1.0mm}
-We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{PLOS Computational Biology}.
+We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{Journal of Neurophysiology}.
 \vspace{3.0mm}
@@
 \\
+Laurence Maloney, New York University, laurence.maloney@nyu.edu
+\\
+\\
 Michael S Landy, New York University, landy@nyu.edu
@@
 \\
-Han L.J. van der Maas, University of Amsterdam, H.L.J.vanderMaas@uva.nl 
+Heather Neyedli, Dalhouse University, hneyedli@dal.ca
+\\
+\\
+Todd Hudson, New York University, Todd.Hudson@nyulangone.org
 \\
@@
 Tony Carlsen, University of Ottawa, acarlsen@uottawa.ca
-\\
-\\
-Martin Wiener, George Mason University, mwiener@gmu.edu
 %\\
@@
 %\\
+\\
+\\
+\noindent \textcolor{myudblue}{EDITOR SUGGESTIONS}
+\\
+\\
+Monica Perez
 \end{document}
